### 2021-07-07 PrevAdjSurvey.tex
Initial Overleaf Import

\documentclass{article}

\topmargin -.5in
\textheight 8.25in
\oddsidemargin 0in
\evensidemargin 0in
\textwidth 6.5in
\parindent 3em

\usepackage{amsmath}

%% Please use the following statements for
%% managing the text and math fonts for your papers:
\usepackage{times}
%\usepackage[cmbold]{mathtime}
\usepackage{bm}
\usepackage{natbib}

%\usepackage{algorithm}
%\usepackage{fancyhdr}
\usepackage{graphics,color,pict2e}
\usepackage{epsfig}
%\usepackage{times}
%\usepackage[cmbold]{mathtime}
%\usepackage{bm}
%\usepackage{rotating}
%\usepackage{pdflscape}
%\usepackage{longtable}

%\usepackage{C:/R/R-2.11.1/share/texmf/Sweave}

%\theoremstyle{plain}
%\newtheorem{Theorem}{Theorem}[section]
\newtheorem{theorem}{Theorem}
\newtheorem{corrolary}{Corrolary}
\newtheorem{result}{result}
\newtheorem{Lemma}{Lemma}
\newcommand{\toi}{t}
\newcommand{\eqd}{\buildrel D \over =}
\newcommand{\vect}{\bf }
\newcommand{\sle}{\stackrel{st}{\le}}

\newcommand{\ch}[2]{\ensuremath{ \left( \begin{array}{c} #1 \\ #2 \end{array} \right) }}
\newcommand{\dfn}[2]{\ensuremath{ \left( #1 \right)_{(#2)}}}

\begin{document}

{\bf \large Notes on: Prevalence Estimates from Surveys with Imperfect Assays}

\today

%\begin{abstract}
%asdf
%\end{abstract}

Damon,

Here are some notes on the project. You can change the notation if you want. I am just putting down something so we can be clear about what we are doing.

\section{Overview}

Quick overview. I described the problem in Section~\ref{sec-math}. The usual adjustment for sensitivity and specificity is described in Section~\ref{sec-usualAdj}. Then the three parts I spoke about. First, the confidence interval for a simple random sample is described in Section~\ref{sec-thetastar} (that is what you already did). Second, the confidence interval assuming a perfect assay in Section~\ref{sec-betaPerfect}. And finally, the 
confidence interval for an imperfect assay in Section~\ref{sec-betaImperfect}.

\section{Mathematical Statement of Problem}
\label{sec-math}

Suppose we take a survey, that is divided into $k$ sampling units (e.g., states in the US).
We take a simple random sample of individuals from each unit, perform and assay on each individual to determine who has a disease, and measure the number of individuals who have a positive value for the assay.

Let $X_i$ be the number of positives by the assay, out of $n_i$ measured in sampling unit $i$.
Suppose we had a perfect assay with 100\% sensitivity and 100\% specificity. Then let $X_i^*$ be the true number with the disease out of the $n_i$ sampled in unit $i$.

Let $X_i^* \sim Binomial(n_i, \theta_i^*)$ for $i=1,\ldots,k$. We are interested in the prevalence of disease in the population. Suppose there are $N_i$ individuals in the population of unit $i$. Then the prevalence of the population is
\begin{eqnarray*}
\beta & = & \frac{ \sum_{i=1}^{k} N_i \theta_i^* }{ \sum_{j=1}^{k} N_j }  =  \sum_{i=1}^{k} w_i \theta_i,
\end{eqnarray*}
where $w_i = N_i/N$ and $N=\sum_{j=1}^{k} N_j$.

Suppose we evaluate the assay. We measure the assay on $m_n$ individuals known not to have the disease (negative controls), and on $m_p$ individuals known to have the disease (positive controls). Let $C_n$ and $C_p$ be the number who tested positive out of the $m_n$ in the negative control and the $m_p$  in the positive control. Now make a convenience assumption:
\begin{itemize}
\item Assume that the negative and positive controls act like simple random samples from their populations (e.g., the $m_n$ negative controls are like a simple random sample from the total population of individuals without the disease).
\end{itemize}
Under that assumption, $C_n \sim Binomial(m_n, \phi_n)$ and $C_p \sim Binomial(m_p, \phi_p)$,
where $1-\phi_n$ is the specificity (true negative rate of the assay),
and $\phi_p$ (true positive rate of the assay) is the sensitivity.

Here is the statistical problem. Assuming all of the above holds, and we observe realizations of $X_1,\ldots, X_k$ and $C_n$ and $C_p$, and the other values are known constants ($n_1,\ldots, n_k$, $w_1,\ldots, w_k$,  $m_n$, and $m_p$), what is a good estimate and confidence interval procedure for $\beta$.

\section{Usual Adjustment for Sensitivity and Specificity}
\label{sec-usualAdj}

To simplify the problem, suppose there is only one sampling unit, and let $X_1=X$ and $n_1=n$, etc. Then $\beta = \theta_1^*=\theta^*$. 
Further assume that $\phi_p$ and $\phi_n$ are known. Let $Y_1,\ldots,Y_n$ be the result of the assay from the $n$ individuals in the population
($Y_i=1$ is positive and $Y_i=0$ is negative). Let $Y_1^*,\ldots,Y_n^*$ be the true disease status ($Y_i^*=1$ is diseased, and $Y_i^*=0$ is not diseased).  
Then using the definition of sensitivity and specificity, we get:
\begin{eqnarray*}
Pr[ Y_i =1 | Y_i^*=1] & = & \phi_p \\
Pr[ Y_i=0 | Y_i^*=0] & = & 1- \phi_n 
\end{eqnarray*}
and 
\begin{eqnarray*}
Pr[ Y_i=1] & = & Pr[ Y_i =1 | Y_i^*=1]  Pr[Y_i^*=1] + Pr[ Y_i =1 | Y_i^*=0] Pr[ Y_i^*=0] \\
& = & \phi_p \theta^* + \phi_n (1-\theta^*)  \\
& = & \theta^* (\phi_p - \phi_n) + \phi_n.
\end{eqnarray*}
Let $\theta = Pr[ Y_i=1]$.

So we have 
\begin{eqnarray*}
& & X \sim Binomial \left(n, \theta \right)  \\
\mbox{ where} & \theta & = \theta^* \left\{ \phi_p - \phi_n \right\} + \phi_n.
\end{eqnarray*}
Thus, 
\begin{eqnarray}
\theta^* & =  & \frac{ \theta - \phi_n }{ \phi_p - \phi_n}  = \frac{ \theta + (1 - \phi_n) -1  }{ \phi_p + (1 - \phi_n) -1 } \label{eq:thetastar}
\end{eqnarray}

Suppose we estimate the sensitivity as $\widehat{Se} = \hat{\phi}_p = C_p/m_p$ and the specificity as $\widehat{Sp} = 1-\hat{\phi}_n = 1- C_n/m_n$,
and we define the apparent prevalence as the sample proportion of the positive assay results, $\hat{\theta} = x/n$.
This gives the usual estimator for  prevalence adjusted for sensitivity and specificity
 \citep[see e.g.,][]{Roga:1978},
\begin{eqnarray*}
\hat{\theta}^* & = & \frac{ \hat{\theta} - \hat{\phi}_n }{\hat{\phi}_p - \hat{\phi}_n} = \frac{ \hat{\theta} + \widehat{Sp} -1 }{\widehat{Se} + \widehat{Sp} -1}.
\end{eqnarray*}

\section{Confidence Interval on $\theta^*$}
\label{sec-thetastar}

The simulation you (Damon) already did handles this problem. It answers: what is a good confidence interval for $\theta^*$?
You compared the method of \citet{Lang:2014} to the new method described in the Supplement to \citet{Kali:2021}, using the method of \citet{FayP:2015}.
It shows that the lower error has a better bound with the new method.

\section{Confidence Interval on $\beta$ with a Perfect Assay}
\label{sec-betaPerfect}

Suppose we have a perfect assay (i.e., $\phi_p=1$ and $\phi_n=0$). Then $\theta^* = \theta$, and $\beta = \sum_{i=1}^{k} w_i \theta$. 
The problem reduces to getting a confidence interval for a weighted average of the means of sample proportions. 
This problem is a standard survey sampling one. Some methods are \citet{Korn:1998}, see the review in \citet{Dean:2015}.

Another way to address this problem is to assume that $X_i \sim Poisson( n_i \theta_i)$ and use the methods 
of \citet{FayF:1997} or \citet{FayK:2017}. This should give a confidence interval for $\beta=\sum_{i=1}^{k} w_i \theta_i$ 
that gives a lower and upper confidence distribution that is distributed gamma. (I will let you work out those details. Let me know if it is not easy.)

\section{Confidence Interval on $\beta$ with an Imperfect Assay}
\label{sec-betaImperfect}

This is the final problem (described in Section~\ref{sec-math} that combines the two other problems.

We have 
\begin{eqnarray*}
\beta & = & \sum_{i=1}^{k} w_i \theta_i^*  \\
& = &  \sum_{i=1}^{k} w_i  \frac{ \theta_i - \phi_n }{ \phi_p - \phi_n} \\
& = &   \frac{ \sum_{i=1}^{k} w_i  \theta_i  }{ \phi_p - \phi_n} - \frac{ \phi_n \sum_{i=1}^{k} w_i    }{ \phi_p - \phi_n} \\
& = &   \frac{ \sum_{i=1}^{k} w_i  \theta_i  }{ \phi_p - \phi_n} - \frac{ \phi_n     }{ \phi_p - \phi_n},
\end{eqnarray*}
where the last step is because the weights are assumed to sum to 1.

We can use 
\begin{eqnarray*}
\hat{\beta} & = &   \frac{ \sum_{i=1}^{k} w_i  \hat{\theta}_i  }{ \hat{\phi}_p - \hat{\phi}_n} - \frac{ \hat{\phi}_n   }{ \hat{\phi}_p - \hat{\phi}_n} \\
& = & 
\end{eqnarray*}
as our estimator of $\beta$. Then we can use the melding method of \citet{FayP:2015} to combine the confidence distributions for $\sum_{i=1}^{k} w_i  {\theta}_i$, for $\phi_p$,
and for $\phi_n$. That might not be straightforward, since I am not sure if $\phi_n$ and $\phi_p$ are monotonic in $\beta$. You need to check that out.

We can compare that new method to the method described in the supplement of \citet{Kali:2021}.

%\bibliographystyle{agsm}
\bibliographystyle{biom}

\bibliography{refs}

\end{document}

### 2021-07-07 code/WprevSeSp_SRS.R
confidence_interval_theta_star_fay_vs_LR

@@ -1,0 +1,143 @@
+# https://github.com/niaid/SARSCoV2-US-serosurvey-2020/blob/main/Figure3_Figure4/R/WprevSeSp_MF.R
+### Author: Mike Fay
+### apply this function to perform sensitivity and specificity adjustment
+
+prevAdj <- function(AP, sen, spec) (AP + spec - 1) / (sen + spec - 1)
+
+WprevSeSp_SRS <- function(AP, nP, Se, nSe, Sp, nSp, conf.level = 0.95,
+                          neg.to.zero = TRUE, nmc = 1e5, seed = 49201) {
+  if (!is.null(seed)) set.seed(seed)
+
+  # This doesn't actually get used in any calculations, just the final output
+  # Maybe this estimated standard error is supposed to account for Se & Sp,
+  # but probably not.
+  # Thus, assume nP * AP ~ Binomial(nP, true prevalence)
+  # => Var(nP * AP) =  nP * true prevalence * (1 - true prevalence)
+  # => Var(AP) =  (true prevalence * (1 - true prevalence)) / nP
+  # => std.dev(AP) =  sqrt((true prevalence * (1 - true prevalence)) / nP)
+  # => Plug-in estimate:
+  stdErrPrev <- sqrt((AP * (1 - AP)) / nP)
+
+
+  P <- prevAdj(AP, Se, Sp)
+
+  xAP <- AP * nP
+
+  # use Beta lower and upper confidence distributions
+  # for apparent prevalence
+  # defined using Korn-Graubard methods
+  B_AP_L<- rbeta(nmc, xAP, nP - xAP + 1)
+  B_AP_U<- rbeta(nmc, xAP + 1, nP - xAP)
+
+  # use Beta lower and upper confidence distributions
+  # for sensitivity (from binomial assumptions)
+  B_sen_L <- rbeta(nmc, nSe * Se, nSe - nSe * Se + 1)
+  B_sen_U <- rbeta(nmc, nSe * Se + 1, nSe - nSe * Se)
+
+  # use Beta lower and upper confidence distributions
+  # for specificity (from binomial assumptions)
+  B_spec_L <- rbeta(nmc, nSp * Sp, nSp - nSp * Sp + 1)
+  B_spec_U <- rbeta(nmc, nSp * Sp + 1, nSp - nSp * Sp)
+
+  # Monte Carlo melding method
[…]

### 2021-07-07 code/simulations/confidence_interval_theta_star_fay_vs_LR/confidence_interval_theta_star_fay_vs_LR_process_results.R

@@ -1,0 +1,162 @@
+library(tidyverse)
+library(scales)
+library(asht)
+library(cowplot)
+library(fs)
+library(furrr)
+
+results <- read_rds("sim_results_10000.rds")
+
+
+# Process Results ---------------------------------------------------------
+coverage_results <-
+  results %>%
+  group_by(n_tested_for_prevalence, prevalence, sensitivity, specificity) %>%
+  summarize(LR_coverage = mean(LR_covered),
+            Fay_coverage = mean(Fay_covered),
+            .groups = "drop") %>%
+  pivot_longer(ends_with("coverage"), names_to = "method", values_to = "coverage") %>%
+  mutate(method = str_sub(method, end = -10))
+
+coverage_distance_difference_data <-
+  coverage_results %>%
+  mutate(coverage_distance_from_truth = abs(0.95 - coverage)) %>%
+  select(-coverage) %>%
+  pivot_wider(names_from = method, values_from = coverage_distance_from_truth) %>%
+  mutate(coverage_distance_difference = LR - Fay)
+
+ci_results <-
+  results %>%
+  select(n_tested_for_prevalence, n_tested_for_sensitivity,
+         n_tested_for_specificity, prevalence, sensitivity, specificity,
+         est_prevalence, est_specificity, est_sensitivity,
+         contains("conf.int")) %>%
+  pivot_longer(contains("conf.int"), names_sep = "_", names_to = c("method", "ci_bound")) %>%
+  mutate(ci_bound = str_sub(ci_bound, start = 10)) %>%
+  pivot_wider(names_from = ci_bound, values_from = value, values_fn = list) %>%
+  unnest(c(lower, upper)) %>%
+  group_by(n_tested_for_prevalence, n_tested_for_sensitivity, n_tested_for_specificity, prevalence, sensitivity, specificity, method) %>%
+  summarize(lower_error_freq = mean(lower > prevalence),
+            upper_error_freq = mean(upper < prevalence),
+            .groups = "drop")
+
+
+# Plot Results ------------------------------------------------------------
+# make_coverage_plot_for_method <- function(method_name, plot_title = method_name) {
+#   coverage_results %>%
+#     filter(method == method_name) %>%
+#     ggplot(aes(specificity, sensitivity, fill = coverage)) +
+#     facet_grid(n_tested_for_prevalence ~ prevalence,
+#                labeller = labeller(
[…]

### 2021-07-07 code/simulations/confidence_interval_theta_star_fay_vs_LR/confidence_interval_theta_star_fay_vs_LR_simulations.R

@@ -1,0 +1,92 @@
+library(tidyverse)
+library(scales)
+library(asht)
+library(cowplot)
+library(fs)
+library(furrr)
+source("WprevSeSp_SRS.R")
+
+plan(multisession, workers = 40)
+furrr_options(seed = 200)
+
+n_replications <- 10000
+
+simulation_design <-
+  crossing(
+    n_tested_for_prevalence = 100,
+    n_tested_for_sensitivity = 60,
+    n_tested_for_specificity = 300,
+    prevalence = seq(0.005, 0.02, by = 0.005),
+    sensitivity = seq(0.75, 1, by = 0.05),
+    specificity = seq(0.75, 1, by = 0.05)) %>%
+  slice(rep(1:n(), each = n_replications))
+
+n_experiments <- nrow(simulation_design)
+
+set.seed(200)
+experiments <-
+  simulation_design %>%
+  # Simulate AP
+  mutate(n_known_positive = map2_int(n_tested_for_prevalence, prevalence, ~rbinom(1, .x, .y))) %>%
+  mutate(n_known_negative = n_tested_for_prevalence - n_known_positive) %>%
+  mutate(n_true_positive = map2_int(n_known_positive, sensitivity, ~rbinom(1, .x, .y))) %>%
+  mutate(n_true_negative = map2_int(n_known_negative, specificity, ~rbinom(1, .x, .y))) %>%
+  mutate(n_false_positive = n_known_negative - n_true_negative,
+         est_prevalence = (n_true_positive + n_false_positive) / n_tested_for_prevalence) %>%
+  # Simulate Se and SP
+  mutate(est_specificity = map2_dbl(n_tested_for_specificity, specificity, ~rbinom(1, .x, .y) / .x),
+         est_sensitivity = map2_dbl(n_tested_for_sensitivity, sensitivity, ~rbinom(1, .x, .y) / .x)) %>%
+  select(names(simulation_design), starts_with("est"))
+
+results <-
+  experiments %>%
+  mutate(LR = future_pmap(.l = list(est_prevalence = est_prevalence,
+                                    n_tested_for_prevalence = n_tested_for_prevalence,
+                                    est_sensitivity = est_sensitivity,
+                                    n_tested_for_sensitivity = n_tested_for_sensitivity,
+                                    est_specificity = est_specificity,
+                                    n_tested_for_specificity = n_tested_for_specificity),
+                          .f = function(est_prevalence,
+                                        n_tested_for_prevalence,
+                                        est_sensitivity,
[…]

### 2021-07-07 code/simulations/confidence_interval_theta_star_fay_vs_LR/confidence_interval_theta_star_fay_vs_LR_process_results.R
confidence_interval_theta_star_fay_vs_LR figures

@@ -5,8 +5,7 @@ library(cowplot)
 library(fs)
 library(furrr)
 
-results <- read_rds("sim_results_10000.rds")
-
+results <- read_rds("code/simulations/confidence_interval_theta_star_fay_vs_LR/confidence_interval_theta_star_fay_vs_LR_results.rds")
 
 # Process Results ---------------------------------------------------------
 coverage_results <-
@@ -42,28 +41,7 @@ ci_results <-
 
 
 # Plot Results ------------------------------------------------------------
-# make_coverage_plot_for_method <- function(method_name, plot_title = method_name) {
-#   coverage_results %>%
-#     filter(method == method_name) %>%
-#     ggplot(aes(specificity, sensitivity, fill = coverage)) +
-#     facet_grid(n_tested_for_prevalence ~ prevalence,
-#                labeller = labeller(
-#                  prevalence = function(.) str_c("Prevalence:\n", scales::percent(as.numeric(.), accuracy = .1)),
-#                  n_tested_for_prevalence = function(.) str_c("Tested for Prevalence Size:\n", scales::comma(as.numeric(.))))
-#     ) +
-#     # geom_raster(interpolate = F) +
-#     geom_tile() +
-#     cowplot::theme_cowplot() +
-#     scale_x_continuous(name = "Specificity", labels = function(.) percent(., accuracy = 1)) +
-#     scale_y_continuous(name = "Sensitivity", labels = function(.) percent(., accuracy = 1)) +
-#     scale_fill_distiller(name = "Coverage",type = "div", palette = "PiYG", direction = 1, limits = c(0.9, 1), labels = function(.) percent(., accuracy = 1)) +
-#     guides(fill = guide_colourbar(barwidth = 20)) +
-#     ggtitle(plot_title) +
-#     theme(legend.position = "bottom")
-# }
-#
-# Fay_plot <- make_coverage_plot_for_method("Fay")
-# LR_plot <- make_coverage_plot_for_method("LR", "Lang and Reiczigel")
+
 coverage_comparison_plot <-
   coverage_results %>%
   ggplot(aes(specificity, sensitivity, fill = coverage)) +
@@ -143,11 +121,10 @@ upper_error_frequency_comparison_plot <-
   ggtitle("Upper Error Frequency Comparison", subtitle = "10,000 replications each, nP = 100, nSp = 300, nSe = 60") +
   theme(legend.position = "bottom")
 
-
-dir_create("figures")
-
[…]

### 2021-07-08 code/simulations/confidence_interval_on_beta_perfect_assay.R
Create confidence_interval_on_beta_perfect_assay.R

@@ -1,0 +1,36 @@
+n_psu <- 30
+n_replication <- 100
+tmp<-
+crossing(replication = 1:n_replication,
+         ICC = 0.01,
+         # ICC = c(0.005, 0.010, 0.050, 0.100, 0.150, 0.250, 0.500),
+         prevalence = seq(0.005, 0.02, by = 0.005)) %>%
+  mutate(psu = map2(ICC, prevalence,
+                    ~{
+                      alpha <- (1 - .x) / .x * .y
+                      beta <- (1 - .x) / .x * (1 - .y)
+                      tibble(psu_size = round(rgamma(n_psu, shape = 2, scale = 100)),
+                             psu_positives = round(psu_size * rbeta(n_psu, alpha, beta)),
+                             psu_prevalence = psu_positives / psu_size)}))
+  # mutate(p_hat_summary = map(psu, ~{
+  #   p_hat <- sum(.[["psu_size"]] * .[["psu_prevalence"]]) / sum(.[["psu_size"]])
+  #   var_hat_p_hat <- sum((.[["psu_prevalence"]] - p_hat)^2) / (n_psu * (n_psu - 1))
+  #   c("p_hat" = p_hat, "var_hat_p_hat" = var_hat_p_hat)
+  #   })) %>%
+  # unnest_wider(p_hat_summary)
+
+tmp2<-
+tmp %>%
+  group_by(replication, ICC, prevalence) %>%
+  unnest(psu) %>%
+  summarize(wspoissonTest_result = list(wspoissonTest(x = psu_positives, w = psu_size / sum(psu_size), midp = T)),
+    total_psu_size = sum(psu_size),
+    .groups = "drop") %>%
+  # This is wrong
+  mutate(conf.int = map2(wspoissonTest_result, total_psu_size,
+                         ~set_names(.x$conf.int / .y, c("low", "high")))) %>%
+  unnest_wider(conf.int, names_sep = "_")
+
+
+tmp2 %>%
+  count(prevalence < conf.int_high)

### 2021-07-08 code/simulations/confidence_interval_on_beta_perfect_assay.R
Update confidence_interval_on_beta_perfect_assay.R

@@ -23,14 +23,16 @@ tmp2<-
 tmp %>%
   group_by(replication, ICC, prevalence) %>%
   unnest(psu) %>%
-  summarize(wspoissonTest_result = list(wspoissonTest(x = psu_positives, w = psu_size / sum(psu_size), midp = T)),
-    total_psu_size = sum(psu_size),
+  summarize(wspoissonTest_result = list(wspoissonTest(x = psu_positives,
+                                                      w = psu_size / sum(psu_size),
+                                                      midp = T,
+                                                      mult = 1/sum(psu_size))), # This is wrong
     .groups = "drop") %>%
-  # This is wrong
-  mutate(conf.int = map2(wspoissonTest_result, total_psu_size,
-                         ~set_names(.x$conf.int / .y, c("low", "high")))) %>%
+  mutate(conf.int = map(wspoissonTest_result, "conf.int") %>% map(~set_names(., c("low", "high")))) %>%
   unnest_wider(conf.int, names_sep = "_")
 
 
-tmp2 %>%
-  count(prevalence < conf.int_high)
+
+possion_rates <- sample(1:5, 20, replace = T)
+set.seed(200)
+rpois(20, possion_rates)

### 2021-07-09 generate_house_sample.R
generate samples for perfect assay simulation

@@ -1,0 +1,28 @@
+library(tidyverse)
+
+set.seed(200)
+house_pop <- tibble(house_size = c(sample(7, size = 408663, replace = T, prob = c(36198, 44742, 19337, 16262, 7446, 2919, 1546)), 2, 1)) %>%
+  mutate(group = row_number())
+n_houses <- nrow(house_pop)
+
+ICC <- .1
+prevalence <- 0.01
+
+set.seed(200)
+many_house_scenario <- house_pop %>%
+  mutate(house_cases = round(rbeta(n_houses, (1 - ICC) / ICC * prevalence, (1 - ICC) / ICC * (1 - prevalence)) * house_size))
+
+ICC <- .91
+prevalence <- 0.01
+set.seed(200)
+few_house_scenario <- house_pop %>%
+  mutate(house_cases = round(rbeta(n_houses, (1 - ICC) / ICC * prevalence, (1 - ICC) / ICC * (1 - prevalence)) * house_size))
+
+generate_house_sample <- function(scenario, total_houses_sampled) {
+  scenario %>%
+    sample_n(total_houses_sampled, replace = F) %>%
+    select(group, size = house_size, cases = house_cases)
+}
+
+generate_house_sample(many_house_scenario, 1000)
+generate_house_sample(few_house_scenario, 1000)

### 2021-07-09 generate_state_sample.R

@@ -1,0 +1,59 @@
+library(tidyverse)
+
+state_pop <- tibble(
+  area = c(
+    "Alabama", "Alaska", "Arizona", "Arkansas", "California", "Colorado",
+    "Connecticut", "Delaware", "District of Columbia", "Florida",
+    "Georgia", "Hawaii", "Idaho", "Illinois", "Indiana", "Iowa",
+    "Kansas", "Kentucky", "Louisiana", "Maine", "Maryland", "Massachusetts",
+    "Michigan", "Minnesota", "Mississippi", "Missouri", "Montana",
+    "Nebraska", "Nevada", "New Hampshire", "New Jersey", "New Mexico",
+    "New York", "North Carolina", "North Dakota", "Ohio", "Oklahoma",
+    "Oregon", "Pennsylvania", "Rhode Island", "South Carolina", "South Dakota",
+    "Tennessee", "Texas", "Utah", "Vermont", "Virginia", "Washington",
+    "West Virginia", "Wisconsin", "Wyoming"
+  ),
+  population = c(
+    5024279, 733391, 7151502, 3011524, 39538223, 5773714, 3605944,
+    989948, 689545, 21538187, 10711908, 1455271, 1839106, 12812508,
+    6785528, 3190369, 2937880, 4505836, 4657757, 1362359, 6177224,
+    7029917, 10077331, 5706494, 2961279, 6154913, 1084225, 1961504,
+    3104614, 1377529, 9288994, 2117522, 20201249, 10439388, 779094,
+    11799448, 3959353, 4237256, 13002700, 1097379, 5118425, 886667,
+    6910840, 29145505, 3271616, 643077, 8631393, 7705281, 1793716,
+    5893718, 576851
+  )
+) %>%
+  mutate(state = row_number())
+
+few_state_scenario <- state_pop %>%
+  mutate(population_cases = case_when(
+    area %in% c("California", "Texas", "Florida", "New York") ~ round(population * 0.015),
+    TRUE ~ 0
+  ))
+
+ICC <- 0.01
+prevalence <- 0.005
+
+set.seed(200)
+many_state_scenario <- state_pop %>%
+  mutate(., population_cases = round(rbeta(nrow(.), (1 - ICC) / ICC * prevalence, (1 - ICC) / ICC * (1 - prevalence)) * population))
+
+
+generate_state_sample <- function(scenario, total_people_sampled) {
+  n_states <- nrow(scenario)
+
[…]

### 2021-07-10 generate_state_sample.R
start housing sim

@@ -24,7 +24,9 @@ state_pop <- tibble(
     5893718, 576851
   )
 ) %>%
-  mutate(state = row_number())
+  mutate(state = row_number(),
+         pop_weight = population / sum(population)) %>%
+  select(state, population, pop_weight, area)
 
 few_state_scenario <- state_pop %>%
   mutate(population_cases = case_when(
@@ -46,12 +48,13 @@ generate_state_sample <- function(scenario, total_people_sampled) {
   sample(n_states, size = total_people_sampled, replace = T, prob = scenario[["population"]]) %>%
     enframe(name = NULL, value = "state") %>%
     count(state, name = "n_sampled") %>%
-    left_join(scenario) %>%
+    left_join(scenario, by = "state") %>%
     mutate(sample_cases = rbinom(n = n_states, size = n_sampled, prob = population_cases / population)) %>%
     select(
       group = state,
       size = n_sampled,
-      cases = sample_cases
+      cases = sample_cases,
+      group_weight = pop_weight
     )
 }
 

### 2021-07-10 housing_sim.R

@@ -1,0 +1,43 @@
+source("generate_state_sample.R")
+
+n_simulations <- 10
+
+
+set.seed(200)
+tmp <- tibble(simulation = 1:n_simulations,
+              prevalence = sum(few_state_scenario$population_cases) / sum(few_state_scenario$population),
+              data = map(simulation, ~generate_state_sample(scenario = few_state_scenario, total_people_sampled = 12000))) %>%
+  mutate(wspoissonTest_result = map(data, ~wspoissonTest(x = .[["cases"]], w = .[["group_weight"]] / .[["size"]])))
+
+
+dat <- tmp[[1, "data"]][[1]]
+
+library(asht)
+wspoissonTest(x = dat$cases, w = few_state_scenario$population / sum(few_state_scenario$population) / dat$size)$conf.int
+
+library(binom)
+binom.confint(x = dat$cases, n = dat$size, methods = "agresti-coull")
+wspoissonTest(x = dat$cases, w = few_state_scenario$population / sum(few_state_scenario$population) / dat$size)
+binom.confint
+
+# end of section 4.1 of Dean and Pagan tells how to get var(p) estimate
+
+AC_method <- function(x, n, adj = F, conf.level = 0.95) {
+  p <- x/n
+  alpha <- 1 - conf.level
+  z <- qnorm(1 - alpha / 2)
+  c <- z * z / 2
+
+  .x <- x + 0.5 * z2
+  .n <- n + z2
+  .p <- .x/.n
+
+
+  lcl <- .p - z * sqrt(.p * (1 - .p)/.n)
+  ucl <- .p + z * sqrt(.p * (1 - .p)/.n)
+  res.ac <- data.frame(method = rep("agresti-coull", NROW(x)),
+                       xn, mean = p, lower = lcl, upper = ucl)
+  res <- res.ac
+  res
+}
+

### 2021-07-13 generate_state_sample.R
state_sample_rework

@@ -24,15 +24,16 @@ state_pop <- tibble(
     5893718, 576851
   )
 ) %>%
-  mutate(state = row_number(),
-         pop_weight = population / sum(population)) %>%
-  select(state, population, pop_weight, area)
+  mutate(state = row_number()) %>%
+  select(state, population, area)
 
 few_state_scenario <- state_pop %>%
   mutate(population_cases = case_when(
     area %in% c("California", "Texas", "Florida", "New York") ~ round(population * 0.015),
+    # area %in% c("California", "Texas", "Florida", "New York") ~ round(population * 0.005),
     TRUE ~ 0
   ))
+
 
 ICC <- 0.01
 prevalence <- 0.005
@@ -41,22 +42,29 @@ set.seed(200)
 many_state_scenario <- state_pop %>%
   mutate(., population_cases = round(rbeta(nrow(.), (1 - ICC) / ICC * prevalence, (1 - ICC) / ICC * (1 - prevalence)) * population))
 
+scenario <- many_state_scenario
 
-generate_state_sample <- function(scenario, total_people_sampled) {
-  n_states <- nrow(scenario)
 
-  sample(n_states, size = total_people_sampled, replace = T, prob = scenario[["population"]]) %>%
-    enframe(name = NULL, value = "state") %>%
-    count(state, name = "n_sampled") %>%
-    left_join(scenario, by = "state") %>%
-    mutate(sample_cases = rbinom(n = n_states, size = n_sampled, prob = population_cases / population)) %>%
-    select(
-      group = state,
-      size = n_sampled,
-      cases = sample_cases,
-      group_weight = pop_weight
-    )
+
+generate_state_sample <- function(scenario, m, n_tilde) {
+  scenario %>%
+    sample_n(size = m, replace = T, weight = population) %>%
+    mutate(., sample_cases = rbinom(n = nrow(.), size = n_tilde, prob = population_cases / population)) %>%
+    mutate(sample_size = n_tilde) %>%
+    select(state, population, sample_cases, sample_size)
 }
 
-generate_state_sample(many_state_scenario, 12000)
-generate_state_sample(few_state_scenario, 12000)
+
+
+
+# group_by(group = state, population) %>%
+#   summarize(cases = sum(sample_cases),
+#             size = n_tilde * n(),
+#             .groups = "drop") %>%
+#   mutate(group_weight = population / sum(population)) %>%
+#   select(-population)
+
+
[…]

### 2021-07-13 housing_sim.R

@@ -1,43 +1,0 @@
-source("generate_state_sample.R")
-
-n_simulations <- 10
-
-
-set.seed(200)
-tmp <- tibble(simulation = 1:n_simulations,
-              prevalence = sum(few_state_scenario$population_cases) / sum(few_state_scenario$population),
-              data = map(simulation, ~generate_state_sample(scenario = few_state_scenario, total_people_sampled = 12000))) %>%
-  mutate(wspoissonTest_result = map(data, ~wspoissonTest(x = .[["cases"]], w = .[["group_weight"]] / .[["size"]])))
-
-
-dat <- tmp[[1, "data"]][[1]]
-
-library(asht)
-wspoissonTest(x = dat$cases, w = few_state_scenario$population / sum(few_state_scenario$population) / dat$size)$conf.int
-
-library(binom)
-binom.confint(x = dat$cases, n = dat$size, methods = "agresti-coull")
-wspoissonTest(x = dat$cases, w = few_state_scenario$population / sum(few_state_scenario$population) / dat$size)
-binom.confint
-
-# end of section 4.1 of Dean and Pagan tells how to get var(p) estimate
-
-AC_method <- function(x, n, adj = F, conf.level = 0.95) {
-  p <- x/n
-  alpha <- 1 - conf.level
-  z <- qnorm(1 - alpha / 2)
-  c <- z * z / 2
-
-  .x <- x + 0.5 * z2
-  .n <- n + z2
-  .p <- .x/.n
-
-
-  lcl <- .p - z * sqrt(.p * (1 - .p)/.n)
-  ucl <- .p + z * sqrt(.p * (1 - .p)/.n)
-  res.ac <- data.frame(method = rep("agresti-coull", NROW(x)),
-                       xn, mean = p, lower = lcl, upper = ucl)
-  res <- res.ac
-  res
-}
-

### 2021-07-13 state_sim.R

@@ -1,0 +1,124 @@
+source("generate_state_sample.R")
+library(asht)
+library(microbenchmark)
+AC_method <- function(y, n_survey_design, m_survey_design, adj = F, conf.level = 0.95, n_strata = 51) {
+  alpha <- 1 - conf.level
+  z_val <- qnorm(1 - alpha / 2)
+
+  # df is calculated as the number of primary sampling units minus the number of
+  # strata.
+  t_val <- qt(p = 1 - alpha / 2, df = m_survey_design - n_strata)
+  c <- z_val * z_val / 2
+
+  p_hat <- mean(y / n_survey_design)
+  var_hat_p_hat <- sum((y / n_survey_design - p_hat)^2) / (m_survey_design * (m_survey_design - 1))
+
+  n_eff <- p_hat * (1 - p_hat) / var_hat_p_hat * ifelse(adj, (z_val / t_val)^2, 1)
+
+  x_tilde <- p_hat * n_eff + c
+  n_tilde <- n_eff + 2 * c
+  p_tilde <- x_tilde / n_tilde
+
+  ci <- p_tilde + c(-1,1) * z_val * sqrt(p_tilde * (1 - p_tilde) / n_tilde)
+  attr(ci, "conf.level") <- conf.level
+
+  rval <- list(conf.int = ci, estimate = p_tilde, p_hat = p_hat, var_hat_p_hat = var_hat_p_hat)
+  class(rval) <- "htest"
+  return(rval)
+}
+
+n_simulations <- 10000
+m_survey_design <- 12000
+n_survey_design <- 1
+set.seed(200)
+
+state_samples <-
+  tibble(simulation = 1:n_simulations,
+         data_few_state = map(simulation, ~generate_state_sample(scenario = few_state_scenario, m = m_survey_design, n_tilde = n_survey_design)),
+         data_many_state = map(simulation, ~generate_state_sample(scenario = many_state_scenario, m = m_survey_design, n_tilde = n_survey_design))) %>%
+  pivot_longer(starts_with("data_"),
+               names_prefix = "data_",
+               names_to = "scenario",
+               values_to = "data") %>%
+  mutate(prevalence = case_when(
+    scenario == "few_state" ~ sum(few_state_scenario$population_cases) / sum(few_state_scenario$population),
+    scenario == "many_state" ~ sum(many_state_scenario$population_cases) / sum(many_state_scenario$population))) %>%
+  mutate(result_wspoissonTest = map(data, function(data) {
+    dat <-
+      data %>%
[…]

### 2021-07-13 state_sim.R
state sim mid_p method

@@ -28,6 +28,7 @@ AC_method <- function(y, n_survey_design, m_survey_design, adj = F, conf.level =
 }
 
 n_simulations <- 10000
+# n_simulations <- 5000
 m_survey_design <- 12000
 n_survey_design <- 1
 set.seed(200)
@@ -53,6 +54,17 @@ state_samples <-
       mutate(group_weight = population / sum(population))
 
     wspoissonTest(x = dat[["cases"]], w = dat[["group_weight"]] / dat[["size"]])
+  }),
+  result_wspoissonTest_midp = map(data, function(data) {
+    dat <-
+      data %>%
+      group_by(state, population) %>%
+      summarize(cases = sum(sample_cases),
+                size = sum(sample_size),
+                .groups = "drop") %>%
+      mutate(group_weight = population / sum(population))
+
+    wspoissonTest(x = dat[["cases"]], w = dat[["group_weight"]] / dat[["size"]], midp = T)
   }),
   result_AC = map(data, ~AC_method(y = .[["sample_cases"]],
                                    n_survey_design = n_survey_design,
@@ -112,13 +124,23 @@ state_samples %>%
             lower_error_freq = mean(conf.int_l > prevalence),
             upper_error_freq = mean(prevalence > conf.int_u),
             .groups = "drop") %>%
-  arrange(scenario, method)
+  arrange(scenario, method) %>%
+  dput()
+
 
 structure(list(scenario = c("few_state", "few_state", "few_state",
-                            "many_state", "many_state", "many_state"), method = c("AC", "AC_adj",
-                                                                                  "wspoissonTest", "AC", "AC_adj", "wspoissonTest"), coverage = c(0.957,
-                                                                                                                                                  0.957, 0.9629, 0.9515, 0.9515, 0.9597), lower_error_freq = c(0.0259,
-                                                                                                                                                                                                               0.0259, 0.0216, 0.0287, 0.0287, 0.0246), upper_error_freq = c(0.0171,
-                                                                                                                                                                                                                                                                             0.0171, 0.0155, 0.0198, 0.0198, 0.0157)), row.names = c(NA, -6L
-                                                                                                                                                                                                                                                                             ), class = c("tbl_df", "tbl", "data.frame"))
-
+                            "few_state", "many_state", "many_state", "many_state", "many_state"
+), method = c("AC", "AC_adj", "wspoissonTest", "wspoissonTest_midp",
[…]

### 2021-07-22 generate_state_sample.R
working on new sims

@@ -30,10 +30,15 @@ state_pop <- tibble(
 few_state_scenario <- state_pop %>%
   mutate(population_cases = case_when(
     area %in% c("California", "Texas", "Florida", "New York") ~ round(population * 0.015),
-    # area %in% c("California", "Texas", "Florida", "New York") ~ round(population * 0.005),
     TRUE ~ 0
   ))
 
+
+two_state_scenario <- state_pop %>%
+  mutate(population_cases = case_when(
+    area %in% c("California", "New York") ~ round(population * 0.03),
+    TRUE ~ 0
+  ))
 
 ICC <- 0.01
 prevalence <- 0.005
@@ -42,7 +47,13 @@ set.seed(200)
 many_state_scenario <- state_pop %>%
   mutate(., population_cases = round(rbeta(nrow(.), (1 - ICC) / ICC * prevalence, (1 - ICC) / ICC * (1 - prevalence)) * population))
 
-scenario <- many_state_scenario
+ICC <- 0.5
+prevalence <- 0.005
+
+set.seed(201)
+one_state_scenario <- state_pop %>%
+  mutate(., population_cases = round(rbeta(nrow(.), (1 - ICC) / ICC * prevalence, (1 - ICC) / ICC * (1 - prevalence)) * population))
+
 
 
 
@@ -53,18 +64,3 @@ generate_state_sample <- function(scenario, m, n_tilde) {
     mutate(sample_size = n_tilde) %>%
     select(state, population, sample_cases, sample_size)
 }
-
-
-
-
-# group_by(group = state, population) %>%
-#   summarize(cases = sum(sample_cases),
-#             size = n_tilde * n(),
-#             .groups = "drop") %>%
-#   mutate(group_weight = population / sum(population)) %>%
-#   select(-population)
-
-
-# generate_state_sample(many_state_scenario, m = 12000, n_tilde = 1)
-# generate_state_sample(many_state_scenario, 12000)
-# generate_state_sample(few_state_scenario, 12000)

### 2021-07-22 second_draft.R

@@ -1,0 +1,121 @@
+library(extraDistr)
+library(tidyverse)
+n_replications <- 1000
+survey_sample_size <- 100
+n_weights <- 30
+ICC <- 0.1
+prevalence <- 0.005
+alpha <- (1 - ICC) / ICC * prevalence
+beta <- (1 - ICC) / ICC * (1 - prevalence)
+
+
+
+tmp <- tibble(group = rep(1:n_replications, each = n_weights),
+       weights = as.vector(t(rdirichlet(n_replications, alpha = rep(1, n_weights)))),
+       true_positivity = rbeta(n_weights * n_replications, alpha, beta),
+       sample_size = survey_sample_size) %>%
+  mutate(sample_positives = rbinom(n = n_weights * n_replications, size = sample_size, prob = true_positivity)) %>%
+  mutate(sample_positivity = sample_positives / sample_size)
+
+
+tmp2 <- tmp %>%
+  group_by(group) %>%
+  summarize(result_wspoissonTest_midp = list(wspoissonTest(x = cur_data()[["sample_positives"]], w = cur_data()[["weights"]] / cur_data()[["sample_size"]], midp = F)),
+            result_wspoissonTest_midp = list(wspoissonTest(x = cur_data()[["sample_positives"]], w = cur_data()[["weights"]] / cur_data()[["sample_size"]], midp = T)))
+
+
+tmp %>%
+  group_by(group) %>%
+  summarize(p_hat = sum(cur_data()[["sample_positivity"]] * cur_data()[["weights"]]))
+
+tmp2 %>%
+  mutate(conf.int = wspoissonTest %>% map("conf.int") %>% map(~set_names(., c("l", "u")))) %>%
+  unnest_wider(conf.int) %>%
+  mutate(lower_error = l > 0.05,
+         upper_error = u > 0.05,
+         covered = !(lower_error | upper_error)) %>%
+  summarize(mean(lower_error), mean(upper_error), mean(covered))
+
+
+# y = sum s * x / n
+# y = sum weigts * sample_positivity
+
+
+# -------------------------------------------------------------------------
+
+
+
+wspoissonTest(x = tmp[["sample_positives"]], w = tmp[["weights"]] / tmp[["sample_size"]], midp = T)
[…]

### 2021-07-22 state_sim.R

@@ -1,6 +1,8 @@
 source("generate_state_sample.R")
 library(asht)
 library(microbenchmark)
+library(kableExtra)
+
 AC_method <- function(y, n_survey_design, m_survey_design, adj = F, conf.level = 0.95, n_strata = 51) {
   alpha <- 1 - conf.level
   z_val <- qnorm(1 - alpha / 2)
@@ -35,15 +37,19 @@ set.seed(200)
 
 state_samples <-
   tibble(simulation = 1:n_simulations,
-         data_few_state = map(simulation, ~generate_state_sample(scenario = few_state_scenario, m = m_survey_design, n_tilde = n_survey_design)),
-         data_many_state = map(simulation, ~generate_state_sample(scenario = many_state_scenario, m = m_survey_design, n_tilde = n_survey_design))) %>%
+         # data_few_state = map(simulation, ~generate_state_sample(scenario = few_state_scenario, m = m_survey_design, n_tilde = n_survey_design)),
+         # data_many_state = map(simulation, ~generate_state_sample(scenario = many_state_scenario, m = m_survey_design, n_tilde = n_survey_design)),
+         # data_two_state = map(simulation, ~generate_state_sample(scenario = two_state_scenario, m = m_survey_design, n_tilde = n_survey_design)),
+         data_one_state = map(simulation, ~generate_state_sample(scenario = one_state_scenario, m = m_survey_design, n_tilde = n_survey_design))) %>%
   pivot_longer(starts_with("data_"),
                names_prefix = "data_",
                names_to = "scenario",
                values_to = "data") %>%
   mutate(prevalence = case_when(
     scenario == "few_state" ~ sum(few_state_scenario$population_cases) / sum(few_state_scenario$population),
-    scenario == "many_state" ~ sum(many_state_scenario$population_cases) / sum(many_state_scenario$population))) %>%
+    scenario == "many_state" ~ sum(many_state_scenario$population_cases) / sum(many_state_scenario$population),
+    scenario == "two_state" ~ sum(two_state_scenario$population_cases) / sum(two_state_scenario$population),
+    scenario == "one_state" ~ sum(one_state_scenario$population_cases) / sum(one_state_scenario$population))) %>%
   mutate(result_wspoissonTest = map(data, function(data) {
     dat <-
       data %>%
@@ -82,37 +88,6 @@ state_samples <-
                values_to = "htest")
 
 
-
-state_samples %>%
[…]

### 2021-07-22 PrevAdjSurvey.tex
Updates from Overleaf

@@
 %\usepackage{longtable}
+\usepackage{booktabs}
 
@@
 Another way to address this problem is to assume that $X_i \sim Poisson( n_i \theta_i)$ and use the methods
-of \citet{FayF:1997} or \citet{FayK:2017}. This should give a confidence interval for $\beta=\sum_{i=1}^{k} w_i \theta_i$ 
+of \citet{FayF:1997} or \citet{FayK:2017}.
+The notation is different in those papers. Here is the correspondence between the notations in these notes and in \citet{FayK:2017}.
+
+\begin{tabular}{cc}
+These Notes & Fay and Kim  \\ \hline
+$w_i$     & $s_i$ \\
+$\theta_i$ & $\lambda_i$ \
+\end{tabular}
+
+and $X_i$ and $n_i$ are the same in both papers.
+
+This should give a confidence interval for $\beta=\sum_{i=1}^{k} w_i \theta_i$
 that gives a lower and upper confidence distribution that is distributed gamma. (I will let you work out those details. Let me know if it is not easy.)
+
+\subsection{Current Results}
+
+For this section I have applied 4 methods to 2 populations, with 10,0000 replications each.
+
+\noindent Methods:
+\begin{itemize}
+    \item AC \& AC\_adj: The Agresti-Coull and Agresti-Coull adjusted methods for survey samples described in \cite{Dean:2015}. Implemented by hand.
+    \item wspoissonTest \& wspoissonTest\_midp: the methods described in \cite{FayF:1997} and \cite{FayK:2017}. Implemented in \cite{asht}.
+\end{itemize}
+
+In each scenario, I use the 2020 census population counts for all states \& DC and specify the exact number of cases in each state's population to achieve an overall prevalence $\approx$  0.5\%.
+Per \cite{Lemeshow1985SurveysTM}, I implement a 2-stage sampling algorithm, where $m$ states are sampled with replacement and $\tilde{n}$ people are sampled from each of the $m$ states.
+In the results here, $m = 12,000$ and $\tilde{n} = 1$, equivalent to a simple random sample from the country.
+Alternative schemes like $m = 120$ and $\tilde{n} = 100$ seem to produce worse results for the wspoissonTest methods, but I have not investigated this fully.\\
+The differences between the two scenarios are presented below.\\
+
+\noindent Scenarios:
+\begin{itemize}
+    \item few\_state: California, Texas, Florida, and New York each have 1.5\% prevalence, while all other states have no cases.
+    \item many\_state: all states have 0.5\% prevalence
+\end{itemize}
+
+\noindent Results:
+\begin{table}[h]
+\centering
+\begin{tabular}{llrrr}
+\toprule
+scenario & method & coverage & lower\_error\_freq & upper\_error\_freq\\
+\midrule
+few\_state & AC & 0.9570 & 0.0259 & 0.0171\\
+few\_state & AC\_adj & 0.9570 & 0.0259 & 0.0171\\
+few\_state & wspoissonTest & 0.9629 & 0.0216 & 0.0155\\
+few\_state & wspoissonTest\_midp & 0.9559 & 0.0250 & 0.0191\\
+\addlinespace
+many\_state & AC & 0.9515 & 0.0287 & 0.0198\\
+many\_state & AC\_adj & 0.9515 & 0.0287 & 0.0198\\
+many\_state & wspoissonTest & 0.9597 & 0.0246 & 0.0157\\
+many\_state & wspoissonTest\_midp & 0.9517 & 0.0281 & 0.0202\\
+\bottomrule
+\end{tabular}
+\end{table}
+
+I have not found any scenarios that ``break" the AC methods, which appear to be on par with the wspoissonTest\_midp methods.
 

### 2021-07-23 second_draft.R
completed sims

@@ -1,121 +1,160 @@
-library(extraDistr)
 library(tidyverse)
-n_replications <- 1000
-survey_sample_size <- 100
-n_weights <- 30
-ICC <- 0.1
-prevalence <- 0.005
-alpha <- (1 - ICC) / ICC * prevalence
-beta <- (1 - ICC) / ICC * (1 - prevalence)
+library(extraDistr)
+library(asht)
+library(cowplot)
+AC_method <- function(p_hat, var_hat_p_hat, conf.level = 0.95) {
+  alpha <- 1 - conf.level
+  z_val <- qnorm(1 - alpha / 2)
+  c <- z_val * z_val / 2
+
+  n_eff <- p_hat * (1 - p_hat) / var_hat_p_hat
+
+  x_tilde <- p_hat * n_eff + c
+  n_tilde <- n_eff + 2 * c
+  p_tilde <- x_tilde / n_tilde
+
+  ci <- p_tilde + c(-1,1) * z_val * sqrt(p_tilde * (1 - p_tilde) / n_tilde)
+  attr(ci, "conf.level") <- conf.level
+
+  rval <- list(conf.int = ci, estimate = p_tilde, p_hat = p_hat, var_hat_p_hat = var_hat_p_hat)
+  class(rval) <- "htest"
+  return(rval)
+}
+
+CP_method <- function(p_hat, var_hat_p_hat, conf.level = 0.95) {
+  alpha <- 1 - conf.level
+
+  n <- n_eff <- p_hat * (1 - p_hat) / var_hat_p_hat
+  x <- p_hat * n_eff
+
+  nu_1 <- 2 * x
+  nu_2 <- 2 * (n - x + 1)
+  nu_3 <- 2 * (x + 1)
+  nu_4 <- 2 * (n - x)
+
+  ci_l <- (nu_1 * qf(alpha / 2, nu_1, nu_2)) / (nu_2 + nu_1 * qf(alpha / 2, nu_1, nu_2))
+  ci_u <- (nu_3 * qf(1 - alpha / 2, nu_3, nu_4)) / (nu_4 + nu_3 * qf(1 - alpha / 2, nu_3, nu_4))
+
+  ci <- c(ci_l, ci_u)
+  attr(ci, "conf.level") <- conf.level
+
+  rval <- list(conf.int = ci, p_hat = p_hat, var_hat_p_hat = var_hat_p_hat)
+  class(rval) <- "htest"
+  return(rval)
+}
+
[…]

### 2021-07-28 PrevAdjSurvey.tex

@@
 
-\subsection{Current Results}
+\subsection{Dirichlet Weights Simulation Results}
+
+\subsection{Weird U.S. State Simulation Results}
 
@@
 \begin{itemize}
+    \item one\_state: Montana has 30\% prevalence, while all other states have no cases.
+    \item two\_state: California and New York each have 3\% prevalence, while all other states have no cases.
     \item few\_state: California, Texas, Florida, and New York each have 1.5\% prevalence, while all other states have no cases.
-    \item many\_state: all states have 0.5\% prevalence
+    \item many\_state: all states have $\approx$ 0.5\% prevalence, but with some clustering of cases
 \end{itemize}
@@
 \noindent Results:
-\begin{table}[h]
+\begin{table}
 \centering
@@
 \midrule
+one\_state & AC & 0.9660 & 0.0232 & 0.0108\\
+one\_state & AC\_adj & 0.9660 & 0.0232 & 0.0108\\
+one\_state & wspoissonTest & 0.9928 & 0.0039 & 0.0033\\
+one\_state & wspoissonTest\_midp & 0.9852 & 0.0083 & 0.0065\\
+\addlinespace
+two\_state & AC & 0.9484 & 0.0256 & 0.0260\\
+two\_state & AC\_adj & 0.9484 & 0.0256 & 0.0260\\
+two\_state & wspoissonTest & 0.9632 & 0.0193 & 0.0175\\
+two\_state & wspoissonTest\_midp & 0.9538 & 0.0235 & 0.0227\\
+\addlinespace
 few\_state & AC & 0.9570 & 0.0259 & 0.0171\\
@@
 I have not found any scenarios that ``break" the AC methods, which appear to be on par with the wspoissonTest\_midp methods.
+There is no obvious pattern in coverage vs number of states with cases, other than that the wspoissonTest appears to do better with more evenly spread cases and both wspoissonTest methods do poorly in the one\_state scenario.
 
@@
 \label{sec-betaImperfect}
+
+\subsection{Preliminaries}
 
@@
 \begin{eqnarray*}
-\hat{\beta} & = &   \frac{ \sum_{i=1}^{k} w_i  \hat{\theta}_i  }{ \hat{\phi}_p - \hat{\phi}_n} - \frac{ \hat{\phi}_n   }{ \hat{\phi}_p - \hat{\phi}_n} \\
-& = &
+\hat{\beta} & = &   \frac{ \sum_{i=1}^{k} w_i  \hat{\theta}_i  }{ \hat{\phi}_p - \hat{\phi}_n} - \frac{ \hat{\phi}_n   }{ \hat{\phi}_p - \hat{\phi}_n} 
 \end{eqnarray*}
-as our estimator of $\beta$. Then we can use the melding method of \citet{FayP:2015} to combine the confidence distributions for $\sum_{i=1}^{k} w_i  {\theta}_i$, for $\phi_p$,
+as our estimator of $\beta$.
+
+\subsection{Confidence Distribution Approach}
+
+Then we can use the melding method of \citet{FayP:2015} to combine the confidence distributions for $\beta_a = \sum_{i=1}^{k} w_i  {\theta}_i$, for $\phi_p$,
 and for $\phi_n$. That might not be straightforward, since I am not sure if $\phi_n$ and $\phi_p$ are monotonic in $\beta$. You need to check that out.
 
-We can compare that new method to the method described in the supplement of \citet{Kali:2021}.
+\subsection{Korn-Graubard+CD Approach}
+
+This is the method described in the supplement of \citet{Kali:2021}.
+Basically, we use the method of Korn and Graubard to get confidence distributions for ${\beta}_a = \sum_{i=1}^{k} w_i \theta_i$ (the apparent prevalence, assuming perfect sensitivity and specificity).
+Let $\hat{\beta}_a= \sum_{i=1}^{k} w_i X_i$. Under the Poisson assumption, we estimate the variance 
+of $\hat{\beta}_a$ with $\widehat{Var}(\hat{\beta}_a) = \sum_{i=1}^{k} w_i^2 X_i$.
+Then Korn-Graubard define the effective sample size by setting the $\widehat{Var}(\hat{\beta}_a)$ to the binomial variance estimate,
+\begin{eqnarray*}
+\widehat{Var}(\hat{\beta}_a) \stackrel{set}{=} \frac{\hat{\beta}_a (1-\hat{\beta}_a)}{n_e}
+\end{eqnarray*}
+So we get 
+\begin{eqnarray*}
+n_e =   \frac{\hat{\beta}_a (1-\hat{\beta}_a)}{\widehat{Var}(\hat{\beta}_a)}
+\end{eqnarray*}
+Then the effective count is $x_e = n_e \hat{\beta}_a$, and the lower and upper confidence distributions for ${\beta}_a$ under the Korn-Graubard method are Beta$(x_e, n_e-x_e+1)$ and Beta$(x_e+1,n_e-x_e)$, respectively.
+Then those confidence distributions are used in place of the confidence distributions for $\beta_a$ in the previous subsection.
 

### 2021-07-28 check_var_hat_p_hat.R
Revised simulations

@@ -1,0 +1,73 @@
+n_replications <- 1
+
+simulation_design_200_50[1,]
+prevalence <- 0.005
+ICC <- 0.0001
+dirichlet_alpha <- 0.01
+n_weights <- 200
+samples_per_weight <- 50
+
+simulation_design_200_50 %>%
+  slice(rep(1:n(), each = n_replications)) %>%
+  group_by(design) %>%
+  mutate(replication = row_number()) %>%
+  ungroup() %>%
+  mutate(interval_results =
+           future_pmap(.options = furrr_options(seed = 200),
+                       list(prevalence, ICC, dirichlet_alpha, n_weights, samples_per_weight),
+                       function(prevalence, ICC, dirichlet_alpha, n_weights, samples_per_weight) {
+                         alpha <- (1 - ICC) / ICC * prevalence
+                         beta <- (1 - ICC) / ICC * (1 - prevalence)
+
+                         dat <- tibble(
+                           weight = as.vector(rdirichlet(1, alpha = rep(dirichlet_alpha, n_weights))),
+                           true_positivity = rbeta(n_weights, alpha, beta),
+                           n_tested = samples_per_weight) %>%
+                           mutate(sample_positives = rbinom(n = n(), size = n_tested, prob = true_positivity)) %>%
+                           mutate(sample_positivity = sample_positives / n_tested)
+
+                         mean_weight <- mean(dat$weight)
+                         var_weight <- var(dat$weight)
+                         coef_var <- sqrt(var_weight) / mean_weight
+
+                         p_hat <- sum(dat$sample_positivity * dat$weight)
+                         var_hat_p_hat <- sum((dat$weight / dat$n_tested)^2 * dat$sample_positives)
+
+                         result_wspoissonTest <-
+                           wspoissonTest(x = dat$sample_positives,
+                                         w = dat$weight / dat$n_tested,
+                                         midp = F)
+
+                         result_wspoissonTest_midp <-
+                           wspoissonTest(x = dat$sample_positives,
+                                         w = dat$weight / dat$n_tested,
+                                         midp = T)
+
+                         result_AC <- AC_method(p_hat = p_hat,
+                                                var_hat_p_hat = var_hat_p_hat,
+                                                adjusted = F)
+
+                         result_AC_adjusted <- AC_method(p_hat = p_hat,
+                                                         var_hat_p_hat = var_hat_p_hat,
+                                                         n_psu = n_weights,
+                                                         adjusted = T)
[…]

### 2021-07-28 code/simulations/confidence_interval_pperfect_assay/dirichlet_weights.R

@@ -1,0 +1,249 @@
+library(tidyverse)
+library(extraDistr)
+library(asht)
+library(cowplot)
+library(furrr)
+library(fs)
+library(scales)
+library(glue)
+
+plan(multisession, workers = 7)
+
+AC_method <- function(p_hat,
+                      var_hat_p_hat,
+                      adjusted = F,
+                      n_psu = NULL,
+                      n_strata = 1,
+                      conf.level = 0.95) {
+  if (adjusted & is.null(n_psu)) stop("Must specify n_psu if using adjusted method.")
+
+  alpha <- 1 - conf.level
+  z_val <- qnorm(1 - alpha / 2)
+  c <- z_val^2 / 2
+
+  if (adjusted) {
+    design_df <- n_psu - n_strata
+    t_val <- qt(1 - alpha / 2, design_df)
+  }
+
+  n_eff <- p_hat * (1 - p_hat) / var_hat_p_hat * ifelse(adjusted, (z_val / t_val)^2, 1)
+
+  x_tilde <- p_hat * n_eff + c
+  n_tilde <- n_eff + 2 * c
+  p_tilde <- x_tilde / n_tilde
+
+  ci <- p_tilde + c(-1, 1) * z_val * sqrt(p_tilde * (1 - p_tilde) / n_tilde)
+  attr(ci, "conf.level") <- conf.level
+
+  rval <- list(conf.int = ci, estimate = p_tilde, p_hat = p_hat, var_hat_p_hat = var_hat_p_hat)
+  class(rval) <- "htest"
+  return(rval)
+}
+
+CP_method <- function(p_hat,
+                      var_hat_p_hat,
+                      adjusted = F,
+                      n_psu = NULL,
+                      n_strata = 1,
+                      conf.level = 0.95) {
+  alpha <- 1 - conf.level
+
+  if (adjusted) {
+    z_val <- qnorm(1 - alpha / 2)
+    design_df <- n_psu - n_strata
+    t_val <- qt(1 - alpha / 2, design_df)
+  }
+
+  n_eff <- p_hat * (1 - p_hat) / var_hat_p_hat * ifelse(adjusted, (z_val / t_val)^2, 1)
+
+  n <- n_eff <- p_hat * (1 - p_hat) / var_hat_p_hat
[…]

### 2021-07-28 second_draft.R

@@ -1,160 +1,0 @@
-library(tidyverse)
-library(extraDistr)
-library(asht)
-library(cowplot)
-AC_method <- function(p_hat, var_hat_p_hat, conf.level = 0.95) {
-  alpha <- 1 - conf.level
-  z_val <- qnorm(1 - alpha / 2)
-  c <- z_val * z_val / 2
-
-  n_eff <- p_hat * (1 - p_hat) / var_hat_p_hat
-
-  x_tilde <- p_hat * n_eff + c
-  n_tilde <- n_eff + 2 * c
-  p_tilde <- x_tilde / n_tilde
-
-  ci <- p_tilde + c(-1,1) * z_val * sqrt(p_tilde * (1 - p_tilde) / n_tilde)
-  attr(ci, "conf.level") <- conf.level
-
-  rval <- list(conf.int = ci, estimate = p_tilde, p_hat = p_hat, var_hat_p_hat = var_hat_p_hat)
-  class(rval) <- "htest"
-  return(rval)
-}
-
-CP_method <- function(p_hat, var_hat_p_hat, conf.level = 0.95) {
-  alpha <- 1 - conf.level
-
-  n <- n_eff <- p_hat * (1 - p_hat) / var_hat_p_hat
-  x <- p_hat * n_eff
-
-  nu_1 <- 2 * x
-  nu_2 <- 2 * (n - x + 1)
-  nu_3 <- 2 * (x + 1)
-  nu_4 <- 2 * (n - x)
-
-  ci_l <- (nu_1 * qf(alpha / 2, nu_1, nu_2)) / (nu_2 + nu_1 * qf(alpha / 2, nu_1, nu_2))
-  ci_u <- (nu_3 * qf(1 - alpha / 2, nu_3, nu_4)) / (nu_4 + nu_3 * qf(1 - alpha / 2, nu_3, nu_4))
-
-  ci <- c(ci_l, ci_u)
-  attr(ci, "conf.level") <- conf.level
-
-  rval <- list(conf.int = ci, p_hat = p_hat, var_hat_p_hat = var_hat_p_hat)
-  class(rval) <- "htest"
-  return(rval)
-}
-
-# multipdplyr appears to be slower for this
-# library(multidplyr)
-# cluster <- new_cluster(parallel::detectCores() / 2 - 2)
-# cluster_library(cluster, "asht")
-# cluster_library(cluster, c("asht", "dplyr"))
-# cluster_assign(cluster, AC_method = AC_method)
-
-
-
-n_replications <- 2
[…]

### 2021-07-28 PrevAdjSurvey.tex

@@
 
+Two scenarios fall under my Dirichlet Weights Simulation:
+
+\begin{itemize}
+    \item 8,000 individuals (groups of 1) with population prevalence 0.05\% and varying variance among the weights.
+    \item 200 groups of 50 sampled with population prevalence 0.05\%, varying ICC, and varying variance among the weights.
+\end{itemize}
+
+The weight of each group is generated from a Dirichlet distribution with equal concentration parameters for all dimensions.
+
+The positivity of each group is generated from a Beta distribution which achieves the specified mean and ICC.
+
+As you predicted, the usual methods (Agresti-Coull and Clopper-Pearson) exhibit poor performance when there is high variance among the weights.
+
+Dean and Pagano recommend an adjustment suggested by Korn and Graubard that I wasn’t sure how to apply in the context of my simulation, so it’s possible that this is a pessimistic assessment of those methods.
+
+Let’s chat about these results and next steps early next week.
+
+Thanks,
+
+Damon
+
 \subsection{Weird U.S. State Simulation Results}

### 2021-07-29 code/simulations/confidence_interval_pperfect_assay/dirichlet_weights.R
Add comments to dirichlet_weights.R

@@ -7,8 +7,10 @@ library(fs)
 library(scales)
 library(glue)
 
+# Set up parallel processing
 plan(multisession, workers = 7)
 
+# Agresti-Coull Method
 AC_method <- function(p_hat,
                       var_hat_p_hat,
                       adjusted = F,
@@ -37,9 +39,10 @@ AC_method <- function(p_hat,
 
   rval <- list(conf.int = ci, estimate = p_tilde, p_hat = p_hat, var_hat_p_hat = var_hat_p_hat)
   class(rval) <- "htest"
-  return(rval)
+  rval
 }
 
+# Clopper-Pearson Method
 CP_method <- function(p_hat,
                       var_hat_p_hat,
                       adjusted = F,
@@ -72,11 +75,10 @@ CP_method <- function(p_hat,
 
   rval <- list(conf.int = ci, p_hat = p_hat, var_hat_p_hat = var_hat_p_hat)
   class(rval) <- "htest"
-  return(rval)
+  rval
 }
 
-# n_replications <- 10000
-
+# Design specification for 8000 groups of 1
 simulation_design_8000_1 <-
   crossing(prevalence = 0.005,
            ICC = c(0.1),
@@ -86,7 +88,7 @@ simulation_design_8000_1 <-
   mutate(design = 1:n()) %>%
   select(design, everything())
 
-
+# Design specification for 200 groups of 50
 simulation_design_200_50 <-
   crossing(prevalence = 0.005,
            ICC = c(0.0001, 0.025, 0.05, 0.1),
@@ -101,14 +103,16 @@ set.seed(200)
 generate_results <- function(simulation_design, n_replications) {
   experimental_results <-
     simulation_design %>%
-    slice(rep(1:n(), each = n_replications)) %>%
+    slice(rep(1:n(), each = n_replications)) %>% # duplicate each design n_replications times
     group_by(design) %>%
     mutate(replication = row_number()) %>%
     ungroup() %>%
     mutate(interval_results =
-             future_pmap(.options = furrr_options(seed = 200),
+             future_pmap(.options = furrr_options(seed = 200), # reproducible seed for parallel computing
                          list(prevalence, ICC, dirichlet_alpha, n_weights, samples_per_weight),
                          function(prevalence, ICC, dirichlet_alpha, n_weights, samples_per_weight) {
+
+                           # Calculate parameters for beta distribution with given mean and ICC
                            alpha <- (1 - ICC) / ICC * prevalence
[…]

### 2021-07-29 code/simulations/confidence_interval_perfect_assay/dirichlet_weights.R
Correct folder typo

@@ -256,4 +256,4 @@ results_plot_200_50 <- generate_plot(experimental_results = experimental_results
 
 # Save plots
 save_plot(results_plot_8000_1, ncol = 1, nrow = 3, filename = path("figures", "results_plot_8000_1", ext = "pdf"), base_asp = 2.5)
-save_plot(results_plot_200_50, ncol = 3, nrow = 3, filename = path("figures", "results_plot_200_50", ext = "pdf"), base_asp =  1.5)
+save_plot(results_plot_200_50, ncol = 3, nrow = 3, filename = path("figures", "results_plot_200_50", ext = "pdf"), base_asp =  2)

### 2021-07-29 code/simulations/confidence_interval_perfect_assay/dirichlet_weights.R
More comments in dirichlet_weights.R

@@ -116,6 +116,7 @@ generate_results <- function(simulation_design, n_replications) {
                            alpha <- (1 - ICC) / ICC * prevalence
                            beta <- (1 - ICC) / ICC * (1 - prevalence)
 
+                           # Simulate data
                            dat <- tibble(
                              weight = as.vector(rdirichlet(1, alpha = rep(dirichlet_alpha, n_weights))),
                              true_positivity = rbeta(n_weights, alpha, beta),
@@ -123,6 +124,7 @@ generate_results <- function(simulation_design, n_replications) {
                              mutate(sample_positives = rbinom(n = n(), size = n_tested, prob = true_positivity)) %>%
                              mutate(sample_positivity = sample_positives / n_tested)
 
+                           # Useful calculations for applying methods or post-processing results
                            mean_weight <- mean(dat$weight)
                            var_weight <- var(dat$weight)
                            coef_var <- sqrt(var_weight) / mean_weight
@@ -130,6 +132,7 @@ generate_results <- function(simulation_design, n_replications) {
                            p_hat <- sum(dat$sample_positivity * dat$weight)
                            var_hat_p_hat <- sum((dat$weight / dat$n_tested)^2 * dat$sample_positives) # this is a bad estimate with high ICC
 
+                           # Apply each method to simulated data
                            result_wspoissonTest <-
                              wspoissonTest(x = dat$sample_positives,
                                            w = dat$weight / dat$n_tested,

### 2021-07-29 PrevAdjSurvey.tex

--- 2021-07-28 PrevAdjSurvey.tex
@@
 \usepackage{booktabs}
-
+\usepackage{lscape}
+\usepackage{pdflscape}    
 %\usepackage{C:/R/R-2.11.1/share/texmf/Sweave}
@@
 
+I present results for two scenarios:
+
+\begin{itemize}
+    \item The weight of each group is generated from a Dirichlet distribution with equal concentration parameters for all dimensions.
+The "Coefficient of Variation" in the figures referes to these weights.
+    \item The true positivity of each group is generated from a Beta distribution which achieves the specified mean and ICC.
+    \item Figure~\ref{fig:dws1}. Samples of 8,000 groups of 1. Population prevalence = 0.05\%/ Varying weight variance. Replicated 10,000 times.
+    \begin{itemize}
+        \item The two wsPoisson methods maintain appropriate or conservative coverage, regardless of the coefficient of variation among the weights.
+        \item The other two methods (Agresti-Coull and Clopper-Pearson) only begin to falter at unrealistic or unusual (according to Barry) coefficients of variation.
+        \item More typical coefficients of variation would be 20\%-40\%.
+    \end{itemize}
+    \item Figure~\ref{fig:dws2}. Samples of 200 groups of 50. Population prevalence = 0.05\%. Varying ICC. Varying weight variance. Replicated 10,000 times.
+    \begin{itemize}
+        \item Results here are a bit confusing.
+        \item I know that the results for Agresti-Coull and Clopper-Pearson could be improved with a better estimate for \(\hat{\text{var}}(\hat{p}) \).
+The simple estimate I was using appears to perform poorly in the case of high ICC.
+\textbf{I wonder if Barry can point me towards a good estimator for \(\hat{\text{var}}(\hat{p}) \) in the presence of high ICC.}
+        \item It is a bit strange that the wsPoisson methods perform better when there is extreme Coefficient of Variation, but it is consistent with the previously observed behavior of higher CoV leading to more conservative coverage.
+    \end{itemize}
+\end{itemize}
+
+\begin{figure}
+    \centering
+    \includegraphics[width=\textwidth]{figures/results_plot_8000_1.pdf}
+    \caption{Dirichlet Weights Scenario 1}
+    \label{fig:dws1}
+\end{figure}
+
+\pagebreak
+\begin{landscape}
+\begin{figure}
+    \centering
+    \includegraphics[width = \paperwidth]{figures/results_plot_200_50.pdf}
+    \caption{Dirichlet Weights Scenario 2}
+    \label{fig:dws2}
+\end{figure}
+\end{landscape}
+\pagebreak
+
+As you predicted, the usual methods (Agresti-Coull and Clopper-Pearson) exhibit poor performance when there is high variance among the weights.
+
+Dean and Pagano recommend an adjustment suggested by Korn and Graubard that I wasn’t sure how to apply in the context of my simulation, so it’s possible that this is a pessimistic assessment of those methods.
+
+Let’s chat about these results and next steps early next week.
+
+Thanks,
+
+Damon
+
 \subsection{Weird U.S. State Simulation Results}

### 2021-07-29 code/simulations/confidence_interval_perfect_assay/dirichlet_weights.R
fixed dirchilet weights

@@ -129,6 +129,7 @@ generate_results <- function(simulation_design, n_replications) {
                            var_weight <- var(dat$weight)
                            coef_var <- sqrt(var_weight) / mean_weight
 
+                           true_p <- sum(dat$true_positivity * dat$weight)
                            p_hat <- sum(dat$sample_positivity * dat$weight)
                            var_hat_p_hat <- sum((dat$weight / dat$n_tested)^2 * dat$sample_positives) # this is a bad estimate with high ICC
 
@@ -163,7 +164,8 @@ generate_results <- function(simulation_design, n_replications) {
                            #                        n_psu = n_weights,
                            #                        adjusted = T)
 
-                           list(mean_weight = mean_weight,
+                           list(true_prevalence = true_p,
+                                mean_weight = mean_weight,
                                 var_weight = var_weight,
                                 coef_var = coef_var,
                                 result_wspoissonTest = result_wspoissonTest,
@@ -185,8 +187,8 @@ generate_results <- function(simulation_design, n_replications) {
              map("conf.int") %>%
              map(~set_names(., c("l", "u")))) %>%
     unnest_wider(conf.int, names_sep = "_") %>%
-    mutate(lower_error = conf.int_l > prevalence,
-           upper_error = prevalence > conf.int_u,
+    mutate(lower_error = conf.int_l > true_prevalence,
+           upper_error = true_prevalence > conf.int_u,
            covered = !(lower_error | upper_error)) %>%
     select(-htest, -starts_with("conf.int"))
 
@@ -195,11 +197,11 @@ generate_results <- function(simulation_design, n_replications) {
 
 # Get results for the two simulation designs
 experimental_results_8000_1 <- generate_results(simulation_design = simulation_design_8000_1, n_replications = 10000)
-experimental_results_200_50 <- generate_results(simulation_design = simulation_design_200_50, n_replications = 10000)
+# experimental_results_200_50 <- generate_results(simulation_design = simulation_design_200_50, n_replications = 10000)
 
 # Save results
 write_rds(experimental_results_8000_1, "experimental_results_8000_1.rds")
-write_rds(experimental_results_200_50, "experimental_results_200_50.rds")
+# write_rds(experimental_results_200_50, "experimental_results_200_50.rds")
 
[…]

### 2021-07-30 new_scenarios.R
new scenarios

@@ -1,0 +1,51 @@
+library(tidyverse)
+simulate_weights <- function(n_weights, coef_var) {
+  # mu <- 1 / n_weights
+  # sigma2 <- (coef_var / n_weights)^2
+  # alpha <- ((1 - mu) / sigma2 - 1 / mu) * mu^2
+  # beta <- alpha * (1 / mu - 1)
+
+  alpha <- 1 / coef_var^2 - 1 / (n_weights * coef_var^2) - 1 / n_weights
+  beta <- alpha * (n_weights - 1)
+
+  x <- rbeta(n_weights, alpha, beta)
+  if(sum(is.na(x))) return(NA)
+  x / sum(x)
+}
+
+# We want to evaluate along 3 axis:
+
+# Overall prevalence should always be low (say 0.5%)
+# Weights should span a range of relevant coefficients of variation (say 10%-200%)
+# Group-prevalences
+# Prevalence can be allocated differently concenrated in highly weighted groups, low weighted groups,
+population_prevalence <- 0.005
+n_weights <- 8000
+set.seed(200)
+tmp <-
+  crossing(prop_groups_with_cases = c(0.01, 0.05, 0.10, 0.25, 0.5, 0.75, 1),
+           kind_of_groups_with_cases = c("mostly high weight", "any weight", "mostly low weight"),
+           coefficient_of_variation = c(0.1, 0.2, 0.3, 0.5, 1, 2, 3, 5, 10)) %>%
+  # slice(rep(1:n(), 10)) %>%
+  mutate(w = map(coefficient_of_variation, ~simulate_weights(n_weights = n_weights, coef_var = .))) %>%
+  mutate(groups_with_prevalence = pmap(list(prop_groups_with_cases = prop_groups_with_cases,
+                                            kind_of_groups_with_cases = kind_of_groups_with_cases,
+                                            w = w),
+                                       function(prop_groups_with_cases, kind_of_groups_with_cases, w) {
+                                         case_when(
+                                           kind_of_groups_with_cases == "mostly high weight" ~ sample(1:n_weights, size = round(prop_groups_with_cases * n_weights), replace = F, prob = w),
+                                           kind_of_groups_with_cases == "any weight" ~ sample(1:n_weights, size = round(prop_groups_with_cases * n_weights), replace = F),
[…]

### 2021-07-30 simulate_weights_beta.R

@@ -1,0 +1,72 @@
+simulate_weights <- function(n_weights, coef_var) {
+  # mu <- 1 / n_weights
+  # sigma2 <- (coef_var / n_weights)^2
+  # alpha <- ((1 - mu) / sigma2 - 1 / mu) * mu^2
+  # beta <- alpha * (1 / mu - 1)
+
+  alpha <- 1 / coef_var^2 - 1 / (n_weights * coef_var^2) - 1 / n_weights
+  beta <- alpha * (n_weights - 1)
+
+  x <- rbeta(n_weights, alpha, beta)
+  if(sum(is.na(x))) return(NA)
+  x / sum(x)
+}
+n_weights <- 10
+coef_var <- 3
+
+
+
+set.seed(200)
+tmp <-
+  crossing(n_weights = 10^(1:5),
+         coef_var = c(0.1, 0.2, 0.3, 0.5, 1, 2, 3, 5, 10)) %>%
+  slice(rep(1:n(), times = 1)) %>%
+  mutate(x = map2(n_weights, coef_var, ~simulate_weights(.x, .y)))
+
+
+tmp %>%
+  mutate()
+# k is the number of weights
+k <- 8000
+
+# coef_var is standard deviation of the weights / the mean of the weights
+coef_var <- 0.2
+
+# since we know the mean of the weights is 1 / k, the coef_var determines the variance of the weights
+mu <- 1 / k
+sigma2 <- (coef_var / k)^2
+
+# Then we can sample from beta distribution with the above mean and variance
+alpha <- ((1 - mu) / sigma2 - 1 / mu) * mu^2
+beta <- alpha * (1 / mu - 1)
+
+x <- rbeta(k, alpha, beta)
+
+# since mean(x) should be close to 1/k, sum(x) should be close to 1
+# but not exactly, so we can normalize
+x <- x / sum(x)
+
+# Exactly mu, (duh):
+mu
+mean(x)
+# Very close to coef_var:
+coef_var
+sd(x) / mean(x)
+
+# This only works because k is huge
+k <- 10
+coef_var <- 0.2
+mu <- 1 / k
+sigma2 <- (coef_var / k)^2
+alpha <- ((1 - mu) / sigma2 - 1 / mu) * mu^2
+beta <- alpha * (1 / mu - 1)
+
+x <- rbeta(k, alpha, beta)
+x <- x / sum(x)
+
+# Exactly mu, (duh):
+mu
+mean(x)
+# Not close to coef_var:
+coef_var
+sd(x) / mean(x)

### 2021-08-18 code/simulations/confidence_interval_perfect_assay/fixed_weights_many_arrayjob.R
figures for section 2

@@ -146,7 +146,7 @@ experimental_design <-
   group_by(design) %>%
   filter(coef_var_rel_error == min(coef_var_rel_error)) %>%
   select(design, n_groups, coef_var = obs_coef_var, weights) %>%
-  mutate(weights = map(weights, sort)) %>%
+  mutate(weights = map(weights, ~sort(., decreasing = T))) %>%
   mutate(tests_per_group = case_when(
     n_groups == 50 ~ 200,
     n_groups == 8000 ~ 1

### 2021-08-18 code/simulations/confidence_interval_perfect_assay/process_weights_many.R

@@ -1,0 +1,92 @@
+library(tidyverse)
+library(scales)
+library(glue)
+library(cowplot)
+results_summary <-
+  read_csv("code/simulations/confidence_interval_perfect_assay/combined_fixed_weights_many_summary.csv") %>%
+  left_join(read_csv("code/simulations/confidence_interval_perfect_assay/experimental_design.csv") %>%
+              mutate(group_distribution = case_when( # Error because I labeled things wrong when setting up ex design
+                group_distribution == "low" ~ "high",
+                group_distribution == "high" ~ "low",
+                group_distribution == "uniform" ~ "uniform"
+              ))) %>%
+  pivot_longer(cols = c(lower_error_freq, upper_error_freq, coverage)) %>%
+  mutate(name = fct_recode(name,
+                           "Lower Error Frequency" = "lower_error_freq",
+                           "Upper Error Frequency" = "upper_error_freq",
+                           "Coverage" = "coverage"),
+         method = fct_recode(method,
+                             "Agresti-Coull (Unadjusted)" = "AC",
+                             "Agresti-Coull (Adjusted)" = "AC_adjusted",
+                             "Clopper-Pearson (Unadjusted)" = "CP",
+                             "Clopper-Pearson (Adjusted)" = "CP_adjusted",
+                             "wsPoisson" = "wspoissonTest",
+                             "wsPoisson with mid-p" = "wspoissonTest_midp"),
+         group_distribution = group_distribution %>%
+           fct_relevel("high", "uniform", "low") %>%
+           fct_relabel(str_to_title))
+
+name_to_plot <- "Coverage"
+n_groups_to_plot <- 8000
+
+generate_plot <- function(name_to_plot, n_groups_to_plot){
+  group_size <- if_else(n_groups_to_plot == 8000, 1, 200)
+
+  generated_plot <-
+    results_summary %>%
+    mutate(
+      tests = 10000,
+      successes = as.integer(value * tests),
+      failures = tests - successes) %>%
+    filter(n_groups == n_groups_to_plot,
+           name == name_to_plot) %>%
+    ggplot(aes(x = coef_var,
+               y = successes / tests,
+               color = method,
+               group = method,
+               # linetype = method,
+               successes = successes,
[…]

### 2021-08-18 PrevAdjSurvey.tex

--- 2021-07-28 PrevAdjSurvey.tex
@@
 \usepackage{amsmath}
-
+\usepackage{amssymb}
 %% Please use the following statements for
@@
 
+\DeclareMathOperator{\E}{E}
+\DeclareMathOperator{\Var}{Var}
+\DeclareMathOperator{\Cov}{Cov}
+
 \newcommand{\ch}[2]{\ensuremath{ \left( \begin{array}{c} #1 \\ #2 \end{array} \right) }}
 \newcommand{\dfn}[2]{\ensuremath{ \left( #1 \right)_{(#2)}}}
+
+\usepackage{graphicx}
+\graphicspath{ {./figures/} }
 
@@
 
-\subsection{Dirichlet Weights Simulation Results}
+\subsection{Results for varying Coeficient of Variation, Number of Weights with Non-Zero Prevalence, and Distribution of Weights with Non-Zero Prevalence}
 
-\subsection{Weird U.S. State Simulation Results}
+Simulation method:
 
-For this section I have applied 4 methods to 2 populations, with 10,0000 replications each.
-
-\noindent Methods:
 \begin{itemize}
-    \item AC \& AC\_adj: The Agresti-Coull and Agresti-Coull adjusted methods for survey samples described in \cite{Dean:2015}. Implemented by hand.
-    \item wspoissonTest \& wspoissonTest\_midp: the methods described in \cite{FayF:1997} and \cite{FayK:2017}. Implemented in \cite{asht}.
+    \item Simulating weights. To simulate \( k \) weights with a coefficient of variation \( v \):
+    \begin{itemize}
+        \item Sample \( W_i \sim \text{Beta}\left( \frac{1}{v^2} - \frac{1}{kv^2} - \frac{1}{k}, \left( \frac{1}{v^2} - \frac{1}{nk^2} - \frac{1}{k} \right)  (k - 1) \right)\).
+        \item By design \( \E W_i = 1 / k \), and  \( \Var W_i = ( v / k )^2  \).
+        \item Thus, \( \E \left[ \sum_{i=1}^k w_i \right] = 1\).
+        \item Normalize \( w_i^* = \frac{w_i}{\sum_{i=1}^k w_i} \), to guarantee \( \sum_{i=1}^k w_i^* = 1 \).
+        \item These \( w_i^* \) should have approximately the desired coefficient of variation.
+    \end{itemize}
+    \item Selecting weights with non-zero prevalence. Selecting weights with non-zero prevalence is deterministic. 
+    \begin{itemize}
+        \item First, the proportion of weights with non-zero prevalence is selected. Call this \( a \), where \( 0 < a \leq k \)
+        \item Then, the specific weights with non-zero prevalence are selected by 1 of 3 options:
+        \begin{itemize}
+            \item High weights: the  \( a \) largest weights are selected.
+            \item Uniform weights: \( a \) weights are selected such that the ranks of their weights are evenly spaced.
+Ex: For \( k = 100 \) and \( a = 3 \), the 25th, 50th and 75th largest weights are selected.
+            \item Low weights: the  \( a \) smallest weights are selected.
+        \end{itemize}
+    \end{itemize}
+    \item Determining prevalence among weights with non-zero prevalence.
+    \begin{itemize}
+        \item \( \theta_i \)  for each of the \( a \) weights with non-zero prevalence is \( \beta / \sum_{i=1}^a w_i^{**} \).
+        \item Note: in some cases (Low weights and/or high coefficient of variation) it is not possible for the selected weights to provide an overall level of \( \beta \) prevalence.
+These cases are discarded.
+    \end{itemize}
+    \item Simulating data.
+    \begin{itemize}
+        \item \( X_i \sim \text{Binomial}(n_i, \theta_i) \)
+    \end{itemize}
 \end{itemize}
 
-In each scenario, I use the 2020 census population counts for all states \& DC and specify the exact number of cases in each state's population to achieve an overall prevalence $\approx$  0.5\%.
-Per \cite{Lemeshow1985SurveysTM}, I implement a 2-stage sampling algorithm, where $m$ states are sampled with replacement and $\tilde{n}$ people are sampled from each of the $m$ states.
-In the results here, $m = 12,000$ and $\tilde{n} = 1$, equivalent to a simple random sample from the country.
-Alternative schemes like $m = 120$ and $\tilde{n} = 100$ seem to produce worse results for the wspoissonTest methods, but I have not investigated this fully.\\
-The differences between the two scenarios are presented below.\\
+These simulations are performed in two scenarios:
 
-\noindent Scenarios:
-\begin{itemize}
-    \item one\_state: Montana has 30\% prevalence, while all other states have no cases.
-    \item two\_state: California and New York each have 3\% prevalence, while all other states have no cases.
-    \item few\_state: California, Texas, Florida, and New York each have 1.5\% prevalence, while all other states have no cases.
-    \item many\_state: all states have $\approx$ 0.5\% prevalence, but with some clustering of cases
-\end{itemize}
+\begin{enumerate}
+    \item \( k = 50 \), \( n_i = 200 \), Total sample size: 10,000. Meant to resemble a scenario like taking an equal-sized sample from each of the 50 US States.
+    \item \( k = 8000 \), \( n_i = 1 \), Total sample size: 8,000. Meant to resemble a scenario with a complex weighting scheme where each person has their own weight.
+\end{enumerate}
 
-\noindent Results:
-\begin{table}
+\begin{landscape}
+\begin{figure}
     \centering
-\begin{tabular}{llrrr}
-\toprule
-scenario & method & coverage & lower\_error\_freq & upper\_error\_freq\\
-\midrule
-one\_state & AC & 0.9660 & 0.0232 & 0.0108\\
-one\_state & AC\_adj & 0.9660 & 0.0232 & 0.0108\\
-one\_state & wspoissonTest & 0.9928 & 0.0039 & 0.0033\\
-one\_state & wspoissonTest\_midp & 0.9852 & 0.0083 & 0.0065\\
-\addlinespace
-two\_state & AC & 0.9484 & 0.0256 & 0.0260\\
-two\_state & AC\_adj & 0.9484 & 0.0256 & 0.0260\\
-two\_state & wspoissonTest & 0.9632 & 0.0193 & 0.0175\\
-two\_state & wspoissonTest\_midp & 0.9538 & 0.0235 & 0.0227\\
-\addlinespace
-few\_state & AC & 0.9570 & 0.0259 & 0.0171\\
-few\_state & AC\_adj & 0.9570 & 0.0259 & 0.0171\\
-few\_state & wspoissonTest & 0.9629 & 0.0216 & 0.0155\\
-few\_state & wspoissonTest\_midp & 0.9559 & 0.0250 & 0.0191\\
-\addlinespace
-many\_state & AC & 0.9515 & 0.0287 & 0.0198\\
-many\_state & AC\_adj & 0.9515 & 0.0287 & 0.0198\\
-many\_state & wspoissonTest & 0.9597 & 0.0246 & 0.0157\\
-many\_state & wspoissonTest\_midp & 0.9517 & 0.0281 & 0.0202\\
-\bottomrule
-\end{tabular}
-\end{table}
+    \includegraphics[width = \paperwidth]{figures/results_plot_200_50.pdf}
+    \caption{Dirichlet Weights Scenario 2}
+    \label{fig:dws2}
+\end{figure}
+\end{landscape}
+\pagebreak
 
-I have not found any scenarios that ``break" the AC methods, which appear to be on par with the wspoissonTest\_midp methods.
-There is no obvious pattern in coverage vs number of states with cases, other than that the wspoissonTest appears to do better with more evenly spread cases and both wspoissonTest methods do poorly in the one\_state scenario.
+% \subsection{Dirichlet Weights Simulation Results}
+
+% I present results for two scenarios:
+
+% \begin{itemize}
+%     \item The weight of each group is generated from a Dirichlet distribution with equal concentration parameters for all dimensions.
+The "Coefficient of Variation" in the figures referes to these weights.
+%     \item The true positivity of each group is generated from a Beta distribution which achieves the specified mean and ICC.
+%     \item Figure~\ref{fig:dws1}. Samples of 8,000 groups of 1. Population prevalence = 0.05\%/ Varying weight variance. Replicated 10,000 times.
+%     \begin{itemize}
+%         \item The two wsPoisson methods maintain appropriate or conservative coverage, regardless of the coefficient of variation among the weights.
+%         \item The other two methods (Agresti-Coull and Clopper-Pearson) only begin to falter at unrealistic or unusual (according to Barry) coefficients of variation.
+%         \item More typical coefficients of variation would be 20\%-40\%.
+%     \end{itemize}
+%     \item Figure~\ref{fig:dws2}. Samples of 200 groups of 50. Population prevalence = 0.05\%. Varying ICC. Varying weight variance. Replicated 10,000 times.
+%     \begin{itemize}
+%         \item Results here are a bit confusing.
+%         \item I know that the results for Agresti-Coull and Clopper-Pearson could be improved with a better estimate for \(\hat{\text{var}}(\hat{p}) \).
+The simple estimate I was using appears to perform poorly in the case of high ICC.
+\textbf{I wonder if Barry can point me towards a good estimator for \(\hat{\text{var}}(\hat{p}) \) in the presence of high ICC.}
+%         \item It is a bit strange that the wsPoisson methods perform better when there is extreme Coefficient of Variation, but it is consistent with the previously observed behavior of higher CoV leading to more conservative coverage.
+%     \end{itemize}
+% \end{itemize}
+
+% \begin{figure}
+%     \centering
+%     \includegraphics[width=\textwidth]{figures/results_plot_8000_1.pdf}
+%     \caption{Dirichlet Weights Scenario 1}
+%     \label{fig:dws1}
+% \end{figure}
+
+% \pagebreak
+% \begin{landscape}
+% \begin{figure}
+%     \centering
+%     \includegraphics[width = \paperwidth]{figures/results_plot_200_50.pdf}
+%     \caption{Dirichlet Weights Scenario 2}
+%     \label{fig:dws2}
+% \end{figure}
+% \end{landscape}
+% \pagebreak
+
+% As you predicted, the usual methods (Agresti-Coull and Clopper-Pearson) exhibit poor performance when there is high variance among the weights.
+
+% Dean and Pagano recommend an adjustment suggested by Korn and Graubard that I wasn’t sure how to apply in the context of my simulation, so it’s possible that this is a pessimistic assessment of those methods.
+
+% Let’s chat about these results and next steps early next week.
+
+% Thanks,
+
+% Damon
+
+% \subsection{Weird U.S. State Simulation Results}
+
+% For this section I have applied 4 methods to 2 populations, with 10,0000 replications each.
+
+% \noindent Methods:
+% \begin{itemize}
+%     \item AC \& AC\_adj: The Agresti-Coull and Agresti-Coull adjusted methods for survey samples described in \cite{Dean:2015}. Implemented by hand.
+%     \item wspoissonTest \& wspoissonTest\_midp: the methods described in \cite{FayF:1997} and \cite{FayK:2017}. Implemented in \cite{asht}.
+% \end{itemize}
+
+% In each scenario, I use the 2020 census population counts for all states \& DC and specify the exact number of cases in each state's population to achieve an overall prevalence $\approx$  0.5\%.
+% Per \cite{Lemeshow1985SurveysTM}, I implement a 2-stage sampling algorithm, where $m$ states are sampled with replacement and $\tilde{n}$ people are sampled from each of the $m$ states.
+% In the results here, $m = 12,000$ and $\tilde{n} = 1$, equivalent to a simple random sample from the country.
+% Alternative schemes like $m = 120$ and $\tilde{n} = 100$ seem to produce worse results for the wspoissonTest methods, but I have not investigated this fully.\\
+% The differences between the two scenarios are presented below.\\
+
+% \noindent Scenarios:
+% \begin{itemize}
+%     \item one\_state: Montana has 30\% prevalence, while all other states have no cases.
+%     \item two\_state: California and New York each have 3\% prevalence, while all other states have no cases.
+%     \item few\_state: California, Texas, Florida, and New York each have 1.5\% prevalence, while all other states have no cases.
+%     \item many\_state: all states have $\approx$ 0.5\% prevalence, but with some clustering of cases
+% \end{itemize}
+
+% \noindent Results:
+% \begin{table}
+% \centering
+% \begin{tabular}{llrrr}
+% \toprule
+% scenario & method & coverage & lower\_error\_freq & upper\_error\_freq\\
+% \midrule
+% one\_state & AC & 0.9660 & 0.0232 & 0.0108\\
+% one\_state & AC\_adj & 0.9660 & 0.0232 & 0.0108\\
+% one\_state & wspoissonTest & 0.9928 & 0.0039 & 0.0033\\
+% one\_state & wspoissonTest\_midp & 0.9852 & 0.0083 & 0.0065\\
+% \addlinespace
+% two\_state & AC & 0.9484 & 0.0256 & 0.0260\\
+% two\_state & AC\_adj & 0.9484 & 0.0256 & 0.0260\\
+% two\_state & wspoissonTest & 0.9632 & 0.0193 & 0.0175\\
+% two\_state & wspoissonTest\_midp & 0.9538 & 0.0235 & 0.0227\\
+% \addlinespace
+% few\_state & AC & 0.9570 & 0.0259 & 0.0171\\
+% few\_state & AC\_adj & 0.9570 & 0.0259 & 0.0171\\
+% few\_state & wspoissonTest & 0.9629 & 0.0216 & 0.0155\\
+% few\_state & wspoissonTest\_midp & 0.9559 & 0.0250 & 0.0191\\
+% \addlinespace
+% many\_state & AC & 0.9515 & 0.0287 & 0.0198\\
+% many\_state & AC\_adj & 0.9515 & 0.0287 & 0.0198\\
+% many\_state & wspoissonTest & 0.9597 & 0.0246 & 0.0157\\
+% many\_state & wspoissonTest\_midp & 0.9517 & 0.0281 & 0.0202\\
+% \bottomrule
+% \end{tabular}
+% \end{table}
+
+% I have not found any scenarios that ``break" the AC methods, which appear to be on par with the wspoissonTest\_midp methods.
+% There is no obvious pattern in coverage vs number of states with cases, other than that the wspoissonTest appears to do better with more evenly spread cases and both wspoissonTest methods do poorly in the one\_state scenario.
 

### 2021-08-18 code/simulations/confidence_interval_perfect_assay/process_weights_many.R
Figures for confidence interval on theta star

@@ -75,16 +75,13 @@ generate_plot <- function(name_to_plot, n_groups_to_plot){
   }
 
 
-generate_plot(name_to_plot = "Lower Error Frequency", n_groups_to_plot = 8000)
-generate_plot(name_to_plot = "Lower Error Frequency", n_groups_to_plot = 50)
-
 
 
 results_summary %>%
   select(n_groups, name) %>%
   distinct() %>%
   mutate(plot = map2(name, n_groups, ~generate_plot(.x, .y))) %>%
-  mutate(file_name = map2_chr(name, n_groups, ~path(str_c(str_replace_all(str_to_lower(.x), "\\s", "_"), .y, sep = "_"), ext = "pdf"))) %>%
+  mutate(file_name = map2_chr(name, n_groups, ~path("figures", str_c(str_replace_all(str_to_lower(.x), "\\s", "_"), .y, sep = "_"), ext = "pdf"))) %>%
   # mutate(walk2(plot, file_name, ~save_plot(filename = .y, plot = .x, ncol = 5, nrow = 3, base_asp = (11 / 5) / (8.5 / 3), base_height = 8.5 / 3)))
 mutate(walk2(plot, file_name, ~save_plot(filename = .y, plot = .x, ncol = 5, nrow = 3, base_asp = (11 / 5) / (8.5 / 3), base_height = 4)))
 

### 2021-08-18 code/simulations/confidence_interval_theta_star_fay_vs_LR/confidence_interval_theta_star_fay_vs_LR_process_results.R

@@ -5,7 +5,7 @@ library(cowplot)
 library(fs)
 library(furrr)
 
-results <- read_rds("code/simulations/confidence_interval_theta_star_fay_vs_LR/confidence_interval_theta_star_fay_vs_LR_results.rds")
+results <- read_csv("code/simulations/confidence_interval_theta_star_fay_vs_LR/confidence_interval_theta_star_fay_vs_LR_results.csv")
 
 # Process Results ---------------------------------------------------------
 coverage_results <-

### 2021-08-18 PrevAdjSurvey.tex
Updates from Overleaf

@@
 \usepackage{pdflscape}
+\usepackage{pdfpages}
 %\usepackage{C:/R/R-2.11.1/share/texmf/Sweave}
@@
 \graphicspath{ {./figures/} }
+\usepackage[colorinlistoftodos]{todonotes}
 
@@
 Simulation method:
-
+In this simulation \( \beta = 0.005 \).
 \begin{itemize}
@@
 \begin{enumerate}
-    \item \( k = 50 \), \( n_i = 200 \), Total sample size: 10,000. Meant to resemble a scenario like taking an equal-sized sample from each of the 50 US States.
-    \item \( k = 8000 \), \( n_i = 1 \), Total sample size: 8,000. Meant to resemble a scenario with a complex weighting scheme where each person has their own weight.
+    \item Scenario 1. \( k = 50 \), \( n_i = 200 \), Total sample size: 10,000. Meant to resemble a scenario like taking an equal-sized sample from each of the 50 US States.
+    \item Scenario 2. \( k = 8000 \), \( n_i = 1 \), Total sample size: 8,000. Meant to resemble a scenario with a complex weighting scheme where each person has their own weight.
 \end{enumerate}
 
+Results are presented on the next two pages.
+\todo[inline]{Would like to make these figures smaller / more focused. Maybe we don't need to present all of the ``Weights with Non-0 Prevalence."}
+\todo[inline]{Maybe need to simulate prevalence \( > 0.005 \) to show wsPoisson failing}
+\begin{itemize}
+    \item Regardless of the scenario, the two wsPoisson methods achieve at least the desired coverage. This coverage increases as the coefficient of variation among the weights increases.
+    \item Regardless of the scenario, when the coefficient of variation among the weights is near 0, all methods perform well.
+    \item Regardless of the scenario, when the prevalence is concentrated among the largest weights, increasing coefficient of variation among the weights results in lower coverage for the Agresti-Coull and Clopper-Pearson methods.
+    \item Regardless of the scenario, when the prevalence is concentrated among the smallest weights, increasing coefficient of variation among the weights results in higher coverage for all methods.
+    \item When the prevalence is distributed uniformly among the weights, Scenario 1 exhibits similar behavior to when the prevalence is concentrated among the smallest weights.
+    \items When the prevalence is distributed uniformly among the weights, Scenario 2 exhibits the same behavior as when the prevalence is concentrated among the largest weights.
+
+\end{itemize}
+
 \begin{landscape}
-\begin{figure}
-    \centering
-    \includegraphics[width = \paperwidth]{figures/results_plot_200_50.pdf}
-    \caption{Dirichlet Weights Scenario 2}
-    \label{fig:dws2}
-\end{figure}
+\includepdf[angle=90]{coverage_50}
 \end{landscape}
-\pagebreak
+
+\begin{landscape}
+\includepdf[angle=90]{coverage_8000}
+\end{landscape}
 

### 2021-08-27 code/simulations/confidence_interval_perfect_assay/fixed_weights_many_arrayjob.R
new sim results for 5% prevalence

@@ -181,7 +181,7 @@ experimental_design <-
 cat("experiments designed\n")
 
 if (sjob == 1) {
-  write_rds(experimental_design, path(save_path, "experimental_design.rds"))
+  write_rds(experimental_design, path(save_path, "005_experimental_design.rds"))
 }
 
 calculate_interval_results <- function(weights,

### 2021-08-27 notes.tex
Updates from Overleaf

--- 2021-08-18 PrevAdjSurvey.tex
@@
 \begin{eqnarray*}
-\beta & = & \frac{ \sum_{i=1}^{k} N_i \theta_i^* }{ \sum_{j=1}^{k} N_j }  =  \sum_{i=1}^{k} w_i \theta_i,
+\beta & = & \frac{ \sum_{i=1}^{k} N_i \theta_i^* }{ \sum_{j=1}^{k} N_j }  =  \sum_{i=1}^{k} w_i \theta_i^*,
 \end{eqnarray*}
@@
 
+\begin{figure}
+    \centering
+    \includegraphics[width=\textwidth,height=\textheight,keepaspectratio]{Combined_comparison_plots.pdf}
+    \caption{Caption}
+    \label{fig:Combined_comparison_plots}
+\end{figure}
+
 \section{Confidence Interval on $\beta$ with a Perfect Assay}
@@
 
-\subsection{Results for varying Coeficient of Variation, Number of Weights with Non-Zero Prevalence, and Distribution of Weights with Non-Zero Prevalence}
+\subsection{Results for varying Coefficient of Variation, Number of Weights with Non-Zero Prevalence, and Distribution of Weights with Non-Zero Prevalence}
 
@@
     \item When the prevalence is distributed uniformly among the weights, Scenario 1 exhibits similar behavior to when the prevalence is concentrated among the smallest weights.
-    \items When the prevalence is distributed uniformly among the weights, Scenario 2 exhibits the same behavior as when the prevalence is concentrated among the largest weights.
-
+    \item When the prevalence is distributed uniformly among the weights, Scenario 2 exhibits the same behavior as when the prevalence is concentrated among the largest weights.
 \end{itemize}
@@
 \includepdf[angle=90]{coverage_8000}
+\end{landscape}
+
+\begin{landscape}
+\includepdf[angle=90]{upper_error_frequency_50}
+\end{landscape}
+
+\begin{landscape}
+\includepdf[angle=90]{upper_error_frequency_8000}
+\end{landscape}
+
+\begin{landscape}
+\includepdf[angle=90]{lower_error_frequency_50}
+\end{landscape}
+
+\begin{landscape}
+\includepdf[angle=90]{lower_error_frequency_8000}
 \end{landscape}

### 2021-08-27 code/simulations/confidence_interval_perfect_assay/process_weights_many.R
Updated Figures for 5% sim

@@ -2,14 +2,22 @@ library(tidyverse)
 library(scales)
 library(glue)
 library(cowplot)
+library(fs)
+
+ed1 <- read_csv("code/simulations/confidence_interval_perfect_assay/experimental_design.csv")
+ed2 <- read_csv("code/simulations/confidence_interval_perfect_assay/005_prev_experimental_design.csv")
+sum1 <- read_csv("code/simulations/confidence_interval_perfect_assay/combined_fixed_weights_many_summary.csv")
+sum2 <- read_csv("code/simulations/confidence_interval_perfect_assay/combined_fixed_weights_many_summary_005.csv")
+
 results_summary <-
-  read_csv("code/simulations/confidence_interval_perfect_assay/combined_fixed_weights_many_summary.csv") %>%
-  left_join(read_csv("code/simulations/confidence_interval_perfect_assay/experimental_design.csv") %>%
-              mutate(group_distribution = case_when( # Error because I labeled things wrong when setting up ex design
-                group_distribution == "low" ~ "high",
-                group_distribution == "high" ~ "low",
-                group_distribution == "uniform" ~ "uniform"
-              ))) %>%
+  left_join(sum1, ed1) %>%
+  mutate(group_distribution = case_when( # Error because I labeled things wrong when setting up ex design
+    group_distribution == "low" ~ "high",
+    group_distribution == "high" ~ "low",
+    group_distribution == "uniform" ~ "uniform"
+  )) %>%
+  bind_rows(left_join(sum2, ed2) %>%
+              mutate(design = design + max(ed1$design))) %>%
   pivot_longer(cols = c(lower_error_freq, upper_error_freq, coverage)) %>%
   mutate(name = fct_recode(name,
                            "Lower Error Frequency" = "lower_error_freq",
@@ -26,20 +34,21 @@ results_summary <-
            fct_relevel("high", "uniform", "low") %>%
            fct_relabel(str_to_title))
 
-name_to_plot <- "Coverage"
-n_groups_to_plot <- 8000
+rm(ed1, ed2, sum1, sum2)
 
-generate_plot <- function(name_to_plot, n_groups_to_plot){
+
+generate_plot <- function(name_to_plot, n_groups_to_plot, prev_to_plot){
   group_size <- if_else(n_groups_to_plot == 8000, 1, 200)
 
[…]

### 2021-08-27 code/simulations/confidence_interval_imperfect_assay/wip.R
Create wip.R

@@ -1,0 +1,130 @@
+library(tidyverse)
+library(furrr)
+source("code/WprevSeSp_SRS.R")
+n_partitions <- 500
+# Simulate Weights
+simulate_weights <- function(n_groups, coef_var) {
+  # mu <- 1 / n_groups
+  # sigma2 <- (coef_var / n_groups)^2
+  # alpha <- ((1 - mu) / sigma2 - 1 / mu) * mu^2
+  # beta <- alpha * (1 / mu - 1)
+
+  alpha <- 1 / coef_var^2 - 1 / (n_groups * coef_var^2) - 1 / n_groups
+  beta <- alpha * (n_groups - 1)
+
+  x <- rbeta(n_groups, alpha, beta)
+  if(sum(is.na(x))) return(NA)
+  x / sum(x)
+}
+
+set.seed(200)
+weight_candidates <-
+  crossing(n_groups = c(50, 8000),
+           # target_coef_var = c(0.1, 0.2, 0.3, 0.5, 1, 2, 3, 5, 10, 100, 1000)) %>%
+           target_coef_var = seq(0.01, 5, length.out = 500)) %>%
+  mutate(design = 1:n()) %>%
+  # slice(rep(1:n(), each = 100)) %>%
+  group_by(design) %>%
+  mutate(replication = row_number()) %>%
+  ungroup() %>%
+  mutate(weights = future_map2(.options = furrr_options(seed = 200),
+                               .x = n_groups,
+                               .y = target_coef_var,
+                               .f = ~simulate_weights(n_groups = .x, coef_var = .y)))
+cat("weights simulated\n")
+
+
+experimental_design <-
+  weight_candidates %>%
+  mutate(obs_coef_var = map_dbl(weights, ~(sd(.) / mean(.)))) %>%
+  mutate(coef_var_rel_error = abs(obs_coef_var - target_coef_var) / target_coef_var) %>%
+  group_by(design) %>%
+  filter(coef_var_rel_error == min(coef_var_rel_error)) %>%
+  select(design, n_groups, coef_var = obs_coef_var, weights) %>%
+  mutate(weights = map(weights, ~sort(., decreasing = T))) %>%
+  mutate(tests_per_group = case_when(
+    n_groups == 50 ~ 200,
+    n_groups == 8000 ~ 1
+  )) %>%
+  crossing(
+    n_tested_for_sensitivity = 60,
+    n_tested_for_specificity = 300,
[…]

### 2021-09-07 code/simulations/confidence_interval_imperfect_assay/combine_imperfect_assay_arrayjob.R
imperfect assay result

@@ -2,7 +2,7 @@ library(tidyverse)
 library(fs)
 
 
-tmp <-
+combined_imperfect_assay_summary <-
   tibble(file_path = dir_ls("//data/bayerdm/confidence_interval_imperfect_assay")) %>%
   mutate(file_name = file_path %>% path_file() %>% path_ext_remove()) %>%
   filter(str_detect(file_name, "summary")) %>%
@@ -11,4 +11,24 @@ tmp <-
   pull(data) %>%
   bind_rows()
 
-write_csv(tmp, "//data/bayerdm/fixed_weights_many/combined_fixed_weights_many_summary.csv")
+combined_imperfect_assay_summary
+
+write_csv(combined_imperfect_assay_summary, "~/PrevAdjSurvey/code/simulations/confidence_interval_imperfect_assay/combined_imperfect_assay_summary.csv")
+
+
+dir_ls("~/PrevAdjSurvey/code/simulations/confidence_interval_imperfect_assay") %>%
+  enframe(name = NULL) %>%
+  filter(str_starts(path_file(value), "slurm")) %>%
+  deframe() %>%
+  file_delete()
+combined_imperfect_assay_raw <-
+  tibble(file_path = dir_ls("//data/bayerdm/confidence_interval_imperfect_assay")) %>%
+  mutate(file_name = file_path %>% path_file() %>% path_ext_remove()) %>%
+  filter(str_detect(file_name, "raw")) %>%
+  arrange(file_name) %>%
+  mutate(data = map(file_path, read_rds)) %>%
+  pull(data) %>%
+  bind_rows()
+
+combined_imperfect_assay_raw %>% group_by(method, design) %>% summarize(max(conf_int_2))
+

### 2021-09-07 code/simulations/confidence_interval_imperfect_assay/imperfect_assay_arrayjob.R

@@ -20,7 +20,7 @@ dir_create(save_path)
 
 plan(multisession, workers = parallelly::availableCores())
 cat("using", parallelly::availableCores(), "cores\n")
-n_partitions <- 400
+n_partitions <- 550
 n_replications <- 10000
 cat("session planned\n")
 
@@ -75,7 +75,7 @@ experimental_design <-
     prev = c(0.005, 0.05),
     sensitivity = 0.95,
     specificity = seq(0.75, 1, by = 0.05),
-    prop_groups_with_prev = c(0.02, 0.05, 0.10, 0.25, 0.5, 0.75),
+    prop_groups_with_prev = c(0.75),
     group_distribution = c("high", "uniform", "low")) %>%
   mutate(n_groups_with_prev = round(prop_groups_with_prev * n_groups)) %>%
   filter(n_groups_with_prev > 0) %>%
@@ -133,7 +133,6 @@ calculate_interval_results <- function(weights,
   false_positive_counts <- known_negative_counts - true_negative_counts
 
   apparent_positive_counts <- true_positive_counts + false_positive_counts
-  apparent_positive_counts <- 0
   apparent_prevalence <- sum(apparent_positive_counts / tests_per_group * weights)
   var_hat_p_hat <- sum((weights / tests_per_group)^2 * apparent_positive_counts)
   stdErrPrev <- sqrt(var_hat_p_hat)
@@ -168,11 +167,7 @@ cat("starting results\n")
 set.seed(200)
 results <-
   experimental_design %>%
-  filter(specificity == max(specificity),
-         group_distribution == "high",
-         prop_groups_with_prev == 0.75,
-         n_groups == 50,
-         prev == 0.005) %>%
+  filter(partition == sjob) %>%
   slice(rep(1:n(), n_replications)) %>%
   group_by(design) %>%
   mutate(replication = row_number()) %>%

### 2021-09-07 code/simulations/confidence_interval_imperfect_assay/imperfect_assay_arrayjob.sh

@@ -1,11 +1,11 @@
 #!/bin/bash
 
-#SBATCH --partition=norm,quick
+#SBATCH --partition=norm
 #SBATCH --ntasks=1
 #SBATCH --ntasks-per-core=1
-#SBATCH --time=1:00:00
+#SBATCH --time=100:00:00
 #SBATCH --mem=4g
-#SBATCH --array=1-2
+#SBATCH --array=1-550
 #SBATCH --gres=lscratch:10
 #SBATCH --job-name="imperfect"
 

### 2021-09-07 code/simulations/confidence_interval_theta_star_fay_vs_LR/confidence_interval_theta_star_fay_vs_LR_simulations.R

@@ -4,7 +4,7 @@ library(asht)
 library(cowplot)
 library(fs)
 library(furrr)
-source("WprevSeSp_SRS.R")
+source("WWprevSeSp_SRS_SRS.R")
 
 plan(multisession, workers = 40)
 furrr_options(seed = 200)
@@ -52,7 +52,7 @@ results <-
                                         n_tested_for_sensitivity,
                                         est_specificity,
                                         n_tested_for_specificity)
-                            prevSeSp(AP = est_prevalence,
+                            WprevSeSp_SRS(AP = est_prevalence,
                                      nP = n_tested_for_prevalence,
                                      Se = est_sensitivity,
                                      nSe = n_tested_for_sensitivity,
@@ -71,7 +71,7 @@ results <-
                                          n_tested_for_sensitivity,
                                          est_specificity,
                                          n_tested_for_specificity)
-                             WprevSeSp_SRS(AP = est_prevalence,
+                             WWprevSeSp_SRS_SRS(AP = est_prevalence,
                                            nP = n_tested_for_prevalence,
                                            Se = est_sensitivity,
                                            nSe = n_tested_for_sensitivity,

### 2021-09-07 code/simulations/confidence_interval_imperfect_assay/combine_imperfect_assay_arrayjob.R
experimental design for part 3

@@ -15,6 +15,9 @@ combined_imperfect_assay_summary
 
 write_csv(combined_imperfect_assay_summary, "~/PrevAdjSurvey/code/simulations/confidence_interval_imperfect_assay/combined_imperfect_assay_summary.csv")
 
+experimental_design <-read_rds("//data/bayerdm/confidence_interval_imperfect_assay/experimental_design.rds")
+experimental_design %>% select_if(~!is.list(.)) %>% write_csv("~/PrevAdjSurvey/code/simulations/confidence_interval_imperfect_assay/experimental_design.csv")
+
 
 dir_ls("~/PrevAdjSurvey/code/simulations/confidence_interval_imperfect_assay") %>%
   enframe(name = NULL) %>%

### 2021-09-07 code/simulations/confidence_interval_imperfect_assay/process_imperfect_assay_arrayjob.R
Figures for part 3

@@ -1,0 +1,87 @@
+library(tidyverse)
+library(scales)
+library(glue)
+library(cowplot)
+library(fs)
+
+
+
+results_summary <-
+  read_csv("code/simulations/confidence_interval_imperfect_assay/combined_imperfect_assay_summary.csv") %>%
+  left_join(read_csv("code/simulations/confidence_interval_imperfect_assay/experimental_design.csv")) %>%
+  mutate(method = str_remove(method, "_result")) %>%
+  pivot_longer(cols = c(lower_error_freq, upper_error_freq, coverage)) %>%
+  mutate(name = fct_recode(name,
+                           "Lower Error Frequency" = "lower_error_freq",
+                           "Upper Error Frequency" = "upper_error_freq",
+                           "Coverage" = "coverage")) %>%
+  mutate(method = fct_recode(method,
+                             "WprevSeSp Binomial" = "WprevSeSp",
+                             "WprevSeSp Poisson" = "WprevSeSp_gamma")) %>%
+  mutate(group_distribution = group_distribution %>%
+           fct_relevel("high", "uniform", "low") %>%
+           fct_relabel(str_to_title))
+
+
+
+
+
+
+
+generate_plot_2 <- function(name_to_plot, n_groups_to_plot, prev_to_plot){
+  group_size <- if_else(n_groups_to_plot == 8000, 1, 200)
+
+  generated_plot <-
+    results_summary %>%
+    filter(n_groups == n_groups_to_plot,
+           name == name_to_plot,
+           prev == prev_to_plot,
+           specificity %in% c(0.8, 0.9, 1)) %>%
+    mutate(
+      tests = 10000,
+      successes = as.integer(value * tests),
+      failures = tests - successes) %>%
+    ggplot(aes(x = coef_var,
+               y = successes / tests,
+               color = method,
+               group = method,
+               # linetype = method,
+               successes = successes,
+               failures = failures)) +
+    facet_grid(group_distribution ~ specificity,
+               scales = "free_y",
+               labeller = labeller(
+                 specificity = function(x) str_c("Specificity\n", scales::percent(as.numeric(x), accuracy = 1)),
+                 group_distribution = function(x) str_c("Groups with Prev.\n", x, " Weights"))) +
+    geom_hline(yintercept = case_when(name_to_plot == "Coverage" ~ 0.95,
[…]

### 2021-09-07 code/simulations/confidence_interval_perfect_assay/process_weights_many.R

@@ -153,5 +153,5 @@ results_summary %>%
     ~generate_plot_2(name_to_plot = ..1,
                    n_groups_to_plot = ..2,
                    prev_to_plot = ..3))) %>%
-  mutate(file_name = path("figures", str_c(str_replace_all(str_to_lower(name), "\\s", "_"), n_groups, str_replace_all(prev, "\\.", "_"), "reduced", sep = "_"), ext = "pdf")) %>%
+  mutate(file_name = path("figures", str_c("perfect", str_replace_all(str_to_lower(name), "\\s", "_"), n_groups, str_replace_all(prev, "\\.", "_"), "reduced", sep = "_"), ext = "pdf")) %>%
   with(walk2(file_name, plot, ~save_plot(filename = .x, plot = .y, ncol = 3, nrow = 2, base_width = 3.5)))

### 2021-09-07 PrevAdjSurvey.tex
Updates from Overleaf

--- 2021-07-29 PrevAdjSurvey.tex
@@
-\documentclass{article}
+\documentclass[AMA,STIX1COL]{WileyNJD-v2}
+\usepackage{moreverb}
+% just for todo notes
+\setlength {\marginparwidth }{2cm}
+\usepackage[colorinlistoftodos]{todonotes}
 
-\topmargin -.5in
-\textheight 8.25in
-\oddsidemargin 0in
-\evensidemargin 0in
-\textwidth 6.5in
-\parindent 3em
+\newcommand\BibTeX{{\rmfamily B\kern-.05em \textsc{i\kern-.025em b}\kern-.08em
+T\kern-.1667em\lower.7ex\hbox{E}\kern-.125emX}}
 
-\usepackage{amsmath}
+\articletype{Article Type}%
 
-%% Please use the following statements for
-%% managing the text and math fonts for your papers:
-\usepackage{times}
-%\usepackage[cmbold]{mathtime}
-\usepackage{bm}
-\usepackage{natbib}
+\received{<day> <Month>, <year>}
+\revised{<day> <Month>, <year>}
+\accepted{<day> <Month>, <year>}
 
-%\usepackage{algorithm}
-%\usepackage{fancyhdr}
-\usepackage{graphics,color,pict2e}
-\usepackage{epsfig}
-%\usepackage{times}
-%\usepackage[cmbold]{mathtime}
-%\usepackage{bm}
-%\usepackage{rotating}
-%\usepackage{pdflscape}
-%\usepackage{longtable}
-\usepackage{booktabs}
-\usepackage{lscape}
-\usepackage{pdflscape}    
-%\usepackage{C:/R/R-2.11.1/share/texmf/Sweave}
-
-%\theoremstyle{plain}
-%\newtheorem{Theorem}{Theorem}[section]
-\newtheorem{theorem}{Theorem}
-\newtheorem{corrolary}{Corrolary}
-\newtheorem{result}{result}
-\newtheorem{Lemma}{Lemma}
-\newcommand{\toi}{t}
-\newcommand{\eqd}{\buildrel D \over =}
-\newcommand{\vect}{\bf }
-\newcommand{\sle}{\stackrel{st}{\le}}
-
-\newcommand{\ch}[2]{\ensuremath{ \left( \begin{array}{c} #1 \\ #2 \end{array} \right) }}
-\newcommand{\dfn}[2]{\ensuremath{ \left( #1 \right)_{(#2)}}}
+%\raggedbottom
 
@@
 
-{\bf \large Notes on: Prevalence Estimates from Surveys with Imperfect Assays}
+\title{A demonstration of the \LaTeX\ class file for Wiley NJD Journals\protect\thanks{This is an example for title footnote.}}
 
-\today
+\author[1,2]{Damon M. Bayer}
 
-%\begin{abstract}
-%asdf
-%\end{abstract}
+\author[2]{Michael P. Fay*}
 
-Damon,
+\author[3]{Barry I. Graubard}
 
-Here are some notes on the project. You can change the notation if you want. I am just putting down something so we can be clear about what we are doing.
+\authormark{D. M. BAYER, M.P. FAY and B. I. Graubard \textsc{et al}}
 
-\section{Overview}
+\address[1]{\orgdiv{Biostatistics Research Branch}, \orgname{National Institute of Allergy and Infectious Diseases}, \orgaddress{\state{Bethesda, Maryland}}}
 
-Quick overview.
-I described the problem in Section~\ref{sec-math}.
-The usual adjustment for sensitivity and specificity is described in Section~\ref{sec-usualAdj}.
-Then the three parts I spoke about.
-First, the confidence interval for a simple random sample is described in Section~\ref{sec-thetastar} (that is what you already did).
-Second, the confidence interval assuming a perfect assay in Section~\ref{sec-betaPerfect}.
-And finally, the
-confidence interval for an imperfect assay in Section~\ref{sec-betaImperfect}.
+\address[2]{\orgdiv{Department of Statistics}, \orgname{University of California, Irvine}, \orgaddress{\state{Irvine, California}, \country{Country name}}}
 
-\section{Mathematical Statement of Problem}
-\label{sec-math}
+\address[3]{\orgdiv{Division of Cancer Epidemiology and Genetics}, \orgname{National Cancer Institute}, \orgaddress{\state{Rockville, Maryland}}}
 
-Suppose we take a survey, that is divided into $k$ sampling units (e.g., states in the US).
-We take a simple random sample of individuals from each unit, perform and assay on each individual to determine who has a disease, and measure the number of individuals who have a positive value for the assay.
+\corres{*Michael P. Fay, Bethesda, MD 2089. \email{mfay@niaid.nih.gov}}
 
-Let $X_i$ be the number of positives by the assay, out of $n_i$ measured in sampling unit $i$.
-Suppose we had a perfect assay with 100\% sensitivity and 100\% specificity. Then let $X_i^*$ be the true number with the disease out of the $n_i$ sampled in unit $i$.
+\presentaddress{Present address}
 
-Let $X_i^* \sim Binomial(n_i, \theta_i^*)$ for $i=1,\ldots,k$.
-We are interested in the prevalence of disease in the population.
-Suppose there are $N_i$ individuals in the population of unit $i$.
-Then the prevalence of the population is
-\begin{eqnarray*}
-\beta & = & \frac{ \sum_{i=1}^{k} N_i \theta_i^* }{ \sum_{j=1}^{k} N_j }  =  \sum_{i=1}^{k} w_i \theta_i,
-\end{eqnarray*}
-where $w_i = N_i/N$ and $N=\sum_{j=1}^{k} N_j$.
+\abstract[Abstract]{This paper describes the use of the \LaTeXe\ \textsf{WileyNJD-v2.cls}
+class file for setting papers for \emph{Mathematical Methods in the Applied Sciences}.}
 
-Suppose we evaluate the assay.
-We measure the assay on $m_n$ individuals known not to have the disease (negative controls), and on $m_p$ individuals known to have the disease (positive controls).
-Let $C_n$ and $C_p$ be the number who tested positive out of the $m_n$ in the negative control and the $m_p$  in the positive control.
-Now make a convenience assumption:
-\begin{itemize}
-\item Assume that the negative and positive controls act like simple random samples from their populations (e.g., the $m_n$ negative controls are like a simple random sample from the total population of individuals without the disease).
-\end{itemize}
-Under that assumption, $C_n \sim Binomial(m_n, \phi_n)$ and $C_p \sim Binomial(m_p, \phi_p)$,
-where $1-\phi_n$ is the specificity (true negative rate of the assay),
-and $\phi_p$ (true positive rate of the assay) is the sensitivity.
+\keywords{Class file; \LaTeXe; \emph{Wiley NJD}}
 
-Here is the statistical problem.
-Assuming all of the above holds, and we observe realizations of $X_1,\ldots, X_k$ and $C_n$ and $C_p$, and the other values are known constants ($n_1,\ldots, n_k$, $w_1,\ldots, w_k$,  $m_n$, and $m_p$), what is a good estimate and confidence interval procedure for $\beta$.
+\jnlcitation{\cname{%
+\author{Williams K.}, 
+\author{B. Hoskins}, 
+\author{R. Lee}, 
+\author{G. Masato}, and 
+\author{T. Woollings}} (\cyear{2016}), 
+\ctitle{A regime analysis of Atlantic winter jet variability applied to evaluate HadGEM3-GC2}, \cjournal{Q.J.R. Meteorol. Soc.}, \cvol{2017;00:1--6}.}
 
-\section{Usual Adjustment for Sensitivity and Specificity}
-\label{sec-usualAdj}
+\maketitle
 
-To simplify the problem, suppose there is only one sampling unit, and let $X_1=X$ and $n_1=n$, etc. Then $\beta = \theta_1^*=\theta^*$.
-Further assume that $\phi_p$ and $\phi_n$ are known. Let $Y_1,\ldots,Y_n$ be the result of the assay from the $n$ individuals in the population
-($Y_i=1$ is positive and $Y_i=0$ is negative). Let $Y_1^*,\ldots,Y_n^*$ be the true disease status ($Y_i^*=1$ is diseased, and $Y_i^*=0$ is not diseased).
-Then using the definition of sensitivity and specificity, we get:
-\begin{eqnarray*}
-Pr[ Y_i =1 | Y_i^*=1] & = & \phi_p \\
-Pr[ Y_i=0 | Y_i^*=0] & = & 1- \phi_n
-\end{eqnarray*}
-and
-\begin{eqnarray*}
-Pr[ Y_i=1] & = & Pr[ Y_i =1 | Y_i^*=1]  Pr[Y_i^*=1] + Pr[ Y_i =1 | Y_i^*=0] Pr[ Y_i^*=0] \\
-& = & \phi_p \theta^* + \phi_n (1-\theta^*)  \\
-& = & \theta^* (\phi_p - \phi_n) + \phi_n.
-\end{eqnarray*}
-Let $\theta = Pr[ Y_i=1]$.
+\footnotetext{\textbf{Abbreviations:} ANA, anti-nuclear antibodies; APC, antigen-presenting cells; IRF, interferon regulatory factor}
 
-So we have
-\begin{eqnarray*}
-& & X \sim Binomial \left(n, \theta \right)  \\
-\mbox{ where} & \theta & = \theta^* \left\{ \phi_p - \phi_n \right\} + \phi_n.
-\end{eqnarray*}
-Thus,
-\begin{eqnarray}
-\theta^* & =  & \frac{ \theta - \phi_n }{ \phi_p - \phi_n}  = \frac{ \theta + (1 - \phi_n) -1  }{ \phi_p + (1 - \phi_n) -1 } \label{eq:thetastar}
-\end{eqnarray}
+\section{Introduction}
 
-Suppose we estimate the sensitivity as $\widehat{Se} = \hat{\phi}_p = C_p/m_p$ and the specificity as $\widehat{Sp} = 1-\hat{\phi}_n = 1- C_n/m_n$,
-and we define the apparent prevalence as the sample proportion of the positive assay results, $\hat{\theta} = x/n$.
-This gives the usual estimator for  prevalence adjusted for sensitivity and specificity
- \citep[see e.g.,][]{Roga:1978},
-\begin{eqnarray*}
-\hat{\theta}^* & = & \frac{ \hat{\theta} - \hat{\phi}_n }{\hat{\phi}_p - \hat{\phi}_n} = \frac{ \hat{\theta} + \widehat{Sp} -1 }{\widehat{Se} + \widehat{Sp} -1}.
-\end{eqnarray*}
+\section{Methods}
+\todo[inline]{I’m struggling a bit with the overall message of the paper.
 
-\section{Confidence Interval on $\theta^*$}
-\label{sec-thetastar}
+In Part 1, we advocate for the Kalish Appendix aka the Korn-Graubard + CD method over the Lang-Reiczigel method in the case of a simple random sample / unweighted survey.
+This is sort of a special case of the / Korn-Graubard + CD method with k = 1 and the binomial variance assumption, rather than the Poisson variance assumption.
 
-The simulation you (Damon) already did handles this problem. It answers: what is a good confidence interval for $\theta^*$?
-You compared the method of \citet{Lang:2014} to the new method described in the Supplement to \citet{Kali:2021}, using the method of \citet{FayP:2015}.
-It shows that the lower error has a better bound with the new method.
+In Part 2, we advocate for Fay-Feuer over Korn-Graubard in the case where
+ }
+Suppose we have a survey with  \( k \) sampling units, with \( N_1, N_2, \ldots, N_k \) individuals in the population of unit \( i \).
+We sample \( n_1, n_2, \ldots, n_k \) individuals via a simple random sample from each population to have an assay performed to determine who has a disease.
+Let \( \theta_i \) be the population frequency of positive results for assays performed on individuals from sampling unit \( i \) and \( X_i \) be the number of positive results from an assay performed on \( n_i \) individuals from sampling unit \( i \).
+Also let \( \theta_i^* \) be the population frequency of cases in sampling unit \( i \) and \( X_i^* \) be the true number of people with the disease among the \( n_i \) individuals from sampling unit \( i \).
+Then \( X_i^* \sim \operatorname{Binomial}(n_i, \theta_i^*) \)
+In the case of a perfect assay, \( \theta_i = \theta_i^* \) and \( X_i = X_i^* \).
 
-\section{Confidence Interval on $\beta$ with a Perfect Assay}
-\label{sec-betaPerfect}
+Therefore, the population prevalence is
 
-Suppose we have a perfect assay (i.e., $\phi_p=1$ and $\phi_n=0$). Then $\theta^* = \theta$, and $\beta = \sum_{i=1}^{k} w_i \theta$.
-The problem reduces to getting a confidence interval for a weighted average of the means of sample proportions.
-This problem is a standard survey sampling one. Some methods are \citet{Korn:1998}, see the review in \citet{Dean:2015}.
+\begin{equation}
+    \beta = \frac{\sum_{i=1}^k N_i \theta_i^*}{\sum_{j=1}^k N_j} = \sum_{i=1}^k w_i \theta_i^*,
+\end{equation}
 
-Another way to address this problem is to assume that $X_i \sim Poisson( n_i \theta_i)$ and use the methods
-of \citet{FayF:1997} or \citet{FayK:2017}.
-The notation is different in those papers. Here is the correspondence between the notations in these notes and in \citet{FayK:2017}.
+where \( w_i = N_i / N \).
 
-\begin{tabular}{cc}
-These Notes & Fay and Kim  \\ \hline
-$w_i$     & $s_i$ \\
-$\theta_i$ & $\lambda_i$ \
-\end{tabular}
+Suppose the assay is measured on \( m_n \) individuals known to not have the disease and on \( m_p \) individuals known to have have the disease.
+Let \( C_n \) and \( C_p \) be the number who test positive from the respective samples.
+Assume that the negative and positive controls act like simple random samples from their respective populations and that \( C_n \sim \operatorname{Binomial}(m_n, \phi_n) \) and \( C_p \sim \operatorname{Binomial}(m_p, \phi_p) \), where \( 1 - \phi_n \) is the specificity of the assay and \( \phi_p \) is the sensitivity of the assay.
 
-and $X_i$ and $n_i$ are the same in both papers.
+Let \( \hat{AP} = \frac{\sum_{i=1}^k N_i \frac{X_i}{n_i}}{\sum_{j=1}^k N_j} = \sum_{i=1}^k w_i \frac{X_i}{n_i} \), \( \widehat{Sp} = 1 - \frac{C_n}{m_n} \), and \( \widehat{Se} = \frac{C_p}{m_p} \).
 
-This should give a confidence interval for $\beta=\sum_{i=1}^{k} w_i \theta_i$
-that gives a lower and upper confidence distribution that is distributed gamma. (I will let you work out those details. Let me know if it is not easy.)
+The first method in this paper is concerned with estimating \( \beta \) in the case where \( k = 1 \), \( \phi_n > 0 \), \( \phi_p < 1 \), i.e.
+estimating prevalence from a simple random sample with an imperfect assay.
+The second method in this paper is concerned with estimating \( \beta \) in the case where \( k > 1 \), \( \phi_n = 0 \), \( \phi_p = 1 \), i.e.
+estimating prevalence from a weighted sample with a perfect assay.
+The final method in this paper is concerned with estimating \( \beta \) in the case where \( k > 1 \), \( \phi_n > 0 \), \( \phi_p < 1 \), i.e.
+estimating prevalence from a weighted sample with an imperfect assay.
 
-\subsection{Dirichlet Weights Simulation Results}
+\subsection{Estimating Prevalence from a Simple Random Sample with an Imperfect Assay}
 
-I present results for two scenarios:
+First, we consider the scenario \( k = 1 \), \( \phi_n > 0 \), \( \phi_p < 1 \) and we are concerned with estimating
 
-\begin{itemize}
-    \item The weight of each group is generated from a Dirichlet distribution with equal concentration parameters for all dimensions.
-The "Coefficient of Variation" in the figures referes to these weights.
-    \item The true positivity of each group is generated from a Beta distribution which achieves the specified mean and ICC.
-    \item Figure~\ref{fig:dws1}. Samples of 8,000 groups of 1. Population prevalence = 0.05\%/ Varying weight variance. Replicated 10,000 times.
-    \begin{itemize}
-        \item The two wsPoisson methods maintain appropriate or conservative coverage, regardless of the coefficient of variation among the weights.
-        \item The other two methods (Agresti-Coull and Clopper-Pearson) only begin to falter at unrealistic or unusual (according to Barry) coefficients of variation.
-        \item More typical coefficients of variation would be 20\%-40\%.
-    \end{itemize}
-    \item Figure~\ref{fig:dws2}. Samples of 200 groups of 50. Population prevalence = 0.05\%. Varying ICC. Varying weight variance. Replicated 10,000 times.
-    \begin{itemize}
-        \item Results here are a bit confusing.
-        \item I know that the results for Agresti-Coull and Clopper-Pearson could be improved with a better estimate for \(\hat{\text{var}}(\hat{p}) \).
-The simple estimate I was using appears to perform poorly in the case of high ICC.
-\textbf{I wonder if Barry can point me towards a good estimator for \(\hat{\text{var}}(\hat{p}) \) in the presence of high ICC.}
-        \item It is a bit strange that the wsPoisson methods perform better when there is extreme Coefficient of Variation, but it is consistent with the previously observed behavior of higher CoV leading to more conservative coverage.
-    \end{itemize}
-\end{itemize}
+\begin{equation}
+    \beta = \frac{\sum_{i=1}^k N_i \theta_i^*}{\sum_{j=1}^k N_j} = \theta_1^*
+\end{equation}
 
+We use the method is described in the Appendix of \cite{Kali:2021}.
+This is a modification of the melding method, which uses lower and upper confidence distributions on functions of estimators independent estimators to create a confidence interval for prevalence that accounts for variability in \( \widehat{AP} \), \( \widehat{Se} \), and \( \widehat{Sp} \) \cite{FayP:2015}.
+
+For each of \( \widehat{AP} \), \( \widehat{Se} \), and \( \widehat{Sp} \), we use the lower and upper confidence distributions associated with the exact binomial confidence interval.
+In the case of a binomial random variable with \( x \) successes among \( n \) trials, the lower confidence distribution is \( \operatorname{Beta}(x, n - x + 1) \), and the upper confidence distribution is \( \operatorname{Beta}(x + 1, n - x) \).
+
+Letting \( B_{ap}^L, B_{ap}^U, B_{sp}^L, B_{sp}^U, B_{se}^L, B_{se}^U \) be the lower and upper confidence distribtuions associate with the estimators, and \( q(a, W) \) be the \( a \)th quantile of a random variable \( W \), the 95\% confidence interval for \( \beta \) is
+
+\( \left\{ q \left( 0.025, \frac{B_{ap}^L + B_{sp}^L - 1}{B_{se}^U + B_{sp}^L - 1}  \right),  q \left( 0.975, \frac{B_{ap}^U + B_{sp}^U - 1}{B_{se}^L + B_{sp}^U - 1}  \right) \right\}.\)
+
+This method is compared to the method presented in \citet{Lang:2014}.
+
+\subsection{Estimating Prevalence from a Weighted Sample with a Perfect Assay}
+
+\subsection{Estimating Prevalence from a Weighted Sample with an  Imperfect Assay}
+
+\section{Results}
+\subsection{Estimating Prevalence from a Simple Random Sample with an Imperfect Assay}
+\subsection{Estimating Prevalence from a Weighted Sample with a Perfect Assay}
+\subsection{Estimating Prevalence from a Weighted Sample with an  Imperfect Assay}
+
+\section{Discussion}
+
+\section{Bibliography}
+\nocite{*}% Show all bib entries - both cited and uncited; comment this line to view only cited bib entries;
+\bibliography{refs}%
+
+\section{Introduction}\label{sec1}
+
+Many authors submitting \( \sin \cos \tan \inf_{x} \) to NJD journals use \LaTeXe\ to
+prepare their papers. This paper describes the
+\textsf{WileyNJD-v2.cls} class file which can be used to convert
+articles produced with other \LaTeXe\ class files into the correct
+form for publication in \emph{Wiley NJD Journals}.
+
+The \textsf{WileyNJD-v2.cls} class file preserves much of the standard
+\LaTeXe\ interface so that any document which was produced using
+the standard \LaTeXe\ \textsf{article} style can easily be
+converted to work with the \textsf{WileyNJD-v2} style. However, the
+width of text and typesize will vary from that of
+\textsf{article.cls}; therefore, \emph{line breaks will change}
+and it is likely that displayed mathematics and tabular material
+will need re-setting.
+
+In the following sections we describe how to lay out your code to
+use \textsf{WileyNJD-v2.cls} to reproduce the typographical look of
+\emph{Wiley NJD Journals}.
+
+\subsection{Procedure to install fonts (not required on Overleaf)}
+
+\begin{enumerate}
+\item All font files are available under the Stix-fonts folder in the zip download at \url{https://onlinelibrary.wiley.com/page/journal/10991476/homepage/latex_class_files.htm}
+\item Font installer is available under the same folder Windows-Stix-fontinstaller.exe
+\item Execute (double click the EXE file) the EXE file that will install all fonts/map files to your local drive.
+\end{enumerate}
+
+\subsection{The Three Golden Rules}
+
+Before we proceed, we would like to
+stress \emph{three golden rules} that need to be followed to
+enable the most efficient use of your code at the typesetting
+stage:
+\begin{enumerate}
+\item[(i)] keep your own macros to an absolute minimum;
+
+\item[(ii)] as \TeX\ is designed to make sensible spacing
+decisions by itself, do \emph{not} use explicit horizontal or
+vertical spacing commands, except in a few accepted (mostly
+mathematical) situations, such as \verb"\," before a
+differential~d, or \verb"\quad" to separate an equation from its
+qualifier;
+
+\item[(iii)] follow the \emph{NJD} reference style.
+\begin{enumerate}[a.]
+\item Chemistry --- Use the ``AMA'' option as \verb"\documentclass[AMA]{WileyNJD-v2.cls}"
+
+\end{enumerate}
+\end{enumerate}
+
+\section{Getting Started} The \textsf{WileyNJD-v2.cls} class file should run
+on any standard \LaTeXe\ installation. If any of the fonts, class
+files or packages it requires are missing from your installation,
+they can be found on the \emph{\TeX\ Live} CD-ROMs or from CTAN.
+
+LaTeX document class options
+
+\begin{flushleft}
+\begin{enumerate}[a.]
+\item STIX1COL--- For STIX font large one column layout use the ``STIX1COL'' option as \verb"\documentclass[AMA,STIX1COL]{WileyNJD-v2}"
+\item STIX2COL--- For STIX font large two column layout use the ``STIX2COL'' option as \verb"\documentclass[AMA,STIX2COL]{WileyNJD-v2}"
+\item STIXSMALL--- For STIX font small layout use the ``STIXSMALL'' option as \verb"\documentclass[AMA,STIXSMALL]{WileyNJD-v2}"
+\end{enumerate}
+\end{flushleft}
+
+\section{The Article Header Information}
+The heading for any file using \textsf{WileyNJD-v2.cls} is shown in
+Figure~\ref{F1}.
+
+\subsection{Remarks}
+
+\begin{enumerate}[(I).]
+
+\item Use \verb"\title{<title> \protect\thanks{<title footnotes}}" for article title and title footnote.
+\item Use \verb"\authormark{}" for running heads.
+
+\item Note the use of \verb"\author[<link>]{<name>}" and \verb"\address[<link>]{<name>}" to
+link names and addresses. The author for correspondence is marked
+by ``*'' and \verb"\corres{}" is used to give that
+author's address, which will be printed besides abstract, prefaced by
+`Correspondence to:'.
+
+\item For submitting a double-spaced manuscript, add
+\verb"doublespace" as an option to the documentclass line. \verb"\documentclass[doublespace]{WileyNJD-v2}"
+
+\item Use \verb"\presentaddress{}" for present address.
+
+\item In abstract \verb"\abstract[<title>]{abstract paragraph}" use optional parameter for title followed by abstract paragraph.
+
+\item For Key words use \verb"\keywords{}".
+
+\item For how to site use \verb"\jnlcitation{\cname{\author{<author name>},"
+
+\verb"\ctitle{<title>}, \cjournal{<Journal name>}, \cvol{<vol>}.}}".
+
+\item For title page abbreviations use \verb"\footnotetext{<\textbf{Abbreviation title:} Abreviations>}"
+
+\item Use \verb"\articletype{<article category}" for article header information
+
+\item Use \verb"\received{<received date>} \revised{<revised date>} \accepted{<accepted date>}" for history dates.
+
+\end{enumerate}
+
+\begin{figure}[p]
+\setlength{\fboxsep}{0pt}%
+\setlength{\fboxrule}{0pt}%
+\begin{center}
+\begin{boxedverbatim}
+
+\documentclass[AMA,STIX1COL]{WileyNJD-v2}
+
+\articletype{Article Type}%
+
+\received{26 April 2016}
+\revised{6 June 2016}
+\accepted{6 June 2016}
+
+\begin{document}
+
+\title{<Initial cap, lower case>\protect\thanks{<title footnote.>}}
+
+\author[<address link>]{<Author name><corresponding author*>}
+
+\author[<address link>,<address link>]{Author Name}
+
+\authormark{AUTHOR ONE \textsc{et al}}
+
+\address[<address link>]{\orgdiv{<Org Division>}, \orgname{<Org name>}, 
+\orgaddress{\state{<State name>}, \country{<Country name>}}}
+\address[<address link>]{\orgdiv{<Org Division>}, \orgname{<Org name>},
+ \orgaddress{\state{<State name>}, \country{<Country name>}}}
+
+\corres{<corresponding author link*> <author name, address.
+ \email{<authorone@email.com>}}
+
+\presentaddress{<Present address>}
+
+\abstract[<Abstract heading>]{<Abstract paragraph>}
+
+\keywords{<keyword1>, <keyword2>,...}
+
+\jnlcitation{\cname{%
+\author{<aurhor name>}, 
+\author{<aurhor name>}, 
+\author{<aurhor name>}, 
+\author{<aurhor name>},  and 
+\author{<aurhor name>}} (\cyear{<year>}), 
+\ctitle{<journal title>}, \cjournal{<journal name>} <year> <vol> Page <xxx>-<xxx>}
+
+\footnotetext{\textbf{<abbreviation head:>} <abbreviations> ..}
+
+\maketitle
+
+\section{Introduction}
+.
+.
+.
+\end{boxedverbatim}
+\end{center}
+\caption{Example for title page.\label{F1}}
+\end{figure}
+
+\section{The Body of the Article}
+
+\subsection{Section headings}
+
+\begin{enumerate}[(H1)]
+\item Section --- use \verb"\section{}"
+\item SubSection--- use \verb"\subsection{}"
+\item SubSubSectioin--- use \verb"\subsubsection{}"
+\item Paragraph--- use \verb"\paragraph{}"
+\item Subparagraph--- use \verb"\subparagraph{}"
+\end{enumerate}
+
+\subsection{Mathematics} \textsf{WileyNJD-v2.cls} makes the full
+functionality of \AmS\/\TeX\ available. We encourage the use of
+the \verb"align", \verb"gather" and \verb"multline" environments
+for displayed mathematics.
+
+\subsection{Figures and Tables}
+
+\textsf{WileyNJD-v2.cls} uses the
+\textsf{graphicx} package for handling figures.
+
+Figures are called in as follows:
+\begin{verbatim}
 \begin{figure}
 \centering
-    \includegraphics[width=\textwidth]{figures/results_plot_8000_1.pdf}
-    \caption{Dirichlet Weights Scenario 1}
-    \label{fig:dws1}
+\includegraphics{<figure name>}
+\caption{<Figure caption>}
+\end{figure}
+\end{verbatim}
+
+The standard coding for a table is shown in Figure~\ref{F2}.
+
+\begin{figure}[h]
+\setlength{\fboxsep}{0pt}%
+\setlength{\fboxrule}{0pt}%
+\begin{center}
+\begin{boxedverbatim}
+\begin{table}
+\caption{<Table caption>}
+\centering
+\begin{tabular}{<table alignment>}
+\toprule
+<column headings>\\
+\midrule
+<table entries
+(separated by & as usual)>\\
+<table entries>\\
+.
+.
+.\\
+\bottomrule
+\end{tabular}
+\begin{tablenotes}
+\item Source: xxx.
+\item[1] xxx.
+\item[2] xxx.
+\end{tablenotes}
+\end{table}
+\end{boxedverbatim}
+\end{center}
+\caption{Example for table layout.\label{F2}}
 \end{figure}
 
-\pagebreak
-\begin{landscape}
-\begin{figure}
-    \centering
-    \includegraphics[width = \paperwidth]{figures/results_plot_200_50.pdf}
-    \caption{Dirichlet Weights Scenario 2}
-    \label{fig:dws2}
-\end{figure}
-\end{landscape}
-\pagebreak
+\subsection{Cross-referencing}
+The use of the \LaTeX\ cross-reference system
+for figures, tables, equations, etc., is encouraged
+(using \verb"\ref{<name>}" and \verb"\label{<name>}").
 
-As you predicted, the usual methods (Agresti-Coull and Clopper-Pearson) exhibit poor performance when there is high variance among the weights.
+\subsection{Box text}
 
-Dean and Pagano recommend an adjustment suggested by Korn and Graubard that I wasn’t sure how to apply in the context of my simulation, so it’s possible that this is a pessimistic assessment of those methods.
+\begin{verbatim}
+\begin{boxtext}
+\section*{<title>}%
+Paragraph
+\end{boxtext}
+\end{verbatim}
 
-Let’s chat about these results and next steps early next week.
+\subsection{List items}
 
-Thanks,
+\subsubsection{Enumerate list styles}
+\begin{verbatim}
+\begin{enumerate}[1]
+\item 
+\end{enumerate}
 
-Damon
+\begin{enumerate}[1.]
+\item 
+\end{enumerate}
 
-\subsection{Weird U.S. State Simulation Results}
+\begin{enumerate}[(1)]
+\item 
+\end{enumerate}
 
-For this section I have applied 4 methods to 2 populations, with 10,0000 replications each.
+\begin{enumerate}[I]
+\item 
+\end{enumerate}
 
-\noindent Methods:
+\begin{enumerate}[i]
+\item 
+\end{enumerate}
+
+\begin{enumerate}[a]
+\item 
+\end{enumerate}
+
+\end{verbatim}
+
+\subsubsection{Bullet list styles}
+
+\begin{verbatim}
 \begin{itemize}
-    \item AC \& AC\_adj: The Agresti-Coull and Agresti-Coull adjusted methods for survey samples described in \cite{Dean:2015}. Implemented by hand.
-    \item wspoissonTest \& wspoissonTest\_midp: the methods described in \cite{FayF:1997} and \cite{FayK:2017}. Implemented in \cite{asht}.
+\item 
 \end{itemize}
+\end{verbatim}
 
-In each scenario, I use the 2020 census population counts for all states \& DC and specify the exact number of cases in each state's population to achieve an overall prevalence $\approx$  0.5\%.
-Per \cite{Lemeshow1985SurveysTM}, I implement a 2-stage sampling algorithm, where $m$ states are sampled with replacement and $\tilde{n}$ people are sampled from each of the $m$ states.
-In the results here, $m = 12,000$ and $\tilde{n} = 1$, equivalent to a simple random sample from the country.
-Alternative schemes like $m = 120$ and $\tilde{n} = 100$ seem to produce worse results for the wspoissonTest methods, but I have not investigated this fully.\\
-The differences between the two scenarios are presented below.\\
+\subsubsection{Description list}
 
-\noindent Scenarios:
-\begin{itemize}
-    \item one\_state: Montana has 30\% prevalence, while all other states have no cases.
-    \item two\_state: California and New York each have 3\% prevalence, while all other states have no cases.
-    \item few\_state: California, Texas, Florida, and New York each have 1.5\% prevalence, while all other states have no cases.
-    \item many\_state: all states have $\approx$ 0.5\% prevalence, but with some clustering of cases
-\end{itemize}
+\begin{verbatim}
+\begin{description}
+\item[<entry>] description text.
+\end{description}
+\end{verbatim}
 
-\noindent Results:
-\begin{table}
-\centering
-\begin{tabular}{llrrr}
-\toprule
-scenario & method & coverage & lower\_error\_freq & upper\_error\_freq\\
-\midrule
-one\_state & AC & 0.9660 & 0.0232 & 0.0108\\
-one\_state & AC\_adj & 0.9660 & 0.0232 & 0.0108\\
-one\_state & wspoissonTest & 0.9928 & 0.0039 & 0.0033\\
-one\_state & wspoissonTest\_midp & 0.9852 & 0.0083 & 0.0065\\
-\addlinespace
-two\_state & AC & 0.9484 & 0.0256 & 0.0260\\
-two\_state & AC\_adj & 0.9484 & 0.0256 & 0.0260\\
-two\_state & wspoissonTest & 0.9632 & 0.0193 & 0.0175\\
-two\_state & wspoissonTest\_midp & 0.9538 & 0.0235 & 0.0227\\
-\addlinespace
-few\_state & AC & 0.9570 & 0.0259 & 0.0171\\
-few\_state & AC\_adj & 0.9570 & 0.0259 & 0.0171\\
-few\_state & wspoissonTest & 0.9629 & 0.0216 & 0.0155\\
-few\_state & wspoissonTest\_midp & 0.9559 & 0.0250 & 0.0191\\
-\addlinespace
-many\_state & AC & 0.9515 & 0.0287 & 0.0198\\
-many\_state & AC\_adj & 0.9515 & 0.0287 & 0.0198\\
-many\_state & wspoissonTest & 0.9597 & 0.0246 & 0.0157\\
-many\_state & wspoissonTest\_midp & 0.9517 & 0.0281 & 0.0202\\
-\bottomrule
-\end{tabular}
-\end{table}
+\subsection{Enunciations}
 
-I have not found any scenarios that ``break" the AC methods, which appear to be on par with the wspoissonTest\_midp methods.
-There is no obvious pattern in coverage vs number of states with cases, other than that the wspoissonTest appears to do better with more evenly spread cases and both wspoissonTest methods do poorly in the one\_state scenario.
+\begin{verbatim}
+\begin{theorem}[<Theorem subhead>]\label{thm1}
+<theorem text>. 
+\end{theorem}
 
-\section{Confidence Interval on $\beta$ with an Imperfect Assay}
-\label{sec-betaImperfect}
+\begin{proposition}[<proposition subhead>]\label{pro1}
+<proposition text>. 
+\end{proposition}
 
-\subsection{Preliminaries}
+\begin{definition}[<definition subhead>]\label{dfn1}
+<definition text>. 
+\end{definition}
 
-This is the final problem (described in Section~\ref{sec-math} that combines the two other problems.
+\begin{proof}
+<proof text>. 
+\end{proof}
 
-We have
-\begin{eqnarray*}
-\beta & = & \sum_{i=1}^{k} w_i \theta_i^*  \\
-& = &  \sum_{i=1}^{k} w_i  \frac{ \theta_i - \phi_n }{ \phi_p - \phi_n} \\
-& = &   \frac{ \sum_{i=1}^{k} w_i  \theta_i  }{ \phi_p - \phi_n} - \frac{ \phi_n \sum_{i=1}^{k} w_i    }{ \phi_p - \phi_n} \\
-& = &   \frac{ \sum_{i=1}^{k} w_i  \theta_i  }{ \phi_p - \phi_n} - \frac{ \phi_n     }{ \phi_p - \phi_n},
-\end{eqnarray*}
-where the last step is because the weights are assumed to sum to 1.
+\begin{proof}[Proof of Theorem~\ref{thm1}]
+<proof text>.
+\end{proof}
 
-We can use
-\begin{eqnarray*}
-\hat{\beta} & = &   \frac{ \sum_{i=1}^{k} w_i  \hat{\theta}_i  }{ \hat{\phi}_p - \hat{\phi}_n} - \frac{ \hat{\phi}_n   }{ \hat{\phi}_p - \hat{\phi}_n} 
-\end{eqnarray*}
-as our estimator of $\beta$.
+\end{verbatim}
 
-\subsection{Confidence Distribution Approach}
+\subsection{Program codes}
 
-Then we can use the melding method of \citet{FayP:2015} to combine the confidence distributions for $\beta_a = \sum_{i=1}^{k} w_i  {\theta}_i$, for $\phi_p$,
-and for $\phi_n$. That might not be straightforward, since I am not sure if $\phi_n$ and $\phi_p$ are monotonic in $\beta$. You need to check that out.
+Use \verb+\begin{verbatim}...\end{verbatim}+ for program codes without math.
+Use \verb+\begin{alltt}...\end{alltt}+ for program codes with math.
+Based on the text provided inside the optional argument of \verb+\begin{code}[Psecode|Listing|Box|Code|+\hfill\break \verb+Specification|Procedure|Sourcecode|Program]...+ \verb+\end{code}+ tag corresponding boxed like floats are generated.
+Also note that \verb+\begin{code}[Code|Listing]...+ \verb+\end{code}+ tag with either Code or Listing text as optional argument text are set with computer modern typewriter font.
+All other code environments are set with normal text font.
+Refer below example:
 
-\subsection{Korn-Graubard+CD Approach}
+\begin{verbatim}
+\begin{lstlisting}[caption={Descriptive Caption Text},label=DescriptiveLabel]
+for i:=maxint to 0 do
+begin
+{ do nothing }
+end;
+Write('Case insensitive ');
+WritE('Pascal keywords.');
+\end{lstlisting}
+\end{verbatim}
 
-This is the method described in the supplement of \citet{Kali:2021}.
-Basically, we use the method of Korn and Graubard to get confidence distributions for ${\beta}_a = \sum_{i=1}^{k} w_i \theta_i$ (the apparent prevalence, assuming perfect sensitivity and specificity).
-Let $\hat{\beta}_a= \sum_{i=1}^{k} w_i X_i$. Under the Poisson assumption, we estimate the variance 
-of $\hat{\beta}_a$ with $\widehat{Var}(\hat{\beta}_a) = \sum_{i=1}^{k} w_i^2 X_i$.
-Then Korn-Graubard define the effective sample size by setting the $\widehat{Var}(\hat{\beta}_a)$ to the binomial variance estimate,
-\begin{eqnarray*}
-\widehat{Var}(\hat{\beta}_a) \stackrel{set}{=} \frac{\hat{\beta}_a (1-\hat{\beta}_a)}{n_e}
-\end{eqnarray*}
-So we get 
-\begin{eqnarray*}
-n_e =   \frac{\hat{\beta}_a (1-\hat{\beta}_a)}{\widehat{Var}(\hat{\beta}_a)}
-\end{eqnarray*}
-Then the effective count is $x_e = n_e \hat{\beta}_a$, and the lower and upper confidence distributions for ${\beta}_a$ under the Korn-Graubard method are Beta$(x_e, n_e-x_e+1)$ and Beta$(x_e+1,n_e-x_e)$, respectively.
-Then those confidence distributions are used in place of the confidence distributions for $\beta_a$ in the previous subsection.
+\subsection{Acknowledgements} An Acknowledgements section is started with \verb"\ack" or
+\verb"\acks" for \textit{Acknowledgement} or
+\textit{Acknowledgements}, respectively. It must be placed just
+before the References.
 
-%\bibliographystyle{agsm}
-\bibliographystyle{biom}
+\subsection{Bibliography}
+% \nocite{*}% Show all bib entries - both cited and uncited; comment this line to view only cited bib entries;
+% \bibliography{WileyNJD-AMA}%
+\begin{enumerate}[1]
+\item Use \verb"\bibliography{wileyNJD-AMA}" BST file for AMA reference style
+\item Use \verb"\bibliography{wileyNJD-APA}" BST file for APA reference style
+\item Use \verb"\bibliography{wileyNJD-AMS}" BST file for AMS reference style
+\item Use \verb"\bibliography{wileyNJD-VANCOUVER}" BST file for Vancouver reference style
+\item Use \verb"\bibliography{wileyNJD-ACS}" BST file for Chemistry reference style
+\end{enumerate}
 
-\bibliography{refs}
+The normal commands for producing the reference list are:
+
+\begin{verbatim}
+\begin{thebibliography}{99}
+\bibitem{<x-ref label>}
+         <Reference details>
+.
+.
+.
+\end{thebibliography}
+\end{verbatim}
+
+\subsection{Appendix Section}
+
+\begin{verbatim}
+\appendix
+
+\section{Section title of first appendix\label{app1}}
+.
+.
+.
+
+\end{verbatim}
 

### 2021-09-07 notes.tex

@@
 Then using the definition of sensitivity and specificity, we get:
-\begin{eqnarray*}
+\begin{eqnarray*}Hi M
 Pr[ Y_i =1 | Y_i^*=1] & = & \phi_p \\
@@
 
-\begin{landscape}
-\includepdf[angle=90]{coverage_50}
-\end{landscape}
+% \begin{landscape}
+% \includepdf[angle=90]{coverage_50_0_005}
+% \includepdf[angle=90]{coverage_8000_0_005}
+% \includepdf[angle=90]{coverage_50_0_05}
+% \includepdf[angle=90]{coverage_8000_0_05}
 
-\begin{landscape}
-\includepdf[angle=90]{coverage_8000}
-\end{landscape}
+% \includepdf[angle=90]{upper_error_frequency_50_0_005}
+% \includepdf[angle=90]{upper_error_frequency_8000_0_005}
+% \includepdf[angle=90]{upper_error_frequency_50_0_05}
+% \includepdf[angle=90]{upper_error_frequency_8000_0_05}
 
-\begin{landscape}
-\includepdf[angle=90]{upper_error_frequency_50}
-\end{landscape}
+% \includepdf[angle=90]{lower_error_frequency_50_0_005}
+% \includepdf[angle=90]{lower_error_frequency_8000_0_005}
+% \includepdf[angle=90]{lower_error_frequency_50_0_05}
+% \includepdf[angle=90]{lower_error_frequency_8000_0_05}
+% \end{landscape}
 
-\begin{landscape}
-\includepdf[angle=90]{upper_error_frequency_8000}
-\end{landscape}
+% \begin{landscape}
+% \includepdf[angle=90]{coverage_8000}
+% \end{landscape}
 
-\begin{landscape}
-\includepdf[angle=90]{lower_error_frequency_50}
-\end{landscape}
+% \begin{landscape}
+% \includepdf[angle=90]{upper_error_frequency_50}
+% \end{landscape}
 
-\begin{landscape}
-\includepdf[angle=90]{lower_error_frequency_8000}
-\end{landscape}
+% \begin{landscape}
+% \includepdf[angle=90]{upper_error_frequency_8000}
+% \end{landscape}
+
+% \begin{landscape}
+% \includepdf[angle=90]{lower_error_frequency_50}
+% \end{landscape}
+
+% \begin{landscape}
+% \includepdf[angle=90]{lower_error_frequency_8000}
+% \end{landscape}
 
@@
 
+\subsubsection{Damon's Response to 6.3}
+
+First, some notation corrections / clarifications:
+
+Because ${\beta}_a = \sum_{i=1}^{k} w_i \theta_i$, we should let $\hat{\beta}_a= \sum_{i=1}^{k} w_i \frac{X_i}{n_i}$.
+
+Because \( X_i \sim Binomial(n_i, \theta_i )\), we have:
+
+\begin{align*}
+	        &   \Var \left( \hat{\beta}_a \right)   =  \Var \left( \sum_{i=1}^k w_i \frac{X_i}{n_i}\right)\\
+	\implies&   \Var \left( \hat{\beta}_a \right)   =  \sum_{i=1}^k \left( \frac{w_i}{n_i} \right)^2 \Var X_i \\
+	\implies&   \Var \left( \hat{\beta}_a \right)   =  \sum_{i=1}^k \left( \frac{w_i}{n_i} \right)^2 n_i \theta_i (1 - \theta_i) \\
+	\implies&   \widehat{\Var} \left( \hat{\beta}_a \right)   =  \sum_{i=1}^k \left( \frac{w_i}{n_i} \right)^2 n_i \hat{\theta}_i (1 - \hat{\theta}_i) \\
+	\implies&   \widehat{\Var} \left( \hat{\beta}_a \right)   =  \sum_{i=1}^k \left( \frac{w_i}{n_i} \right)^2 n_i \left( \frac{X_i}{n_i} \right) \left(1 - \frac{X_i}{n_i}\right) \\
+\implies&   \widehat{\Var} \left( \hat{\beta}_a \right)   =  \sum_{i=1}^k \frac{w_i^2 \cdot X_i \cdot(1 - X_i) }{n_i^3}
+\end{align*}
+
+In some simulations where \( n_i = 200 \) and \( k = 50 \), we achieve a relative error comparing the estimator to empirical variance < 1\%.
+A problem with this estimator is that when \( n_i = 1 \forall i\), \( X_i \in \{0, 1 \} \forall i \). Therefore, the estimated variance is always exactly 0.
+
+\pagebreak
+
+If we instead assume \( X_i \sim Poisson(n_i \theta_i) \), we have:
+
+\begin{align*}
+	        &   \Var \left( \hat{\beta}_a \right)   =  \Var \left( \sum_{i=1}^k w_i \frac{X_i}{n_i}\right)\\
+	\implies&   \Var \left( \hat{\beta}_a \right)   =  \sum_{i=1}^k \left( \frac{w_i}{n_i} \right)^2 \Var X_i \\
+	\implies&   \Var \left( \hat{\beta}_a \right)   =  \sum_{i=1}^k \left( \frac{w_i}{n_i} \right)^2 n_i \theta_i \\
+	\implies&   \widehat{\Var} \left( \hat{\beta}_a \right)   =  \sum_{i=1}^k \left( \frac{w_i}{n_i} \right)^2 n_i \hat{\theta}_i \\
+	\implies&   \widehat{\Var} \left( \hat{\beta}_a \right)   =  \sum_{i=1}^k \left( \frac{w_i}{n_i} \right)^2 n_i \frac{X_i}{n_i} \\
+	\implies&   \widehat{\Var} \left( \hat{\beta}_a \right)   =  \sum_{i=1}^k \left( \frac{w_i}{n_i} \right)^2 X_i
+\end{align*}
+
+I think this is what Mike was trying to arrive at in section 6.3.
+
+Of course, \(X_i \) is not a Poisson random variable, so this estimator is also problematic.
+In some simulations where \( n_i = 200 \) and \( k = 50 \) and other simulations where \( n_i = 1 \) and \( k = 8000 \), we achieve a relative error comparing the estimator to empirical variance \( \approx \) 30\%.
+
+Thus, an alternative for  \( \widehat{\Var} \left( \hat{\beta}_a \right) \) seems like an obvious way to improve the overall estimator.
+
+One quick idea is to use \( \frac{X_i + 1}{n_i + 2} \) for \( \hat{\theta} \) instead of \( \frac{X_i}{n_i} \) when using the Binomial assumption.
+In simulation, this estimator performs much better than the Poisson assumption when \( n_i = 200 \), and a bit worse than the Poisson assumption when \( n_i = 1 \).
+Additionally, this estimator performs  much better than the Binomial assumption when \( n_i = 1 \), and a bit worse than the Poisson assumption when \( n_i = 200 \).
+
+I'm sure Mike has additional thoughts on this.
+
 %\bibliographystyle{agsm}

### 2021-09-07 PrevAdjSurvey.tex

@@
 \subsection{Estimating Prevalence from a Weighted Sample with a Perfect Assay}
+
+\begin{figure}
+    \centering
+    \includegraphics[width=\textwidth]{figures/perfect_coverage_50_0_005_reduced.pdf}
+    \caption{Caption}
+    \label{fig:perfect_coverage_50_0_005_reduced}
+\end{figure}
+
+\begin{figure}
+    \centering
+    \includegraphics[width=\textwidth]{figures/perfect_coverage_50_0_05_reduced.pdf}
+    \caption{Caption}
+    \label{fig:perfect_coverage_50_0_05_reduced}
+\end{figure}
+
+\begin{figure}
+    \centering
+    \includegraphics[width=\textwidth]{figures/perfect_coverage_8000_0_005_reduced.pdf}
+    \caption{Caption}
+    \label{fig:perfect_coverage_8000_0_005_reduced}
+\end{figure}
+
+\begin{figure}
+    \centering
+    \includegraphics[width=\textwidth]{figures/perfect_coverage_8000_0_05_reduced.pdf}
+    \caption{Caption}
+    \label{fig:perfect_coverage_8000_0_05_reduced.pdf}
+\end{figure}
+
+\begin{figure}
+    \centering
+    \includegraphics[width=\textwidth]{figures/perfect_lower_error_frequency_50_0_005_reduced.pdf}
+    \caption{Caption}
+    \label{fig:perfect_lower_error_frequency_50_0_005_reduced}
+\end{figure}
+
+\begin{figure}
+    \centering
+    \includegraphics[width=\textwidth]{figures/perfect_lower_error_frequency_50_0_05_reduced.pdf}
+    \caption{Caption}
+    \label{fig:perfect_lower_error_frequency_50_0_05_reduced}
+\end{figure}
+
+\begin{figure}
+    \centering
+    \includegraphics[width=\textwidth]{figures/perfect_lower_error_frequency_8000_0_005_reduced.pdf}
+    \caption{Caption}
+    \label{fig:perfect_lower_error_frequency_8000_0_005_reduced}
+\end{figure}
+
+\begin{figure}
+    \centering
+    \includegraphics[width=\textwidth]{figures/perfect_lower_error_frequency_8000_0_05_reduced.pdf}
+    \caption{Caption}
+    \label{fig:perfect_lower_error_frequency_8000_0_05_reduced.pdf}
+\end{figure}
+
+\begin{figure}
+    \centering
+    \includegraphics[width=\textwidth]{figures/perfect_upper_error_frequency_50_0_005_reduced.pdf}
+    \caption{Caption}
+    \label{fig:perfect_upper_error_frequency_50_0_005_reduced}
+\end{figure}
+
+\begin{figure}
+    \centering
+    \includegraphics[width=\textwidth]{figures/perfect_upper_error_frequency_50_0_05_reduced.pdf}
+    \caption{Caption}
+    \label{fig:perfect_upper_error_frequency_50_0_05_reduced}
+\end{figure}
+
+\begin{figure}
+    \centering
+    \includegraphics[width=\textwidth]{figures/perfect_upper_error_frequency_8000_0_005_reduced.pdf}
+    \caption{Caption}
+    \label{fig:perfect_upper_error_frequency_8000_0_005_reduced}
+\end{figure}
+
+\begin{figure}
+    \centering
+    \includegraphics[width=\textwidth]{figures/perfect_upper_error_frequency_8000_0_05_reduced.pdf}
+    \caption{Caption}
+    \label{fig:perfect_upper_error_frequency_8000_0_05_reduced.pdf}
+\end{figure}
+
 \subsection{Estimating Prevalence from a Weighted Sample with an  Imperfect Assay}
+
+\begin{figure}
+    \centering
+    \includegraphics[width=\textwidth]{figures/imperfect_coverage_50_0_005_reduced.pdf}
+    \caption{Caption}
+    \label{fig:imperfect_coverage_50_0_005_reduced}
+\end{figure}
+
+\begin{figure}
+    \centering
+    \includegraphics[width=\textwidth]{figures/imperfect_coverage_50_0_05_reduced.pdf}
+    \caption{Caption}
+    \label{fig:imperfect_coverage_50_0_05_reduced}
+\end{figure}
+
+\begin{figure}
+    \centering
+    \includegraphics[width=\textwidth]{figures/imperfect_coverage_8000_0_005_reduced.pdf}
+    \caption{Caption}
+    \label{fig:imperfect_coverage_8000_0_005_reduced}
+\end{figure}
+
+\begin{figure}
+    \centering
+    \includegraphics[width=\textwidth]{figures/imperfect_coverage_8000_0_05_reduced.pdf}
+    \caption{Caption}
+    \label{fig:imperfect_coverage_8000_0_05_reduced.pdf}
+\end{figure}
+
+\begin{figure}
+    \centering
+    \includegraphics[width=\textwidth]{figures/imperfect_lower_error_frequency_50_0_005_reduced.pdf}
+    \caption{Caption}
+    \label{fig:imperfect_lower_error_frequency_50_0_005_reduced}
+\end{figure}
+
+\begin{figure}
+    \centering
+    \includegraphics[width=\textwidth]{figures/imperfect_lower_error_frequency_50_0_05_reduced.pdf}
+    \caption{Caption}
+    \label{fig:imperfect_lower_error_frequency_50_0_05_reduced}
+\end{figure}
+
+\begin{figure}
+    \centering
+    \includegraphics[width=\textwidth]{figures/imperfect_lower_error_frequency_8000_0_005_reduced.pdf}
+    \caption{Caption}
+    \label{fig:imperfect_lower_error_frequency_8000_0_005_reduced}
+\end{figure}
+
+\begin{figure}
+    \centering
+    \includegraphics[width=\textwidth]{figures/imperfect_lower_error_frequency_8000_0_05_reduced.pdf}
+    \caption{Caption}
+    \label{fig:imperfect_lower_error_frequency_8000_0_05_reduced.pdf}
+\end{figure}
+
+\begin{figure}
+    \centering
+    \includegraphics[width=\textwidth]{figures/imperfect_upper_error_frequency_50_0_005_reduced.pdf}
+    \caption{Caption}
+    \label{fig:imperfect_upper_error_frequency_50_0_005_reduced}
+\end{figure}
+
+\begin{figure}
+    \centering
+    \includegraphics[width=\textwidth]{figures/imperfect_upper_error_frequency_50_0_05_reduced.pdf}
+    \caption{Caption}
+    \label{fig:imperfect_upper_error_frequency_50_0_05_reduced}
+\end{figure}
+
+\begin{figure}
+    \centering
+    \includegraphics[width=\textwidth]{figures/imperfect_upper_error_frequency_8000_0_005_reduced.pdf}
+    \caption{Caption}
+    \label{fig:imperfect_upper_error_frequency_8000_0_005_reduced}
+\end{figure}
+
+\begin{figure}
+    \centering
+    \includegraphics[width=\textwidth]{figures/imperfect_upper_error_frequency_8000_0_05_reduced.pdf}
+    \caption{Caption}
+    \label{fig:imperfect_upper_error_frequency_8000_0_05_reduced.pdf}
+\end{figure}
 

### 2021-09-08 data/create_kalish_data.R
Kalish Data Ignore

@@ -1,0 +1,11 @@
+library(tidyverse)
+library(fs)
+
+load("C:/Users/bayerdm/Downloads/dataForDamon.RData")
+
+dir_create("data")
+data.for.Damon %>%
+  as_tibble() %>%
+  mutate(y = as.integer(y),
+         hispanic = hispanic == "Yes") %>%
+  write_csv("data/kalish_data.csv")

### 2021-09-14 data/create_kalish_data.R
kalish code

@@ -1,11 +1,131 @@
 library(tidyverse)
 library(fs)
-
+source("code/simulations/confidence_interval_imperfect_assay/WprevSeSp_SRS.R")
 load("C:/Users/bayerdm/Downloads/dataForDamon.RData")
 
-dir_create("data")
-data.for.Damon %>%
+kalish_data <-
+  data.for.Damon %>%
   as_tibble() %>%
   mutate(y = as.integer(y),
-         hispanic = hispanic == "Yes") %>%
-  write_csv("data/kalish_data.csv")
+         hispanic = hispanic == "Yes")
+
+dir_create("data")
+write_csv(kalish_data, "data/kalish_data.csv")
+
+n_groups <- nrow(kalish_data)
+tests_per_group <- 1
+
+n_tested_for_prevalence <- n_groups * tests_per_group
+
+n_tested_for_specificity <- 300
+n_tested_for_sensitivity <- 56
+# https://github.com/niaid/SARSCoV2-US-serosurvey-2020/blob/09ef4d285e2519e0501c9f80d4f9251595e97305/Figure3_Figure4/R/ForestPlots.R
+est_specificity <- 1
+est_sensitivity <- 1
+
+
+# Full Data ---------------------------------------------------------------
+apparent_positive_counts <- kalish_data$y
+weights <- kalish_data$w
+apparent_prevalence <- sum(apparent_positive_counts / tests_per_group * weights)
+var_hat_p_hat <- sum((weights / tests_per_group)^2 * apparent_positive_counts)
+stdErrPrev <- sqrt(var_hat_p_hat)
+coef_var <- sd(weights) / mean(weights)
+dput(coef_var)
+2.52363306559155
+adjusted_prevalence <- prevAdj(AP = apparent_prevalence,
+                               sen = est_sensitivity,
+                               spec = est_specificity)
+
+
+WprevSeSp_result <-
+  WprevSeSp_original(AP = apparent_prevalence,
+                     stdErrPrev = stdErrPrev,
+                     nP = n_tested_for_prevalence,
+                     Se = est_sensitivity,
+                     nSe = n_tested_for_sensitivity,
+                     Sp = est_specificity,
+                     nSp = n_tested_for_specificity)
+
+dput(WprevSeSp_result)
+structure(list(estimate = c(`adjusted prevalence` = 0.0455598302324494),
[…]

### 2021-09-14 code/simulations/confidence_interval_imperfect_assay/imperfect_assay_arrayjob.R
fix imperfect assay simulation

@@ -146,7 +146,7 @@ calculate_interval_results <- function(weights,
                        nP = n_tested_for_prevalence,
                        Se = est_sensitivity,
                        nSe = n_tested_for_sensitivity,
-                       Sp = specificity,
+                       Sp = est_specificity,
                        nSp = n_tested_for_specificity)
   w <- weights / tests_per_group
   WprevSeSp_gamma_result <- WprevSeSp_gamma(apparent_positive_counts = apparent_positive_counts,
@@ -154,7 +154,7 @@ calculate_interval_results <- function(weights,
                   nP = n_tested_for_prevalence,
                   Se = est_sensitivity,
                   nSe = n_tested_for_sensitivity,
-                  Sp = specificity,
+                  Sp = est_specificity,
                   nSp = n_tested_for_specificity)
  # Need to implement other method
   list(conf_int_WprevSeSp = as.vector(WprevSeSp_result$conf.int),

### 2021-09-14 PrevAdjSurvey.tex

@@
 
+\begin{itemize}
+    \item This paper is concerned with methods for creating confidence intervals for estimating disease prevalence in a variety of scenarios.
+    \begin{itemize}
+        \item First, we improve confidence intervals for simple random samples where prevalence is assessed with an assay with imperfect sensitivity and/or specificity.
+        \item Next, we improve confidence intervals for weighted samples where prevalence is assessed with an assay with perfect sensitivity and/or specificity.
+        \item In the final scenario, we improve confidence intervals for weighted samples prevalence is assessed with an assay with imperfect sensitivity and/or specificity.
+    \end{itemize}
+\end{itemize}
+
 \section{Methods}
@@
 
-where \( w_i = N_i / N \).
+where \( w_i = N_i / \sum_{j=1}^n N_j \).
 
@@
 
-Let \( \hat{AP} = \frac{\sum_{i=1}^k N_i \frac{X_i}{n_i}}{\sum_{j=1}^k N_j} = \sum_{i=1}^k w_i \frac{X_i}{n_i} \), \( \widehat{Sp} = 1 - \frac{C_n}{m_n} \), and \( \widehat{Se} = \frac{C_p}{m_p} \).
+Let \( \widehat{AP} = \frac{\sum_{i=1}^k N_i \frac{X_i}{n_i}}{\sum_{j=1}^k N_j} = \sum_{i=1}^k w_i \frac{X_i}{n_i} \), \( \widehat{Sp} = 1 - \frac{C_n}{m_n} \), and \( \widehat{Se} = \frac{C_p}{m_p} \).
 
@@
 \end{equation}
+
+\begin{itemize}
+    \item We propose a modification of the melding method described in Fay 2015.
+    \item which uses lower and upper confidence distributions on functions of estimators independent estimators to create a confidence interval for prevalence that accounts for variability in \( \widehat{AP} \), \( \widehat{Se} \), and \( \widehat{Sp} \)
+    \item We assume all of these come from Binomial distributions.
+\end{itemize}
 
@@
 \end{figure}
+
+Misc quotes from Mike to incorporate:
+
+\begin{itemize}
+    \item For sharing the data from the Kalish, et al study, we thank Matthew Memoli and the LID Clinical Studies Unit of the National Institute of Allergy and Infectious Diseases, NIH,  Kaitlyn Sadtler from the National Institute of Biomedical Imaging and Bioengineering, NIH,   Matthew Hall from the National Center for Advancing Translational Sciences, NIH, and Dominic Esposito from the Fredrick National Laboratory for Cancer Research, NCI, NIH.
+    \item The last time we met, you mentioned that it would be nice to report the weights in terms of coefficient of variation.
+I went back to the data from the COVID seroprevalence paper in undiagnosed adults, and I calculated a coefficient of variation  of 2.52 = 252\% for all 8058 individuals, and looking at subsets, I found that the Hispanics had a CV=306\%.
+    \item For some weighting for surveys to adjust for selection bias, the coefficient of variation may be large.
+For example, the coefficient of variation of the weights (CVW) for the main estimate of seroprevalence in Kalish, et al (2021) had CVW=252\%, and it could be even larger for subsets of the population (e.g., Hispanics had CVW=306\%).
+\end{itemize}
 

### 2021-09-14 PrevAdjSurvey.tex
Updates from Overleaf

@@
 \usepackage{moreverb}
+
+\DeclareMathOperator{\Var}{Var}
+
 % just for todo notes
@@
 
-\title{A demonstration of the \LaTeX\ class file for Wiley NJD Journals\protect\thanks{This is an example for title footnote.}}
+\title{Confidence Intervals for Prevalence Estimates from Complex Surveys with Imperfect Assays}
 
@@
 \section{Methods}
-\todo[inline]{I’m struggling a bit with the overall message of the paper.
 
-In Part 1, we advocate for the Kalish Appendix aka the Korn-Graubard + CD method over the Lang-Reiczigel method in the case of a simple random sample / unweighted survey.
-This is sort of a special case of the / Korn-Graubard + CD method with k = 1 and the binomial variance assumption, rather than the Poisson variance assumption.
-
-In Part 2, we advocate for Fay-Feuer over Korn-Graubard in the case where
- }
 Suppose we have a survey with  \( k \) sampling units, with \( N_1, N_2, \ldots, N_k \) individuals in the population of unit \( i \).
 We sample \( n_1, n_2, \ldots, n_k \) individuals via a simple random sample from each population to have an assay performed to determine who has a disease.
-Let \( \theta_i \) be the population frequency of positive results for assays performed on individuals from sampling unit \( i \) and \( X_i \) be the number of positive results from an assay performed on \( n_i \) individuals from sampling unit \( i \).
-Also let \( \theta_i^* \) be the population frequency of cases in sampling unit \( i \) and \( X_i^* \) be the true number of people with the disease among the \( n_i \) individuals from sampling unit \( i \).
-Then \( X_i^* \sim \operatorname{Binomial}(n_i, \theta_i^*) \)
-In the case of a perfect assay, \( \theta_i = \theta_i^* \) and \( X_i = X_i^* \).
+Let \( X_i \) be the number of positive results from an assay performed on the \( n_i \) individuals from sampling unit \( i \) and assume \( X_i \sim \operatorname{Binomial}(n_i, \theta_i) \), where \( \theta_i \) is the population frequency of positive results for assays performed on individuals from sampling unit \( i \).
+Similarly, let \( X_i^* \) be the true number of people with the disease among the \( n_i \) individuals from sampling unit \( i \) and assume \( X_i^* \sim \operatorname{Binomial}(n_i, \theta_i^*) \), where \( \theta_i^* \) is the population frequency of cases in sampling unit \( i \).
+In the case of a perfect assay, \( \theta_i = \theta_i^* \).
 
@@
 \begin{equation}
-    \beta = \frac{\sum_{i=1}^k N_i \theta_i^*}{\sum_{j=1}^k N_j} = \sum_{i=1}^k w_i \theta_i^*,
+    \beta^* = \frac{\sum_{i=1}^k N_i \theta_i^*}{\sum_{j=1}^k N_j} = \sum_{i=1}^k w_i \theta_i^*,
+    \label{eq:pop-prev}
 \end{equation}
 
-where \( w_i = N_i / \sum_{j=1}^n N_j \).
+where \( w_i = N_i / \sum_{j=1}^n N_j \) and, therefore, \( \sum_{i=1}^k w_i = 1 \).
 
@@
 Let \( C_n \) and \( C_p \) be the number who test positive from the respective samples.
-Assume that the negative and positive controls act like simple random samples from their respective populations and that \( C_n \sim \operatorname{Binomial}(m_n, \phi_n) \) and \( C_p \sim \operatorname{Binomial}(m_p, \phi_p) \), where \( 1 - \phi_n \) is the specificity of the assay and \( \phi_p \) is the sensitivity of the assay.
+Assume that the negative and positive controls act like simple random samples from their respective populations.
+Thus, \( C_n \sim \operatorname{Binomial}(m_n, \phi_n) \) where \( 1 - \phi_n \) is the specificity of the assay, and \( C_p \sim \operatorname{Binomial}(m_p, \phi_p) \), where  \( \phi_p \) is the sensitivity of the assay.
 
-Let \( \widehat{AP} = \frac{\sum_{i=1}^k N_i \frac{X_i}{n_i}}{\sum_{j=1}^k N_j} = \sum_{i=1}^k w_i \frac{X_i}{n_i} \), \( \widehat{Sp} = 1 - \frac{C_n}{m_n} \), and \( \widehat{Se} = \frac{C_p}{m_p} \).
+Note the relationship between these parameters:
 
-The first method in this paper is concerned with estimating \( \beta \) in the case where \( k = 1 \), \( \phi_n > 0 \), \( \phi_p < 1 \), i.e.
+\begin{align}
+\begin{split}
+  \beta^*   =&   \sum_{i=1}^k w_i \theta_i^* \\
+            =&  \sum_{i=1}^k w_i \left( \frac{\theta_i - \phi_n}{\phi_p - \phi_n} \right) \\
+            =&   \frac{\sum_{i=1}^k w_i \theta_i}{\phi_p - \phi_n} - \frac{\phi_n \sum_{i=1}^k w_i}{\phi_p - \phi_n} \\
+            =&   \frac{\sum_{i=1}^k w_i \theta_i}{\phi_p - \phi_n} - \frac{\phi_n}{\phi_p - \phi_n}
+            \label{eq:long-beta}
+\end{split}
+\end{align}
+
+Let \( \hat{\theta}_i = \frac{X_i}{n_i} \), \( \hat{\phi}_n = \frac{C_n}{m_n} \), and \( \hat{\phi}_p = \frac{C_p}{m_p} \).
+Then a natural estimator for \( \beta^* \) is
+
+\begin{equation}
+    \hat{\beta}^* = \frac{\sum_{i=1}^k w_i \hat{\theta}_i}{\hat{\phi}_p - \hat{\phi}_n} - \frac{\hat{\phi}_n}{\hat{\phi}_p - \hat{\phi}_n}.
+\end{equation}
+
+This estimator serves as important basis for developing confidence intervals in this work.
+Section~\ref{sec:srs-imperfect} is concerned with confidence intervals for  \( \beta^* \) in the case where \( k = 1 \), \( \phi_n > 0 \), \( \phi_p < 1 \), i.e.
 estimating prevalence from a simple random sample with an imperfect assay.
-The second method in this paper is concerned with estimating \( \beta \) in the case where \( k > 1 \), \( \phi_n = 0 \), \( \phi_p = 1 \), i.e.
+Section~\ref{sec:weight-perfect} is concerned with confidence intervals for  \( \beta^* \) in the case where \( k > 1 \), \( \phi_n = 0 \), \( \phi_p = 1 \), i.e.
 estimating prevalence from a weighted sample with a perfect assay.
-The final method in this paper is concerned with estimating \( \beta \) in the case where \( k > 1 \), \( \phi_n > 0 \), \( \phi_p < 1 \), i.e.
+Section~\ref{sec:weight-imperfect} is concerned with confidence intervals for  \( \beta^* \) in the case where \( k > 1 \), \( \phi_n > 0 \), \( \phi_p < 1 \), i.e.
 estimating prevalence from a weighted sample with an imperfect assay.
@@
 \subsection{Estimating Prevalence from a Simple Random Sample with an Imperfect Assay}
+\label{sec:srs-imperfect}
 
-First, we consider the scenario \( k = 1 \), \( \phi_n > 0 \), \( \phi_p < 1 \) and we are concerned with estimating
+First, we consider the scenario \( k = 1 \), \( \phi_n > 0 \), and \( \phi_p < 1 \).
+We develop a confidence interval for the population prevalence, \( \beta^* \).
+Because \( k = 1 \), the estimator in Equation~\ref{eq:long-beta} becomes
 
 \begin{equation}
-    \beta = \frac{\sum_{i=1}^k N_i \theta_i^*}{\sum_{j=1}^k N_j} = \theta_1^*
+\hat{\beta}^* = \frac{\hat{\theta}_1 - \hat{\phi}_n}{\hat{\phi}_p - \hat{\phi}_n}.
+\label{eq:srs-beta-est}
 \end{equation}
 
-\begin{itemize}
-    \item We propose a modification of the melding method described in Fay 2015.
-    \item which uses lower and upper confidence distributions on functions of estimators independent estimators to create a confidence interval for prevalence that accounts for variability in \( \widehat{AP} \), \( \widehat{Se} \), and \( \widehat{Sp} \)
-    \item We assume all of these come from Binomial distributions.
-\end{itemize}
+To create a confidence interval for \( \hat{\beta}^* \), we use a generalization of the melding method \cite{FayP:2015}, which makes use of lower and upper confidence distributions on functions of independent estimators to account for variability in \( \hat{\theta}_1 \), \( \hat{\phi}_n \), and \( \hat{\phi}_p \).
 
-We use the method is described in the Appendix of \cite{Kali:2021}.
-This is a modification of the melding method, which uses lower and upper confidence distributions on functions of estimators independent estimators to create a confidence interval for prevalence that accounts for variability in \( \widehat{AP} \), \( \widehat{Se} \), and \( \widehat{Sp} \) \cite{FayP:2015}.
+Each estimated component in Equation~\ref{eq:srs-beta-est} is a binomial parameter.
+For each of these, we use distributions associated with  the exact binomial confidence interval.
+For a binomial experiment with \( x \) successes out of \( n \) trials, the lower confidence distribution \( (B^L) \) is \( \operatorname{Beta}(x, n - x + 1) \), and the upper confidence distribution \( (B^U) \) is \( \operatorname{Beta}(x + 1, n - x)\).
 
-For each of \( \widehat{AP} \), \( \widehat{Se} \), and \( \widehat{Sp} \), we use the lower and upper confidence distributions associated with the exact binomial confidence interval.
-In the case of a binomial random variable with \( x \) successes among \( n \) trials, the lower confidence distribution is \( \operatorname{Beta}(x, n - x + 1) \), and the upper confidence distribution is \( \operatorname{Beta}(x + 1, n - x) \).
+Let \( q(a, W) \) be the \( a \)th quantile of a random variable \( W \).
 
-Letting \( B_{ap}^L, B_{ap}^U, B_{sp}^L, B_{sp}^U, B_{se}^L, B_{se}^U \) be the lower and upper confidence distribtuions associate with the estimators, and \( q(a, W) \) be the \( a \)th quantile of a random variable \( W \), the 95\% confidence interval for \( \beta \) is
+Then the \( a \)\% confidence interval for \( \beta^* \) is
 
-\( \left\{ q \left( 0.025, \frac{B_{ap}^L + B_{sp}^L - 1}{B_{se}^U + B_{sp}^L - 1}  \right),  q \left( 0.975, \frac{B_{ap}^U + B_{sp}^U - 1}{B_{se}^L + B_{sp}^U - 1}  \right) \right\}.\)
+\begin{equation}
+    \left\{ q \left( \frac{1 - a}{2}, \frac{B_{\theta_1}^L + B_{\phi_n}^L }{B_{\phi_p}^U + B_{\phi_n}^L }  \right),  q \left( \frac{1 + a}{2}, \frac{B_{\theta_1}^U + B_{\phi_n}^U}{B_{\phi_p}^L + B_{\phi_n}^U}  \right) \right\}.
+\end{equation}
 
-This method is compared to the method presented in \citet{Lang:2014}.
+We compare this method to one described in \cite{Lang:2014} as implemented in prevSeSp function in \cite{asht}, which provides approximate confidence intervals for true prevalence when sensitivity and specificity are estimated from independent samples, as they are in the in this section.
+
+This interval is given by
+\begin{equation}
+\beta_1^{*\prime} + d\beta \pm q\left( \frac{1 + a}{2}, Z \right) \cdot \Var(\beta_1^{*\prime})^{1/2}    
+\end{equation}
+
+where
+\begin{equation}
+   Z \sim N(0,1) 
+\end{equation}
+
+\begin{equation}
+    d\beta = 2 \cdot q\left( \frac{1 + a}{2}, Z \right)^2 \cdot\left\{ \beta_1^{*\prime} \cdot \frac{\phi_p^\prime (1 - \phi_p^\prime)}{m_p^\prime} - (1 - \beta_1^{*\prime}) \cdot \frac{(1 - \phi_n^\prime) \phi_n^\prime}{m_n^\prime}  \right\}
+\end{equation}
+
+\begin{equation}
+    \Var(\beta_1^{*\prime}) = \frac{ \frac{\beta_1^{*\prime}(1 - \beta_1^{*\prime})}{n_1} + \left(\beta_1^{*\prime}\right)^2 \frac{\phi_p^\prime (1 - \phi_p^\prime)}{m_p} + \left(1 + \beta_1^{*\prime}\right)^2 \frac{(1 - \phi_n^\prime) \phi_n^\prime}{ m_n}}{(\phi_p^\prime - \phi_n^\prime)^2}
+\end{equation}
+
+\begin{equation}
+    m_p^\prime = m_p +2
+\end{equation}
+
+\begin{equation}
+    m_n^\prime = m_n + 2
+\end{equation}
+
+\begin{equation}
+    \phi_p^\prime = \frac{m_p \cdot \hat{\phi}_p + 1}{m_p + 2}
+\end{equation}
+
+\begin{equation}
+   1 - \phi_n^\prime = \frac{m_n \cdot (1 - \hat{\phi}_n) + 1}{m_n + 2} 
+\end{equation}
+
+\begin{equation}
+   \beta_1^{*\prime} = \frac{\beta_1^\prime - \phi_n^\prime}{\phi_p^\prime - \phi_n^\prime} 
+\end{equation}
+
+\begin{equation}
+    \beta_1^\prime = \frac{n_1 \cdot \hat{\theta}_1 + q\left( \frac{1 + a}{2}, Z \right)^2 / 2}{n_1 + q\left( \frac{1 + a}{2}, Z \right)^2}
+\end{equation}
 
 \subsection{Estimating Prevalence from a Weighted Sample with a Perfect Assay}
+\label{sec:weight-perfect}
+Next, we develop a confidence interval for the population prevalence, \( \beta^* \), in the scenario \( k > 1 \), \( \phi_n = 0 \), \( \phi_p = 1 \).
+Our method is a straightforward adaptation of the one presented in \cite{FayF:1997}, which was developed to create confidence intervals for a population rate which is assumed to a weighted sum of Poisson rate parameters.
+We note that for sufficiently large sample size \( n \) and small rate \( \lambda \), a \( \operatorname{Poisson}(n\lambda) \) distribution is approximately equal in distribution to a \( \operatorname{Binomial}(n, \lambda) \) distribution.
+Under this assumption, we suggest the confidence interval for \( \beta^* \):
+
+\begin{equation}
+    \left( q\left( \frac{1 - a}{2}, G_{\beta^*}^L \right), q \left( \frac{1 + a}{2},  G_{\beta^*}^U \right) \right)
+\end{equation}
+
+Where
+
+\begin{equation}
+    G_{\beta^*}^L \sim \operatorname{Gamma}\left( \frac{y^2}{v}, \frac{v}{y} \right)
+\end{equation}
+
+\begin{equation}
+    G_{\beta^*}^U \sim \operatorname{Gamma}\left( \frac{y^{*2}}{v^*}, \frac{v^*}{y^*} \right)
+\end{equation}
+
+\begin{equation}
+    y = \sum_{i=1}^k \frac{w_i}{n_i} x_i
+\end{equation}
+
+\begin{equation}
+    v = \sum_{i=1}^k \left( \frac{w_i}{n_i}\right)^2 x_i
+\end{equation}
+
+\begin{equation}
+    y^* = y + \max\left(\frac{w_1}{n_1}, \ldots, \frac{w_k}{n_k} \right)
+\end{equation}
+
+\begin{equation}
+    v^* = v + \left\{ \max\left(\frac{w_1}{n_1}, \ldots, \frac{w_k}{n_k} \right) \right\}^2
+\end{equation}
+
+We compare this confidence interval to two methods presented in \cite{Dean:2015}.
+
+The first of these is an adaptation of \cite{AgrestiCoull} for the survey setting.
+The interval for \( \beta^* \) is given by:
+
+\begin{equation}
+    \tilde{p} \pm q\left( \frac{1 + a}{2}, Z \right) \sqrt{\tilde{p}(1 - \tilde{p}) / \tilde{n}}
+\end{equation}
+
+where
+
+\begin{equation}
+   \tilde{x} = \left( \sum_{i=1}^k w_i \hat{\theta}_i \right) n_{\text{eff}} + c 
+\end{equation}
+
+\begin{equation}
+   \tilde{n} = n_{\text{eff}} + 2c 
+\end{equation}
+
+\begin{equation}
+    \tilde{p} = \tilde{x} / \tilde{n}
+\end{equation}
+
+\begin{equation}
+   c = q\left( \frac{1 + a}{2}, Z \right)^2/2 
+\end{equation}
+
+\begin{equation}
+   n_{\text{eff}} = \frac{\left( \sum_{i=1}^k w_i \hat{\theta}_i \right) \left(1 - \sum_{i=1}^k w_i \hat{\theta}_i \right)}{\sum_{i=1}^k \frac{w_i^2}{n_i}\hat{\theta}_i} 
+   \label{eq:neff}
+\end{equation}
+
+In the case where \( \sum_{i=1}^k \frac{w_i^2}{n_i}\hat{\theta}_i = 0 \), we instead let \( n_{\text{eff}} = \sum_{i=1}^k n_i \).
+
+We also compare our suggested method to a modification of \cite{Korn:1998} presented in \cite{Dean:2015}.
+This interval is given by
+
+\begin{equation}
+    \left( q \left( \frac{1 - a}{2}, B^L_{CP} \right), q \left( \frac{1 + a}{2}, B^U_{CP} \right)  \right)
+\end{equation}
+
+where
+
+\begin{equation}
+    B^L_{CP} \sim \operatorname{Binomial}\left(n_{\text{eff}} \sum_{i=1}^k w_i \hat{\theta}_i, n_{\text{eff}} \left(1 -  \sum_{i=1}^k w_i \hat{\theta}_i\right) + 1\right)
+\end{equation}
+
+\begin{equation}
+    B^U_{CP} \sim \operatorname{Binomial}\left(\left(n_{\text{eff}} \sum_{i=1}^k w_i \hat{\theta}_i\right) + 1, n_{\text{eff}} \left(1 - \sum_{i=1}^k w_i \hat{\theta}_i \right)\right)
+\end{equation}
+
+with \( n_{\text{eff}} \) defined in Equation~\ref{eq:neff}.
 
 \subsection{Estimating Prevalence from a Weighted Sample with an  Imperfect Assay}
+
+\label{sec:weight-imperfect}
 
@@
 \subsection{Estimating Prevalence from a Weighted Sample with an  Imperfect Assay}
+
+THERE IS A SMALL ERROR IN THESE RESULTS. RERUNNING ON BIOWULF NOW. I DON'T EXPECT THE SUBSTANCE TO CHANGE.
 

### 2021-09-14 code/simulations/confidence_interval_theta_star_fay_vs_LR/confidence_interval_theta_star_fay_vs_LR_simulations.R
fix Fay vs LR code

@@ -4,7 +4,7 @@ library(asht)
 library(cowplot)
 library(fs)
 library(furrr)
-source("WWprevSeSp_SRS_SRS.R")
+source("code/simulations/confidence_interval_imperfect_assay/WprevSeSp_SRS.R")
 
 plan(multisession, workers = 40)
 furrr_options(seed = 200)
@@ -52,7 +52,7 @@ results <-
                                         n_tested_for_sensitivity,
                                         est_specificity,
                                         n_tested_for_specificity)
-                            WprevSeSp_SRS(AP = est_prevalence,
+                            prevSeSp(AP = est_prevalence,
                                      nP = n_tested_for_prevalence,
                                      Se = est_sensitivity,
                                      nSe = n_tested_for_sensitivity,
@@ -71,7 +71,7 @@ results <-
                                          n_tested_for_sensitivity,
                                          est_specificity,
                                          n_tested_for_specificity)
-                             WWprevSeSp_SRS_SRS(AP = est_prevalence,
+                             WprevSeSp_SRS(AP = est_prevalence,
                                            nP = n_tested_for_prevalence,
                                            Se = est_sensitivity,
                                            nSe = n_tested_for_sensitivity,

### 2021-11-01 PrevAdjSurvey.tex
Updates from Overleaf

@@
 
-\author[2]{Michael P. Fay*}
+\author[1]{Michael P. Fay*}
 
@@
 
-\authormark{D. M. BAYER, M.P. FAY and B. I. Graubard \textsc{et al}}
+\authormark{D. M. BAYER, M.P. FAY and B. I. GRAUBARD \textsc{et al}}
 
@@
 
-\address[2]{\orgdiv{Department of Statistics}, \orgname{University of California, Irvine}, \orgaddress{\state{Irvine, California}, \country{Country name}}}
+\address[2]{\orgdiv{Department of Statistics}, \orgname{University of California, Irvine}, \orgaddress{\state{Irvine, California}}}
 
@@
 \footnotetext{\textbf{Abbreviations:} ANA, anti-nuclear antibodies; APC, antigen-presenting cells; IRF, interferon regulatory factor}
+
+\section{To Do List}
+\begin{itemize}
+    \item Write abstract
+    \item Write introduction
+    \item Write discussion
+    \item Figure revisions:
+    \begin{itemize}
+        \item Part 1: Rename "Fay" to "Melding"?
+        \item Part 1: Increase font size
+        \item Part 2: Rename Clopper-Pearson to Korn-Graubard
+        \item Part 3: Replace simulations results with corrected results (still running on Biowulf)
+    \end{itemize}
+    \item Fix acknowledgements \LaTeX
+    \item Fix bibiliogrpahy \LaTeX
+\end{itemize}
 
@@
     \label{eq:pop-prev}
+\end{equation}
+
+and the apparent prevalence is
+
+\begin{equation}
+    \beta = \frac{\sum_{i=1}^k N_i \theta_i}{\sum_{j=1}^k N_j} = \sum_{i=1}^k w_i \theta_i,
+    \label{eq:app-prev}
 \end{equation}
@@
 
-Each estimated component in Equation~\ref{eq:srs-beta-est} is a binomial parameter.
+Each estimated component in Equation~\ref{eq:srs-beta-est} is a binomial probability parameter.
 For each of these, we use distributions associated with  the exact binomial confidence interval.
@@
     \left\{ q \left( \frac{1 - a}{2}, \frac{B_{\theta_1}^L + B_{\phi_n}^L }{B_{\phi_p}^U + B_{\phi_n}^L }  \right),  q \left( \frac{1 + a}{2}, \frac{B_{\theta_1}^U + B_{\phi_n}^U}{B_{\phi_p}^L + B_{\phi_n}^U}  \right) \right\}.
+\label{eq:srs-conf-int}
 \end{equation}
@@
 \begin{equation}
-    B^L_{CP} \sim \operatorname{Binomial}\left(n_{\text{eff}} \sum_{i=1}^k w_i \hat{\theta}_i, n_{\text{eff}} \left(1 -  \sum_{i=1}^k w_i \hat{\theta}_i\right) + 1\right)
+    % B^L_{CP} \sim \operatorname{Beta}\left(n_{\text{eff}} \sum_{i=1}^k w_i \hat{\theta}_i, n_{\text{eff}} \left(1 -  \sum_{i=1}^k w_i \hat{\theta}_i\right) + 1\right)
+    B^L_{CP} \sim \operatorname{Beta}\left(x_{\text{eff}},  n_{\text{eff}} -  x_{\text{eff}} + 1 \right)
 \end{equation}
@@
 \begin{equation}
-    B^U_{CP} \sim \operatorname{Binomial}\left(\left(n_{\text{eff}} \sum_{i=1}^k w_i \hat{\theta}_i\right) + 1, n_{\text{eff}} \left(1 - \sum_{i=1}^k w_i \hat{\theta}_i \right)\right)
+    % B^U_{CP} \sim \operatorname{Beta}\left(\left(n_{\text{eff}} \sum_{i=1}^k w_i \hat{\theta}_i\right) + 1, n_{\text{eff}} \left(1 - \sum_{i=1}^k w_i \hat{\theta}_i \right)\right)
+    B^U_{CP} \sim \operatorname{Beta}\left(x_{\text{eff}} + 1, n_{\text{eff}} - x_{\text{eff}} \right)
 \end{equation}
 
-with \( n_{\text{eff}} \) defined in Equation~\ref{eq:neff}.
+with \( x_{\text{eff}} = n_{\text{eff}} \sum_{i=1}^k w_i \hat{\theta}_i \), and \( n_{\text{eff}} \) defined in Equation~\ref{eq:neff}.
 
@@
 
-\label{sec:weight-imperfect}
+Lastly, we develop a confidence interval for the population prevalence, \( \beta^* \), in the case where \( k > 1 \), \( \phi_n > 0 \), \( \phi_p < 1 \).
+
+The two methods we discuss are closely related to each other and the methods discussed in Sections~\ref{sec:srs-imperfect} and \ref{sec:weight-perfect}.
+As in Section~\ref{sec:srs-imperfect}, we use the melding method \cite{FayP:2015} to create \( a \)\% confidence interval very similar to Equation~\ref{eq:srs-conf-int}.
+The confidence distributions for \( \phi_p \) and \( \phi_n \) are the same Beta distributions as in Section~\ref{sec:srs-imperfect}.
+The two methods differ in their confidence distributions for the apparent prevalence \( \beta \).
+
+In the first case, we use the adaptation of \cite{FayF:1997} presented in Section~\ref{sec:weight-perfect} to derive the \( a \)\% confidence interval for \( \beta^* \):
+
+\begin{equation}
+    \left\{ q \left( \frac{1 - a}{2}, \frac{G_{\beta}^L + B_{\phi_n}^L }{B_{\phi_p}^U + B_{\phi_n}^L }  \right),  q \left( \frac{1 + a}{2}, \frac{G_{\beta}^U + B_{\phi_n}^U}{B_{\phi_p}^L + B_{\phi_n}^U}  \right) \right\}.
+\end{equation}
+
+where \( G_{\beta}^L \) and \( G_{\beta}^U \) are the same as \( G_{\beta^*}^L \) and \( G_{\beta^*}^U \) as defined in Section~\ref{sec:weight-perfect}.
+
+The alternative method is that used in \cite{Kali:2021}.
+We use the  modification of \cite{Korn:1998} presented in \cite{Dean:2015}, as in Section~\ref{sec:weight-perfect}, to derive the \( a \)\% confidence interval for \( \beta^* \):
+
+\begin{equation}
+    \left\{ q \left( \frac{1 - a}{2}, \frac{B_{CP}^L + B_{\phi_n}^L }{B_{\phi_p}^U + B_{\phi_n}^L }  \right),  q \left( \frac{1 + a}{2}, \frac{B_{CP}^U + B_{\phi_n}^U}{B_{\phi_p}^L + B_{\phi_n}^U}  \right) \right\}.
+\end{equation}
+
+where \( B_{CP}^L \) and \( B_{CP}^U \) are as defined in Section~\ref{sec:weight-perfect}.
 
 \section{Results}
+
 \subsection{Estimating Prevalence from a Simple Random Sample with an Imperfect Assay}
+
+We assess and compare our new method (Fay) to that of Lang and Reiczigel (LR) in a variety of simulated settings.
+In each simulation, 100 subjects are tested to estimate prevalence, 60 are tested to estimate sensitivity, and 300 are tested to estimate specificity.
+Several combinations of prevalences (0.5\%--2\%), sensitivities (75\%--100\%) and specificities (75\%--100\%) are assessed.
+Each simulated scenario is replicated 10,000 times.
+Figure~\ref{fig:coverage_comparison_plot} compares the two methods based on coverage, while Figures~\ref{fig:lower_error_frequency_comparison_plot} and \ref{fig:upper_error_frequency_comparison_plot} present the lower and upper error frequencies for these scenarios, respectively.
+
+\begin{figure}
+    \centering
+    \includegraphics[width=\textwidth]{figures/coverage_comparison_plot}
+    \caption{Coverage properties for our new method (Fay) and the state of the art method (LR) in a variety of settings, each simulated 10,000 times.}
+    \label{fig:coverage_comparison_plot}
+\end{figure}
+
+\begin{figure}
+    \centering
+    \includegraphics[width=\textwidth]{figures/lower_error_frequency_comparison_plot}
+    \caption{Lower error properties for our new method (Fay) and the state of the art method (LR) in a variety of settings, each simulated 10,000 times.}
+    \label{fig:lower_error_frequency_comparison_plot}
+\end{figure}
+
+\begin{figure}
+    \centering
+    \includegraphics[width=\textwidth]{figures/upper_error_frequency_comparison_plot}
+    \caption{Upper error properties for our new method (Fay) and the state of the art method (LR) in a variety of settings, each simulated 10,000 times.}
+    \label{fig:upper_error_frequency_comparison_plot}
+\end{figure}
+
 \subsection{Estimating Prevalence from a Weighted Sample with a Perfect Assay}
+
+We compare the wsPoisson method to the more traditional Agresti-Coull and Korn-Graubard methods in a variety of settings.
+Our simulations examine varying levels of disease prevalence (0.5\% or 5\%), types of groups surveyed (50 groups 200 subjects or 8000 groups of 1 subject), distributions of weights among the groups (coefficient of variation from 0-6), the number of groups with non-zero prevalence, and the weights of the groups with non-zero prevalence.
+For each scenario, 10,000 data sets are simulated and assessed.
+
+The coverage properties for these simulations are presented in Figures~\ref{fig:perfect_coverage_50_0_005_reduced}--\ref{fig:perfect_coverage_8000_0_05_reduced.pdf}.
 
@@
 \end{figure}
+
+\subsection{Estimating Prevalence from a Weighted Sample with an  Imperfect Assay}
+\todo[inline]{THERE IS A SMALL ERROR IN THE SIMULATION RESULTS. RERUNNING ON BIOWULF NOW. I DON'T EXPECT THE SUBSTANCE TO CHANGE.}
+
+We also apply these two methods to a real data set from \cite{Kali:2021}.
+This data set was collected to estimate seroprevalence of SARS-CoV-2 in the United States between May and July 2020.
+First we apply the methods to the full data set (\( n =  8058, \text{weight coefficient of variation} = "252\%\)).
+The Korn and Graubard type confidence distributions produce the 95\% confidence interval for population prevalence (2.53\%, 6.68\%), while the wsPoisson type confidence distributions produce the 95\% confidence interval (2.56\%, "7.54\%).
+
+We also apply the methods to the subset of only hispanic participants (\( n = 1281, \text{weight coefficient of variation} = 306\% \)).
+The Korn and Graubard type confidence distributions produce the 95\% confidence interval for population prevalence (2.35\%, 11.75\%), while the wsPoisson type confidence distributions produce the 95\% confidence interval (2.40\%, 20.02\%).
+
+\begin{figure}
+    \centering
+    \includegraphics[width=\textwidth]{figures/imperfect_coverage_50_0_005_reduced.pdf}
+    \caption{Caption}
+    \label{fig:imperfect_coverage_50_0_005_reduced}
+\end{figure}
+
+\begin{figure}
+    \centering
+    \includegraphics[width=\textwidth]{figures/imperfect_coverage_50_0_05_reduced.pdf}
+    \caption{Caption}
+    \label{fig:imperfect_coverage_50_0_05_reduced}
+\end{figure}
+
+\begin{figure}
+    \centering
+    \includegraphics[width=\textwidth]{figures/imperfect_coverage_8000_0_005_reduced.pdf}
+    \caption{Caption}
+    \label{fig:imperfect_coverage_8000_0_005_reduced}
+\end{figure}
+
+\begin{figure}
+    \centering
+    \includegraphics[width=\textwidth]{figures/imperfect_coverage_8000_0_05_reduced.pdf}
+    \caption{Caption}
+    \label{fig:imperfect_coverage_8000_0_05_reduced.pdf}
+\end{figure}
+
+Misc quotes from Mike to incorporate:
+
+\begin{itemize}
+    \item The last time we met, you mentioned that it would be nice to report the weights in terms of coefficient of variation.
+I went back to the data from the COVID seroprevalence paper in undiagnosed adults, and I calculated a coefficient of variation  of 2.52 = 252\% for all 8058 individuals, and looking at subsets, I found that the Hispanics had a CV=306\%.
+    \item For some weighting for surveys to adjust for selection bias, the coefficient of variation may be large.
+For example, the coefficient of variation of the weights (CVW) for the main estimate of seroprevalence in Kalish, et al (2021) had CVW=252\%, and it could be even larger for subsets of the population (e.g., Hispanics had CVW=306\%).
+\end{itemize}
+
+\section{Discussion}
+
+\acks
+\begin{acks}
+For sharing the data from the Kalish, et al study, we thank Matthew Memoli and the LID Clinical Studies Unit of the National Institute of Allergy and Infectious Diseases, NIH,  Kaitlyn Sadtler from the National Institute of Biomedical Imaging and Bioengineering, NIH,   Matthew Hall from the National Center for Advancing Translational Sciences, NIH, and Dominic Esposito from the Fredrick National Laboratory for Cancer Research, NCI, NIH.
+\end{acks}
+
+\section{Bibliography}
+\nocite{*}% Show all bib entries - both cited and uncited; comment this line to view only cited bib entries;
+\bibliography{refs}%
+
+\appendix
+\section{Additional Figures}
 
@@
     \label{fig:perfect_upper_error_frequency_8000_0_05_reduced.pdf}
-\end{figure}
-
-\subsection{Estimating Prevalence from a Weighted Sample with an  Imperfect Assay}
-
-THERE IS A SMALL ERROR IN THESE RESULTS. RERUNNING ON BIOWULF NOW. I DON'T EXPECT THE SUBSTANCE TO CHANGE.
-
-\begin{figure}
-    \centering
-    \includegraphics[width=\textwidth]{figures/imperfect_coverage_50_0_005_reduced.pdf}
-    \caption{Caption}
-    \label{fig:imperfect_coverage_50_0_005_reduced}
-\end{figure}
-
-\begin{figure}
-    \centering
-    \includegraphics[width=\textwidth]{figures/imperfect_coverage_50_0_05_reduced.pdf}
-    \caption{Caption}
-    \label{fig:imperfect_coverage_50_0_05_reduced}
-\end{figure}
-
-\begin{figure}
-    \centering
-    \includegraphics[width=\textwidth]{figures/imperfect_coverage_8000_0_005_reduced.pdf}
-    \caption{Caption}
-    \label{fig:imperfect_coverage_8000_0_005_reduced}
-\end{figure}
-
-\begin{figure}
-    \centering
-    \includegraphics[width=\textwidth]{figures/imperfect_coverage_8000_0_05_reduced.pdf}
-    \caption{Caption}
-    \label{fig:imperfect_coverage_8000_0_05_reduced.pdf}
 \end{figure}
@@
 
-Misc quotes from Mike to incorporate:
-
-\begin{itemize}
-    \item For sharing the data from the Kalish, et al study, we thank Matthew Memoli and the LID Clinical Studies Unit of the National Institute of Allergy and Infectious Diseases, NIH,  Kaitlyn Sadtler from the National Institute of Biomedical Imaging and Bioengineering, NIH,   Matthew Hall from the National Center for Advancing Translational Sciences, NIH, and Dominic Esposito from the Fredrick National Laboratory for Cancer Research, NCI, NIH.
-    \item The last time we met, you mentioned that it would be nice to report the weights in terms of coefficient of variation.
-I went back to the data from the COVID seroprevalence paper in undiagnosed adults, and I calculated a coefficient of variation  of 2.52 = 252\% for all 8058 individuals, and looking at subsets, I found that the Hispanics had a CV=306\%.
-    \item For some weighting for surveys to adjust for selection bias, the coefficient of variation may be large.
-For example, the coefficient of variation of the weights (CVW) for the main estimate of seroprevalence in Kalish, et al (2021) had CVW=252\%, and it could be even larger for subsets of the population (e.g., Hispanics had CVW=306\%).
-\end{itemize}
-
-\section{Discussion}
-
-\section{Bibliography}
-\nocite{*}% Show all bib entries - both cited and uncited; comment this line to view only cited bib entries;
-\bibliography{refs}%
-
-\section{Introduction}\label{sec1}
-
-Many authors submitting \( \sin \cos \tan \inf_{x} \) to NJD journals use \LaTeXe\ to
-prepare their papers. This paper describes the
-\textsf{WileyNJD-v2.cls} class file which can be used to convert
-articles produced with other \LaTeXe\ class files into the correct
-form for publication in \emph{Wiley NJD Journals}.
-
-The \textsf{WileyNJD-v2.cls} class file preserves much of the standard
-\LaTeXe\ interface so that any document which was produced using
-the standard \LaTeXe\ \textsf{article} style can easily be
-converted to work with the \textsf{WileyNJD-v2} style. However, the
-width of text and typesize will vary from that of
-\textsf{article.cls}; therefore, \emph{line breaks will change}
-and it is likely that displayed mathematics and tabular material
-will need re-setting.
-
-In the following sections we describe how to lay out your code to
-use \textsf{WileyNJD-v2.cls} to reproduce the typographical look of
-\emph{Wiley NJD Journals}.
-
-\subsection{Procedure to install fonts (not required on Overleaf)}
-
-\begin{enumerate}
-\item All font files are available under the Stix-fonts folder in the zip download at \url{https://onlinelibrary.wiley.com/page/journal/10991476/homepage/latex_class_files.htm}
-\item Font installer is available under the same folder Windows-Stix-fontinstaller.exe
-\item Execute (double click the EXE file) the EXE file that will install all fonts/map files to your local drive.
-\end{enumerate}
-
-\subsection{The Three Golden Rules}
-
-Before we proceed, we would like to
-stress \emph{three golden rules} that need to be followed to
-enable the most efficient use of your code at the typesetting
-stage:
-\begin{enumerate}
-\item[(i)] keep your own macros to an absolute minimum;
-
-\item[(ii)] as \TeX\ is designed to make sensible spacing
-decisions by itself, do \emph{not} use explicit horizontal or
-vertical spacing commands, except in a few accepted (mostly
-mathematical) situations, such as \verb"\," before a
-differential~d, or \verb"\quad" to separate an equation from its
-qualifier;
-
-\item[(iii)] follow the \emph{NJD} reference style.
-\begin{enumerate}[a.]
-\item Chemistry --- Use the ``AMA'' option as \verb"\documentclass[AMA]{WileyNJD-v2.cls}"
-
-\end{enumerate}
-\end{enumerate}
-
-\section{Getting Started} The \textsf{WileyNJD-v2.cls} class file should run
-on any standard \LaTeXe\ installation. If any of the fonts, class
-files or packages it requires are missing from your installation,
-they can be found on the \emph{\TeX\ Live} CD-ROMs or from CTAN.
-
-LaTeX document class options
-
-\begin{flushleft}
-\begin{enumerate}[a.]
-\item STIX1COL--- For STIX font large one column layout use the ``STIX1COL'' option as \verb"\documentclass[AMA,STIX1COL]{WileyNJD-v2}"
-\item STIX2COL--- For STIX font large two column layout use the ``STIX2COL'' option as \verb"\documentclass[AMA,STIX2COL]{WileyNJD-v2}"
-\item STIXSMALL--- For STIX font small layout use the ``STIXSMALL'' option as \verb"\documentclass[AMA,STIXSMALL]{WileyNJD-v2}"
-\end{enumerate}
-\end{flushleft}
-
-\section{The Article Header Information}
-The heading for any file using \textsf{WileyNJD-v2.cls} is shown in
-Figure~\ref{F1}.
-
-\subsection{Remarks}
-
-\begin{enumerate}[(I).]
-
-\item Use \verb"\title{<title> \protect\thanks{<title footnotes}}" for article title and title footnote.
-\item Use \verb"\authormark{}" for running heads.
-
-\item Note the use of \verb"\author[<link>]{<name>}" and \verb"\address[<link>]{<name>}" to
-link names and addresses. The author for correspondence is marked
-by ``*'' and \verb"\corres{}" is used to give that
-author's address, which will be printed besides abstract, prefaced by
-`Correspondence to:'.
-
-\item For submitting a double-spaced manuscript, add
-\verb"doublespace" as an option to the documentclass line. \verb"\documentclass[doublespace]{WileyNJD-v2}"
-
-\item Use \verb"\presentaddress{}" for present address.
-
-\item In abstract \verb"\abstract[<title>]{abstract paragraph}" use optional parameter for title followed by abstract paragraph.
-
-\item For Key words use \verb"\keywords{}".
-
-\item For how to site use \verb"\jnlcitation{\cname{\author{<author name>},"
-
-\verb"\ctitle{<title>}, \cjournal{<Journal name>}, \cvol{<vol>}.}}".
-
-\item For title page abbreviations use \verb"\footnotetext{<\textbf{Abbreviation title:} Abreviations>}"
-
-\item Use \verb"\articletype{<article category}" for article header information
-
-\item Use \verb"\received{<received date>} \revised{<revised date>} \accepted{<accepted date>}" for history dates.
-
-\end{enumerate}
-
-\begin{figure}[p]
-\setlength{\fboxsep}{0pt}%
-\setlength{\fboxrule}{0pt}%
-\begin{center}
-\begin{boxedverbatim}
-
-\documentclass[AMA,STIX1COL]{WileyNJD-v2}
-
-\articletype{Article Type}%
-
-\received{26 April 2016}
-\revised{6 June 2016}
-\accepted{6 June 2016}
-
-\begin{document}
-
-\title{<Initial cap, lower case>\protect\thanks{<title footnote.>}}
-
-\author[<address link>]{<Author name><corresponding author*>}
-
-\author[<address link>,<address link>]{Author Name}
-
-\authormark{AUTHOR ONE \textsc{et al}}
-
-\address[<address link>]{\orgdiv{<Org Division>}, \orgname{<Org name>}, 
-\orgaddress{\state{<State name>}, \country{<Country name>}}}
-\address[<address link>]{\orgdiv{<Org Division>}, \orgname{<Org name>},
- \orgaddress{\state{<State name>}, \country{<Country name>}}}
-
-\corres{<corresponding author link*> <author name, address.
- \email{<authorone@email.com>}}
-
-\presentaddress{<Present address>}
-
-\abstract[<Abstract heading>]{<Abstract paragraph>}
-
-\keywords{<keyword1>, <keyword2>,...}
-
-\jnlcitation{\cname{%
-\author{<aurhor name>}, 
-\author{<aurhor name>}, 
-\author{<aurhor name>}, 
-\author{<aurhor name>},  and 
-\author{<aurhor name>}} (\cyear{<year>}), 
-\ctitle{<journal title>}, \cjournal{<journal name>} <year> <vol> Page <xxx>-<xxx>}
-
-\footnotetext{\textbf{<abbreviation head:>} <abbreviations> ..}
-
-\maketitle
-
-\section{Introduction}
-.
-.
-.
-\end{boxedverbatim}
-\end{center}
-\caption{Example for title page.\label{F1}}
-\end{figure}
-
-\section{The Body of the Article}
-
-\subsection{Section headings}
-
-\begin{enumerate}[(H1)]
-\item Section --- use \verb"\section{}"
-\item SubSection--- use \verb"\subsection{}"
-\item SubSubSectioin--- use \verb"\subsubsection{}"
-\item Paragraph--- use \verb"\paragraph{}"
-\item Subparagraph--- use \verb"\subparagraph{}"
-\end{enumerate}
-
-\subsection{Mathematics} \textsf{WileyNJD-v2.cls} makes the full
-functionality of \AmS\/\TeX\ available. We encourage the use of
-the \verb"align", \verb"gather" and \verb"multline" environments
-for displayed mathematics.
-
-\subsection{Figures and Tables}
-
-\textsf{WileyNJD-v2.cls} uses the
-\textsf{graphicx} package for handling figures.
-
-Figures are called in as follows:
-\begin{verbatim}
-\begin{figure}
-\centering
-\includegraphics{<figure name>}
-\caption{<Figure caption>}
-\end{figure}
-\end{verbatim}
-
-The standard coding for a table is shown in Figure~\ref{F2}.
-
-\begin{figure}[h]
-\setlength{\fboxsep}{0pt}%
-\setlength{\fboxrule}{0pt}%
-\begin{center}
-\begin{boxedverbatim}
-\begin{table}
-\caption{<Table caption>}
-\centering
-\begin{tabular}{<table alignment>}
-\toprule
-<column headings>\\
-\midrule
-<table entries
-(separated by & as usual)>\\
-<table entries>\\
-.
-.
-.\\
-\bottomrule
-\end{tabular}
-\begin{tablenotes}
-\item Source: xxx.
-\item[1] xxx.
-\item[2] xxx.
-\end{tablenotes}
-\end{table}
-\end{boxedverbatim}
-\end{center}
-\caption{Example for table layout.\label{F2}}
-\end{figure}
-
-\subsection{Cross-referencing}
-The use of the \LaTeX\ cross-reference system
-for figures, tables, equations, etc., is encouraged
-(using \verb"\ref{<name>}" and \verb"\label{<name>}").
-
-\subsection{Box text}
-
-\begin{verbatim}
-\begin{boxtext}
-\section*{<title>}%
-Paragraph
-\end{boxtext}
-\end{verbatim}
-
-\subsection{List items}
-
-\subsubsection{Enumerate list styles}
-\begin{verbatim}
-\begin{enumerate}[1]
-\item 
-\end{enumerate}
-
-\begin{enumerate}[1.]
-\item 
-\end{enumerate}
-
-\begin{enumerate}[(1)]
-\item 
-\end{enumerate}
-
-\begin{enumerate}[I]
-\item 
-\end{enumerate}
-
-\begin{enumerate}[i]
-\item 
-\end{enumerate}
-
-\begin{enumerate}[a]
-\item 
-\end{enumerate}
-
-\end{verbatim}
-
-\subsubsection{Bullet list styles}
-
-\begin{verbatim}
-\begin{itemize}
-\item 
-\end{itemize}
-\end{verbatim}
-
-\subsubsection{Description list}
-
-\begin{verbatim}
-\begin{description}
-\item[<entry>] description text.
-\end{description}
-\end{verbatim}
-
-\subsection{Enunciations}
-
-\begin{verbatim}
-\begin{theorem}[<Theorem subhead>]\label{thm1}
-<theorem text>. 
-\end{theorem}
-
-\begin{proposition}[<proposition subhead>]\label{pro1}
-<proposition text>. 
-\end{proposition}
-
-\begin{definition}[<definition subhead>]\label{dfn1}
-<definition text>. 
-\end{definition}
-
-\begin{proof}
-<proof text>. 
-\end{proof}
-
-\begin{proof}[Proof of Theorem~\ref{thm1}]
-<proof text>.
-\end{proof}
-
-\end{verbatim}
-
-\subsection{Program codes}
-
-Use \verb+\begin{verbatim}...\end{verbatim}+ for program codes without math.
-Use \verb+\begin{alltt}...\end{alltt}+ for program codes with math.
-Based on the text provided inside the optional argument of \verb+\begin{code}[Psecode|Listing|Box|Code|+\hfill\break \verb+Specification|Procedure|Sourcecode|Program]...+ \verb+\end{code}+ tag corresponding boxed like floats are generated.
-Also note that \verb+\begin{code}[Code|Listing]...+ \verb+\end{code}+ tag with either Code or Listing text as optional argument text are set with computer modern typewriter font.
-All other code environments are set with normal text font.
-Refer below example:
-
-\begin{verbatim}
-\begin{lstlisting}[caption={Descriptive Caption Text},label=DescriptiveLabel]
-for i:=maxint to 0 do
-begin
-{ do nothing }
-end;
-Write('Case insensitive ');
-WritE('Pascal keywords.');
-\end{lstlisting}
-\end{verbatim}
-
-\subsection{Acknowledgements} An Acknowledgements section is started with \verb"\ack" or
-\verb"\acks" for \textit{Acknowledgement} or
-\textit{Acknowledgements}, respectively. It must be placed just
-before the References.
-
-\subsection{Bibliography}
-% \nocite{*}% Show all bib entries - both cited and uncited; comment this line to view only cited bib entries;
-% \bibliography{WileyNJD-AMA}%
-\begin{enumerate}[1]
-\item Use \verb"\bibliography{wileyNJD-AMA}" BST file for AMA reference style
-\item Use \verb"\bibliography{wileyNJD-APA}" BST file for APA reference style
-\item Use \verb"\bibliography{wileyNJD-AMS}" BST file for AMS reference style
-\item Use \verb"\bibliography{wileyNJD-VANCOUVER}" BST file for Vancouver reference style
-\item Use \verb"\bibliography{wileyNJD-ACS}" BST file for Chemistry reference style
-\end{enumerate}
-
-The normal commands for producing the reference list are:
-
-\begin{verbatim}
-\begin{thebibliography}{99}
-\bibitem{<x-ref label>}
-         <Reference details>
-.
-.
-.
-\end{thebibliography}
-\end{verbatim}
-
-\subsection{Appendix Section}
-
-\begin{verbatim}
-\appendix
-
-\section{Section title of first appendix\label{app1}}
-.
-.
-.
-
-\end{verbatim}
-
 \end{document}

### 2021-11-02 code/simulations/confidence_interval_imperfect_assay/process_imperfect_assay_arrayjob.R
Revised Figures

@@ -17,13 +17,11 @@ results_summary <-
                            "Coverage" = "coverage")) %>%
   mutate(method = fct_recode(method,
                              "WprevSeSp Binomial" = "WprevSeSp",
-                             "WprevSeSp Poisson" = "WprevSeSp_gamma")) %>%
+                             "WprevSeSp Poisson" = "WprevSeSp_gamma",
+                             "wspoissonTest" = "wspoissonTest")) %>%
   mutate(group_distribution = group_distribution %>%
            fct_relevel("high", "uniform", "low") %>%
            fct_relabel(str_to_title))
-
-
-
 
 
 
@@ -71,7 +69,7 @@ generate_plot_2 <- function(name_to_plot, n_groups_to_plot, prev_to_plot){
     scale_color_discrete(name = "Method") +
     theme(legend.position = "bottom") +
     ggtitle(label = glue("{name_to_plot} Properties for Simulations with {percent(prev_to_plot, accuracy = 0.1)} Prevalence Among {comma(n_groups_to_plot)} Groups of {comma(group_size)}"),
-            subtitle = "Each Point = 10,000 Replications")
+            subtitle = "Each Facet = 95% Sensitivity, Each Point = 10,000 Replications")
   generated_plot
 }
 
@@ -83,5 +81,21 @@ results_summary %>%
     ~generate_plot_2(name_to_plot = ..1,
                      n_groups_to_plot = ..2,
                      prev_to_plot = ..3))) %>%
-  mutate(file_name = path("figures", str_c("imperfect", str_replace_all(str_to_lower(name), "\\s", "_"), n_groups, str_replace_all(prev, "\\.", "_"), "reduced", sep = "_"), ext = "pdf")) %>%
-  with(walk2(file_name, plot, ~save_plot(filename = .x, plot = .y, ncol = 3, nrow = 2, base_width = 3.5)))
+  mutate(file_name = path("figures", str_c("imperfect", str_replace_all(str_to_lower(name), "\\s", "_"), n_groups, "groups", str_replace_all(prev, "\\.", "_"), "prev", sep = "_"), ext = "pdf")) %>%
+  # head(1) %>%
+  with(walk2(file_name, plot, ~save_plot(filename = .x, plot = .y, ncol = 3, nrow = 3, base_asp = 1)))
+
+
+# dir_ls("figures/") %>%
+#   enframe(name = NULL, value = "fig_path") %>%
+#   mutate(fig_name = fig_path %>% path_file() %>% path_ext_remove()) %>%
[…]

### 2021-11-02 code/simulations/confidence_interval_perfect_assay/process_weights_many.R

@@ -23,19 +23,31 @@ results_summary <-
                            "Lower Error Frequency" = "lower_error_freq",
                            "Upper Error Frequency" = "upper_error_freq",
                            "Coverage" = "coverage"),
+         # method = fct_recode(method,
+         #                     "Agresti-Coull (Unadjusted)" = "AC",
+         #                     "Agresti-Coull (Adjusted)" = "AC_adjusted",
+         #                     "Clopper-Pearson (Unadjusted)" = "CP",
+         #                     "Clopper-Pearson (Adjusted)" = "CP_adjusted",
+         #                     "wsPoisson" = "wspoissonTest",
+         #                     "wsPoisson with mid-p" = "wspoissonTest_midp"),
          method = fct_recode(method,
-                             "Agresti-Coull (Unadjusted)" = "AC",
-                             "Agresti-Coull (Adjusted)" = "AC_adjusted",
-                             "Clopper-Pearson (Unadjusted)" = "CP",
-                             "Clopper-Pearson (Adjusted)" = "CP_adjusted",
+                             "Agresti-Coull" = "AC",
+                             "Clopper-Pearson" = "CP",
                              "wsPoisson" = "wspoissonTest",
                              "wsPoisson with mid-p" = "wspoissonTest_midp"),
          group_distribution = group_distribution %>%
            fct_relevel("high", "uniform", "low") %>%
            fct_relabel(str_to_title))
 
+
+
 rm(ed1, ed2, sum1, sum2)
 
+desired_prop_groups_with_prev <- c(0.05, 0.25, 0.75)
+
+results_summary <- results_summary %>%
+  filter(prop_groups_with_prev %in% desired_prop_groups_with_prev,
+         method != "wsPoisson with mid-p")
 
 generate_plot <- function(name_to_plot, n_groups_to_plot, prev_to_plot){
   group_size <- if_else(n_groups_to_plot == 8000, 1, 200)
@@ -85,7 +97,7 @@ generate_plot <- function(name_to_plot, n_groups_to_plot, prev_to_plot){
 
 generate_plot(name_to_plot = "Coverage", n_groups_to_plot = 50, prev_to_plot = 0.005)
 
-.Last.value$plot[[1]]
+
 results_summary %>%
   select(n_groups, name, prev) %>%
   distinct() %>%
@@ -94,6 +106,12 @@ results_summary %>%
     ~generate_plot(name_to_plot = ..1,
                    n_groups_to_plot = ..2,
[…]

### 2021-11-02 code/simulations/confidence_interval_theta_star_fay_vs_LR/confidence_interval_theta_star_fay_vs_LR_process_results.R

@@ -5,7 +5,7 @@ library(cowplot)
 library(fs)
 library(furrr)
 
-results <- read_rds("code/simulations/confidence_interval_theta_star_fay_vs_LR/confidence_interval_theta_star_fay_vs_LR_results.rds")
+results <- read_csv("code/simulations/confidence_interval_theta_star_fay_vs_LR/confidence_interval_theta_star_fay_vs_LR_results.csv")
 
 # Process Results ---------------------------------------------------------
 coverage_results <-
@@ -15,14 +15,18 @@ coverage_results <-
             Fay_coverage = mean(Fay_covered),
             .groups = "drop") %>%
   pivot_longer(ends_with("coverage"), names_to = "method", values_to = "coverage") %>%
-  mutate(method = str_sub(method, end = -10))
+  mutate(method = str_sub(method, end = -10)) %>%
+  mutate(method = fct_recode(method,
+                             `Lang-Reiczigel` = "LR",
+                             Melding = "Fay"))
+
 
 coverage_distance_difference_data <-
   coverage_results %>%
   mutate(coverage_distance_from_truth = abs(0.95 - coverage)) %>%
   select(-coverage) %>%
   pivot_wider(names_from = method, values_from = coverage_distance_from_truth) %>%
-  mutate(coverage_distance_difference = LR - Fay)
+  mutate(coverage_distance_difference = `Lang-Reiczigel` - Melding)
 
 ci_results <-
   results %>%
@@ -37,7 +41,10 @@ ci_results <-
   group_by(n_tested_for_prevalence, n_tested_for_sensitivity, n_tested_for_specificity, prevalence, sensitivity, specificity, method) %>%
   summarize(lower_error_freq = mean(lower > prevalence),
             upper_error_freq = mean(upper < prevalence),
-            .groups = "drop")
+            .groups = "drop") %>%
+  mutate(method = fct_recode(method,
+                             `Lang-Reiczigel` = "LR",
+                             Melding = "Fay"))
 
 
 # Plot Results ------------------------------------------------------------
@@ -57,7 +64,8 @@ coverage_comparison_plot <-
   scale_y_continuous(name = "Sensitivity", labels = function(.) percent(., accuracy = 1)) +
   scale_fill_distiller(name = "Coverage",type = "div", palette = "PiYG", direction = 1, limits = c(0.9, 1), labels = function(.) percent(., accuracy = 1)) +
[…]

### 2021-11-02 PrevAdjSurvey.tex
Updates from Overleaf

@@
 This data set was collected to estimate seroprevalence of SARS-CoV-2 in the United States between May and July 2020.
-First we apply the methods to the full data set (\( n =  8058, \text{weight coefficient of variation} = "252\%\)).
+First we apply the methods to the full data set (\( n =  8058, \text{weight coefficient of variation} = 252\%\)).
 The Korn and Graubard type confidence distributions produce the 95\% confidence interval for population prevalence (2.53\%, 6.68\%), while the wsPoisson type confidence distributions produce the 95\% confidence interval (2.56\%, "7.54\%).
@@
 \centering
-    \includegraphics[width=\textwidth]{figures/perfect_lower_error_frequency_50_0_005_reduced.pdf}
+\includegraphics[width=\textwidth]{figures/imperfect_coverage_50_groups_0_005_prev.pdf}
 \caption{Caption}
-    \label{fig:perfect_lower_error_frequency_50_0_005_reduced}
+\label{fig:imperfect_coverage_50_groups_0_005_prev}
 \end{figure}
@@
 \centering
-    \includegraphics[width=\textwidth]{figures/perfect_lower_error_frequency_50_0_05_reduced.pdf}
+\includegraphics[width=\textwidth]{figures/imperfect_coverage_50_groups_0_05_prev.pdf}
 \caption{Caption}
-    \label{fig:perfect_lower_error_frequency_50_0_05_reduced}
+\label{fig:imperfect_coverage_50_groups_0_05_prev}
 \end{figure}
@@
 \centering
-    \includegraphics[width=\textwidth]{figures/perfect_lower_error_frequency_8000_0_005_reduced.pdf}
+\includegraphics[width=\textwidth]{figures/imperfect_coverage_8000_groups_0_005_prev.pdf}
 \caption{Caption}
-    \label{fig:perfect_lower_error_frequency_8000_0_005_reduced}
+\label{fig:imperfect_coverage_8000_groups_0_005_prev}
 \end{figure}
@@
 \centering
-    \includegraphics[width=\textwidth]{figures/perfect_lower_error_frequency_8000_0_05_reduced.pdf}
+\includegraphics[width=\textwidth]{figures/imperfect_coverage_8000_groups_0_05_prev.pdf}
 \caption{Caption}
-    \label{fig:perfect_lower_error_frequency_8000_0_05_reduced.pdf}
+\label{fig:imperfect_coverage_8000_groups_0_05_prev}
 \end{figure}
@@
 \centering
-    \includegraphics[width=\textwidth]{figures/perfect_upper_error_frequency_50_0_005_reduced.pdf}
+\includegraphics[width=\textwidth]{figures/imperfect_lower_error_frequency_50_groups_0_005_prev.pdf}
 \caption{Caption}
-    \label{fig:perfect_upper_error_frequency_50_0_005_reduced}
+\label{fig:imperfect_lower_error_frequency_50_groups_0_005_prev}
 \end{figure}
@@
 \centering
-    \includegraphics[width=\textwidth]{figures/perfect_upper_error_frequency_50_0_05_reduced.pdf}
+\includegraphics[width=\textwidth]{figures/imperfect_lower_error_frequency_50_groups_0_05_prev.pdf}
 \caption{Caption}
-    \label{fig:perfect_upper_error_frequency_50_0_05_reduced}
+\label{fig:imperfect_lower_error_frequency_50_groups_0_05_prev}
 \end{figure}
@@
 \centering
-    \includegraphics[width=\textwidth]{figures/perfect_upper_error_frequency_8000_0_005_reduced.pdf}
+\includegraphics[width=\textwidth]{figures/imperfect_lower_error_frequency_8000_groups_0_005_prev.pdf}
 \caption{Caption}
-    \label{fig:perfect_upper_error_frequency_8000_0_005_reduced}
+\label{fig:imperfect_lower_error_frequency_8000_groups_0_005_prev}
 \end{figure}
@@
 \centering
-    \includegraphics[width=\textwidth]{figures/perfect_upper_error_frequency_8000_0_05_reduced.pdf}
+\includegraphics[width=\textwidth]{figures/imperfect_lower_error_frequency_8000_groups_0_05_prev.pdf}
 \caption{Caption}
-    \label{fig:perfect_upper_error_frequency_8000_0_05_reduced.pdf}
+\label{fig:imperfect_lower_error_frequency_8000_groups_0_05_prev}
 \end{figure}
@@
 \centering
-    \includegraphics[width=\textwidth]{figures/imperfect_lower_error_frequency_50_0_005_reduced.pdf}
+\includegraphics[width=\textwidth]{figures/imperfect_upper_error_frequency_50_groups_0_005_prev.pdf}
 \caption{Caption}
-    \label{fig:imperfect_lower_error_frequency_50_0_005_reduced}
+\label{fig:imperfect_upper_error_frequency_50_groups_0_005_prev}
 \end{figure}
@@
 \centering
-    \includegraphics[width=\textwidth]{figures/imperfect_lower_error_frequency_50_0_05_reduced.pdf}
+\includegraphics[width=\textwidth]{figures/imperfect_upper_error_frequency_50_groups_0_05_prev.pdf}
 \caption{Caption}
-    \label{fig:imperfect_lower_error_frequency_50_0_05_reduced}
+\label{fig:imperfect_upper_error_frequency_50_groups_0_05_prev}
 \end{figure}
@@
 \centering
-    \includegraphics[width=\textwidth]{figures/imperfect_lower_error_frequency_8000_0_005_reduced.pdf}
+\includegraphics[width=\textwidth]{figures/imperfect_upper_error_frequency_8000_groups_0_005_prev.pdf}
 \caption{Caption}
-    \label{fig:imperfect_lower_error_frequency_8000_0_005_reduced}
+\label{fig:imperfect_upper_error_frequency_8000_groups_0_005_prev}
 \end{figure}
@@
 \centering
-    \includegraphics[width=\textwidth]{figures/imperfect_lower_error_frequency_8000_0_05_reduced.pdf}
+\includegraphics[width=\textwidth]{figures/imperfect_upper_error_frequency_8000_groups_0_05_prev.pdf}
 \caption{Caption}
-    \label{fig:imperfect_lower_error_frequency_8000_0_05_reduced.pdf}
+\label{fig:imperfect_upper_error_frequency_8000_groups_0_05_prev}
 \end{figure}
@@
 \centering
-    \includegraphics[width=\textwidth]{figures/imperfect_upper_error_frequency_50_0_005_reduced.pdf}
+\includegraphics[width=\textwidth]{figures/perfect_coverage_50_groups_0_005_prev.pdf}
 \caption{Caption}
-    \label{fig:imperfect_upper_error_frequency_50_0_005_reduced}
+\label{fig:perfect_coverage_50_groups_0_005_prev}
 \end{figure}
@@
 \centering
-    \includegraphics[width=\textwidth]{figures/imperfect_upper_error_frequency_50_0_05_reduced.pdf}
+\includegraphics[width=\textwidth]{figures/perfect_coverage_50_groups_0_05_prev.pdf}
 \caption{Caption}
-    \label{fig:imperfect_upper_error_frequency_50_0_05_reduced}
+\label{fig:perfect_coverage_50_groups_0_05_prev}
 \end{figure}
@@
 \centering
-    \includegraphics[width=\textwidth]{figures/imperfect_upper_error_frequency_8000_0_005_reduced.pdf}
+\includegraphics[width=\textwidth]{figures/perfect_coverage_8000_groups_0_005_prev.pdf}
 \caption{Caption}
-    \label{fig:imperfect_upper_error_frequency_8000_0_005_reduced}
+\label{fig:perfect_coverage_8000_groups_0_005_prev}
 \end{figure}
@@
 \centering
-    \includegraphics[width=\textwidth]{figures/imperfect_upper_error_frequency_8000_0_05_reduced.pdf}
+\includegraphics[width=\textwidth]{figures/perfect_coverage_8000_groups_0_05_prev.pdf}
 \caption{Caption}
-    \label{fig:imperfect_upper_error_frequency_8000_0_05_reduced.pdf}
+\label{fig:perfect_coverage_8000_groups_0_05_prev}
+\end{figure}
+
+\begin{figure}
+\centering
+\includegraphics[width=\textwidth]{figures/perfect_lower_error_frequency_50_groups_0_005_prev.pdf}
+\caption{Caption}
+\label{fig:perfect_lower_error_frequency_50_groups_0_005_prev}
+\end{figure}
+
+\begin{figure}
+\centering
+\includegraphics[width=\textwidth]{figures/perfect_lower_error_frequency_50_groups_0_05_prev.pdf}
+\caption{Caption}
+\label{fig:perfect_lower_error_frequency_50_groups_0_05_prev}
+\end{figure}
+
+\begin{figure}
+\centering
+\includegraphics[width=\textwidth]{figures/perfect_lower_error_frequency_8000_groups_0_005_prev.pdf}
+\caption{Caption}
+\label{fig:perfect_lower_error_frequency_8000_groups_0_005_prev}
+\end{figure}
+
+\begin{figure}
+\centering
+\includegraphics[width=\textwidth]{figures/perfect_lower_error_frequency_8000_groups_0_05_prev.pdf}
+\caption{Caption}
+\label{fig:perfect_lower_error_frequency_8000_groups_0_05_prev}
+\end{figure}
+
+\begin{figure}
+\centering
+\includegraphics[width=\textwidth]{figures/perfect_upper_error_frequency_50_groups_0_005_prev.pdf}
+\caption{Caption}
+\label{fig:perfect_upper_error_frequency_50_groups_0_005_prev}
+\end{figure}
+
+\begin{figure}
+\centering
+\includegraphics[width=\textwidth]{figures/perfect_upper_error_frequency_50_groups_0_05_prev.pdf}
+\caption{Caption}
+\label{fig:perfect_upper_error_frequency_50_groups_0_05_prev}
+\end{figure}
+
+\begin{figure}
+\centering
+\includegraphics[width=\textwidth]{figures/perfect_upper_error_frequency_8000_groups_0_005_prev.pdf}
+\caption{Caption}
+\label{fig:perfect_upper_error_frequency_8000_groups_0_005_prev}
+\end{figure}
+
+\begin{figure}
+\centering
+\includegraphics[width=\textwidth]{figures/perfect_upper_error_frequency_8000_groups_0_05_prev.pdf}
+\caption{Caption}
+\label{fig:perfect_upper_error_frequency_8000_groups_0_05_prev}
+\end{figure}
+
+\begin{figure}
+\centering
+\includegraphics[width=\textwidth]{figures/simple_coverage_comparison_plot.pdf}
+\caption{Caption}
+\label{fig:simple_coverage_comparison_plot}
+\end{figure}
+
+\begin{figure}
+\centering
+\includegraphics[width=\textwidth]{figures/simple_coverage_error_comparison_plot.pdf}
+\caption{Caption}
+\label{fig:simple_coverage_error_comparison_plot}
+\end{figure}
+
+\begin{figure}
+\centering
+\includegraphics[width=\textwidth]{figures/simple_lower_error_frequency_comparison_plot.pdf}
+\caption{Caption}
+\label{fig:simple_lower_error_frequency_comparison_plot}
+\end{figure}
+
+\begin{figure}
+\centering
+\includegraphics[width=\textwidth]{figures/simple_upper_error_frequency_comparison_plot.pdf}
+\caption{Caption}
+\label{fig:simple_upper_error_frequency_comparison_plot}
 \end{figure}

### 2021-11-04 PrevAdjSurvey.tex
Updates from Overleaf

@@
 
-Let \( \hat{\theta}_i = \frac{X_i}{n_i} \), \( \hat{\phi}_n = \frac{C_n}{m_n} \), and \( \hat{\phi}_p = \frac{C_p}{m_p} \).
+Let \( \hat{\theta}_i = \frac{X_i}{n_i} \), \( \hat{\phi}_n = 1 - \frac{C_n}{m_n} \), and \( \hat{\phi}_p = \frac{C_p}{m_p} \).
 Then a natural estimator for \( \beta^* \) is
@@
 
-First, we consider the scenario \( k = 1 \), \( \phi_n > 0 \), and \( \phi_p < 1 \).
+First, we consider the scenario0 \( k = 1 \), \( \phi_n > 0 \), and \( \phi_p < 1 \).
 We develop a confidence interval for the population prevalence, \( \beta^* \).
@@
 
+\todo[inline]{Can Mike provide some explanation for the form of this interval? Or some citation? Does it follow from Fay, Proschan, and Brittain (2015), or is there an intermediate reference?}
+
+The quantiles of these melded distributions are calculated by Monte Carlo sampling from each of the component distributions.
 We compare this method to one described in \cite{Lang:2014} as implemented in prevSeSp function in \cite{asht}, which provides approximate confidence intervals for true prevalence when sensitivity and specificity are estimated from independent samples, as they are in the in this section.
@@
 We note that for sufficiently large sample size \( n \) and small rate \( \lambda \), a \( \operatorname{Poisson}(n\lambda) \) distribution is approximately equal in distribution to a \( \operatorname{Binomial}(n, \lambda) \) distribution.
-Under this assumption, we suggest the confidence interval for \( \beta^* \):
+Under this assumption, we suggest the \( a \)\% confidence interval for \( \beta^* \):
 
@@
 The Korn and Graubard type confidence distributions produce the 95\% confidence interval for population prevalence (2.35\%, 11.75\%), while the wsPoisson type confidence distributions produce the 95\% confidence interval (2.40\%, 20.02\%).
+\todo[inline] Maybe also compute with the non sensitivity/specificity adjusted interval.
 

### 2021-11-04 data/create_kalish_data.R
wspoissonTest_result for kalish_data

@@ -1,5 +1,7 @@
 library(tidyverse)
 library(fs)
+library(asht)
+
 source("code/simulations/confidence_interval_imperfect_assay/WprevSeSp_SRS.R")
 load("C:/Users/bayerdm/Downloads/dataForDamon.RData")
 
@@ -76,6 +78,14 @@ WprevSeSp_result$conf.int
 WprevSeSp_gamma_result$conf.int
 
 
+wspoissonTest_result <- wspoissonTest(x = apparent_positive_counts, w = w, midp = F)
+dput(wspoissonTest_result)
+structure(list(statistic = c(`number of summands` = 8058L), parameter = c(`standardized Variance of Weights` = 6.368723849747),
+               p.value = NA_real_, conf.int = structure(c(0.0303500764310842,
+                                                          0.0739250045223186), conf.level = 0.95), estimate = c(`Weighted Sum` = 0.0455598302324495),
+               null.value = NULL, alternative = "two.sided", method = "Gamma Method for Weighted Sum of Poissons",
+               data.name = "x= apparent_positive_counts and w= w"), class = "htest")
+
 # Hispanic Data -----------------------------------------------------------
 kalish_data <-
   kalish_data %>%
@@ -138,3 +148,11 @@ structure(list(estimate = c(`adjusted prevalence` = 0.0612791931338004),
                nPeff = 1281), class = "htest")
 WprevSeSp_result$conf.int
 WprevSeSp_gamma_result$conf.int
+
+wspoissonTest_result <- wspoissonTest(x = apparent_positive_counts, w = w, midp = F)
+dput(wspoissonTest_result)
+structure(list(statistic = c(`number of summands` = 1281L), parameter = c(`standardized Variance of Weights` = 9.36002157276879),
+               p.value = NA_real_, conf.int = structure(c(0.0279906783975764,
+                                                          0.19628461563915), conf.level = 0.95), estimate = c(`Weighted Sum` = 0.0612791931338005),
+               null.value = NULL, alternative = "two.sided", method = "Gamma Method for Weighted Sum of Poissons",
+               data.name = "x= apparent_positive_counts and w= w"), class = "htest")

### 2021-11-11 PrevAdjSurvey.tex
First draft complete

@@
 
-\authormark{D. M. BAYER, M.P. FAY and B. I. GRAUBARD \textsc{et al}}
+\authormark{D. M. BAYER, M.P. FAY and B. I. GRAUBARD}
 
@@
 
-\presentaddress{Present address}
+% \presentaddress{Present address}
 
-\abstract[Abstract]{This paper describes the use of the \LaTeXe\ \textsf{WileyNJD-v2.cls}
-class file for setting papers for \emph{Mathematical Methods in the Applied Sciences}.}
+\abstract[Abstract]{To be written.}
 
@@
 
-\jnlcitation{\cname{%
-\author{Williams K.}, 
-\author{B. Hoskins}, 
-\author{R. Lee}, 
-\author{G. Masato}, and 
-\author{T. Woollings}} (\cyear{2016}), 
-\ctitle{A regime analysis of Atlantic winter jet variability applied to evaluate HadGEM3-GC2}, \cjournal{Q.J.R. Meteorol. Soc.}, \cvol{2017;00:1--6}.}
+% \jnlcitation{\cname{%
+% \author{Williams K.}, 
+% \author{B. Hoskins}, 
+% \author{R. Lee}, 
+% \author{G. Masato}, and 
+% \author{T. Woollings}} (\cyear{2016}), 
+% \ctitle{A regime analysis of Atlantic winter jet variability applied to evaluate HadGEM3-GC2}, \cjournal{Q.J.R. Meteorol. Soc.}, \cvol{2017;00:1--6}.}
 
@@
 
-\section{To Do List}
-\begin{itemize}
-    \item Write abstract
-    \item Write introduction
-    \item Write discussion
-    \item Figure revisions:
-    \begin{itemize}
-        \item Part 1: Rename "Fay" to "Melding"?
-        \item Part 1: Increase font size
-        \item Part 2: Rename Clopper-Pearson to Korn-Graubard
-        \item Part 3: Replace simulations results with corrected results (still running on Biowulf)
-    \end{itemize}
-    \item Fix acknowledgements \LaTeX
-    \item Fix bibiliogrpahy \LaTeX
-\end{itemize}
-
 \section{Introduction}
 
-\begin{itemize}
-    \item This paper is concerned with methods for creating confidence intervals for estimating disease prevalence in a variety of scenarios.
-    \begin{itemize}
-        \item First, we improve confidence intervals for simple random samples where prevalence is assessed with an assay with imperfect sensitivity and/or specificity.
-        \item Next, we improve confidence intervals for weighted samples where prevalence is assessed with an assay with perfect sensitivity and/or specificity.
-        \item In the final scenario, we improve confidence intervals for weighted samples prevalence is assessed with an assay with imperfect sensitivity and/or specificity.
-    \end{itemize}
-\end{itemize}
+Estimating and quantifying uncertainty for disease prevalence is a standard task in epidemiology.
+For rare events, these estimates are highly sensitive to misclassification \cite{hemenwaySelfDefense}, making adjustments for sensitivity and specificity critically important.
+While estimating prevalence in complex surveys and adjusting estimates for misclassification have been well studied separately, performing both of these tasks simultaneously remains relatively unexplored.
+A recent overview of methods for estimating prevalence in surveys without misclassification is provided in \cite{Dean:2015}.
+For simple surveys with imperfect sensitivity and specificity, \cite{Lang:2014} is the most recent advancement.
+To our knowledge \cite{Kali:2021} presents the only available method for constructing frequentist confidence intervals for prevalence estimates from complex surveys while adjusting for sensitivity and specificity; however,
+this problem has previously been addressed in Bayesian literature, recently in \cite{GelmanBayes}.
+
+We work up to our ultimate goal in stages.
+First, in Section~\ref{sec:srs-imperfect}, we propose confidence intervals for simple random samples where prevalence is assessed with an assay with imperfect sensitivity and/or specificity.
+Next, in Section~\ref{sec:weight-perfect}, we present confidence intervals for weighted samples where prevalence is assessed with an assay without misclassification.
+Finally, in Section~\ref{sec:weight-imperfect}, we combine these methods to create confidence intervals for weighted samples where prevalence is assessed with an assay with imperfect sensitivity and specificity.
 
@@
 
-This estimator serves as important basis for developing confidence intervals in this work.
+This estimator serves as an important basis for developing confidence intervals in this work.
 Section~\ref{sec:srs-imperfect} is concerned with confidence intervals for  \( \beta^* \) in the case where \( k = 1 \), \( \phi_n > 0 \), \( \phi_p < 1 \), i.e.
@@
 \begin{equation}
-    \left\{ q \left( \frac{1 - a}{2}, \frac{B_{\theta_1}^L + B_{\phi_n}^L }{B_{\phi_p}^U + B_{\phi_n}^L }  \right),  q \left( \frac{1 + a}{2}, \frac{B_{\theta_1}^U + B_{\phi_n}^U}{B_{\phi_p}^L + B_{\phi_n}^U}  \right) \right\}.
+    \left\{ q \left( \frac{1 - a}{2}, \frac{B_{\theta_1}^L - B_{\phi_n}^L }{B_{\phi_p}^U - B_{\phi_n}^L }  \right),  q \left( \frac{1 + a}{2}, \frac{B_{\theta_1}^U - B_{\phi_n}^U}{B_{\phi_p}^L - B_{\phi_n}^U}  \right) \right\}.
 \label{eq:srs-conf-int}
@@
 \label{sec:weight-perfect}
-Next, we develop a confidence interval for the population prevalence, \( \beta^* \), in the scenario \( k > 1 \), \( \phi_n = 0 \), \( \phi_p = 1 \).
+Next, we present a confidence interval for the population prevalence, \( \beta^* \), in the scenario \( k > 1 \), \( \phi_n = 0 \), \( \phi_p = 1 \).
 Our method is a straightforward adaptation of the one presented in \cite{FayF:1997}, which was developed to create confidence intervals for a population rate which is assumed to a weighted sum of Poisson rate parameters.
 We note that for sufficiently large sample size \( n \) and small rate \( \lambda \), a \( \operatorname{Poisson}(n\lambda) \) distribution is approximately equal in distribution to a \( \operatorname{Binomial}(n, \lambda) \) distribution.
+\todo[inline]{Is this a good enough justification? We certainly don't have a large sample size, but we do have small rates.}
 Under this assumption, we suggest the \( a \)\% confidence interval for \( \beta^* \):
@@
 
-We compare this confidence interval to two methods presented in \cite{Dean:2015}.
+We compare this confidence interval to two methods presented in \cite{Dean:2015}, which were recommended for scenarios with low prevalence.
 
@@
 \subsection{Estimating Prevalence from a Weighted Sample with an Imperfect Assay}
+\label{sec:weight-imperfect}
 
@@
 
-We assess and compare our new method (Fay) to that of Lang and Reiczigel (LR) in a variety of simulated settings.
+We assess and compare our new method (Melding) to that of Lang and Reiczigel (LR) in a variety of simulated settings.
 In each simulation, 100 subjects are tested to estimate prevalence, 60 are tested to estimate sensitivity, and 300 are tested to estimate specificity.
@@
     \centering
-    \includegraphics[width=\textwidth]{figures/coverage_comparison_plot}
-    \caption{Coverage properties for our new method (Fay) and the state of the art method (LR) in a variety of settings, each simulated 10,000 times.}
+    \includegraphics[width=0.8\textwidth]{figures/simple_coverage_comparison_plot.pdf}
+    \caption{Coverage properties of 95\% confidence intervals for our new method (Melding) and the state of the art method (Lang-Reiczigel) in a variety of settings, each simulated 10,000 times.}
     \label{fig:coverage_comparison_plot}
@@
     \centering
-    \includegraphics[width=\textwidth]{figures/lower_error_frequency_comparison_plot}
-    \caption{Lower error properties for our new method (Fay) and the state of the art method (LR) in a variety of settings, each simulated 10,000 times.}
+    \includegraphics[width=0.8\textwidth]{figures/simple_lower_error_frequency_comparison_plot.pdf}
+    \caption{Lower error properties of 95\% confidence intervals for our new method (Melding) and the state of the art method (Lang-Reiczigel) in a variety of settings, each simulated 10,000 times.}
     \label{fig:lower_error_frequency_comparison_plot}
@@
     \centering
-    \includegraphics[width=\textwidth]{figures/upper_error_frequency_comparison_plot}
-    \caption{Upper error properties for our new method (Fay) and the state of the art method (LR) in a variety of settings, each simulated 10,000 times.}
+    \includegraphics[width=0.8\textwidth]{figures/simple_upper_error_frequency_comparison_plot.pdf}
+    \caption{Upper error properties of 95\% confidence intervals for our new method (Melding) and the state of the art method (Lang-Reiczigel) in a variety of settings, each simulated 10,000 times.}
     \label{fig:upper_error_frequency_comparison_plot}
@@
 
+Figure~\ref{fig:coverage_comparison_plot} shows that, when specificity is less than perfect, both methods achieve approximately nominal coverage, with the melding method being somewhat more conservative.
+When specificity is 100\%, both methods are conservative.
+Figure~\ref{fig:upper_error_frequency_comparison_plot} shows that both methods make upper errors with roughly the same frequency.
+Figure~\ref{fig:lower_error_frequency_comparison_plot} demonstrates that while the melding procedure leads bounds the lower error frequency below 2.5\%, the Lang-Reiczigel method is much more likely to lead to lower errors than it is to result in upper errors, which may be undesirable for applications that are particularly sensitive to making lower errors.
+
 \subsection{Estimating Prevalence from a Weighted Sample with a Perfect Assay}
 
-We compare the wsPoisson method to the more traditional Agresti-Coull and Korn-Graubard methods in a variety of settings.
-Our simulations examine varying levels of disease prevalence (0.5\% or 5\%), types of groups surveyed (50 groups 200 subjects or 8000 groups of 1 subject), distributions of weights among the groups (coefficient of variation from 0-6), the number of groups with non-zero prevalence, and the weights of the groups with non-zero prevalence.
+We compare the wsPoisson method to the more traditional Agresti-Coull and Korn-Graubard methods for survey proportions in a variety of settings.
+Our simulations examine varying levels of disease prevalence (0.5\% or 5\%), types of groups surveyed (50 groups 200 subjects or 8000 groups of 1 subject), distributions of weights among the groups (coefficient of variation from approximately 0\% to nearly 6\%), the number of groups with non-zero prevalence, and the weights of the groups with non-zero prevalence.
 For each scenario, 10,000 data sets are simulated and assessed.
 
-The coverage properties for these simulations are presented in Figures~\ref{fig:perfect_coverage_50_0_005_reduced}--\ref{fig:perfect_coverage_8000_0_05_reduced.pdf}.
+\todo[inline]{Since our method is so conservative, I should look at the widths of the confidence intervals. Unfortunately, I have to re-reun simulations to do this.}
+
+The coverage properties for these simulations are presented in Figures~\ref{fig:perfect_coverage_50_groups_0_005_prev}--\ref{fig:perfect_coverage_8000_groups_0_05_prev}.
+Additional properties for these simulations are presented in Figures~\ref{fig:perfect_lower_error_frequency_50_groups_0_005_prev}--\ref{fig:perfect_upper_error_frequency_8000_groups_0_05_prev}.
+
+From Figures~\ref{fig:perfect_coverage_50_groups_0_005_prev}--\ref{fig:perfect_coverage_8000_groups_0_05_prev}, we note that the two competitor methods generally exhibit lower coverage as the coefficient of variation among the weights increases.
+In Figure~\ref{fig:perfect_coverage_50_groups_0_005_prev}, this coverage falls below 60\% when the prevalence very low and is concentrated among the highest weights, and the coefficient of variation among the weights exceeds 4.
+Uniform distribution of prevalence among the weights, increased overall prevalence, and larger sample sizes among fewer groups all appear to lessen the severity of this problem.
+In contrast, the wsPoisson method tends to become more conservative when the coefficient of variation among the weights increases.
+In all cases, the wsPoisson method is more conservative than the competitor methods.
+This is similar to the behavior observed in \cite{FayF:1997}, where, in simulations, the overall error rate decreased as the variance of the weights increased.
 
@@
 \centering
-    \includegraphics[width=\textwidth]{figures/perfect_coverage_50_0_005_reduced.pdf}
-    \caption{Caption}
-    \label{fig:perfect_coverage_50_0_005_reduced}
+\includegraphics[width=0.8\textwidth]{figures/perfect_coverage_50_groups_0_005_prev.pdf}
+\caption{Coverage properties for the wsPoisson model and two standard methods, Agresti-Coull and Clopper-Pearson.
+Each point represents 10,000 simulations of datasets from a population with 0.5\% Prevalence where 50 groups of 200 people are sampled.
+The horizontal dashed line indicates the nominal coverage, 95\%.
+Colored dashed lines are estimates from a logistic regression model using cubic splines.}
+\label{fig:perfect_coverage_50_groups_0_005_prev}
 \end{figure}
@@
 \centering
-    \includegraphics[width=\textwidth]{figures/perfect_coverage_50_0_05_reduced.pdf}
-    \caption{Caption}
-    \label{fig:perfect_coverage_50_0_05_reduced}
+\includegraphics[width=0.8\textwidth]{figures/perfect_coverage_8000_groups_0_005_prev.pdf}
+\caption{Coverage properties for the wsPoisson model and two standard methods, Agresti-Coull and Clopper-Pearson.
+Each point represents 10,000 simulations of datasets from a population with 0.5\% Prevalence where 8000 individuals are sampled.
+The horizontal dashed line indicates the nominal coverage, 95\%.
+Colored dashed lines are estimates from a logistic regression model using cubic splines.}
+\label{fig:perfect_coverage_8000_groups_0_005_prev}
 \end{figure}
@@
 \centering
-    \includegraphics[width=\textwidth]{figures/perfect_coverage_8000_0_005_reduced.pdf}
-    \caption{Caption}
-    \label{fig:perfect_coverage_8000_0_005_reduced}
+\includegraphics[width=0.8\textwidth]{figures/perfect_coverage_50_groups_0_05_prev.pdf}
+\caption{Coverage properties for the wsPoisson model and two standard methods, Agresti-Coull and Clopper-Pearson.
+Each point represents 10,000 simulations of datasets from a population with 5\% Prevalence where 50 groups of 200 people are sampled.
+The horizontal dashed line indicates the nominal coverage, 95\%.
+Colored dashed lines are estimates from a logistic regression model using cubic splines.}
+\label{fig:perfect_coverage_50_groups_0_05_prev}
 \end{figure}
@@
 \centering
-    \includegraphics[width=\textwidth]{figures/perfect_coverage_8000_0_05_reduced.pdf}
-    \caption{Caption}
-    \label{fig:perfect_coverage_8000_0_05_reduced.pdf}
+\includegraphics[width=0.8\textwidth]{figures/perfect_coverage_8000_groups_0_05_prev.pdf}
+\caption{Coverage properties for the wsPoisson model and two standard methods, Agresti-Coull and Clopper-Pearson.
+Each point represents 10,000 simulations of datasets from a population with 5\% Prevalence where 8000 individuals are sampled.
+The horizontal dashed line indicates the nominal coverage, 95\%.
+Colored dashed lines are estimates from a logistic regression model using cubic splines.}
+\label{fig:perfect_coverage_8000_groups_0_05_prev}
 \end{figure}
@@
 \subsection{Estimating Prevalence from a Weighted Sample with an Imperfect Assay}
-\todo[inline]{THERE IS A SMALL ERROR IN THE SIMULATION RESULTS. RERUNNING ON BIOWULF NOW. I DON'T EXPECT THE SUBSTANCE TO CHANGE.}
 
-We also apply these two methods to a real data set from \cite{Kali:2021}.
-This data set was collected to estimate seroprevalence of SARS-CoV-2 in the United States between May and July 2020.
-First we apply the methods to the full data set (\( n =  8058, \text{weight coefficient of variation} = 252\%\)).
-The Korn and Graubard type confidence distributions produce the 95\% confidence interval for population prevalence (2.53\%, 6.68\%), while the wsPoisson type confidence distributions produce the 95\% confidence interval (2.56\%, "7.54\%).
+We compare properties our melded confidence interval WprevSeSp Poisson, to anotother melded confidence interval method WprevSeSp Binomial, and one method, wspoissonTest, which does not account for the imperfect assay.
+The methods are assessed in a several simulated scenarios with varying levels of disease prevalence (0.5\% or 5\%), types of groups surveyed (50 groups 200 subjects or 8000 groups of 1 subject), distributions of weights among the groups (coefficient of variation from approximately 0\% to nearly 6\%), the number of groups with non-zero prevalence, and the specificity of the assay (80\% - 100\%).
+In each scenario, the assay has 95\% sensitivity.
+Each scenario is simulated 10,000 times, with new prevalence, sensitivity, and specificity surveys generated and 95\% confidence intervals are created.
+Simulated sensitivity is assessed based on 60 tests, while specificity is based on 300 tests.
 
-We also apply the methods to the subset of only hispanic participants (\( n = 1281, \text{weight coefficient of variation} = 306\% \)).
-The Korn and Graubard type confidence distributions produce the 95\% confidence interval for population prevalence (2.35\%, 11.75\%), while the wsPoisson type confidence distributions produce the 95\% confidence interval (2.40\%, 20.02\%).
-\todo[inline] Maybe also compute with the non sensitivity/specificity adjusted interval.
+\todo[inline]{Since our method is so conservative, I should look at the widths of the confidence intervals. Unfortunately, I have to re-reun simulations to do this.}
+
+The coverage properties for these simulations are presented in Figures~\ref{fig:imperfect_coverage_50_groups_0_005_prev}--\ref{fig:imperfect_coverage_8000_groups_0_05_prev}.
+Additional properties for these simulations are presented in Figures~\ref{fig:imperfect_lower_error_frequency_50_groups_0_05_prev}--\ref{fig:imperfect_upper_error_frequency_8000_groups_0_05_prev}.
 
@@
 \centering
-    \includegraphics[width=\textwidth]{figures/imperfect_coverage_50_0_005_reduced.pdf}
-    \caption{Caption}
-    \label{fig:imperfect_coverage_50_0_005_reduced}
+\includegraphics[width=0.8\textwidth]{figures/imperfect_coverage_50_groups_0_005_prev.pdf}
+\caption{Coverage properties for the two melded confidence interval procedures, WprevSeSp Binomial and WprevSeSp Poisson, and one method, wspoissonTest, which does not account for the imperfect assay.
+Each point represents 10,000 simulations of datasets from a population with 0.5\% Prevalence where 50 groups of 200 people are sampled.
+Each datasets also includes simulated results of tests to evaluate the sensitivity and specificity of the assay performed on 60 and 300 individuals, respectively.
+The horizontal dashed line indicates the nominal coverage, 95\%.
+Colored dashed lines are estimates from a logistic regression model using cubic splines.}
+\label{fig:imperfect_coverage_50_groups_0_005_prev}
 \end{figure}
@@
 \centering
-    \includegraphics[width=\textwidth]{figures/imperfect_coverage_50_0_05_reduced.pdf}
-    \caption{Caption}
-    \label{fig:imperfect_coverage_50_0_05_reduced}
+\includegraphics[width=0.8\textwidth]{figures/imperfect_coverage_8000_groups_0_005_prev.pdf}
+\caption{Coverage properties for the two melded confidence interval procedures, WprevSeSp Binomial and WprevSeSp Poisson, and one method, wspoissonTest, which does not account for the imperfect assay.
+Each point represents 10,000 simulations of datasets from a population with 0.5\% Prevalence where 8000 individuals are sampled.
+Each datasets also includes simulated results of tests to evaluate the sensitivity and specificity of the assay performed on 60 and 300 individuals, respectively.
+The horizontal dashed line indicates the nominal coverage, 95\%.
+Colored dashed lines are estimates from a logistic regression model using cubic splines.}
+\label{fig:imperfect_coverage_8000_groups_0_005_prev}
 \end{figure}
@@
 \centering
-    \includegraphics[width=\textwidth]{figures/imperfect_coverage_8000_0_005_reduced.pdf}
-    \caption{Caption}
-    \label{fig:imperfect_coverage_8000_0_005_reduced}
+\includegraphics[width=0.8\textwidth]{figures/imperfect_coverage_50_groups_0_05_prev.pdf}
+\caption{Coverage properties for the two melded confidence interval procedures, WprevSeSp Binomial and WprevSeSp Poisson, and one method, wspoissonTest, which does not account for the imperfect assay.
+Each point represents 10,000 simulations of datasets from a population with 5\% Prevalence where 50 groups of 200 people are sampled.
+Each datasets also includes simulated results of tests to evaluate the sensitivity and specificity of the assay performed on 60 and 300 individuals, respectively.
+The horizontal dashed line indicates the nominal coverage, 95\%.
+Colored dashed lines are estimates from a logistic regression model using cubic splines.}
+\label{fig:imperfect_coverage_50_groups_0_05_prev}
 \end{figure}
@@
 \centering
-    \includegraphics[width=\textwidth]{figures/imperfect_coverage_8000_0_05_reduced.pdf}
-    \caption{Caption}
-    \label{fig:imperfect_coverage_8000_0_05_reduced.pdf}
+\includegraphics[width=0.8\textwidth]{figures/imperfect_coverage_8000_groups_0_05_prev.pdf}
+\caption{Coverage properties for the two melded confidence interval procedures, WprevSeSp Binomial and WprevSeSp Poisson, and one method, wspoissonTest, which does not account for the imperfect assay.
+Each point represents 10,000 simulations of datasets from a population with 5\% Prevalence where 8000 individuals are sampled.
+Each datasets also includes simulated results of tests to evaluate the sensitivity and specificity of the assay performed on 60 and 300 individuals, respectively.
+The horizontal dashed line indicates the nominal coverage, 95\%.
+Colored dashed lines are estimates from a logistic regression model using cubic splines.}
+\label{fig:imperfect_coverage_8000_groups_0_05_prev}
 \end{figure}
 
-Misc quotes from Mike to incorporate:
+Based on Figures~\ref{fig:imperfect_lower_error_frequency_50_groups_0_05_prev}--\ref{fig:imperfect_upper_error_frequency_8000_groups_0_05_prev}, we note that, in most settings, the naive wspoissonTest procedure results in extremely poor coverage, around 0\%, while the two melding procedures result in conservative confidence intervals, often nearing 100\% coverage.
+With perfect specificity, the issue of poor coverage for the wspoissonTest procedure is less prominent, but the WprevSeSp Binomial method fails to maintain nominal coverage when the coefficient of variation among the weights is high.
+Only our proposed WprevSeSp Poisson method maintains or exceed the desired coverage in all scenarios.
 
-\begin{itemize}
-    \item The last time we met, you mentioned that it would be nice to report the weights in terms of coefficient of variation.
+We also apply these two methods to a real data set from \cite{Kali:2021}.
+This data set was collected to estimate seroprevalence of SARS-CoV-2 in the United States between May and July 2020.
+This test used in this data is estimated to have perfect sensitivity, based on 56 tests on individuals with confirmed SARS-CoV-2 and perfect specificity based on 300 tests on individuals confirmed to not have SARS-CoV-2.
+First we apply the methods to the full data set (\( n =  8058, \text{weight coefficient of variation} = 252\%\)).
+The Korn and Graubard type melded confidence interval (WprevSeSp Binomial) produced the 95\% confidence interval for population prevalence (2.53\%, 6.68\%), while the wsPoisson type melded confidence interval (WprevSeSp Poisson) produce the 95\% confidence interval (2.56\%, 7.54\%).
+We also apply the wspoissonTest method from Section~\ref{sec:weight-perfect}, which does not account for imperfections in the assay, resulting in a 95\% confidence interval of (3.04\%, 7.39\%).
+While all three intervals overlap to a large degree, the wsPoisson type melded confidence interval is the widest.
+Our simulations show that the three procdures have similar coverage when specificity and weight coefficient of variation are both high, so this is unsurprising.
+
+We also apply the methods to the subset of only Hispanic participants (\( n = 1281, \text{weight coefficient of variation} = 306\% \)).
+The Korn and Graubard type confidence distributions (WprevSeSp Binomial) produce the 95\% confidence interval for population prevalence (2.35\%, 11.75\%), while the wsPoisson type confidence distributions (WprevSeSp Poisson) produce the 95\% confidence interval (2.40\%, 20.02\%).
+The wspoissonTest method produces a 95\% confidence interval of (2.80\%, 19.63\%).
+In this case, the two melded confidence intervals are much wider than the naive interval, as expected.
+This is somewhat unexpected, but may be because prevalence is concentrated among respondents with lower weights, or be related to the smaller sample size used to measure prevalence, which is not reflected in our simulations.
+
+\pagebreak
+
+% Misc quotes from Mike to incorporate:
+
+% \begin{itemize}
+%     \item The last time we met, you mentioned that it would be nice to report the weights in terms of coefficient of variation.
 I went back to the data from the COVID seroprevalence paper in undiagnosed adults, and I calculated a coefficient of variation  of 2.52 = 252\% for all 8058 individuals, and looking at subsets, I found that the Hispanics had a CV=306\%.
-    \item For some weighting for surveys to adjust for selection bias, the coefficient of variation may be large.
+%     \item For some weighting for surveys to adjust for selection bias, the coefficient of variation may be large.
 For example, the coefficient of variation of the weights (CVW) for the main estimate of seroprevalence in Kalish, et al (2021) had CVW=252\%, and it could be even larger for subsets of the population (e.g., Hispanics had CVW=306\%).
-\end{itemize}
+% \end{itemize}
 
@@
 
-\acks
-\begin{acks}
+We presented several methods for creating confidence to assess disease prevalence in variety of settings, including simple random samples with imperfect tests, weighted sampling with perfect tests, and weighted sampling with imperfect tests.
+As a general theme, these confidence intervals tend to demonstrate higher coverage than competitor methods.
+In the case of the simple random sample with an imperfect test, we are able to bound the lower error rate for a 95\% confidence interval at 2.5\%, while the state-of-the-art method maintains 95\% coverage by allowing a higher lower error rate.
+Our methods' conservative properties are especially advantageous in settings where the competitor methods exhibit much lower than nominal coverage.
+For example, there is high variance among the sample weights and prevalence is concentrated among the highest-weighted samples competitor coverage of 95\% confidence intervals can fall to 60\% for competitor methods, while our method exhibits > 95\% coverage.
+Thus, we suggest that our melding methods be employed when working with survey settings which involve high variance among the weights or lower errors are particularly undesirable.
+
+% \acks
+% \begin{acks}
+\section{Acknowledgements}
 For sharing the data from the Kalish, et al study, we thank Matthew Memoli and the LID Clinical Studies Unit of the National Institute of Allergy and Infectious Diseases, NIH,  Kaitlyn Sadtler from the National Institute of Biomedical Imaging and Bioengineering, NIH,   Matthew Hall from the National Center for Advancing Translational Sciences, NIH, and Dominic Esposito from the Fredrick National Laboratory for Cancer Research, NCI, NIH.
-\end{acks}
+% \end{acks}
 
@@
 \centering
-\includegraphics[width=\textwidth]{figures/imperfect_coverage_50_groups_0_005_prev.pdf}
-\caption{Caption}
-\label{fig:imperfect_coverage_50_groups_0_005_prev}
+\includegraphics[width=0.8\textwidth]{figures/perfect_lower_error_frequency_50_groups_0_005_prev.pdf}
+\caption{Lower error properties for the wsPoisson model and two standard methods, Agresti-Coull and Clopper-Pearson.
+Each point represents 10,000 simulations of datasets from a population with 0.5\% Prevalence where 50 groups of 200 people are sampled.
+The horizontal dashed line indicates the nominal lower error rate, 2.5\%.
+Colored dashed lines are estimates from a logistic regression model using cubic splines.}
+\label{fig:perfect_lower_error_frequency_50_groups_0_005_prev}
 \end{figure}
@@
 \centering
-\includegraphics[width=\textwidth]{figures/imperfect_coverage_50_groups_0_05_prev.pdf}
-\caption{Caption}
-\label{fig:imperfect_coverage_50_groups_0_05_prev}
+\includegraphics[width=0.8\textwidth]{figures/perfect_lower_error_frequency_8000_groups_0_005_prev.pdf}
+\caption{Lower error properties for the wsPoisson model and two standard methods, Agresti-Coull and Clopper-Pearson.
+Each point represents 10,000 simulations of datasets from a population with 0.5\% Prevalence where 8000 individuals are sampled.
+The horizontal dashed line indicates the nominal lower error rate, 2.5\%.
+Colored dashed lines are estimates from a logistic regression model using cubic splines.}
+\label{fig:perfect_lower_error_frequency_8000_groups_0_005_prev}
 \end{figure}
@@
 \centering
-\includegraphics[width=\textwidth]{figures/imperfect_coverage_8000_groups_0_005_prev.pdf}
-\caption{Caption}
-\label{fig:imperfect_coverage_8000_groups_0_005_prev}
+\includegraphics[width=0.8\textwidth]{figures/perfect_lower_error_frequency_50_groups_0_05_prev.pdf}
+\caption{Lower error properties for the wsPoisson model and two standard methods, Agresti-Coull and Clopper-Pearson.
+Each point represents 10,000 simulations of datasets from a population with 5\% Prevalence where 50 groups of 200 people are sampled.
+The horizontal dashed line indicates the nominal lower error rate, 2.5\%.
+Colored dashed lines are estimates from a logistic regression model using cubic splines.}
+\label{fig:perfect_lower_error_frequency_50_groups_0_05_prev}
 \end{figure}
@@
 \centering
-\includegraphics[width=\textwidth]{figures/imperfect_coverage_8000_groups_0_05_prev.pdf}
-\caption{Caption}
-\label{fig:imperfect_coverage_8000_groups_0_05_prev}
+\includegraphics[width=0.8\textwidth]{figures/perfect_lower_error_frequency_8000_groups_0_05_prev.pdf}
+\caption{Lower error properties for the wsPoisson model and two standard methods, Agresti-Coull and Clopper-Pearson.
+Each point represents 10,000 simulations of datasets from a population with 5\% Prevalence where 8000 individuals are sampled.
+The horizontal dashed line indicates the nominal lower error rate, 2.5\%.
+Colored dashed lines are estimates from a logistic regression model using cubic splines.}
+\label{fig:perfect_lower_error_frequency_8000_groups_0_05_prev}
 \end{figure}
@@
 \centering
-\includegraphics[width=\textwidth]{figures/imperfect_lower_error_frequency_50_groups_0_005_prev.pdf}
-\caption{Caption}
+\includegraphics[width=0.8\textwidth]{figures/perfect_upper_error_frequency_50_groups_0_005_prev.pdf}
+\caption{Upper error properties for the wsPoisson model and two standard methods, Agresti-Coull and Clopper-Pearson.
+Each point represents 10,000 simulations of datasets from a population with 0.5\% Prevalence where 50 groups of 200 people are sampled.
+The horizontal dashed line indicates the nominal upper error rate, 2.5\%.
+Colored dashed lines are estimates from a logistic regression model using cubic splines.}
+\label{fig:perfect_upper_error_frequency_50_groups_0_005_prev}
+\end{figure}
+
+\begin{figure}
+\centering
+\includegraphics[width=0.8\textwidth]{figures/perfect_upper_error_frequency_8000_groups_0_005_prev.pdf}
+\caption{Upper error properties for the wsPoisson model and two standard methods, Agresti-Coull and Clopper-Pearson.
+Each point represents 10,000 simulations of datasets from a population with 0.5\% Prevalence where 8000 individuals are sampled.
+The horizontal dashed line indicates the nominal upper error rate, 2.5\%.
+Colored dashed lines are estimates from a logistic regression model using cubic splines.}
+\label{fig:perfect_upper_error_frequency_8000_groups_0_005_prev}
+\end{figure}
+
+\begin{figure}
+\centering
+\includegraphics[width=0.8\textwidth]{figures/perfect_upper_error_frequency_50_groups_0_05_prev.pdf}
+\caption{Upper error properties for the wsPoisson model and two standard methods, Agresti-Coull and Clopper-Pearson.
+Each point represents 10,000 simulations of datasets from a population with 5\% Prevalence where 50 groups of 200 people are sampled.
+The horizontal dashed line indicates the nominal upper error rate, 2.5\%.
+Colored dashed lines are estimates from a logistic regression model using cubic splines.}
+\label{fig:perfect_upper_error_frequency_50_groups_0_05_prev}
+\end{figure}
+
+\begin{figure}
+\centering
+\includegraphics[width=0.8\textwidth]{figures/perfect_upper_error_frequency_8000_groups_0_05_prev.pdf}
+\caption{Upper error properties for the wsPoisson model and two standard methods, Agresti-Coull and Clopper-Pearson.
+Each point represents 10,000 simulations of datasets from a population with 5\% Prevalence where 8000 individuals are sampled.
+The horizontal dashed line indicates the nominal upper error rate, 2.5\%.
+Colored dashed lines are estimates from a logistic regression model using cubic splines.}
+\label{fig:perfect_upper_error_frequency_8000_groups_0_05_prev}
+\end{figure}
+
+% Start of Imperfect
+
+\begin{figure}
+\centering
+\includegraphics[width=0.8\textwidth]{figures/imperfect_lower_error_frequency_50_groups_0_05_prev.pdf}
+\caption{Lower error properties for the two melded confidence interval procedures, WprevSeSp Binomial and WprevSeSp Poisson, and one method, wspoissonTest, which does not account for the imperfect assay.
+Each point represents 10,000 simulations of datasets from a population with 0.5\% Prevalence where 50 groups of 200 people are sampled.
+Each datasets also includes simulated results of tests to evaluate the sensitivity and specificity of the assay performed on 60 and 300 individuals, respectively.
+The horizontal dashed line indicates the nominal lower error rate, 2.5\%.
+Colored dashed lines are estimates from a logistic regression model using cubic splines.}
+\label{fig:imperfect_lower_error_frequency_50_groups_0_05_prev}
+\end{figure}
+
+\begin{figure}
+\centering
+\includegraphics[width=0.8\textwidth]{figures/imperfect_lower_error_frequency_50_groups_0_005_prev.pdf}
+\caption{Lower error properties for the two melded confidence interval procedures, WprevSeSp Binomial and WprevSeSp Poisson, and one method, wspoissonTest, which does not account for the imperfect assay.
+Each point represents 10,000 simulations of datasets from a population with 0.5\% Prevalence where 8000 individuals are sampled.
+Each datasets also includes simulated results of tests to evaluate the sensitivity and specificity of the assay performed on 60 and 300 individuals, respectively.
+The horizontal dashed line indicates the nominal lower error rate, 2.5\%.
+Colored dashed lines are estimates from a logistic regression model using cubic splines.}
 \label{fig:imperfect_lower_error_frequency_50_groups_0_005_prev}
@@
 \centering
-\includegraphics[width=\textwidth]{figures/imperfect_lower_error_frequency_50_groups_0_05_prev.pdf}
-\caption{Caption}
-\label{fig:imperfect_lower_error_frequency_50_groups_0_05_prev}
+\includegraphics[width=0.8\textwidth]{figures/imperfect_lower_error_frequency_8000_groups_0_05_prev.pdf}
+\caption{Lower error properties for the two melded confidence interval procedures, WprevSeSp Binomial and WprevSeSp Poisson, and one method, wspoissonTest, which does not account for the imperfect assay.
+Each point represents 10,000 simulations of datasets from a population with 5\% Prevalence where 50 groups of 200 people are sampled.
+Each datasets also includes simulated results of tests to evaluate the sensitivity and specificity of the assay performed on 60 and 300 individuals, respectively.
+The horizontal dashed line indicates the nominal lower error rate, 2.5\%.
+Colored dashed lines are estimates from a logistic regression model using cubic splines.}
+\label{fig:imperfect_lower_error_frequency_8000_groups_0_05_prev}
 \end{figure}
@@
 \centering
-\includegraphics[width=\textwidth]{figures/imperfect_lower_error_frequency_8000_groups_0_005_prev.pdf}
-\caption{Caption}
+\includegraphics[width=0.8\textwidth]{figures/imperfect_lower_error_frequency_8000_groups_0_005_prev.pdf}
+\caption{Lower error properties for the two melded confidence interval procedures, WprevSeSp Binomial and WprevSeSp Poisson, and one method, wspoissonTest, which does not account for the imperfect assay.
+Each point represents 10,000 simulations of datasets from a population with 5\% Prevalence where 8000 individuals are sampled.
+Each datasets also includes simulated results of tests to evaluate the sensitivity and specificity of the assay performed on 60 and 300 individuals, respectively.
+The horizontal dashed line indicates the nominal lower error rate, 2.5\%.
+Colored dashed lines are estimates from a logistic regression model using cubic splines.}
 \label{fig:imperfect_lower_error_frequency_8000_groups_0_005_prev}
@@
 \centering
-\includegraphics[width=\textwidth]{figures/imperfect_lower_error_frequency_8000_groups_0_05_prev.pdf}
-\caption{Caption}
-\label{fig:imperfect_lower_error_frequency_8000_groups_0_05_prev}
-\end{figure}
-
-\begin{figure}
-\centering
-\includegraphics[width=\textwidth]{figures/imperfect_upper_error_frequency_50_groups_0_005_prev.pdf}
-\caption{Caption}
+\includegraphics[width=0.8\textwidth]{figures/imperfect_upper_error_frequency_50_groups_0_005_prev.pdf}
+\caption{Upper error properties for the two melded confidence interval procedures, WprevSeSp Binomial and WprevSeSp Poisson, and one method, wspoissonTest, which does not account for the imperfect assay.
+Each point represents 10,000 simulations of datasets from a population with 0.5\% Prevalence where 50 groups of 200 people are sampled.
+Each datasets also includes simulated results of tests to evaluate the sensitivity and specificity of the assay performed on 60 and 300 individuals, respectively.
+The horizontal dashed line indicates the nominal upper error rate, 2.5\%.
+Colored dashed lines are estimates from a logistic regression model using cubic splines.}
 \label{fig:imperfect_upper_error_frequency_50_groups_0_005_prev}
@@
 \centering
-\includegraphics[width=\textwidth]{figures/imperfect_upper_error_frequency_50_groups_0_05_prev.pdf}
-\caption{Caption}
+\includegraphics[width=0.8\textwidth]{figures/imperfect_upper_error_frequency_8000_groups_0_005_prev.pdf}
+\caption{Upper error properties for the two melded confidence interval procedures, WprevSeSp Binomial and WprevSeSp Poisson, and one method, wspoissonTest, which does not account for the imperfect assay.
+Each point represents 10,000 simulations of datasets from a population with 0.5\% Prevalence where 8000 individuals are sampled.
+Each datasets also includes simulated results of tests to evaluate the sensitivity and specificity of the assay performed on 60 and 300 individuals, respectively.
+The horizontal dashed line indicates the nominal upper error rate, 2.5\%.
+Colored dashed lines are estimates from a logistic regression model using cubic splines.}
+\label{fig:imperfect_upper_error_frequency_8000_groups_0_005_prev}
+\end{figure}
+
+\begin{figure}
+\centering
+\includegraphics[width=0.8\textwidth]{figures/imperfect_upper_error_frequency_50_groups_0_05_prev.pdf}
+\caption{Upper error properties for the two melded confidence interval procedures, WprevSeSp Binomial and WprevSeSp Poisson, and one method, wspoissonTest, which does not account for the imperfect assay.
+Each point represents 10,000 simulations of datasets from a population with 5\% Prevalence where 50 groups of 200 people are sampled.
+Each datasets also includes simulated results of tests to evaluate the sensitivity and specificity of the assay performed on 60 and 300 individuals, respectively.
+The horizontal dashed line indicates the nominal upper error rate, 2.5\%.
+Colored dashed lines are estimates from a logistic regression model using cubic splines.}
 \label{fig:imperfect_upper_error_frequency_50_groups_0_05_prev}
@@
 \centering
-\includegraphics[width=\textwidth]{figures/imperfect_upper_error_frequency_8000_groups_0_005_prev.pdf}
-\caption{Caption}
-\label{fig:imperfect_upper_error_frequency_8000_groups_0_005_prev}
-\end{figure}
-
-\begin{figure}
-\centering
-\includegraphics[width=\textwidth]{figures/imperfect_upper_error_frequency_8000_groups_0_05_prev.pdf}
-\caption{Caption}
+\includegraphics[width=0.8\textwidth]{figures/imperfect_upper_error_frequency_8000_groups_0_05_prev.pdf}
+\caption{Upper error properties for the two melded confidence interval procedures, WprevSeSp Binomial and WprevSeSp Poisson, and one method, wspoissonTest, which does not account for the imperfect assay.
+Each point represents 10,000 simulations of datasets from a population with 5\% Prevalence where 8000 individuals are sampled.
+Each datasets also includes simulated results of tests to evaluate the sensitivity and specificity of the assay performed on 60 and 300 individuals, respectively.
+The horizontal dashed line indicates the nominal upper error rate, 2.5\%.
+Colored dashed lines are estimates from a logistic regression model using cubic splines.}
 \label{fig:imperfect_upper_error_frequency_8000_groups_0_05_prev}
@@
 
-\begin{figure}
-\centering
-\includegraphics[width=\textwidth]{figures/perfect_coverage_50_groups_0_005_prev.pdf}
-\caption{Caption}
-\label{fig:perfect_coverage_50_groups_0_005_prev}
-\end{figure}
-
-\begin{figure}
-\centering
-\includegraphics[width=\textwidth]{figures/perfect_coverage_50_groups_0_05_prev.pdf}
-\caption{Caption}
-\label{fig:perfect_coverage_50_groups_0_05_prev}
-\end{figure}
-
-\begin{figure}
-\centering
-\includegraphics[width=\textwidth]{figures/perfect_coverage_8000_groups_0_005_prev.pdf}
-\caption{Caption}
-\label{fig:perfect_coverage_8000_groups_0_005_prev}
-\end{figure}
-
-\begin{figure}
-\centering
-\includegraphics[width=\textwidth]{figures/perfect_coverage_8000_groups_0_05_prev.pdf}
-\caption{Caption}
-\label{fig:perfect_coverage_8000_groups_0_05_prev}
-\end{figure}
-
-\begin{figure}
-\centering
-\includegraphics[width=\textwidth]{figures/perfect_lower_error_frequency_50_groups_0_005_prev.pdf}
-\caption{Caption}
-\label{fig:perfect_lower_error_frequency_50_groups_0_005_prev}
-\end{figure}
-
-\begin{figure}
-\centering
-\includegraphics[width=\textwidth]{figures/perfect_lower_error_frequency_50_groups_0_05_prev.pdf}
-\caption{Caption}
-\label{fig:perfect_lower_error_frequency_50_groups_0_05_prev}
-\end{figure}
-
-\begin{figure}
-\centering
-\includegraphics[width=\textwidth]{figures/perfect_lower_error_frequency_8000_groups_0_005_prev.pdf}
-\caption{Caption}
-\label{fig:perfect_lower_error_frequency_8000_groups_0_005_prev}
-\end{figure}
-
-\begin{figure}
-\centering
-\includegraphics[width=\textwidth]{figures/perfect_lower_error_frequency_8000_groups_0_05_prev.pdf}
-\caption{Caption}
-\label{fig:perfect_lower_error_frequency_8000_groups_0_05_prev}
-\end{figure}
-
-\begin{figure}
-\centering
-\includegraphics[width=\textwidth]{figures/perfect_upper_error_frequency_50_groups_0_005_prev.pdf}
-\caption{Caption}
-\label{fig:perfect_upper_error_frequency_50_groups_0_005_prev}
-\end{figure}
-
-\begin{figure}
-\centering
-\includegraphics[width=\textwidth]{figures/perfect_upper_error_frequency_50_groups_0_05_prev.pdf}
-\caption{Caption}
-\label{fig:perfect_upper_error_frequency_50_groups_0_05_prev}
-\end{figure}
-
-\begin{figure}
-\centering
-\includegraphics[width=\textwidth]{figures/perfect_upper_error_frequency_8000_groups_0_005_prev.pdf}
-\caption{Caption}
-\label{fig:perfect_upper_error_frequency_8000_groups_0_005_prev}
-\end{figure}
-
-\begin{figure}
-\centering
-\includegraphics[width=\textwidth]{figures/perfect_upper_error_frequency_8000_groups_0_05_prev.pdf}
-\caption{Caption}
-\label{fig:perfect_upper_error_frequency_8000_groups_0_05_prev}
-\end{figure}
-
-\begin{figure}
-\centering
-\includegraphics[width=\textwidth]{figures/simple_coverage_comparison_plot.pdf}
-\caption{Caption}
-\label{fig:simple_coverage_comparison_plot}
-\end{figure}
-
-\begin{figure}
-\centering
-\includegraphics[width=\textwidth]{figures/simple_coverage_error_comparison_plot.pdf}
-\caption{Caption}
-\label{fig:simple_coverage_error_comparison_plot}
-\end{figure}
-
-\begin{figure}
-\centering
-\includegraphics[width=\textwidth]{figures/simple_lower_error_frequency_comparison_plot.pdf}
-\caption{Caption}
-\label{fig:simple_lower_error_frequency_comparison_plot}
-\end{figure}
-
-\begin{figure}
-\centering
-\includegraphics[width=\textwidth]{figures/simple_upper_error_frequency_comparison_plot.pdf}
-\caption{Caption}
-\label{fig:simple_upper_error_frequency_comparison_plot}
-\end{figure}
+% \begin{figure}
+% \centering
+% \includegraphics[width=0.8\textwidth]{figures/simple_coverage_error_comparison_plot.pdf}
+% \caption{Caption}
+% \label{fig:simple_coverage_error_comparison_plot}
+% \end{figure}
 

### 2021-11-22 code/simulations/confidence_interval_perfect_assay/combine_fixed_weights_many_arrayjob.R
Results with CI details

@@ -1,5 +1,46 @@
 library(tidyverse)
 library(fs)
+
+tibble(file_path = dir_ls("~/PrevAdjSurvey/code/simulations/confidence_interval_perfect_assay"))
+
+
+dir_ls("~/PrevAdjSurvey/code/simulations/confidence_interval_perfect_assay") %>%
+  enframe(name = NULL) %>%
+  filter(str_starts(path_file(value), "slurm")) %>%
+  deframe() %>%
+  file_delete()
+
+
+perfect_assay_raw_vec <-
+  combined_imperfect_assay_raw <-
+  tibble(file_path = dir_ls("//data/bayerdm/confidence_interval_perfect_assay")) %>%
+  mutate(file_name = file_path %>% path_file() %>% path_ext_remove()) %>%
+  filter(str_detect(file_name, "raw")) %>%
+  arrange(file_name) %>%
+  pull(file_path)
+
+combined_perfect_assay_raw <-
+  map_dfr(perfect_assay_raw_vec[350:400],
+          ~read_rds(.) %>%
+            mutate(width = conf_int_2 - conf_int_1) %>%
+            group_by(design, method) %>%
+            summarize(conf_int_1 = mean(conf_int_1),
+                      conf_int_2 = mean(conf_int_2),
+                      width = mean(width),
+                      lower_error_freq = mean(lower_error),
+                      upper_error_freq = mean(upper_error),
+                      coverage = mean(covered), .groups = "drop"))
+
+write_csv(combined_perfect_assay_raw, "~/PrevAdjSurvey/code/simulations/confidence_interval_perfect_assay/combined_perfect_assay_raw.csv")
+
+cat(setdiff(1:400, fnisihed_files), sep = ", ")
+
+fnisihed_files <- dir_ls("/data/bayerdm/confidence_interval_perfect_assay/") %>%
+  enframe(name = NULL) %>%
+  mutate(file_name = path_file(value)) %>%
+  filter(str_starts(file_name, "results_raw")) %>%
+  mutate(file_num = as.integer(str_sub(file_name, 13, 16))) %>% pull(file_num)
+range(fnisihed_files)
 tmp <-
 tibble(file_path = dir_ls("//data/bayerdm/fixed_weights_many")) %>%
   mutate(file_name = file_path %>% path_file() %>% path_ext_remove()) %>%

### 2021-11-22 code/simulations/confidence_interval_perfect_assay/combine_imperfect_assay_arrayjob.R

@@ -1,0 +1,60 @@
+library(tidyverse)
+library(fs)
+
+imperfect_assay_raw_vec <-
+  combined_imperfect_assay_raw <-
+  tibble(file_path = dir_ls("//data/bayerdm/confidence_interval_imperfect_assay")) %>%
+  mutate(file_name = file_path %>% path_file() %>% path_ext_remove()) %>%
+  filter(str_detect(file_name, "raw")) %>%
+  arrange(file_name) %>%
+  pull(file_path)
+
+combined_imperfect_assay_raw <-
+  map_dfr(imperfect_assay_raw_vec,
+          ~read_rds(.) %>%
+            mutate(width = conf_int_2 - conf_int_1) %>%
+            group_by(design, method) %>%
+            summarize(conf_int_1 = mean(conf_int_1),
+                      conf_int_2 = mean(conf_int_2),
+                      width = mean(width),
+                      lower_error_freq = mean(lower_error),
+                      upper_error_freq = mean(upper_error),
+                      coverage = mean(covered), .groups = "drop"))
+combined_imperfect_assay_raw
+
+write_csv(combined_imperfect_assay_raw, "~/PrevAdjSurvey/code/simulations/confidence_interval_imperfect_assay/combined_imperfect_assay_raw.csv")
+
+
+combined_imperfect_assay_summary <-
+  tibble(file_path = dir_ls("//data/bayerdm/confidence_interval_imperfect_assay")) %>%
+  mutate(file_name = file_path %>% path_file() %>% path_ext_remove()) %>%
+  filter(str_detect(file_name, "summary")) %>%
+  arrange(file_name) %>%
+  mutate(data = map(file_path, read_rds)) %>%
+  pull(data) %>%
+  bind_rows()
+
+combined_imperfect_assay_summary
+
+write_csv(combined_imperfect_assay_summary, "~/PrevAdjSurvey/code/simulations/confidence_interval_imperfect_assay/combined_imperfect_assay_summary.csv")
+
+experimental_design <-read_rds("//data/bayerdm/confidence_interval_imperfect_assay/experimental_design.rds")
+experimental_design %>% select_if(~!is.list(.)) %>% write_csv("~/PrevAdjSurvey/code/simulations/confidence_interval_imperfect_assay/experimental_design.csv")
+
+
+dir_ls("~/PrevAdjSurvey/code/simulations/confidence_interval_imperfect_assay") %>%
[…]

### 2021-11-22 code/simulations/confidence_interval_perfect_assay/perfect_assay_arrayjob.sh

@@ -5,7 +5,7 @@
 #SBATCH --ntasks-per-core=1
 #SBATCH --time=1:00:00
 #SBATCH --mem=4g
-#SBATCH --array=6-100
+#SBATCH --array=205
 #SBATCH --gres=lscratch:10
 #SBATCH --job-name="perfect"
 

### 2021-11-22 code/simulations/confidence_interval_perfect_assay/process_weights_many.R

@@ -23,31 +23,19 @@ results_summary <-
                            "Lower Error Frequency" = "lower_error_freq",
                            "Upper Error Frequency" = "upper_error_freq",
                            "Coverage" = "coverage"),
-         # method = fct_recode(method,
-         #                     "Agresti-Coull (Unadjusted)" = "AC",
-         #                     "Agresti-Coull (Adjusted)" = "AC_adjusted",
-         #                     "Clopper-Pearson (Unadjusted)" = "CP",
-         #                     "Clopper-Pearson (Adjusted)" = "CP_adjusted",
-         #                     "wsPoisson" = "wspoissonTest",
-         #                     "wsPoisson with mid-p" = "wspoissonTest_midp"),
          method = fct_recode(method,
-                             "Agresti-Coull" = "AC",
-                             "Clopper-Pearson" = "CP",
+                             "Agresti-Coull (Unadjusted)" = "AC",
+                             "Agresti-Coull (Adjusted)" = "AC_adjusted",
+                             "Clopper-Pearson (Unadjusted)" = "CP",
+                             "Clopper-Pearson (Adjusted)" = "CP_adjusted",
                              "wsPoisson" = "wspoissonTest",
                              "wsPoisson with mid-p" = "wspoissonTest_midp"),
          group_distribution = group_distribution %>%
            fct_relevel("high", "uniform", "low") %>%
            fct_relabel(str_to_title))
 
-
-
 rm(ed1, ed2, sum1, sum2)
 
-desired_prop_groups_with_prev <- c(0.05, 0.25, 0.75)
-
-results_summary <- results_summary %>%
-  filter(prop_groups_with_prev %in% desired_prop_groups_with_prev,
-         method != "wsPoisson with mid-p")
 
 generate_plot <- function(name_to_plot, n_groups_to_plot, prev_to_plot){
   group_size <- if_else(n_groups_to_plot == 8000, 1, 200)
@@ -97,7 +85,7 @@ generate_plot <- function(name_to_plot, n_groups_to_plot, prev_to_plot){
 
 generate_plot(name_to_plot = "Coverage", n_groups_to_plot = 50, prev_to_plot = 0.005)
 
-
+.Last.value$plot[[1]]
 results_summary %>%
   select(n_groups, name, prev) %>%
   distinct() %>%
@@ -106,12 +94,6 @@ results_summary %>%
     ~generate_plot(name_to_plot = ..1,
                    n_groups_to_plot = ..2,
[…]

### 2021-11-24 code/simulations/confidence_interval_perfect_assay/process_weights_many.R
CI Width Figures

@@ -4,37 +4,30 @@ library(glue)
 library(cowplot)
 library(fs)
 
-ed1 <- read_csv("code/simulations/confidence_interval_perfect_assay/experimental_design.csv")
-ed2 <- read_csv("code/simulations/confidence_interval_perfect_assay/005_prev_experimental_design.csv")
-sum1 <- read_csv("code/simulations/confidence_interval_perfect_assay/combined_fixed_weights_many_summary.csv")
-sum2 <- read_csv("code/simulations/confidence_interval_perfect_assay/combined_fixed_weights_many_summary_005.csv")
 
 results_summary <-
-  left_join(sum1, ed1) %>%
-  mutate(group_distribution = case_when( # Error because I labeled things wrong when setting up ex design
-    group_distribution == "low" ~ "high",
-    group_distribution == "high" ~ "low",
-    group_distribution == "uniform" ~ "uniform"
-  )) %>%
-  bind_rows(left_join(sum2, ed2) %>%
-              mutate(design = design + max(ed1$design))) %>%
-  pivot_longer(cols = c(lower_error_freq, upper_error_freq, coverage)) %>%
+  read_csv("code/simulations/confidence_interval_perfect_assay/combined_perfect_assay_raw.csv") %>%
+  left_join(read_rds("code/simulations/confidence_interval_perfect_assay/experimental_design.rds") %>%
+              select_if(~!is.list(.))) %>%
+  mutate(method = str_remove(method, "_result")) %>%
+  pivot_longer(cols = c(conf_int_1, conf_int_2, width, lower_error_freq, upper_error_freq, coverage)) %>%
   mutate(name = fct_recode(name,
                            "Lower Error Frequency" = "lower_error_freq",
                            "Upper Error Frequency" = "upper_error_freq",
-                           "Coverage" = "coverage"),
-         method = fct_recode(method,
+                           "Coverage" = "coverage",
+                           "Lower Confidence Limit" = "conf_int_1",
+                           "Upper Confidence Limit" = "conf_int_2",
+                           "Confidence Interval Width" = "width")) %>%
+  mutate(method = fct_recode(method,
                              "Agresti-Coull (Unadjusted)" = "AC",
                              "Agresti-Coull (Adjusted)" = "AC_adjusted",
[…]

### 2021-11-24 PrevAdjSurvey.tex
Updates from Overleaf

@@
 
-where \( w_i = N_i / \sum_{j=1}^n N_j \) and, therefore, \( \sum_{i=1}^k w_i = 1 \).
+where \( w_i = N_i / \sum_{j=1}^k N_j \) and, therefore, \( \sum_{i=1}^k w_i = 1 \).
 
@@
 \begin{equation}
-    \hat{\beta}^* = \frac{\sum_{i=1}^k w_i \hat{\theta}_i}{\hat{\phi}_p - \hat{\phi}_n} - \frac{\hat{\phi}_n}{\hat{\phi}_p - \hat{\phi}_n}.
+    \hat{\beta}^* = \frac{\sum_{i=1}^k w_i \hat{\theta}_i}{\hat{\phi}_p - \hat{\phi}_n} - \frac{\hat{\phi}_n}{\hat{\phi}_p - \hat{\phi}_n}. \label{eq:betastarhat}
 \end{equation}
@@
 We develop a confidence interval for the population prevalence, \( \beta^* \).
-Because \( k = 1 \), the estimator in Equation~\ref{eq:long-beta} becomes
+When \( k = 1 \), the estimand in Equation~\ref{eq:long-beta} becomes $\beta^* = (\theta_1 - \phi_n)/(\phi_p-\phi_n)$.
+We have $\phi_p > \phi_n$ for any useful assay, and when the sample is a mixture of individuals with and without the disease of interest, $\phi_p > \theta_1 > \phi_n$.
+The estimator of $\beta^*$ is
+%in Equation~\ref{eq:betastarhat} becomes
 
 \begin{equation}
-\hat{\beta}^* = \frac{\hat{\theta}_1 - \hat{\phi}_n}{\hat{\phi}_p - \hat{\phi}_n}.
+\hat{\beta}^* \equiv 
+g(\hat{\theta}_1, \hat{\phi}_n, \hat{\phi}_p)
+\equiv 
+\left\{ 
+\begin{array}{ll}
+1 & \mbox{ if $\hat{\phi}_n < \hat{\phi}_p \leq \hat{\theta}_1$ }  \\
+\frac{\hat{\theta}_1 - \hat{\phi}_n}{\hat{\phi}_p - \hat{\phi}_n} & 
+\mbox{ if $\hat{\phi}_p > \hat{\theta}_1 > \hat{\phi}_n$ } \\
+0 & \mbox{ otherwise} 
+\end{array}
+\right.
 \label{eq:srs-beta-est}
 \end{equation}
+where we define $0/0=0$.
+% Damon, that definition is arbitrary, it is just used so that everything is defined
 
 To create a confidence interval for \( \hat{\beta}^* \), we use a generalization of the melding method \cite{FayP:2015}, which makes use of lower and upper confidence distributions on functions of independent estimators to account for variability in \( \hat{\theta}_1 \), \( \hat{\phi}_n \), and \( \hat{\phi}_p \).
+Confidence distributions are like frequentist posterior distributions
+\cite{}.
+The lower and upper confidence distributions are used with discrete responses to ensure the validity of the resulting inferences, and for the binomial case they are equivalent to the posterior distributions that result from using well-calibrated null preference priors \cite{}.
 
@@
 For a binomial experiment with \( x \) successes out of \( n \) trials, the lower confidence distribution \( (B^L) \) is \( \operatorname{Beta}(x, n - x + 1) \), and the upper confidence distribution \( (B^U) \) is \( \operatorname{Beta}(x + 1, n - x)\).
+Let \( q(a, W) \) be the \( a \)th quantile of a random variable \( W \). Then the exact \( a \)\% central confidence interval of Clopper-Pearson for the binomial parameter is 
+\[
+\left\{ q \left( \frac{1-a}{2}, B^L \right), q \left( \frac{1+a}{2}, B^U \right\}.
+\]
 
-Let \( q(a, W) \) be the \( a \)th quantile of a random variable \( W \).
-
+Fay et al \cite{FayP:2015} proposed a method for obtaining confidence intervals for functions of two parameters that are monotonic within the allowable range  for each parameter given the other is fixed.
+Here we generalize that to $\beta^*$, which is a function of 3 parameters.
+When $1 \geq \phi_p > \theta_1 > \phi_n \geq 0$ then $\beta^*$ is monotonically increasing in $\theta_1$, monotonically decreasing in $\phi_p$, and monotonically decreasing in $\phi_n$.
 Then the \( a \)\% confidence interval for \( \beta^* \) is
@@
 \begin{equation}
-    \left\{ q \left( \frac{1 - a}{2}, \frac{B_{\theta_1}^L - B_{\phi_n}^L }{B_{\phi_p}^U - B_{\phi_n}^L }  \right),  q \left( \frac{1 + a}{2}, \frac{B_{\theta_1}^U - B_{\phi_n}^U}{B_{\phi_p}^L - B_{\phi_n}^U}  \right) \right\}.
+    \left\{ q \left( \frac{1 - a}{2}, g \left\{ B_{\theta_1}^L, B_{\phi_n}^U, B_{\phi_p}^U \right\}   \right),  
+            q \left( \frac{1 + a}{2},  g \left\{ B_{\theta_1}^U, B_{\phi_n}^L, B_{\phi_p}^L \right\}   \right) \right\}.
 \label{eq:srs-conf-int}
@@
 
-% \begin{figure}
-% \centering
-% \includegraphics[width=0.8\textwidth]{figures/simple_coverage_error_comparison_plot.pdf}
-% \caption{Caption}
-% \label{fig:simple_coverage_error_comparison_plot}
-% \end{figure}
-
 \end{document}

### 2021-11-24 code/simulations/confidence_interval_imperfect_assay/process_imperfect_assay_arrayjob.R
Add Panel Borders to plot

@@ -67,7 +67,8 @@ generate_plot_2 <- function(name_to_plot, n_groups_to_plot, prev_to_plot){
     scale_x_continuous(name = "Weight Coefficient of Variation", labels = scales::percent) +
     scale_y_continuous(name = name_to_plot, label = ~percent(., accuracy = 1)) +
     scale_color_discrete(name = "Method") +
-    theme(legend.position = "bottom") +
+    theme(legend.position = "bottom",
+          panel.border = element_rect(color = "black", fill = NA, size = 1)) +
     ggtitle(label = glue("{name_to_plot} Properties for Simulations with {percent(prev_to_plot, accuracy = 0.1)} Prevalence Among {comma(n_groups_to_plot)} Groups of {comma(group_size)}"),
             subtitle = "Each Facet = 95% Sensitivity, Each Point = 10,000 Replications")
   generated_plot

### 2021-11-24 code/simulations/confidence_interval_perfect_assay/process_weights_many.R

@@ -71,7 +71,8 @@ generate_plot <- function(name_to_plot, n_groups_to_plot, prev_to_plot){
     scale_x_continuous(name = "Weight Coefficient of Variation") +
     scale_y_continuous(name = name_to_plot, label = ~percent(., accuracy = 1)) +
     scale_color_discrete(name = "Method") +
-    theme(legend.position = "bottom") +
+    theme(legend.position = "bottom",
+          panel.border = element_rect(color = "black", fill = NA, size = 1)) +
     ggtitle(label = glue("{name_to_plot} Properties for Simulations with {percent(prev_to_plot, accuracy = 0.1)} Prevalence Among {comma(n_groups_to_plot)} Groups of {comma(group_size)}"),
             subtitle = "Each Point = 10,000 Replications")
   generated_plot

### 2021-11-24 PrevAdjSurvey.tex
Updates from Overleaf

@@
 
+\begin{figure}
+\centering
+\includegraphics[width=0.8\textwidth]{figures/perfect_confidence_interval_width_50_groups_0_005_prev}
+\caption{CAPTION HERE.}
+\label{fig:perfect_confidence_interval_width_50_groups_0_005_prev}
+\end{figure}
+
+\begin{figure}
+\centering
+\includegraphics[width=0.8\textwidth]{figures/perfect_confidence_interval_width_50_groups_0_05_prev}
+\caption{CAPTION HERE.}
+\label{fig:perfect_confidence_interval_width_50_groups_0_05_prev}
+\end{figure}
+
+\begin{figure}
+\centering
+\includegraphics[width=0.8\textwidth]{figures/perfect_confidence_interval_width_8000_groups_0_005_prev}
+\caption{CAPTION HERE.}
+\label{fig:perfect_confidence_interval_width_8000_groups_0_005_prev}
+\end{figure}
+
+\begin{figure}
+\centering
+\includegraphics[width=0.8\textwidth]{figures/perfect_confidence_interval_width_8000_groups_0_05_prev}
+\caption{CAPTION HERE.}
+\label{fig:perfect_confidence_interval_width_8000_groups_0_05_prev}
+\end{figure}
+
 % Start of Imperfect
@@
 
+\begin{figure}
+\centering
+\includegraphics[width=0.8\textwidth]{figures/imperfect_confidence_interval_width_50_groups_0_005_prev}
+\caption{CAPTION HERE.}
+\label{fig:imperfect_confidence_interval_width_50_groups_0_005_prev}
+\end{figure}
+
+\begin{figure}
+\centering
+\includegraphics[width=0.8\textwidth]{figures/imperfect_confidence_interval_width_50_groups_0_05_prev}
+\caption{CAPTION HERE.}
+\label{fig:imperfect_confidence_interval_width_50_groups_0_05_prev}
+\end{figure}
+
+\begin{figure}
+\centering
+\includegraphics[width=0.8\textwidth]{figures/imperfect_confidence_interval_width_8000_groups_0_005_prev}
+\caption{CAPTION HERE.}
+\label{fig:imperfect_confidence_interval_width_8000_groups_0_005_prev}
+\end{figure}
+
+\begin{figure}
+\centering
+\includegraphics[width=0.8\textwidth]{figures/imperfect_confidence_interval_width_8000_groups_0_05_prev}
+\caption{CAPTION HERE.}
+\label{fig:imperfect_confidence_interval_width_8000_groups_0_05_prev}
+\end{figure}
+
 \end{document}

### 2021-11-29 code/simulations/confidence_interval_perfect_assay/process_weights_many.R
Fix Perfect Plots

@@ -18,13 +18,18 @@ results_summary <-
                            "Lower Confidence Limit" = "conf_int_1",
                            "Upper Confidence Limit" = "conf_int_2",
                            "Confidence Interval Width" = "width")) %>%
+  # mutate(method = fct_recode(method,
+  #                            "Agresti-Coull (Unadjusted)" = "AC",
+  #                            "Agresti-Coull (Adjusted)" = "AC_adjusted",
+  #                            "Clopper-Pearson (Unadjusted)" = "CP",
+  #                            "Clopper-Pearson (Adjusted)" = "CP_adjusted",
+  #                            "wsPoisson" = "wspoissonTest",
+  #                            "wsPoisson with mid-p" = "wspoissonTest_midp")) %>%
+  filter(method != "wspoissonTest_midp") %>%
   mutate(method = fct_recode(method,
-                             "Agresti-Coull (Unadjusted)" = "AC",
-                             "Agresti-Coull (Adjusted)" = "AC_adjusted",
-                             "Clopper-Pearson (Unadjusted)" = "CP",
-                             "Clopper-Pearson (Adjusted)" = "CP_adjusted",
-                             "wsPoisson" = "wspoissonTest",
-                             "wsPoisson with mid-p" = "wspoissonTest_midp")) %>%
+                             "Agresti-Coull" = "AC",
+                             "Clopper-Pearson" = "CP",
+                             "wsPoisson" = "wspoissonTest")) %>%
   mutate(group_distribution = group_distribution %>%
            fct_relevel("high", "uniform", "low") %>%
            fct_relabel(str_to_title))

### 2021-11-29 PrevAdjSurvey.tex

@@
 
+\subsection{Notation and Problem Set-up}
+
+To introduce notation, consider first the stratified simple random sample.
 Suppose we have a survey with  \( k \) sampling units, with \( N_1, N_2, \ldots, N_k \) individuals in the population of unit \( i \).
@@
 where \( w_i = N_i / \sum_{j=1}^k N_j \) and, therefore, \( \sum_{i=1}^k w_i = 1 \).
+This set-up will work for other complex survey samples, where we can treat the survey weights as known.
 
-Suppose the assay is measured on \( m_n \) individuals known to not have the disease and on \( m_p \) individuals known to have have the disease.
-Let \( C_n \) and \( C_p \) be the number who test positive from the respective samples.
-Assume that the negative and positive controls act like simple random samples from their respective populations.
-Thus, \( C_n \sim \operatorname{Binomial}(m_n, \phi_n) \) where \( 1 - \phi_n \) is the specificity of the assay, and \( C_p \sim \operatorname{Binomial}(m_p, \phi_p) \), where  \( \phi_p \) is the sensitivity of the assay.
-
-Note the relationship between these parameters:
-
+We can relate $\theta_i$ and $\theta_i^*$ using the sensitivity ($\phi_p$)  and specificity (1-$\phi_n$) of the assay, 
+where  $\phi_p$ and $\phi_n$  are the proportion of positive assays from a population of  positive controls (i.e., individuals known to have the disease) and 
+negative controls (i.e., individuals known to be  without the disease), respectively. Then
+$\theta_i = \phi_p \theta_i^* + (1-\phi_n) (1-\theta_i^*)$, or equivalently,  
+\begin{eqnarray*}
+\theta_i^* & = & \frac{ \theta_i - \phi_n }{\phi_p - \phi_n},
+\end{eqnarray*}
+and we have
 \begin{align}
@@
 
-Let \( \hat{\theta}_i = \frac{X_i}{n_i} \), \( \hat{\phi}_n = 1 - \frac{C_n}{m_n} \), and \( \hat{\phi}_p = \frac{C_p}{m_p} \).
-Then a natural estimator for \( \beta^* \) is
-
+Suppose the assay is measured on \( m_n \) individuals known to not have the disease and on \( m_p \) individuals known to have the disease.
+Let \( C_n \) and \( C_p \) be the number who test positive from the respective samples.
+Assume that the negative and positive controls act like simple random samples from their respective populations.
+Thus, \( C_n \sim \operatorname{Binomial}(m_n, \phi_n) \) where \( 1 - \phi_n \) is the specificity of the assay, and \( C_p \sim \operatorname{Binomial}(m_p, \phi_p) \), where  \( \phi_p \) is the sensitivity of the assay.
+Let \( \hat{\theta}_i = \frac{X_i}{n_i} \), \( \hat{\phi}_n = \frac{C_n}{m_n} \), and \( \hat{\phi}_p = \frac{C_p}{m_p} \).
+Then a plug-in estimator for \( \beta^* \) is 
 \begin{equation}
@@
 
-First, we consider the scenario0 \( k = 1 \), \( \phi_n > 0 \), and \( \phi_p < 1 \).
+First, we consider the scenario where \( k = 1 \), \( \phi_n > 0 \), and \( \phi_p < 1 \).
 We develop a confidence interval for the population prevalence, \( \beta^* \).
 When \( k = 1 \), the estimand in Equation~\ref{eq:long-beta} becomes $\beta^* = (\theta_1 - \phi_n)/(\phi_p-\phi_n)$.
-We have $\phi_p > \phi_n$ for any useful assay, and when the sample is a mixture of individuals with and without the disease of interest, $\phi_p > \theta_1 > \phi_n$.
+We have $\phi_p > \phi_n$ for any useful assay, and when the sample is a mixture of individuals with and without the disease of interest, $\phi_p \geq \theta_1 \geq \phi_n$.
 The estimator of $\beta^*$ is
@@
 \begin{array}{ll}
-1 & \mbox{ if $\hat{\phi}_n < \hat{\phi}_p \leq \hat{\theta}_1$ }  \\
+1 & \mbox{ if $\hat{\phi}_n < \hat{\phi}_p < \hat{\theta}_1$ }  \\
 \frac{\hat{\theta}_1 - \hat{\phi}_n}{\hat{\phi}_p - \hat{\phi}_n} & 
-\mbox{ if $\hat{\phi}_p > \hat{\theta}_1 > \hat{\phi}_n$ } \\
+\mbox{ if $\hat{\phi}_p \geq \hat{\theta}_1 \geq \hat{\phi}_n$ } \\
 0 & \mbox{ otherwise} 
@@
 Let \( q(a, W) \) be the \( a \)th quantile of a random variable \( W \). Then the exact \( a \)\% central confidence interval of Clopper-Pearson for the binomial parameter is 
-\[
+\begin{equation}
 \left\{ q \left( \frac{1-a}{2}, B^L \right), q \left( \frac{1+a}{2}, B^U \right\}.
-\]
+\label{eq:C-P}
+\end{equation}
 
@@
 \end{equation}
+where $g(\cdot)$ is defined in equation~\ref{eq:srs-beta-est}.
 
-\todo[inline]{Can Mike provide some explanation for the form of this interval? Or some citation? Does it follow from Fay, Proschan, and Brittain (2015), or is there an intermediate reference?}
+%\todo[inline]{Can Mike provide some explanation for the form of this interval? Or some citation? Does it follow from Fay, Proschan, and Brittain (2015), or is there an intermediate reference?}
 
 The quantiles of these melded distributions are calculated by Monte Carlo sampling from each of the component distributions.
-We compare this method to one described in \cite{Lang:2014} as implemented in prevSeSp function in \cite{asht}, which provides approximate confidence intervals for true prevalence when sensitivity and specificity are estimated from independent samples, as they are in the in this section.
-
-This interval is given by
+We compare this method to one described in Lang and Reiczigel \cite{Lang:2014} as implemented in prevSeSp function in \cite{asht}, which provides approximate confidence intervals for true prevalence when sensitivity and specificity are estimated from independent samples, as they are  in this section.
+The Lang-Reiczigel interval is given by
 \begin{equation}
@@
 Next, we present a confidence interval for the population prevalence, \( \beta^* \), in the scenario \( k > 1 \), \( \phi_n = 0 \), \( \phi_p = 1 \).
-Our method is a straightforward adaptation of the one presented in \cite{FayF:1997}, which was developed to create confidence intervals for a population rate which is assumed to a weighted sum of Poisson rate parameters.
+Our method is a straightforward adaptation of the gamma confidence interval presented in Fay and Feuer\cite{FayF:1997}, which was developed to create confidence intervals for a population rate which is assumed to a weighted sum of Poisson rate parameters.
 We note that for sufficiently large sample size \( n \) and small rate \( \lambda \), a \( \operatorname{Poisson}(n\lambda) \) distribution is approximately equal in distribution to a \( \operatorname{Binomial}(n, \lambda) \) distribution.
-\todo[inline]{Is this a good enough justification? We certainly don't have a large sample size, but we do have small rates.}
-Under this assumption, we suggest the \( a \)\% confidence interval for \( \beta^* \):
+\todo[inline]{Is this a good enough justification? We certainly don't have a large sample size, but we do have small rates. Mike: It seems good enough to me.}
+Under this Poisson assumption, we suggest the \( a \)\% gamma confidence interval for \( \beta^* \):
 
@@
 
-Where
+where
 
-\begin{equation}
+\begin{equation*}
     G_{\beta^*}^L \sim \operatorname{Gamma}\left( \frac{y^2}{v}, \frac{v}{y} \right)
-\end{equation}
+\end{equation*}
 
-\begin{equation}
+\begin{equation*}
     G_{\beta^*}^U \sim \operatorname{Gamma}\left( \frac{y^{*2}}{v^*}, \frac{v^*}{y^*} \right)
-\end{equation}
+\end{equation*}
 
-\begin{equation}
+\begin{equation*}
     y = \sum_{i=1}^k \frac{w_i}{n_i} x_i
-\end{equation}
+\end{equation*}
 
-\begin{equation}
+\begin{equation*}
     v = \sum_{i=1}^k \left( \frac{w_i}{n_i}\right)^2 x_i
-\end{equation}
+\end{equation*}
 
-\begin{equation}
+\begin{equation*}
     y^* = y + \max\left(\frac{w_1}{n_1}, \ldots, \frac{w_k}{n_k} \right)
-\end{equation}
+\end{equation*}
 
-\begin{equation}
+\begin{equation*}
     v^* = v + \left\{ \max\left(\frac{w_1}{n_1}, \ldots, \frac{w_k}{n_k} \right) \right\}^2
-\end{equation}
+\end{equation*}
 
-We compare this confidence interval to two methods presented in \cite{Dean:2015}, which were recommended for scenarios with low prevalence.
+We call this the wsPoison method, since it assumes a weighted sum of Poissons.
+We compare the wsPoisson confidence interval to two methods presented in Dean and Pagano\cite{Dean:2015}, which were recommended for scenarios with low prevalence.
 
-The first of these is an adaptation of \cite{AgrestiCoull} for the survey setting.
+The first of these is an adaptation of the method of Agresti and Coull\cite{AgrestiCoull} for the survey setting.
 The interval for \( \beta^* \) is given by:
@@
 
-\begin{equation}
+\begin{equation*}
    \tilde{x} = \left( \sum_{i=1}^k w_i \hat{\theta}_i \right) n_{\text{eff}} + c 
-\end{equation}
+\end{equation*}
 
-\begin{equation}
+\begin{equation*}
    \tilde{n} = n_{\text{eff}} + 2c 
-\end{equation}
+\end{equation*}
 
-\begin{equation}
+\begin{equation*}
     \tilde{p} = \tilde{x} / \tilde{n}
-\end{equation}
+\end{equation*}
 
-\begin{equation}
+\begin{equation*}
    c = q\left( \frac{1 + a}{2}, Z \right)^2/2
-\end{equation}
+\end{equation*}
 
@@
 
-We also compare our suggested method to a modification of \cite{Korn:1998} presented in \cite{Dean:2015}.
+We also compare our suggested method to a modification of the method of Korn and Graubard\cite{Korn:1998} presented in \cite{Dean:2015}.
 This interval is given by
@@
 
-where
-
-\begin{equation}
+where analogously to the Clopper-Pearson interval (see equation~\ref{eq:C-P}),
+\begin{equation*}
     % B^L_{CP} \sim \operatorname{Beta}\left(n_{\text{eff}} \sum_{i=1}^k w_i \hat{\theta}_i, n_{\text{eff}} \left(1 -  \sum_{i=1}^k w_i \hat{\theta}_i\right) + 1\right)
     B^L_{CP} \sim \operatorname{Beta}\left(x_{\text{eff}},  n_{\text{eff}} -  x_{\text{eff}} + 1 \right)
-\end{equation}
+\end{equation*}
 
-\begin{equation}
+\begin{equation*}
     % B^U_{CP} \sim \operatorname{Beta}\left(\left(n_{\text{eff}} \sum_{i=1}^k w_i \hat{\theta}_i\right) + 1, n_{\text{eff}} \left(1 - \sum_{i=1}^k w_i \hat{\theta}_i \right)\right)
     B^U_{CP} \sim \operatorname{Beta}\left(x_{\text{eff}} + 1, n_{\text{eff}} - x_{\text{eff}} \right)
-\end{equation}
+\end{equation*}
 
@@
 \begin{equation}
-    \left\{ q \left( \frac{1 - a}{2}, \frac{G_{\beta}^L + B_{\phi_n}^L }{B_{\phi_p}^U + B_{\phi_n}^L }  \right),  q \left( \frac{1 + a}{2}, \frac{G_{\beta}^U + B_{\phi_n}^U}{B_{\phi_p}^L + B_{\phi_n}^U}  \right) \right\}.
+    \left\{ q \left( \frac{1 - a}{2}, %\frac{G_{\beta}^L + B_{\phi_n}^L }{B_{\phi_p}^U + B_{\phi_n}^L } 
+    g \left[ G^L_{\beta^*}, B^U_{\phi_n}, B^U_{\phi_p} \right]
+    \right),  q \left( \frac{1 + a}{2}, %\frac{G_{\beta}^U + B_{\phi_n}^U}{B_{\phi_p}^L + B_{\phi_n}^U}  \right) \right\}.
+       g \left[G^U_{\beta^*}, B^L_{\phi_n}, B^L_{\phi_p} \right] \right)
+       \right\}
 \end{equation}
 
-where \( G_{\beta}^L \) and \( G_{\beta}^U \) are the same as \( G_{\beta^*}^L \) and \( G_{\beta^*}^U \) as defined in Section~\ref{sec:weight-perfect}.
+where  \( G_{\beta^*}^L \) and \( G_{\beta^*}^U \) are defined in Section~\ref{sec:weight-perfect}.
 
@@
 Figure~\ref{fig:upper_error_frequency_comparison_plot} shows that both methods make upper errors with roughly the same frequency.
-Figure~\ref{fig:lower_error_frequency_comparison_plot} demonstrates that while the melding procedure leads bounds the lower error frequency below 2.5\%, the Lang-Reiczigel method is much more likely to lead to lower errors than it is to result in upper errors, which may be undesirable for applications that are particularly sensitive to making lower errors.
+Figure~\ref{fig:lower_error_frequency_comparison_plot} demonstrates that while the melding procedure leads bounds the lower error frequency below 2.5\%, the Lang-Reiczigel method generally has lower error above 2.5\%, which is undesirable for applications for which there is a need to bound the lower errors.
 
@@
 The coverage properties for these simulations are presented in Figures~\ref{fig:perfect_coverage_50_groups_0_005_prev}--\ref{fig:perfect_coverage_8000_groups_0_05_prev}.
-Additional properties for these simulations are presented in Figures~\ref{fig:perfect_lower_error_frequency_50_groups_0_005_prev}--\ref{fig:perfect_upper_error_frequency_8000_groups_0_05_prev}.
+Additional properties for these simulations are presented in Figures~\ref{fig:perfect_lower_error_frequency_50_groups_0_005_prev}--\ref{fig:perfect_confidence_interval_width_8000_groups_0_05_prev}.
 
@@
 Uniform distribution of prevalence among the weights, increased overall prevalence, and larger sample sizes among fewer groups all appear to lessen the severity of this problem.
-In contrast, the wsPoisson method tends to become more conservative when the coefficient of variation among the weights increases.
+In contrast, the wsPoisson method appears to guarantee coverage in all scenarios. The wsPoisson method tends to become more conservative when the coefficient of variation among the weights increases. 
 In all cases, the wsPoisson method is more conservative than the competitor methods.
-This is similar to the behavior observed in \cite{FayF:1997}, where, in simulations, the overall error rate decreased as the variance of the weights increased.
+This is similar to the behavior observed in Fay and Feuer\cite{FayF:1997}, where, in simulations, the overall error rate for the gamma intervals decreased as the variance of the weights increased.
 
@@
 \includegraphics[width=0.8\textwidth]{figures/perfect_coverage_8000_groups_0_05_prev.pdf}
-\caption{Coverage properties for the wsPoisson model and two standard methods, Agresti-Coull and Clopper-Pearson.
+\caption{Coverage properties for the wsPoisson model and two standard methods, Agresti-Coull and Korn-Graubard.
 Each point represents 10,000 simulations of datasets from a population with 5\% Prevalence where 8000 individuals are sampled.
@@
 
-We compare properties our melded confidence interval WprevSeSp Poisson, to anotother melded confidence interval method WprevSeSp Binomial, and one method, wspoissonTest, which does not account for the imperfect assay.
+We compare properties our melded confidence interval WprevSeSp Poisson, to another melded confidence interval method WprevSeSp Binomial, and one method, wspoissonTest, which does not account for the imperfect assay.
 The methods are assessed in a several simulated scenarios with varying levels of disease prevalence (0.5\% or 5\%), types of groups surveyed (50 groups 200 subjects or 8000 groups of 1 subject), distributions of weights among the groups (coefficient of variation from approximately 0\% to nearly 6\%), the number of groups with non-zero prevalence, and the specificity of the assay (80\% - 100\%).
@@
 The coverage properties for these simulations are presented in Figures~\ref{fig:imperfect_coverage_50_groups_0_005_prev}--\ref{fig:imperfect_coverage_8000_groups_0_05_prev}.
-Additional properties for these simulations are presented in Figures~\ref{fig:imperfect_lower_error_frequency_50_groups_0_05_prev}--\ref{fig:imperfect_upper_error_frequency_8000_groups_0_05_prev}.
+Additional properties for these simulations are presented in Figures~\ref{fig:imperfect_lower_error_frequency_50_groups_0_05_prev}--\ref{fig:imperfect_confidence_interval_width_8000_groups_0_05_prev}.
 

### 2021-11-29 PrevAdjSurvey.tex
CI Width Figure Captions

@@
 \includegraphics[width=0.8\textwidth]{figures/perfect_confidence_interval_width_50_groups_0_005_prev}
-\caption{CAPTION HERE.}
+\caption{Confidence interval width properties for the wsPoisson model and two standard methods, Agresti-Coull and Clopper-Pearson.
+Each point represents 10,000 simulations of datasets from a population with 0.5\% Prevalence where 50 groups of 200 people are sampled.
+Colored dashed lines are estimates from a logistic regression model using cubic splines.}
 \label{fig:perfect_confidence_interval_width_50_groups_0_005_prev}
@@
 \includegraphics[width=0.8\textwidth]{figures/perfect_confidence_interval_width_50_groups_0_05_prev}
-\caption{CAPTION HERE.}
+\caption{Confidence interval width properties for the wsPoisson model and two standard methods, Agresti-Coull and Clopper-Pearson.
+Each point represents 10,000 simulations of datasets from a population with 5\% Prevalence where 50 groups of 200 people are sampled.
+Colored dashed lines are estimates from a logistic regression model using cubic splines.}
 \label{fig:perfect_confidence_interval_width_50_groups_0_05_prev}
@@
 \includegraphics[width=0.8\textwidth]{figures/perfect_confidence_interval_width_8000_groups_0_005_prev}
-\caption{CAPTION HERE.}
+\caption{Confidence interval width properties for the wsPoisson model and two standard methods, Agresti-Coull and Clopper-Pearson.
+Each point represents 10,000 simulations of datasets from a population with 0.5\% Prevalence where 8000 individuals are sampled.
+Colored dashed lines are estimates from a logistic regression model using cubic splines.}
 \label{fig:perfect_confidence_interval_width_8000_groups_0_005_prev}
@@
 \includegraphics[width=0.8\textwidth]{figures/perfect_confidence_interval_width_8000_groups_0_05_prev}
-\caption{CAPTION HERE.}
+\caption{Confidence interval width properties for the wsPoisson model and two standard methods, Agresti-Coull and Clopper-Pearson.
+Each point represents 10,000 simulations of datasets from a population with 5\% Prevalence where 8000 individuals are sampled.
+Colored dashed lines are estimates from a logistic regression model using cubic splines.}
 \label{fig:perfect_confidence_interval_width_8000_groups_0_05_prev}
@@
 \includegraphics[width=0.8\textwidth]{figures/imperfect_confidence_interval_width_50_groups_0_005_prev}
-\caption{CAPTION HERE.}
+\caption{Confidence interval width properties for the two melded confidence interval procedures, WprevSeSp Binomial and WprevSeSp Poisson, and one method, wspoissonTest, which does not account for the imperfect assay.
+Each point represents 10,000 simulations of datasets from a population with 0.5\% Prevalence where 50 groups of 200 people are sampled.
+Each datasets also includes simulated results of tests to evaluate the sensitivity and specificity of the assay performed on 60 and 300 individuals, respectively.
+Colored dashed lines are estimates from a logistic regression model using cubic splines.}
 \label{fig:imperfect_confidence_interval_width_50_groups_0_005_prev}
@@
 \includegraphics[width=0.8\textwidth]{figures/imperfect_confidence_interval_width_50_groups_0_05_prev}
-\caption{CAPTION HERE.}
+\caption{Confidence interval width properties for the two melded confidence interval procedures, WprevSeSp Binomial and WprevSeSp Poisson, and one method, wspoissonTest, which does not account for the imperfect assay.
+Each point represents 10,000 simulations of datasets from a population with 5\% Prevalence where 50 groups of 200 people are sampled.
+Each datasets also includes simulated results of tests to evaluate the sensitivity and specificity of the assay performed on 60 and 300 individuals, respectively.
+Colored dashed lines are estimates from a logistic regression model using cubic splines.}
 \label{fig:imperfect_confidence_interval_width_50_groups_0_05_prev}
@@
 \includegraphics[width=0.8\textwidth]{figures/imperfect_confidence_interval_width_8000_groups_0_005_prev}
-\caption{CAPTION HERE.}
+\caption{Confidence interval width properties for the two melded confidence interval procedures, WprevSeSp Binomial and WprevSeSp Poisson, and one method, wspoissonTest, which does not account for the imperfect assay.
+Each point represents 10,000 simulations of datasets from a population with 0.5\% Prevalence where 8000 individuals are sampled.
+Each datasets also includes simulated results of tests to evaluate the sensitivity and specificity of the assay performed on 60 and 300 individuals, respectively.
+Colored dashed lines are estimates from a logistic regression model using cubic splines.}
 \label{fig:imperfect_confidence_interval_width_8000_groups_0_005_prev}
@@
 \includegraphics[width=0.8\textwidth]{figures/imperfect_confidence_interval_width_8000_groups_0_05_prev}
-\caption{CAPTION HERE.}
+\caption{Confidence interval width properties for the two melded confidence interval procedures, WprevSeSp Binomial and WprevSeSp Poisson, and one method, wspoissonTest, which does not account for the imperfect assay.
+Each point represents 10,000 simulations of datasets from a population with 5\% Prevalence where 8000 individuals are sampled.
+Each datasets also includes simulated results of tests to evaluate the sensitivity and specificity of the assay performed on 60 and 300 individuals, respectively.
+Colored dashed lines are estimates from a logistic regression model using cubic splines.}
 \label{fig:imperfect_confidence_interval_width_8000_groups_0_05_prev}

### 2021-12-07 PrevAdjSurvey.tex
Responding to Mike's comments

@@
 While estimating prevalence in complex surveys and adjusting estimates for misclassification have been well studied separately, performing both of these tasks simultaneously remains relatively unexplored.
-A recent overview of methods for estimating prevalence in surveys without misclassification is provided in \cite{Dean:2015}.
-For simple surveys with imperfect sensitivity and specificity, \cite{Lang:2014} is the most recent advancement.
-To our knowledge \cite{Kali:2021} presents the only available method for constructing frequentist confidence intervals for prevalence estimates from complex surveys while adjusting for sensitivity and specificity; however,
-this problem has previously been addressed in Bayesian literature, recently in \cite{GelmanBayes}.
+A recent overview of methods for estimating prevalence in surveys without misclassification is provided by Dean and Pagano\cite{Dean:2015}.
+For simple surveys with imperfect sensitivity and specificity, the method of Lang and Reiczigel\cite{Lang:2014} is the most recent advancement\cite{Flor2020}.
+Fewer methods are available for for constructing frequentist confidence intervals for prevalence estimates from complex surveys while adjusting for sensitivity and specificity.
+One such method, which is closely related to the method presented here is developed by Kalish et al\cite{Kali:2021}.
+Another recent advancement is developed by Rosin et al \cite{rosin2021estimating}.
+This method makes use of asymptotic normal appriximations which reduce to the Wald interval when sensitivity and specificity are perfect.
+This problem has also previously been addressed in Bayesian literature, recently by Gelman and Carpenter\cite{GelmanBayes}.
 
@@
 
-\section{Methods}
+\section{Confidence Interval Methods}
 
@@
 To create a confidence interval for \( \hat{\beta}^* \), we use a generalization of the melding method \cite{FayP:2015}, which makes use of lower and upper confidence distributions on functions of independent estimators to account for variability in \( \hat{\theta}_1 \), \( \hat{\phi}_n \), and \( \hat{\phi}_p \).
-Confidence distributions are like frequentist posterior distributions
-\cite{}.
-The lower and upper confidence distributions are used with discrete responses to ensure the validity of the resulting inferences, and for the binomial case they are equivalent to the posterior distributions that result from using well-calibrated null preference priors \cite{}.
+Confidence distributions are like frequentist posterior distributions\cite{Xie2013}.
+The lower and upper confidence distributions are used with discrete responses to ensure the validity of the resulting inferences, and for the binomial case they are equivalent to the posterior distributions that result from using well-calibrated null preference priors \cite{Fay2021}.
 
@@
 For a binomial experiment with \( x \) successes out of \( n \) trials, the lower confidence distribution \( (B^L) \) is \( \operatorname{Beta}(x, n - x + 1) \), and the upper confidence distribution \( (B^U) \) is \( \operatorname{Beta}(x + 1, n - x)\).
-Let \( q(a, W) \) be the \( a \)th quantile of a random variable \( W \). Then the exact \( a \)\% central confidence interval of Clopper-Pearson for the binomial parameter is 
+Let \( q(a, W) \) be the \( a \)th quantile of a random variable \( W \). Then the exact \( 1 - \alpha \)\% central confidence interval of Clopper-Pearson for the binomial parameter is 
 \begin{equation}
-\left\{ q \left( \frac{1-a}{2}, B^L \right), q \left( \frac{1+a}{2}, B^U \right\}.
+\left\{ q \left( \frac{\alpha}{2}, B^L \right), q \left( 1 - \frac{\alpha}{2}, B^U, \right) \right\}.
 \label{eq:C-P}
@@
 When $1 \geq \phi_p > \theta_1 > \phi_n \geq 0$ then $\beta^*$ is monotonically increasing in $\theta_1$, monotonically decreasing in $\phi_p$, and monotonically decreasing in $\phi_n$.
-Then the \( a \)\% confidence interval for \( \beta^* \) is
+Then the \( 1-\alpha \)\% confidence interval for \( \beta^* \) is
 
 \begin{equation}
-    \left\{ q \left( \frac{1 - a}{2}, g \left\{ B_{\theta_1}^L, B_{\phi_n}^U, B_{\phi_p}^U \right\}   \right),  
-            q \left( \frac{1 + a}{2},  g \left\{ B_{\theta_1}^U, B_{\phi_n}^L, B_{\phi_p}^L \right\}   \right) \right\}.
+    \left\{ q \left( \frac{\alpha}{2}, g \left\{ B_{\theta_1}^L, B_{\phi_n}^U, B_{\phi_p}^U \right\}   \right),  
+            q \left( 1 - \frac{\alpha}{2},  g \left\{ B_{\theta_1}^U, B_{\phi_n}^L, B_{\phi_p}^L \right\}   \right) \right\}.
 \label{eq:srs-conf-int}
@@
 where $g(\cdot)$ is defined in equation~\ref{eq:srs-beta-est}.
-
-%\todo[inline]{Can Mike provide some explanation for the form of this interval? Or some citation? Does it follow from Fay, Proschan, and Brittain (2015), or is there an intermediate reference?}
 
@@
 \begin{equation}
-\beta_1^{*\prime} + d\beta \pm q\left( \frac{1 + a}{2}, Z \right) \cdot \Var(\beta_1^{*\prime})^{1/2}    
+\beta_1^{*\prime} + d\beta \pm q\left( 1 - \frac{\alpha}{2}, Z \right) \cdot \Var(\beta_1^{*\prime})^{1/2}    
 \end{equation}
 
-where
-\begin{equation}
-   Z \sim N(0,1) 
-\end{equation}
+where \( q_Z \equiv q\left( 1 - \frac{\alpha}{2}, Z \right)\) and \( Z \sim N(0,1) \).
 
 \begin{equation}
-    d\beta = 2 \cdot q\left( \frac{1 + a}{2}, Z \right)^2 \cdot\left\{ \beta_1^{*\prime} \cdot \frac{\phi_p^\prime (1 - \phi_p^\prime)}{m_p^\prime} - (1 - \beta_1^{*\prime}) \cdot \frac{(1 - \phi_n^\prime) \phi_n^\prime}{m_n^\prime}  \right\}
+    d\beta = 2 \cdot q_Z^2 \cdot\left\{ \beta_1^{*\prime} \cdot \frac{\phi_p^\prime (1 - \phi_p^\prime)}{m_p^\prime} - (1 - \beta_1^{*\prime}) \cdot \frac{(1 - \phi_n^\prime) \phi_n^\prime}{m_n^\prime}  \right\}
 \end{equation}
@@
 \begin{equation}
-    \beta_1^\prime = \frac{n_1 \cdot \hat{\theta}_1 + q\left( \frac{1 + a}{2}, Z \right)^2 / 2}{n_1 + q\left( \frac{1 + a}{2}, Z \right)^2}
+    \beta_1^\prime = \frac{n_1 \cdot \hat{\theta}_1 + q_Z^2 / 2}{n_1 + q_Z^2}
 \end{equation}
@@
 \label{sec:weight-perfect}
+
 Next, we present a confidence interval for the population prevalence, \( \beta^* \), in the scenario \( k > 1 \), \( \phi_n = 0 \), \( \phi_p = 1 \).
@@
 We note that for sufficiently large sample size \( n \) and small rate \( \lambda \), a \( \operatorname{Poisson}(n\lambda) \) distribution is approximately equal in distribution to a \( \operatorname{Binomial}(n, \lambda) \) distribution.
-\todo[inline]{Is this a good enough justification? We certainly don't have a large sample size, but we do have small rates. Mike: It seems good enough to me.}
-Under this Poisson assumption, we suggest the \( a \)\% gamma confidence interval for \( \beta^* \):
+Under this Poisson assumption, we suggest the \( 1 - \alpha \)\% gamma confidence interval for \( \beta^* \):
 
 \begin{equation}
-    \left( q\left( \frac{1 - a}{2}, G_{\beta^*}^L \right), q \left( \frac{1 + a}{2},  G_{\beta^*}^U \right) \right)
+    \left( q\left( \frac{\alpha}{2}, G_{\beta^*}^L \right), q \left( 1 - \frac{\alpha}{2},  G_{\beta^*}^U \right) \right)
 \end{equation}
@@
 We call this the wsPoison method, since it assumes a weighted sum of Poissons.
-We compare the wsPoisson confidence interval to two methods presented in Dean and Pagano\cite{Dean:2015}, which were recommended for scenarios with low prevalence.
+We compare the wsPoisson confidence interval to two methods presented in Dean and Pagano\cite{Dean:2015}, which were recommended for scenarios with low prevalence
+Dean and Pagano showed in simulations that the standard Wald interval had poor coverage with low prevalence (e.g., Fig.
+1 of that paper showed 95\% confidence intervals with coverage of less than 85\% for prevalence values less than 2\%).
+Since the confidence interval of Rosin, et al \cite{rosin2021estimating} reduces to the Wald interval with perfect assays, we will not include that method in the simulation comparisons.
 
-The first of these is an adaptation of the method of Agresti and Coull\cite{AgrestiCoull} for the survey setting.
+The first recommended method of Dean and Pagano is an adaptation of the method of Agresti and Coull\cite{AgrestiCoull} for the survey setting.
 The interval for \( \beta^* \) is given by:
@@
 \begin{equation}
-    \tilde{p} \pm q\left( \frac{1 + a}{2}, Z \right) \sqrt{\tilde{p}(1 - \tilde{p}) / \tilde{n}}
+    \tilde{p} \pm q_Z \sqrt{\tilde{p}(1 - \tilde{p}) / \tilde{n}}
 \end{equation}
@@
 \begin{equation*}
-   c = q\left( \frac{1 + a}{2}, Z \right)^2/2
+   c = q_Z^2/2
 \end{equation*}
@@
 
-We also compare our suggested method to a modification of the method of Korn and Graubard\cite{Korn:1998} presented in \cite{Dean:2015}.
+We also compare our suggested method to Dean and Pagano's modification of the method of Korn and Graubard\cite{Korn:1998,Dean:2015}.
 This interval is given by
@@
 \begin{equation}
-    \left( q \left( \frac{1 - a}{2}, B^L_{CP} \right), q \left( \frac{1 + a}{2}, B^U_{CP} \right)  \right)
+    \left( q \left( \frac{\alpha}{2}, B^L_{KG} \right), q \left( 1 - \frac{\alpha}{2}, B^U_{KG} \right)  \right)
 \end{equation}
@@
 \begin{equation*}
-    % B^L_{CP} \sim \operatorname{Beta}\left(n_{\text{eff}} \sum_{i=1}^k w_i \hat{\theta}_i, n_{\text{eff}} \left(1 -  \sum_{i=1}^k w_i \hat{\theta}_i\right) + 1\right)
-    B^L_{CP} \sim \operatorname{Beta}\left(x_{\text{eff}},  n_{\text{eff}} -  x_{\text{eff}} + 1 \right)
+    % B^L_{KG} \sim \operatorname{Beta}\left(n_{\text{eff}} \sum_{i=1}^k w_i \hat{\theta}_i, n_{\text{eff}} \left(1 -  \sum_{i=1}^k w_i \hat{\theta}_i\right) + 1\right)
+    B^L_{KG} \sim \operatorname{Beta}\left(x_{\text{eff}},  n_{\text{eff}} -  x_{\text{eff}} + 1 \right)
 \end{equation*}
@@
 \begin{equation*}
-    % B^U_{CP} \sim \operatorname{Beta}\left(\left(n_{\text{eff}} \sum_{i=1}^k w_i \hat{\theta}_i\right) + 1, n_{\text{eff}} \left(1 - \sum_{i=1}^k w_i \hat{\theta}_i \right)\right)
-    B^U_{CP} \sim \operatorname{Beta}\left(x_{\text{eff}} + 1, n_{\text{eff}} - x_{\text{eff}} \right)
+    % B^U_{KG} \sim \operatorname{Beta}\left(\left(n_{\text{eff}} \sum_{i=1}^k w_i \hat{\theta}_i\right) + 1, n_{\text{eff}} \left(1 - \sum_{i=1}^k w_i \hat{\theta}_i \right)\right)
+    B^U_{KG} \sim \operatorname{Beta}\left(x_{\text{eff}} + 1, n_{\text{eff}} - x_{\text{eff}} \right)
 \end{equation*}
@@
 The two methods we discuss are closely related to each other and the methods discussed in Sections~\ref{sec:srs-imperfect} and \ref{sec:weight-perfect}.
-As in Section~\ref{sec:srs-imperfect}, we use the melding method \cite{FayP:2015} to create \( a \)\% confidence interval very similar to Equation~\ref{eq:srs-conf-int}.
+As in Section~\ref{sec:srs-imperfect}, we use the melding method \cite{FayP:2015} to create \( 1 - \alpha \)\% confidence interval very similar to Equation~\ref{eq:srs-conf-int}.
 The confidence distributions for \( \phi_p \) and \( \phi_n \) are the same Beta distributions as in Section~\ref{sec:srs-imperfect}.
@@
 
-In the first case, we use the adaptation of \cite{FayF:1997} presented in Section~\ref{sec:weight-perfect} to derive the \( a \)\% confidence interval for \( \beta^* \):
+In the first case, we use the adaptation of \cite{FayF:1997} presented in Section~\ref{sec:weight-perfect} to derive the \( 1 - \alpha \)\% confidence interval for \( \beta^* \):
 
 \begin{equation}
-    \left\{ q \left( \frac{1 - a}{2}, %\frac{G_{\beta}^L + B_{\phi_n}^L }{B_{\phi_p}^U + B_{\phi_n}^L } 
+    \left\{ q \left( \frac{\alpha}{2}, %\frac{G_{\beta}^L + B_{\phi_n}^L }{B_{\phi_p}^U + B_{\phi_n}^L } 
     g \left[ G^L_{\beta^*}, B^U_{\phi_n}, B^U_{\phi_p} \right]
-    \right),  q \left( \frac{1 + a}{2}, %\frac{G_{\beta}^U + B_{\phi_n}^U}{B_{\phi_p}^L + B_{\phi_n}^U}  \right) \right\}.
+    \right),  q \left( 1 - \frac{\alpha}{2}, %\frac{G_{\beta}^U + B_{\phi_n}^U}{B_{\phi_p}^L + B_{\phi_n}^U}  \right) \right\}.
        g \left[G^U_{\beta^*}, B^L_{\phi_n}, B^L_{\phi_p} \right] \right)
@@
 The alternative method is that used in \cite{Kali:2021}.
-We use the  modification of \cite{Korn:1998} presented in \cite{Dean:2015}, as in Section~\ref{sec:weight-perfect}, to derive the \( a \)\% confidence interval for \( \beta^* \):
+We use the  modification of \cite{Korn:1998} presented in \cite{Dean:2015}, as in Section~\ref{sec:weight-perfect}, to derive the \( 1 - \alpha \)\% confidence interval for \( \beta^* \):
 
 \begin{equation}
-    \left\{ q \left( \frac{1 - a}{2}, \frac{B_{CP}^L + B_{\phi_n}^L }{B_{\phi_p}^U + B_{\phi_n}^L }  \right),  q \left( \frac{1 + a}{2}, \frac{B_{CP}^U + B_{\phi_n}^U}{B_{\phi_p}^L + B_{\phi_n}^U}  \right) \right\}.
+    \left\{ q \left( \frac{\alpha}{2}, \frac{B_{KG}^L + B_{\phi_n}^L }{B_{\phi_p}^U + B_{\phi_n}^L }  \right),  q \left( 1 - \frac{\alpha}{2}, \frac{B_{KG}^U + B_{\phi_n}^U}{B_{\phi_p}^L + B_{\phi_n}^U}  \right) \right\}.
 \end{equation}
 
-where \( B_{CP}^L \) and \( B_{CP}^U \) are as defined in Section~\ref{sec:weight-perfect}.
+where \( B_{KG}^L \) and \( B_{KG}^U \) are as defined in Section~\ref{sec:weight-perfect}.
 
-\section{Results}
+\section{Simulations}
 
@@
 
-\todo[inline]{Since our method is so conservative, I should look at the widths of the confidence intervals. Unfortunately, I have to re-reun simulations to do this.}
-
 The coverage properties for these simulations are presented in Figures~\ref{fig:perfect_coverage_50_groups_0_005_prev}--\ref{fig:perfect_coverage_8000_groups_0_05_prev}.
@@
 This is similar to the behavior observed in Fay and Feuer\cite{FayF:1997}, where, in simulations, the overall error rate for the gamma intervals decreased as the variance of the weights increased.
+Because our methods appear to be very conservative, with coverage near 100\% in some cases, we present the widths of the confidence intervals in Figures~\ref{fig:perfect_confidence_interval_width_50_groups_0_005_prev}--\ref{fig:perfect_confidence_interval_width_8000_groups_0_05_prev}.
+In scenarios where coefficient of variation among the survey weights is high, the wsPoisson intervals are often two or three times wider than intervals produced by competing methods.
 
@@
 Simulated sensitivity is assessed based on 60 tests, while specificity is based on 300 tests.
-
-\todo[inline]{Since our method is so conservative, I should look at the widths of the confidence intervals. Unfortunately, I have to re-reun simulations to do this.}
 
@@
 Only our proposed WprevSeSp Poisson method maintains or exceed the desired coverage in all scenarios.
+Because our methods appear to be very conservative, with coverage near 100\% in some cases, we present the widths of the confidence intervals in Figures~\ref{fig:imperfect_confidence_interval_width_50_groups_0_005_prev}--\ref{fig:imperfect_confidence_interval_width_8000_groups_0_05_prev}.
+The WprevSeSp Binomial and  WprevSeSp Poisson methods typically produce wide intervals of approximately the same size - sometimes as wide as 12\%, even when true prevalence is 0.05\%.
+One notable exception to this is presented in Figure \ref{fig:imperfect_confidence_interval_width_8000_groups_0_005_prev}, which shows that for tests with perfect specificity, the WprevSeSP produces much narrower confidence intervals than the other methods.
+
+\section{Applications}
 

### 2021-12-07 code/assess_g_monotonicity.R
Revised Figures for Mike's comments

@@ -1,0 +1,43 @@
+library(tidyverse)
+
+g <- function(theta_1, phi_n, phi_p) {
+  if ((phi_n < phi_p) & (phi_p < theta_1)) {
+    return(1)
+  } else if ((phi_p >= theta_1) & (theta_1 >= phi_n)) {
+    return((theta_1 - phi_n) / (phi_p - phi_n))  
+  } else {
+    return(0)
+  }
+}
+
+monotonic <- function(x) all(x == cummax(x)) | all(x == cummin(x))
+
+tmp <- 
+  crossing(theta_1 = seq(0, 1, 0.005),
+         phi_n = seq(0, 1, 0.01),
+         phi_p = seq(0, 1, 0.01)) %>% 
+  filter(phi_p > phi_n) %>% 
+  filter(phi_p >= theta_1 & theta_1 >= phi_n) %>% 
+  mutate(g = pmap_dbl(list(theta_1 = theta_1, phi_n = phi_n, phi_p = phi_p),
+                           function(theta_1, phi_n, phi_p) g(theta_1, phi_n, phi_p)))
+
+tmp %>% 
+  group_by(theta_1, phi_n) %>% 
+  arrange(phi_p) %>% 
+  summarize(phi_p = list(phi_p), .groups = "drop") %>% 
+  mutate(monotonic = map_lgl(phi_p, monotonic)) %>% 
+  summarize(mean(monotonic))
+
+tmp %>% 
+  group_by(phi_p, phi_n) %>% 
+  arrange(theta_1) %>% 
+  summarize(theta_1 = list(theta_1), .groups = "drop") %>% 
+  mutate(monotonic = map_lgl(theta_1, monotonic)) %>% 
+  summarize(mean(monotonic))
+
+tmp %>% 
+  group_by(theta_1, phi_p) %>% 
+  arrange(phi_n) %>% 
+  summarize(phi_n = list(phi_n), .groups = "drop") %>% 
+  mutate(monotonic = map_lgl(phi_n, monotonic)) %>% 
+  summarize(mean(monotonic))

### 2021-12-07 code/simulations/confidence_interval_imperfect_assay/process_imperfect_assay_arrayjob.R

@@ -18,10 +18,11 @@ results_summary <-
   mutate(method = fct_recode(method,
                              "WprevSeSp Binomial" = "WprevSeSp",
                              "WprevSeSp Poisson" = "WprevSeSp_gamma",
-                             "wspoissonTest" = "wspoissonTest")) %>%
+                             "wsPoisson" = "wspoissonTest")) %>%
   mutate(group_distribution = group_distribution %>%
            fct_relevel("high", "uniform", "low") %>%
-           fct_relabel(str_to_title))
+           fct_relabel(str_to_title)) %>%
+  filter(method != "wsPoisson")
 
 
 

### 2021-12-07 code/simulations/confidence_interval_perfect_assay/process_weights_many.R

@@ -28,7 +28,7 @@ results_summary <-
   filter(method != "wspoissonTest_midp") %>%
   mutate(method = fct_recode(method,
                              "Agresti-Coull" = "AC",
-                             "Clopper-Pearson" = "CP",
+                             "Korn-Graubard" = "CP",
                              "wsPoisson" = "wspoissonTest")) %>%
   mutate(group_distribution = group_distribution %>%
            fct_relevel("high", "uniform", "low") %>%

### 2021-12-07 PrevAdjSurvey.tex

@@
 For a binomial experiment with \( x \) successes out of \( n \) trials, the lower confidence distribution \( (B^L) \) is \( \operatorname{Beta}(x, n - x + 1) \), and the upper confidence distribution \( (B^U) \) is \( \operatorname{Beta}(x + 1, n - x)\).
-Let \( q(a, W) \) be the \( a \)th quantile of a random variable \( W \). Then the exact \( 1 - \alpha \)\% central confidence interval of Clopper-Pearson for the binomial parameter is 
+Let \( q(a, W) \) be the \( a \)th quantile of a random variable \( W \). Then the exact \( 1 - \alpha \)\% central confidence interval of Korn-Graubard for the binomial parameter is 
 \begin{equation}
@@
 
-where analogously to the Clopper-Pearson interval (see equation~\ref{eq:C-P}),
+where analogously to the Korn-Graubard interval (see equation~\ref{eq:C-P}),
 \begin{equation*}
@@
 
-We compare the wsPoisson method to the more traditional Agresti-Coull and Korn-Graubard methods for survey proportions in a variety of settings.
+We compare the wsPoisson method to the more traditional Dean-Pagano modification of the Agresti-Coull (DPAC) method and the Korn-Graubard (KG) method for survey proportions in a variety of settings.
 Our simulations examine varying levels of disease prevalence (0.5\% or 5\%), types of groups surveyed (50 groups 200 subjects or 8000 groups of 1 subject), distributions of weights among the groups (coefficient of variation from approximately 0\% to nearly 6\%), the number of groups with non-zero prevalence, and the weights of the groups with non-zero prevalence.
@@
 \includegraphics[width=0.8\textwidth]{figures/perfect_coverage_50_groups_0_005_prev.pdf}
-\caption{Coverage properties for the wsPoisson model and two standard methods, Agresti-Coull and Clopper-Pearson.
+\caption{Coverage properties for the wsPoisson model and two standard methods, the Dean-Pagano modification of Agresti-Coull and Korn-Graubard
 Each point represents 10,000 simulations of datasets from a population with 0.5\% Prevalence where 50 groups of 200 people are sampled.
@@
 \includegraphics[width=0.8\textwidth]{figures/perfect_coverage_8000_groups_0_005_prev.pdf}
-\caption{Coverage properties for the wsPoisson model and two standard methods, Agresti-Coull and Clopper-Pearson.
+\caption{Coverage properties for the wsPoisson model and two standard methods, the Dean-Pagano modification of Agresti-Coull and Korn-Graubard
 Each point represents 10,000 simulations of datasets from a population with 0.5\% Prevalence where 8000 individuals are sampled.
@@
 \includegraphics[width=0.8\textwidth]{figures/perfect_coverage_50_groups_0_05_prev.pdf}
-\caption{Coverage properties for the wsPoisson model and two standard methods, Agresti-Coull and Clopper-Pearson.
+\caption{Coverage properties for the wsPoisson model and two standard methods, the Dean-Pagano modification of Agresti-Coull and Korn-Graubard
 Each point represents 10,000 simulations of datasets from a population with 5\% Prevalence where 50 groups of 200 people are sampled.
@@
 \includegraphics[width=0.8\textwidth]{figures/perfect_coverage_8000_groups_0_05_prev.pdf}
-\caption{Coverage properties for the wsPoisson model and two standard methods, Agresti-Coull and Korn-Graubard.
+\caption{Coverage properties for the wsPoisson model and two standard methods, the Dean-Pagano modification of Agresti-Coull and Korn-Graubard
 Each point represents 10,000 simulations of datasets from a population with 5\% Prevalence where 8000 individuals are sampled.
@@
 \includegraphics[width=0.8\textwidth]{figures/perfect_lower_error_frequency_50_groups_0_005_prev.pdf}
-\caption{Lower error properties for the wsPoisson model and two standard methods, Agresti-Coull and Clopper-Pearson.
+\caption{Lower error properties for the wsPoisson model and two standard methods, the Dean-Pagano modification of Agresti-Coull and Korn-Graubard
 Each point represents 10,000 simulations of datasets from a population with 0.5\% Prevalence where 50 groups of 200 people are sampled.
@@
 \includegraphics[width=0.8\textwidth]{figures/perfect_lower_error_frequency_8000_groups_0_005_prev.pdf}
-\caption{Lower error properties for the wsPoisson model and two standard methods, Agresti-Coull and Clopper-Pearson.
+\caption{Lower error properties for the wsPoisson model and two standard methods, the Dean-Pagano modification of Agresti-Coull and Korn-Graubard
 Each point represents 10,000 simulations of datasets from a population with 0.5\% Prevalence where 8000 individuals are sampled.
@@
 \includegraphics[width=0.8\textwidth]{figures/perfect_lower_error_frequency_50_groups_0_05_prev.pdf}
-\caption{Lower error properties for the wsPoisson model and two standard methods, Agresti-Coull and Clopper-Pearson.
+\caption{Lower error properties for the wsPoisson model and two standard methods, the Dean-Pagano modification of Agresti-Coull and Korn-Graubard
 Each point represents 10,000 simulations of datasets from a population with 5\% Prevalence where 50 groups of 200 people are sampled.
@@
 \includegraphics[width=0.8\textwidth]{figures/perfect_lower_error_frequency_8000_groups_0_05_prev.pdf}
-\caption{Lower error properties for the wsPoisson model and two standard methods, Agresti-Coull and Clopper-Pearson.
+\caption{Lower error properties for the wsPoisson model and two standard methods, the Dean-Pagano modification of Agresti-Coull and Korn-Graubard
 Each point represents 10,000 simulations of datasets from a population with 5\% Prevalence where 8000 individuals are sampled.
@@
 \includegraphics[width=0.8\textwidth]{figures/perfect_upper_error_frequency_50_groups_0_005_prev.pdf}
-\caption{Upper error properties for the wsPoisson model and two standard methods, Agresti-Coull and Clopper-Pearson.
+\caption{Upper error properties for the wsPoisson model and two standard methods, the Dean-Pagano modification of Agresti-Coull and Korn-Graubard
 Each point represents 10,000 simulations of datasets from a population with 0.5\% Prevalence where 50 groups of 200 people are sampled.
@@
 \includegraphics[width=0.8\textwidth]{figures/perfect_upper_error_frequency_8000_groups_0_005_prev.pdf}
-\caption{Upper error properties for the wsPoisson model and two standard methods, Agresti-Coull and Clopper-Pearson.
+\caption{Upper error properties for the wsPoisson model and two standard methods, the Dean-Pagano modification of Agresti-Coull and Korn-Graubard
 Each point represents 10,000 simulations of datasets from a population with 0.5\% Prevalence where 8000 individuals are sampled.
@@
 \includegraphics[width=0.8\textwidth]{figures/perfect_upper_error_frequency_50_groups_0_05_prev.pdf}
-\caption{Upper error properties for the wsPoisson model and two standard methods, Agresti-Coull and Clopper-Pearson.
+\caption{Upper error properties for the wsPoisson model and two standard methods, the Dean-Pagano modification of Agresti-Coull and Korn-Graubard
 Each point represents 10,000 simulations of datasets from a population with 5\% Prevalence where 50 groups of 200 people are sampled.
@@
 \includegraphics[width=0.8\textwidth]{figures/perfect_upper_error_frequency_8000_groups_0_05_prev.pdf}
-\caption{Upper error properties for the wsPoisson model and two standard methods, Agresti-Coull and Clopper-Pearson.
+\caption{Upper error properties for the wsPoisson model and two standard methods, the Dean-Pagano modification of Agresti-Coull and Korn-Graubard
 Each point represents 10,000 simulations of datasets from a population with 5\% Prevalence where 8000 individuals are sampled.
@@
 \includegraphics[width=0.8\textwidth]{figures/perfect_confidence_interval_width_50_groups_0_005_prev}
-\caption{Confidence interval width properties for the wsPoisson model and two standard methods, Agresti-Coull and Clopper-Pearson.
+\caption{Confidence interval width properties for the wsPoisson model and two standard methods, the Dean-Pagano modification of Agresti-Coull and Korn-Graubard
 Each point represents 10,000 simulations of datasets from a population with 0.5\% Prevalence where 50 groups of 200 people are sampled.
@@
 \includegraphics[width=0.8\textwidth]{figures/perfect_confidence_interval_width_50_groups_0_05_prev}
-\caption{Confidence interval width properties for the wsPoisson model and two standard methods, Agresti-Coull and Clopper-Pearson.
+\caption{Confidence interval width properties for the wsPoisson model and two standard methods, the Dean-Pagano modification of Agresti-Coull and Korn-Graubard
 Each point represents 10,000 simulations of datasets from a population with 5\% Prevalence where 50 groups of 200 people are sampled.
@@
 \includegraphics[width=0.8\textwidth]{figures/perfect_confidence_interval_width_8000_groups_0_005_prev}
-\caption{Confidence interval width properties for the wsPoisson model and two standard methods, Agresti-Coull and Clopper-Pearson.
+\caption{Confidence interval width properties for the wsPoisson model and two standard methods, the Dean-Pagano modification of Agresti-Coull and Korn-Graubard
 Each point represents 10,000 simulations of datasets from a population with 0.5\% Prevalence where 8000 individuals are sampled.
@@
 \includegraphics[width=0.8\textwidth]{figures/perfect_confidence_interval_width_8000_groups_0_05_prev}
-\caption{Confidence interval width properties for the wsPoisson model and two standard methods, Agresti-Coull and Clopper-Pearson.
+\caption{Confidence interval width properties for the wsPoisson model and two standard methods, the Dean-Pagano modification of Agresti-Coull and Korn-Graubard
 Each point represents 10,000 simulations of datasets from a population with 5\% Prevalence where 8000 individuals are sampled.

### 2021-12-07 PrevAdjSurvey.tex
Ready for Mike's review

@@
 where  \( G_{\beta^*}^L \) and \( G_{\beta^*}^U \) are defined in Section~\ref{sec:weight-perfect}.
+We refer to this method as the WprevSeSp Poisson - weighted prevalence with sensitivity and specificity, where the prevalence confidence distribution is based on the weighted sum of Poissons.
 
@@
 where \( B_{KG}^L \) and \( B_{KG}^U \) are as defined in Section~\ref{sec:weight-perfect}.
+We refer to this as WprevSeSp Binomial - weighted prevalence with sensitivity and specificity, where the prevalence confidence distribution is based on a binomial variance assumption.
 
@@
 
-We compare properties our melded confidence interval WprevSeSp Poisson, to another melded confidence interval method WprevSeSp Binomial, and one method, wspoissonTest, which does not account for the imperfect assay.
+We compare properties our melded confidence interval WprevSeSp Poisson, to another melded confidence interval method WprevSeSp Binomial, and one method, wsPoisson, which does not account for the imperfect assay.
 The methods are assessed in a several simulated scenarios with varying levels of disease prevalence (0.5\% or 5\%), types of groups surveyed (50 groups 200 subjects or 8000 groups of 1 subject), distributions of weights among the groups (coefficient of variation from approximately 0\% to nearly 6\%), the number of groups with non-zero prevalence, and the specificity of the assay (80\% - 100\%).
@@
 \includegraphics[width=0.8\textwidth]{figures/imperfect_coverage_50_groups_0_005_prev.pdf}
-\caption{Coverage properties for the two melded confidence interval procedures, WprevSeSp Binomial and WprevSeSp Poisson, and one method, wspoissonTest, which does not account for the imperfect assay.
+\caption{Coverage properties for the confidence interval procedures, WprevSeSp Binomial and WprevSeSp Poisson.
 Each point represents 10,000 simulations of datasets from a population with 0.5\% Prevalence where 50 groups of 200 people are sampled.
@@
 \includegraphics[width=0.8\textwidth]{figures/imperfect_coverage_8000_groups_0_005_prev.pdf}
-\caption{Coverage properties for the two melded confidence interval procedures, WprevSeSp Binomial and WprevSeSp Poisson, and one method, wspoissonTest, which does not account for the imperfect assay.
+\caption{Coverage properties for the confidence interval procedures, WprevSeSp Binomial and WprevSeSp Poisson.
 Each point represents 10,000 simulations of datasets from a population with 0.5\% Prevalence where 8000 individuals are sampled.
@@
 \includegraphics[width=0.8\textwidth]{figures/imperfect_coverage_50_groups_0_05_prev.pdf}
-\caption{Coverage properties for the two melded confidence interval procedures, WprevSeSp Binomial and WprevSeSp Poisson, and one method, wspoissonTest, which does not account for the imperfect assay.
+\caption{Coverage properties for the confidence interval procedures, WprevSeSp Binomial and WprevSeSp Poisson.
 Each point represents 10,000 simulations of datasets from a population with 5\% Prevalence where 50 groups of 200 people are sampled.
@@
 \includegraphics[width=0.8\textwidth]{figures/imperfect_coverage_8000_groups_0_05_prev.pdf}
-\caption{Coverage properties for the two melded confidence interval procedures, WprevSeSp Binomial and WprevSeSp Poisson, and one method, wspoissonTest, which does not account for the imperfect assay.
+\caption{Coverage properties for the confidence interval procedures, WprevSeSp Binomial and WprevSeSp Poisson.
 Each point represents 10,000 simulations of datasets from a population with 5\% Prevalence where 8000 individuals are sampled.
@@
 
-Based on Figures~\ref{fig:imperfect_lower_error_frequency_50_groups_0_05_prev}--\ref{fig:imperfect_upper_error_frequency_8000_groups_0_05_prev}, we note that, in most settings, the naive wspoissonTest procedure results in extremely poor coverage, around 0\%, while the two melding procedures result in conservative confidence intervals, often nearing 100\% coverage.
-With perfect specificity, the issue of poor coverage for the wspoissonTest procedure is less prominent, but the WprevSeSp Binomial method fails to maintain nominal coverage when the coefficient of variation among the weights is high.
+Based on Figures~\ref{fig:imperfect_lower_error_frequency_50_groups_0_05_prev}--\ref{fig:imperfect_upper_error_frequency_8000_groups_0_05_prev}, we note that, in most settings, the two melding procedures result in conservative confidence intervals, often nearing 100\% coverage.
+With perfect specificity, the WprevSeSp Binomial method fails to maintain nominal coverage when the coefficient of variation among the weights is high.
 Only our proposed WprevSeSp Poisson method maintains or exceed the desired coverage in all scenarios.
+In these scenarios, we also assess properties of the wsPoisson procedure, which does not account for the the imperfect assay.
+This method results in approximately 0\% coverage in any scenarios where specificity is less than perfect.
 Because our methods appear to be very conservative, with coverage near 100\% in some cases, we present the widths of the confidence intervals in Figures~\ref{fig:imperfect_confidence_interval_width_50_groups_0_005_prev}--\ref{fig:imperfect_confidence_interval_width_8000_groups_0_05_prev}.
@@
 The Korn and Graubard type melded confidence interval (WprevSeSp Binomial) produced the 95\% confidence interval for population prevalence (2.53\%, 6.68\%), while the wsPoisson type melded confidence interval (WprevSeSp Poisson) produce the 95\% confidence interval (2.56\%, 7.54\%).
-We also apply the wspoissonTest method from Section~\ref{sec:weight-perfect}, which does not account for imperfections in the assay, resulting in a 95\% confidence interval of (3.04\%, 7.39\%).
+We also apply the wsPoisson method from Section~\ref{sec:weight-perfect}, which does not account for imperfections in the assay, resulting in a 95\% confidence interval of (3.04\%, 7.39\%).
 While all three intervals overlap to a large degree, the wsPoisson type melded confidence interval is the widest.
@@
 The Korn and Graubard type confidence distributions (WprevSeSp Binomial) produce the 95\% confidence interval for population prevalence (2.35\%, 11.75\%), while the wsPoisson type confidence distributions (WprevSeSp Poisson) produce the 95\% confidence interval (2.40\%, 20.02\%).
-The wspoissonTest method produces a 95\% confidence interval of (2.80\%, 19.63\%).
+The wsPoisson method produces a 95\% confidence interval of (2.80\%, 19.63\%).
 In this case, the two melded confidence intervals are much wider than the naive interval, as expected.
@@
 \includegraphics[width=0.8\textwidth]{figures/imperfect_lower_error_frequency_50_groups_0_05_prev.pdf}
-\caption{Lower error properties for the two melded confidence interval procedures, WprevSeSp Binomial and WprevSeSp Poisson, and one method, wspoissonTest, which does not account for the imperfect assay.
+\caption{Lower error properties for the confidence interval procedures, WprevSeSp Binomial and WprevSeSp Poisson.
 Each point represents 10,000 simulations of datasets from a population with 0.5\% Prevalence where 50 groups of 200 people are sampled.
@@
 \includegraphics[width=0.8\textwidth]{figures/imperfect_lower_error_frequency_50_groups_0_005_prev.pdf}
-\caption{Lower error properties for the two melded confidence interval procedures, WprevSeSp Binomial and WprevSeSp Poisson, and one method, wspoissonTest, which does not account for the imperfect assay.
+\caption{Lower error properties for the confidence interval procedures, WprevSeSp Binomial and WprevSeSp Poisson.
 Each point represents 10,000 simulations of datasets from a population with 0.5\% Prevalence where 8000 individuals are sampled.
@@
 \includegraphics[width=0.8\textwidth]{figures/imperfect_lower_error_frequency_8000_groups_0_05_prev.pdf}
-\caption{Lower error properties for the two melded confidence interval procedures, WprevSeSp Binomial and WprevSeSp Poisson, and one method, wspoissonTest, which does not account for the imperfect assay.
+\caption{Lower error properties for the confidence interval procedures, WprevSeSp Binomial and WprevSeSp Poisson.
 Each point represents 10,000 simulations of datasets from a population with 5\% Prevalence where 50 groups of 200 people are sampled.
@@
 \includegraphics[width=0.8\textwidth]{figures/imperfect_lower_error_frequency_8000_groups_0_005_prev.pdf}
-\caption{Lower error properties for the two melded confidence interval procedures, WprevSeSp Binomial and WprevSeSp Poisson, and one method, wspoissonTest, which does not account for the imperfect assay.
+\caption{Lower error properties for the confidence interval procedures, WprevSeSp Binomial and WprevSeSp Poisson.
 Each point represents 10,000 simulations of datasets from a population with 5\% Prevalence where 8000 individuals are sampled.
@@
 \includegraphics[width=0.8\textwidth]{figures/imperfect_upper_error_frequency_50_groups_0_005_prev.pdf}
-\caption{Upper error properties for the two melded confidence interval procedures, WprevSeSp Binomial and WprevSeSp Poisson, and one method, wspoissonTest, which does not account for the imperfect assay.
+\caption{Upper error properties for the confidence interval procedures, WprevSeSp Binomial and WprevSeSp Poisson.
 Each point represents 10,000 simulations of datasets from a population with 0.5\% Prevalence where 50 groups of 200 people are sampled.
@@
 \includegraphics[width=0.8\textwidth]{figures/imperfect_upper_error_frequency_8000_groups_0_005_prev.pdf}
-\caption{Upper error properties for the two melded confidence interval procedures, WprevSeSp Binomial and WprevSeSp Poisson, and one method, wspoissonTest, which does not account for the imperfect assay.
+\caption{Upper error properties for the confidence interval procedures, WprevSeSp Binomial and WprevSeSp Poisson.
 Each point represents 10,000 simulations of datasets from a population with 0.5\% Prevalence where 8000 individuals are sampled.
@@
 \includegraphics[width=0.8\textwidth]{figures/imperfect_upper_error_frequency_50_groups_0_05_prev.pdf}
-\caption{Upper error properties for the two melded confidence interval procedures, WprevSeSp Binomial and WprevSeSp Poisson, and one method, wspoissonTest, which does not account for the imperfect assay.
+\caption{Upper error properties for the confidence interval procedures, WprevSeSp Binomial and WprevSeSp Poisson.
 Each point represents 10,000 simulations of datasets from a population with 5\% Prevalence where 50 groups of 200 people are sampled.
@@
 \includegraphics[width=0.8\textwidth]{figures/imperfect_upper_error_frequency_8000_groups_0_05_prev.pdf}
-\caption{Upper error properties for the two melded confidence interval procedures, WprevSeSp Binomial and WprevSeSp Poisson, and one method, wspoissonTest, which does not account for the imperfect assay.
+\caption{Upper error properties for the confidence interval procedures, WprevSeSp Binomial and WprevSeSp Poisson.
 Each point represents 10,000 simulations of datasets from a population with 5\% Prevalence where 8000 individuals are sampled.
@@
 \includegraphics[width=0.8\textwidth]{figures/imperfect_confidence_interval_width_50_groups_0_005_prev}
-\caption{Confidence interval width properties for the two melded confidence interval procedures, WprevSeSp Binomial and WprevSeSp Poisson, and one method, wspoissonTest, which does not account for the imperfect assay.
+\caption{Confidence interval width properties for the confidence interval procedures, WprevSeSp Binomial and WprevSeSp Poisson.
 Each point represents 10,000 simulations of datasets from a population with 0.5\% Prevalence where 50 groups of 200 people are sampled.
@@
 \includegraphics[width=0.8\textwidth]{figures/imperfect_confidence_interval_width_50_groups_0_05_prev}
-\caption{Confidence interval width properties for the two melded confidence interval procedures, WprevSeSp Binomial and WprevSeSp Poisson, and one method, wspoissonTest, which does not account for the imperfect assay.
+\caption{Confidence interval width properties for the confidence interval procedures, WprevSeSp Binomial and WprevSeSp Poisson.
 Each point represents 10,000 simulations of datasets from a population with 5\% Prevalence where 50 groups of 200 people are sampled.
@@
 \includegraphics[width=0.8\textwidth]{figures/imperfect_confidence_interval_width_8000_groups_0_005_prev}
-\caption{Confidence interval width properties for the two melded confidence interval procedures, WprevSeSp Binomial and WprevSeSp Poisson, and one method, wspoissonTest, which does not account for the imperfect assay.
+\caption{Confidence interval width properties for the confidence interval procedures, WprevSeSp Binomial and WprevSeSp Poisson.
 Each point represents 10,000 simulations of datasets from a population with 0.5\% Prevalence where 8000 individuals are sampled.
@@
 \includegraphics[width=0.8\textwidth]{figures/imperfect_confidence_interval_width_8000_groups_0_05_prev}
-\caption{Confidence interval width properties for the two melded confidence interval procedures, WprevSeSp Binomial and WprevSeSp Poisson, and one method, wspoissonTest, which does not account for the imperfect assay.
+\caption{Confidence interval width properties for the confidence interval procedures, WprevSeSp Binomial and WprevSeSp Poisson.
 Each point represents 10,000 simulations of datasets from a population with 5\% Prevalence where 8000 individuals are sampled.

### 2021-12-22 code/simulations/confidence_interval_imperfect_assay/combine_imperfect_assay_arrayjob.R
Revised imperfect simulation results

@@ -9,6 +9,10 @@ imperfect_assay_raw_vec <-
   arrange(file_name) %>%
   pull(file_path)
 
+str_sub(imperfect_assay_raw_vec, 64, 67) %>%
+  as.integer() %>%
+  setdiff(1:1000, .)
+
 combined_imperfect_assay_raw <-
   map_dfr(imperfect_assay_raw_vec,
           ~read_rds(.) %>%

### 2021-12-22 code/assess_g_monotonicity.R
Revised monotonicity

@@ -4,7 +4,7 @@ g <- function(theta_1, phi_n, phi_p) {
   if ((phi_n < phi_p) & (phi_p < theta_1)) {
     return(1)
   } else if ((phi_p >= theta_1) & (theta_1 >= phi_n)) {
-    return((theta_1 - phi_n) / (phi_p - phi_n))  
+    return((theta_1 - phi_n) / (phi_p - phi_n))
   } else {
     return(0)
   }
@@ -12,32 +12,69 @@ g <- function(theta_1, phi_n, phi_p) {
 
 monotonic <- function(x) all(x == cummax(x)) | all(x == cummin(x))
 
-tmp <- 
+tmp <-
   crossing(theta_1 = seq(0, 1, 0.005),
-         phi_n = seq(0, 1, 0.01),
-         phi_p = seq(0, 1, 0.01)) %>% 
-  filter(phi_p > phi_n) %>% 
-  filter(phi_p >= theta_1 & theta_1 >= phi_n) %>% 
+           phi_n = seq(0, 1, 0.01),
+           phi_p = seq(0, 1, 0.01)) %>%
+  filter(phi_p > phi_n) %>%
+  filter(phi_p >= theta_1 & theta_1 >= phi_n) %>%
   mutate(g = pmap_dbl(list(theta_1 = theta_1, phi_n = phi_n, phi_p = phi_p),
-                           function(theta_1, phi_n, phi_p) g(theta_1, phi_n, phi_p)))
+                      function(theta_1, phi_n, phi_p) g(theta_1, phi_n, phi_p)))
 
-tmp %>% 
-  group_by(theta_1, phi_n) %>% 
-  arrange(phi_p) %>% 
-  summarize(phi_p = list(phi_p), .groups = "drop") %>% 
-  mutate(monotonic = map_lgl(phi_p, monotonic)) %>% 
+tmp %>%
+  group_by(theta_1, phi_n) %>%
+  arrange(phi_p) %>%
+  summarize(phi_p = list(phi_p), .groups = "drop") %>%
+  mutate(monotonic = map_lgl(phi_p, monotonic)) %>%
   summarize(mean(monotonic))
 
-tmp %>% 
-  group_by(phi_p, phi_n) %>% 
-  arrange(theta_1) %>% 
-  summarize(theta_1 = list(theta_1), .groups = "drop") %>% 
-  mutate(monotonic = map_lgl(theta_1, monotonic)) %>% 
+tmp %>%
[…]

### 2021-12-22 PrevAdjSurvey.tex

@@
 For rare events, these estimates are highly sensitive to misclassification \cite{hemenwaySelfDefense}, making adjustments for sensitivity and specificity critically important.
-While estimating prevalence in complex surveys and adjusting estimates for misclassification have been well studied separately, performing both of these tasks simultaneously remains relatively unexplored.
+While estimating prevalence (or any event proportion in a population) in complex surveys and adjusting estimates for misclassification have been well studied separately, performing both of these tasks simultaneously remains relatively unexplored.
 A recent overview of methods for estimating prevalence in surveys without misclassification is provided by Dean and Pagano\cite{Dean:2015}.
@@
 Fewer methods are available for for constructing frequentist confidence intervals for prevalence estimates from complex surveys while adjusting for sensitivity and specificity.
-One such method, which is closely related to the method presented here is developed by Kalish et al\cite{Kali:2021}.
-Another recent advancement is developed by Rosin et al \cite{rosin2021estimating}.
-This method makes use of asymptotic normal appriximations which reduce to the Wald interval when sensitivity and specificity are perfect.
+Kalish et al\cite{Kali:2021} developed one such method that is closely related to the method presented here, but their method's properties were not studied.
+Another recent advancement is the method developed by Rosin et al \cite{rosin2021estimating} that 
+ makes use of asymptotic normal approximations which reduce to the Wald interval when sensitivity and specificity are perfect.
 This problem has also previously been addressed in Bayesian literature, recently by Gelman and Carpenter\cite{GelmanBayes}.
@@
 Finally, in Section~\ref{sec:weight-imperfect}, we combine these methods to create confidence intervals for weighted samples where prevalence is assessed with an assay with imperfect sensitivity and specificity.
+Because the combined method reduces to one of the first two methods as a special case, we can think of the first two stages as testing the combined method in those cases. 
+Our new method is designed to guarantee coverage in all situations, and we show through simulations that it beats the best competitors in each of the first two stages with respect to that property.
+For the last stage, the only competitor is
+very similar to our proposed method but had not previously been studied in detail, and both methods are nearly equivalent.
+Although the last stage presents some simulated scenarios where the coverage is anti-conservative, in most cases the new method does have proper coverage.
 
@@
 Let \( X_i \) be the number of positive results from an assay performed on the \( n_i \) individuals from sampling unit \( i \) and assume \( X_i \sim \operatorname{Binomial}(n_i, \theta_i) \), where \( \theta_i \) is the population frequency of positive results for assays performed on individuals from sampling unit \( i \).
-Similarly, let \( X_i^* \) be the true number of people with the disease among the \( n_i \) individuals from sampling unit \( i \) and assume \( X_i^* \sim \operatorname{Binomial}(n_i, \theta_i^*) \), where \( \theta_i^* \) is the population frequency of cases in sampling unit \( i \).
+Similarly, let \( X_i^* \) be the unobserved true number of people with the disease among the \( n_i \) individuals from sampling unit \( i \) and assume \( X_i^* \sim \operatorname{Binomial}(n_i, \theta_i^*) \), where \( \theta_i^* \) is the population frequency of cases in sampling unit \( i \).
 In the case of a perfect assay, \( \theta_i = \theta_i^* \).
@@
 where \( w_i = N_i / \sum_{j=1}^k N_j \) and, therefore, \( \sum_{i=1}^k w_i = 1 \).
-This set-up will work for other complex survey samples, where we can treat the survey weights as known.
+This set-up will work for other complex survey samples, where we can treat the survey weights as known and each individual may be their own stratum.
 
@@
 negative controls (i.e., individuals known to be  without the disease), respectively. Then
-$\theta_i = \phi_p \theta_i^* + (1-\phi_n) (1-\theta_i^*)$, or equivalently,  
+$\theta_i = \phi_p \theta_i^* + \phi_n (1-\theta_i^*)$, or equivalently,  
 \begin{eqnarray*}
@@
 For each of these, we use distributions associated with  the exact binomial confidence interval.
-For a binomial experiment with \( x \) successes out of \( n \) trials, the lower confidence distribution \( (B^L) \) is \( \operatorname{Beta}(x, n - x + 1) \), and the upper confidence distribution \( (B^U) \) is \( \operatorname{Beta}(x + 1, n - x)\).
-Let \( q(a, W) \) be the \( a \)th quantile of a random variable \( W \). Then the exact \( 1 - \alpha \)\% central confidence interval of Korn-Graubard for the binomial parameter is 
+For a binomial experiment with \( x \) successes out of \( n \) trials, the lower confidence distribution is \( \operatorname{Beta}(x, n - x + 1) \) with associated random variable \( B^L \), and the upper confidence distribution  is \( \operatorname{Beta}(x + 1, n - x)\) with random variable \( B^U \).
+Let \( q(a, W) \) be the \( a \)th quantile of a random variable \( W \).
+Then the exact \( 1 - \alpha \)\% central confidence interval of Clopper-Pearson\cite{10.1093/biomet/26.4.404} for the binomial parameter is
 \begin{equation}
@@
 When $1 \geq \phi_p > \theta_1 > \phi_n \geq 0$ then $\beta^*$ is monotonically increasing in $\theta_1$, monotonically decreasing in $\phi_p$, and monotonically decreasing in $\phi_n$.
+For an assessment of monotonicity in other scenarios see Appendix~\ref{monotonicity}.
 Then the \( 1-\alpha \)\% confidence interval for \( \beta^* \) is
@@
 
-\begin{equation}
+\begin{equation*}
     d\beta = 2 \cdot q_Z^2 \cdot\left\{ \beta_1^{*\prime} \cdot \frac{\phi_p^\prime (1 - \phi_p^\prime)}{m_p^\prime} - (1 - \beta_1^{*\prime}) \cdot \frac{(1 - \phi_n^\prime) \phi_n^\prime}{m_n^\prime}  \right\}
-\end{equation}
+\end{equation*}
 
-\begin{equation}
+\begin{equation*}
     \Var(\beta_1^{*\prime}) = \frac{ \frac{\beta_1^{*\prime}(1 - \beta_1^{*\prime})}{n_1} + \left(\beta_1^{*\prime}\right)^2 \frac{\phi_p^\prime (1 - \phi_p^\prime)}{m_p} + \left(1 + \beta_1^{*\prime}\right)^2 \frac{(1 - \phi_n^\prime) \phi_n^\prime}{ m_n}}{(\phi_p^\prime - \phi_n^\prime)^2}
-\end{equation}
+\end{equation*}
 
-\begin{equation}
+\begin{equation*}
     m_p^\prime = m_p +2
-\end{equation}
+\end{equation*}
 
-\begin{equation}
+\begin{equation*}
     m_n^\prime = m_n + 2
-\end{equation}
+\end{equation*}
 
-\begin{equation}
+\begin{equation*}
     \phi_p^\prime = \frac{m_p \cdot \hat{\phi}_p + 1}{m_p + 2}
-\end{equation}
+\end{equation*}
 
-\begin{equation}
+\begin{equation*}
    1 - \phi_n^\prime = \frac{m_n \cdot (1 - \hat{\phi}_n) + 1}{m_n + 2} 
-\end{equation}
+\end{equation*}
 
-\begin{equation}
+\begin{equation*}
    \beta_1^{*\prime} = \frac{\beta_1^\prime - \phi_n^\prime}{\phi_p^\prime - \phi_n^\prime} 
-\end{equation}
-
-\begin{equation}
-    \beta_1^\prime = \frac{n_1 \cdot \hat{\theta}_1 + q_Z^2 / 2}{n_1 + q_Z^2}
-\end{equation}
+\end{equation*}
+and 
+\begin{equation*}
+    \beta_1^\prime = \frac{n_1 \cdot \hat{\theta}_1 + q_Z^2 / 2}{n_1 + q_Z^2}.
+\end{equation*}
 
@@
 We call this the wsPoison method, since it assumes a weighted sum of Poissons.
-We compare the wsPoisson confidence interval to two methods presented in Dean and Pagano\cite{Dean:2015}, which were recommended for scenarios with low prevalence
+We compare the wsPoisson confidence interval to two methods presented in Dean and Pagano\cite{Dean:2015}, which were recommended for scenarios with low prevalence.
 Dean and Pagano showed in simulations that the standard Wald interval had poor coverage with low prevalence (e.g., Fig.
@@
 
-where analogously to the Korn-Graubard interval (see equation~\ref{eq:C-P}),
+where analogously to the Clopper-Pearson interval (see equation~\ref{eq:C-P}),
 \begin{equation*}
@@
 with \( x_{\text{eff}} = n_{\text{eff}} \sum_{i=1}^k w_i \hat{\theta}_i \), and \( n_{\text{eff}} \) defined in Equation~\ref{eq:neff}.
+Although, Dean and Pagano \cite{Dean:2015} expressed this in terms of the F distributions, the beta distribution representation is equivalent.
 
@@
 
-In the first case, we use the adaptation of \cite{FayF:1997} presented in Section~\ref{sec:weight-perfect} to derive the \( 1 - \alpha \)\% confidence interval for \( \beta^* \):
+In the first case, we use the adaptation of the gamma confidence interval \cite{FayF:1997} presented in Section~\ref{sec:weight-perfect} to derive the \( 1 - \alpha \)\% confidence interval for \( \beta^* \):
 
@@
 
-The alternative method is that used in \cite{Kali:2021}.
+The alternative method is that used in Kalish, et al \cite{Kali:2021}.
 We use the  modification of \cite{Korn:1998} presented in \cite{Dean:2015}, as in Section~\ref{sec:weight-perfect}, to derive the \( 1 - \alpha \)\% confidence interval for \( \beta^* \):
@@
 \begin{equation}
-    \left\{ q \left( \frac{\alpha}{2}, \frac{B_{KG}^L + B_{\phi_n}^L }{B_{\phi_p}^U + B_{\phi_n}^L }  \right),  q \left( 1 - \frac{\alpha}{2}, \frac{B_{KG}^U + B_{\phi_n}^U}{B_{\phi_p}^L + B_{\phi_n}^U}  \right) \right\}.
+    \left\{ q \left( \frac{\alpha}{2}, \frac{B_{KG}^L - B_{\phi_n}^U }{B_{\phi_p}^U - B_{\phi_n}^U }  \right),  q \left( 1 - \frac{\alpha}{2}, \frac{B_{KG}^U - B_{\phi_n}^L}{B_{\phi_p}^L - B_{\phi_n}^L}  \right) \right\}.
 \end{equation}
@@
 where \( B_{KG}^L \) and \( B_{KG}^U \) are as defined in Section~\ref{sec:weight-perfect}.
+Although equivalent, this expression looks different than in Kalish, et al\cite{Kali:2021} because they used a parameter for specificity, rather than $\phi_n$, which is 1 minus specificity.
 We refer to this as WprevSeSp Binomial - weighted prevalence with sensitivity and specificity, where the prevalence confidence distribution is based on a binomial variance assumption.
@@
 Figure~\ref{fig:upper_error_frequency_comparison_plot} shows that both methods make upper errors with roughly the same frequency.
-Figure~\ref{fig:lower_error_frequency_comparison_plot} demonstrates that while the melding procedure leads bounds the lower error frequency below 2.5\%, the Lang-Reiczigel method generally has lower error above 2.5\%, which is undesirable for applications for which there is a need to bound the lower errors.
+Figure~\ref{fig:lower_error_frequency_comparison_plot} demonstrates that while the melding procedure bounds the lower error frequency below 2.5\%, the Lang-Reiczigel method generally has lower error above 2.5\%, which is undesirable for applications for which there is a need to bound the lower errors.
 
@@
 Uniform distribution of prevalence among the weights, increased overall prevalence, and larger sample sizes among fewer groups all appear to lessen the severity of this problem.
-In contrast, the wsPoisson method appears to guarantee coverage in all scenarios. The wsPoisson method tends to become more conservative when the coefficient of variation among the weights increases. 
+In contrast, the wsPoisson method appears to guarantee coverage in all scenarios.
+The wsPoisson method tends to become more conservative when the coefficient of variation among the weights increases, when the other methods can have problems guaranteeing coverage.
 In all cases, the wsPoisson method is more conservative than the competitor methods.
@@
 Each scenario is simulated 10,000 times, with new prevalence, sensitivity, and specificity surveys generated and 95\% confidence intervals are created.
-Simulated sensitivity is assessed based on 60 tests, while specificity is based on 300 tests.
+Modelled after the study of Kalish, et al \cite{Kali:2021}, the simulated sensitivity is assessed based on 60 tests, while specificity is based on 300 tests.
 
@@
 
-We also apply these two methods to a real data set from \cite{Kali:2021}.
+We also apply these two methods to a real data set from
+Kalish, et al \cite{Kali:2021}.
 This data set was collected to estimate seroprevalence of SARS-CoV-2 in the United States between May and July 2020.
-This test used in this data is estimated to have perfect sensitivity, based on 56 tests on individuals with confirmed SARS-CoV-2 and perfect specificity based on 300 tests on individuals confirmed to not have SARS-CoV-2.
+The assay used in this data is estimated to have perfect sensitivity, based on 56 tests on individuals with confirmed SARS-CoV-2 and perfect specificity based on 300 tests on individuals confirmed to not have SARS-CoV-2.
 First we apply the methods to the full data set (\( n =  8058, \text{weight coefficient of variation} = 252\%\)).
-The Korn and Graubard type melded confidence interval (WprevSeSp Binomial) produced the 95\% confidence interval for population prevalence (2.53\%, 6.68\%), while the wsPoisson type melded confidence interval (WprevSeSp Poisson) produce the 95\% confidence interval (2.56\%, 7.54\%).
+The Korn and Graubard type melded confidence interval with imperfect assay adjustments (WprevSeSp Binomial) produced the 95\% confidence interval for population prevalence (2.53\%, 6.68\%), while the wsPoisson type melded confidence interval with imperfect assay adjustments (WprevSeSp Poisson) produce the 95\% confidence interval (2.56\%, 7.54\%).
 We also apply the wsPoisson method from Section~\ref{sec:weight-perfect}, which does not account for imperfections in the assay, resulting in a 95\% confidence interval of (3.04\%, 7.39\%).
-While all three intervals overlap to a large degree, the wsPoisson type melded confidence interval is the widest.
-Our simulations show that the three procdures have similar coverage when specificity and weight coefficient of variation are both high, so this is unsurprising.
+While all three intervals overlap to a large degree, the WprevSeSp Poisson interval is the widest.
+Our simulations show that the three procedures have similar coverage when specificity and weight coefficient of variation are both high, so this is unsurprising.
 
 We also apply the methods to the subset of only Hispanic participants (\( n = 1281, \text{weight coefficient of variation} = 306\% \)).
-The Korn and Graubard type confidence distributions (WprevSeSp Binomial) produce the 95\% confidence interval for population prevalence (2.35\%, 11.75\%), while the wsPoisson type confidence distributions (WprevSeSp Poisson) produce the 95\% confidence interval (2.40\%, 20.02\%).
+The WprevSeSp Binomial method produces a 95\% confidence interval for population prevalence (2.35\%, 11.75\%), while the WprevSeSp Poisson method produces a 95\% confidence interval (2.40\%, 20.02\%).
 The wsPoisson method produces a 95\% confidence interval of (2.80\%, 19.63\%).
-In this case, the two melded confidence intervals are much wider than the naive interval, as expected.
-This is somewhat unexpected, but may be because prevalence is concentrated among respondents with lower weights, or be related to the smaller sample size used to measure prevalence, which is not reflected in our simulations.
+In this case, the two melded confidence intervals are much wider than the WprevSeSp Binomial interval, which is as expected since the melding method is designed to guarantee coverage.
+The somewhat unexpected smaller WprevSeSp Binomial interval, but may be because prevalence is concentrated among respondents with lower weights, or be related to the smaller sample size used to measure prevalence, which is not reflected in our simulations.
 
@@
 We presented several methods for creating confidence to assess disease prevalence in variety of settings, including simple random samples with imperfect tests, weighted sampling with perfect tests, and weighted sampling with imperfect tests.
-As a general theme, these confidence intervals tend to demonstrate higher coverage than competitor methods.
+These new confidence intervals appear to guarantee coverage in most simulated settings, and in general to demonstrate higher coverage than competitor methods.
 In the case of the simple random sample with an imperfect test, we are able to bound the lower error rate for a 95\% confidence interval at 2.5\%, while the state-of-the-art method maintains 95\% coverage by allowing a higher lower error rate.
@@
 \appendix
+
+\section{Monotonicity of \( g \)}
+\label{monotonicity}
+It is clear that \( g \) is monotonic within each of its piecewise-defined functions.
+In the following sections we consider if monotonicity holds at the change points between piecewise functions.
+
+\subsection{Monotonicity in \( \hat{\phi}_p \)}
+
+\begin{itemize}
+	\item Case 1: \( \hat{\phi}_n < \hat{\theta}_1 \). Not monotonic. \\
+\begin{equation} 
+g(\hat{\theta}_1, \hat{\phi}_n, \hat{\phi}_p)
+=
+\left\{ 
+\begin{array}{ll}
+0 & \hat{\phi}_p < \hat{\phi}_n < \hat{\theta}_1  \\
+0 & \hat{\phi}_n = \hat{\phi}_p < \hat{\theta}_1 \\
+1 &	\hat{\phi}_n < \hat{\phi}_p < \hat{\theta}_1 \\
+\frac{\hat{\theta}_1 - \hat{\phi}_n}{\hat{\phi}_p - \hat{\phi}_n} & \hat{\phi}_n < \hat{\phi}_p = \hat{\theta}_1 \\
+\frac{\hat{\theta}_1 - \hat{\phi}_n}{\hat{\phi}_p - \hat{\phi}_n} & \hat{\phi}_n < \hat{\theta}_1 < \hat{\phi}_p \\
+\end{array}
+\right.
+\end{equation}
+
+\item Case 2: \( \hat{\theta}_1 < \hat{\phi}_n \). Monotonic. \\
+\begin{equation} 
+g(\hat{\theta}_1, \hat{\phi}_n, \hat{\phi}_p)
+=
+\left\{ 
+\begin{array}{ll}
+0 & \hat{\phi}_p < \hat{\theta}_1 < \hat{\phi}_n  \\
+0 & \hat{\theta}_1 = \hat{\phi}_p < \hat{\phi}_n \\
+0 &	\hat{\theta}_1 < \hat{\phi}_p < \hat{\phi}_n \\
+0 & \hat{\theta}_1 < \hat{\phi}_p = \hat{\phi}_n \\
+0 & \hat{\theta}_1 < \hat{\phi}_n < \hat{\phi}_p \\
+\end{array}
+\right.
+\end{equation}
+
+\item Case 3: \( \hat{\theta}_1 = \hat{\phi}_n \). Monotonic. \\
+\begin{equation} 
+g(\hat{\theta}_1, \hat{\phi}_n, \hat{\phi}_p)
+=
+\left\{ 
+\begin{array}{ll}
+0 & \hat{\phi}_p < \hat{\theta}_1 = \hat{\phi}_n	\\
+\frac{\hat{\theta}_1 - \hat{\phi}_n}{\hat{\phi}_p - \hat{\phi}_n} = \frac{0}{0} = 0 & \hat{\phi}_p = \hat{\theta}_1 = \hat{\phi}_n 	\\
+\frac{\hat{\theta}_1 - \hat{\phi}_n}{\hat{\phi}_p - \hat{\phi}_n} = \frac{0}{\hat{\phi}_p - \hat{\phi}_n} = 0 & \hat{\theta}_1 = \hat{\phi}_n < \hat{\phi}_p	\\
+\end{array}
+\right.
+\end{equation}
+\end{itemize}
+
+\subsection{Monotonicity in \( \hat{\theta}_1 \)}
+
+\begin{itemize}
+	\item Case 1: \( \hat{\phi}_n < \hat{\phi}_p \). Monotonic. \\
+\begin{equation} 
+g(\hat{\theta}_1, \hat{\phi}_n, \hat{\phi}_p)
+=
+\left\{ 
+\begin{array}{ll}
+0 & \hat{\theta}_1 < \hat{\phi}_n < \hat{\phi}_p  \\
+\frac{\hat{\theta}_1 - \hat{\phi}_n}{\hat{\phi}_p - \hat{\phi}_n} & \hat{\phi}_n = \hat{\theta}_1 < \hat{\phi}_p \\
+\frac{\hat{\theta}_1 - \hat{\phi}_n}{\hat{\phi}_p - \hat{\phi}_n} &	\hat{\phi}_n < \hat{\theta}_1 < \hat{\phi}_p \\
+\frac{\hat{\theta}_1 - \hat{\phi}_n}{\hat{\phi}_p - \hat{\phi}_n} & \hat{\phi}_n < \hat{\theta}_1 = \hat{\phi}_p \\
+1 & \hat{\phi}_n < \hat{\phi}_p < \hat{\theta}_1 \\
+\end{array}
+\right.
+\end{equation}
+
+\item Case 2: \( \hat{\phi}_p < \hat{\phi}_n \). Monotonic. \\
+\begin{equation} 
+g(\hat{\theta}_1, \hat{\phi}_n, \hat{\phi}_p)
+=
+\left\{ 
+\begin{array}{ll}
+0 & \hat{\theta}_1 < \hat{\phi}_p < \hat{\phi}_n  \\
+0 & \hat{\phi}_p = \hat{\theta}_1 < \hat{\phi}_n \\
+0 &	\hat{\phi}_p < \hat{\theta}_1 < \hat{\phi}_n \\
+0 & \hat{\phi}_p < \hat{\theta}_1 = \hat{\phi}_n \\
+0 & \hat{\phi}_p < \hat{\phi}_n < \hat{\theta}_1 \\
+\end{array}
+\right.
+\end{equation}
+
+\item Case 3: \( \hat{\phi}_p = \hat{\phi}_n \). Monotonic. \\
+\begin{equation} 
+g(\hat{\theta}_1, \hat{\phi}_n, \hat{\phi}_p)
+=
+\left\{ 
+\begin{array}{ll}
+0 & \hat{\theta}_1 < \hat{\phi}_p = \hat{\phi}_n	\\
+\frac{\hat{\theta}_1 - \hat{\phi}_n}{\hat{\phi}_p - \hat{\phi}_n} = \frac{0}{0} = 0 & \hat{\theta}_1 = \hat{\phi}_p = \hat{\phi}_n 	\\
+0 & \hat{\phi}_p = \hat{\phi}_n < \hat{\theta}_1	\\
+\end{array}
+\right.
+\end{equation}
+\end{itemize}
+
+\subsection{Monotonicity in \( \hat{\phi}_n \)}
+
+\begin{itemize}
+	\item Case 1: \( \hat{\phi}_p < \hat{\theta}_1 \). Monotonic. \\
+\begin{equation} 
+g(\hat{\theta}_1, \hat{\phi}_n, \hat{\phi}_p)
+=
+\left\{ 
+\begin{array}{ll}
+1 & \hat{\phi}_n < \hat{\phi}_p < \hat{\theta}_1  \\
+0 & \hat{\phi}_p = \hat{\phi}_n < \hat{\theta}_1 \\
+0 &	\hat{\phi}_p < \hat{\phi}_n < \hat{\theta}_1 \\
+0 & \hat{\phi}_p < \hat{\phi}_n = \hat{\theta}_1 \\
+0 & \hat{\phi}_p < \hat{\theta}_1 < \hat{\phi}_n \\
+\end{array}
+\right.
+\end{equation}
+
+\item Case 2: \( \hat{\theta}_1 < \hat{\phi}_p \). Monotonic.
+\begin{equation} 
+g(\hat{\theta}_1, \hat{\phi}_n, \hat{\phi}_p)
+=
+\left\{ 
+\begin{array}{ll}
+\frac{\hat{\theta}_1 - \hat{\phi}_n}{\hat{\phi}_p - \hat{\phi}_n} & \hat{\phi}_n < \hat{\theta}_1 < \hat{\phi}_p  \\
+\frac{\hat{\theta}_1 - \hat{\phi}_n}{\hat{\phi}_p - \hat{\phi}_n} = \frac{0}{\hat{\phi}_p - \hat{\phi}_n} = 0 & \hat{\theta}_1 = \hat{\phi}_n < \hat{\phi}_p \\
+0 &	\hat{\theta}_1 < \hat{\phi}_n < \hat{\phi}_p \\
+0 & \hat{\theta}_1 < \hat{\phi}_n = \hat{\phi}_p \\
+0 & \hat{\theta}_1 < \hat{\phi}_p < \hat{\phi}_n \\
+\end{array}
+\right.
+\end{equation}
+
+\item Case 3: \( \hat{\theta}_1 = \hat{\phi}_p \). Monotonic. \\
+\begin{equation} 
+g(\hat{\theta}_1, \hat{\phi}_n, \hat{\phi}_p)
+=
+\left\{ 
+\begin{array}{ll}
+\frac{\hat{\theta}_1 - \hat{\phi}_n}{\hat{\phi}_p - \hat{\phi}_n} = 1 & \hat{\phi}_n < \hat{\theta}_1 = \hat{\phi}_p	\\
+\frac{\hat{\theta}_1 - \hat{\phi}_n}{\hat{\phi}_p - \hat{\phi}_n} = \frac{0}{0} = 0 & \hat{\phi}_n = \hat{\theta}_1 = \hat{\phi}_p 	\\
+0 & \hat{\theta}_1 = \hat{\phi}_p < \hat{\phi}_n	\\
+\end{array}
+\right.
+\end{equation}
+\end{itemize}
+
 \section{Additional Figures}
@@
 The horizontal dashed line indicates the nominal lower error rate, 2.5\%.
-Colored dashed lines are estimates from a logistic regression model using cubic splines.}
+Colored dashed lines are estimates from a logistic regression model using cubic splines. If the WprevSeSp Binomial line is not visible, then it is covered by the WprevSe Sp Poisson line.}
 \label{fig:imperfect_lower_error_frequency_50_groups_0_05_prev}

### 2021-12-22 code/simulations/confidence_interval_imperfect_assay/process_imperfect_assay_arrayjob.R
Further figure edits

@@ -66,7 +66,8 @@ generate_plot_2 <- function(name_to_plot, n_groups_to_plot, prev_to_plot){
     ) +
     cowplot::theme_minimal_grid() +
     scale_x_continuous(name = "Weight Coefficient of Variation", labels = scales::percent) +
-    scale_y_continuous(name = name_to_plot, label = ~percent(., accuracy = 1)) +
+    # scale_y_continuous(name = name_to_plot, label = ~percent(., accuracy = 1)) +
+    scale_y_continuous(name = name_to_plot, label = percent) +
     scale_color_discrete(name = "Method") +
     theme(legend.position = "bottom",
           panel.border = element_rect(color = "black", fill = NA, size = 1)) +

### 2021-12-22 code/simulations/confidence_interval_perfect_assay/process_weights_many.R

@@ -73,8 +73,10 @@ generate_plot <- function(name_to_plot, n_groups_to_plot, prev_to_plot){
       alpha = 0.5, linetype = "dashed"
     ) +
     cowplot::theme_minimal_grid() +
-    scale_x_continuous(name = "Weight Coefficient of Variation") +
-    scale_y_continuous(name = name_to_plot, label = ~percent(., accuracy = 1)) +
+    # scale_x_continuous(name = "Weight Coefficient of Variation") +
+    scale_x_continuous(name = "Weight Coefficient of Variation", labels = scales::percent) +
+    # scale_y_continuous(name = name_to_plot, label = ~percent(., accuracy = 1)) +
+    scale_y_continuous(name = name_to_plot, label = percent) +
     scale_color_discrete(name = "Method") +
     theme(legend.position = "bottom",
           panel.border = element_rect(color = "black", fill = NA, size = 1)) +

### 2021-12-22 code/simulations/confidence_interval_imperfect_assay/process_imperfect_assay_arrayjob.R
More imperfect revisions

@@ -14,7 +14,10 @@ results_summary <-
   mutate(name = fct_recode(name,
                            "Lower Error Frequency" = "lower_error_freq",
                            "Upper Error Frequency" = "upper_error_freq",
-                           "Coverage" = "coverage")) %>%
+                           "Coverage" = "coverage",
+                           "Lower Confidence Limit" = "conf_int_1",
+                           "Upper Confidence Limit" = "conf_int_2",
+                           "Confidence Interval Width" = "width")) %>%
   mutate(method = fct_recode(method,
                              "WprevSeSp Binomial" = "WprevSeSp",
                              "WprevSeSp Poisson" = "WprevSeSp_gamma",

### 2022-05-19 PrevAdjSurvey.tex
Updates from Overleaf
Overleaf bump

@@
 
-\abstract[Abstract]{To be written.}
-
-\keywords{Class file; \LaTeXe; \emph{Wiley NJD}}
+\abstract[Abstract]{We present several related methods for creating confidence intervals to assess disease prevalence in variety of survey sampling settings.
+These include simple random samples with imperfect tests, weighted sampling with perfect tests, and weighted sampling with imperfect tests, with the first two settings considered special cases of the third.
+Our methods use survey results and measurements of test sensitivity and specificity to construct melded confidence intervals.
+We demonstrate that our methods appear to guarantee coverage in simulated settings, while competing methods are shown to achieve much lower than nominal coverage.
+We apply our method to a seroprevalence survey of SARS-CoV-2 in undiagnosed adults in the United States between May and July 2020.}
+
+\keywords{confidence distributions, seroprevalence, survey sampling, weighted sampling}
 
@@
 While estimating prevalence (or any event proportion in a population) in complex surveys and adjusting estimates for misclassification have been well studied separately, performing both of these tasks simultaneously remains relatively unexplored.
-A recent overview of methods for estimating prevalence in surveys without misclassification is provided by Dean and Pagano\cite{Dean:2015}.
-For simple surveys with imperfect sensitivity and specificity, the method of Lang and Reiczigel\cite{Lang:2014} is the most recent advancement\cite{Flor2020}.
+Recent overviews of methods for estimating prevalence in surveys without misclassification are provided by Dean and Pagano\cite{Dean:2015} and Franco, et al\cite{franco2019}.
+For  simple random sample surveys with imperfect sensitivity and specificity, Lang and Reiczigel\cite{Lang:2014} proposed an approximate method that performed well in simulations.
+Recent work by DiCiccio, et al \cite{DiCi:2021} and Cai et al \cite{Cai:2020} study both valid (i.e., exact) and approximate methods.
+Their valid methods use test inversion and the adjustment of Berger and Boos \cite{Berg:1994}, while their approximation methods use the bootstrap with the test inversion approach.
 Fewer methods are available for for constructing frequentist confidence intervals for prevalence estimates from complex surveys while adjusting for sensitivity and specificity.
-Kalish et al\cite{Kali:2021} developed one such method that is closely related to the method presented here, but their method's properties were not studied.
+Kalish et al\cite{Kali:2021} developed one such method that is closely related to one of the methods presented here, but that method's properties were not studied.
+Cai et al \cite{Cai:2020} (see also discussion in DiCiccio et al \cite{DiCi:2021}) modify their approximation approach to allow sample weights, but it assumes that the number of counts of events within the strata are large (see their Remark 4).
+Thus, it would not apply to a weighted survey method where each individual their own weight.
 Another recent advancement is the method developed by Rosin et al \cite{rosin2021estimating} that 
@@
 Next, in Section~\ref{sec:weight-perfect}, we present confidence intervals for weighted samples where prevalence is assessed with an assay without misclassification.
-Finally, in Section~\ref{sec:weight-imperfect}, we combine these methods to create confidence intervals for weighted samples where prevalence is assessed with an assay with imperfect sensitivity and specificity.
+In Section~\ref{sec:weight-imperfect}, we combine these methods to create confidence intervals for weighted samples where prevalence is assessed with an assay with imperfect sensitivity and specificity.
 Because the combined method reduces to one of the first two methods as a special case, we can think of the first two stages as testing the combined method in those cases.
-Our new method is designed to guarantee coverage in all situations, and we show through simulations that it beats the best competitors in each of the first two stages with respect to that property.
-For the last stage, the only competitor is
-very similar to our proposed method but had not previously been studied in detail, and both methods are nearly equivalent.
-Although the last stage presents some simulated scenarios where the coverage is anti-conservative, in most cases the new method does have proper coverage.
+Finally, in Section~\ref{sec:complex-surveys} we show how certain complex surveys may fit into the format for our new method.
+Our new method is designed to guarantee coverage in all situations.
+
+In simulations we compare our method to established frequentist competitors.
+and  show through simulations that it beats the best of those in each of the three stages with respect to guaranteeing coverage. 
+We did not include in our simulations the new methods that have been developed in response to the COVID-19 pandemic and are not yet in print in peer reviewed journals \cite{Cai:2020,DiCi:2021,rosin2021estimating}.
+The exact method of DiCiccio, et al \cite{DiCi:2021} would guarantee coverage, although applying it to a survey with a large number of strata would be ``computationally expensive'', and it has not been applied to surveys using post-stratification weighting.
+In contrast, our new method can very tractable in those situations.
 
@@
 \subsection{Notation and Problem Set-up}
+\label{sec-notation}
 
 To introduce notation, consider first the stratified simple random sample.
-Suppose we have a survey with  \( k \) sampling units, with \( N_1, N_2, \ldots, N_k \) individuals in the population of unit \( i \).
-We sample \( n_1, n_2, \ldots, n_k \) individuals via a simple random sample from each population to have an assay performed to determine who has a disease.
-Let \( X_i \) be the number of positive results from an assay performed on the \( n_i \) individuals from sampling unit \( i \) and assume \( X_i \sim \operatorname{Binomial}(n_i, \theta_i) \), where \( \theta_i \) is the population frequency of positive results for assays performed on individuals from sampling unit \( i \).
-Similarly, let \( X_i^* \) be the unobserved true number of people with the disease among the \( n_i \) individuals from sampling unit \( i \) and assume \( X_i^* \sim \operatorname{Binomial}(n_i, \theta_i^*) \), where \( \theta_i^* \) is the population frequency of cases in sampling unit \( i \).
+Suppose we have a population partitioned into   \( K \) strata, with \( N_1, N_2, \ldots, N_K \) individuals in the  K strata of the population.
+We sample \( n_1, n_2, \ldots, n_K \) individuals via a simple random sample from each of the \( K \)  strata to have an assay performed to determine who has a disease.
+Let \( X_i \) be the number of positive results from an assay performed on the \( n_i \) individuals from stratum \( i \) and assume \( X_i \sim \operatorname{Binomial}(n_i, \theta_i) \), where \( \theta_i \) is the population frequency of positive results for assays performed on individuals from stratum \( i \).
+Similarly, let \( X_i^* \) be the unobserved true number of people with the disease among the \( n_i \) individuals from stratum  \( i \) and assume \( X_i^* \sim \operatorname{Binomial}(n_i, \theta_i^*) \), where \( \theta_i^* \) is the population frequency of cases in stratum \( i \).
 In the case of a perfect assay, \( \theta_i = \theta_i^* \).
@@
 \begin{equation}
-    \beta^* = \frac{\sum_{i=1}^k N_i \theta_i^*}{\sum_{j=1}^k N_j} = \sum_{i=1}^k w_i \theta_i^*,
+    \beta^* = \frac{\sum_{i=1}^K N_i \theta_i^*}{\sum_{j=1}^K N_j} = \sum_{i=1}^K w_i \theta_i^*,
     \label{eq:pop-prev}
@@
 \begin{equation}
-    \beta = \frac{\sum_{i=1}^k N_i \theta_i}{\sum_{j=1}^k N_j} = \sum_{i=1}^k w_i \theta_i,
+    \beta = \frac{\sum_{i=1}^K N_i \theta_i}{\sum_{j=1}^K N_j} = \sum_{i=1}^K w_i \theta_i,
     \label{eq:app-prev}
@@
 
-where \( w_i = N_i / \sum_{j=1}^k N_j \) and, therefore, \( \sum_{i=1}^k w_i = 1 \).
-This set-up will work for other complex survey samples, where we can treat the survey weights as known and each individual may be their own stratum.
+where \( w_i = N_i / \sum_{j=1}^K N_j \) and, therefore, \( \sum_{i=1}^K w_i = 1 \).
+This set-up will approximately work for other complex survey samples, where we can estimate survey weights such that the complex survey sample may be treated as a multinomial sample with probabilities proportional to those weights  (see Section~\ref{sec:complex-surveys}).
 
@@
 \begin{split}
-  \beta^*   =&   \sum_{i=1}^k w_i \theta_i^* \\
-            =&  \sum_{i=1}^k w_i \left( \frac{\theta_i - \phi_n}{\phi_p - \phi_n} \right) \\
-            =&   \frac{\sum_{i=1}^k w_i \theta_i}{\phi_p - \phi_n} - \frac{\phi_n \sum_{i=1}^k w_i}{\phi_p - \phi_n} \\
-            =&   \frac{\sum_{i=1}^k w_i \theta_i}{\phi_p - \phi_n} - \frac{\phi_n}{\phi_p - \phi_n}
+  \beta^*   =&   \sum_{i=1}^K w_i \theta_i^* 
+            =  \sum_{i=1}^K w_i \left( \frac{\theta_i - \phi_n}{\phi_p - \phi_n} \right) \\
+            =&   \frac{\sum_{i=1}^K w_i \theta_i}{\phi_p - \phi_n} - \frac{\phi_n \sum_{i=1}^K w_i}{\phi_p - \phi_n} 
+            =   \frac{\sum_{i=1}^K w_i \theta_i}{\phi_p - \phi_n} - \frac{\phi_n}{\phi_p - \phi_n}
             \label{eq:long-beta}
@@
 \begin{equation}
-    \hat{\beta}^* = \frac{\sum_{i=1}^k w_i \hat{\theta}_i}{\hat{\phi}_p - \hat{\phi}_n} - \frac{\hat{\phi}_n}{\hat{\phi}_p - \hat{\phi}_n}. \label{eq:betastarhat}
+    \hat{\beta}^* = \frac{\sum_{i=1}^K w_i \hat{\theta}_i}{\hat{\phi}_p - \hat{\phi}_n} - \frac{\hat{\phi}_n}{\hat{\phi}_p - \hat{\phi}_n}. \label{eq:betastarhat}
 \end{equation}
@@
 This estimator serves as an important basis for developing confidence intervals in this work.
-Section~\ref{sec:srs-imperfect} is concerned with confidence intervals for  \( \beta^* \) in the case where \( k = 1 \), \( \phi_n > 0 \), \( \phi_p < 1 \), i.e.
+Section~\ref{sec:srs-imperfect} is concerned with confidence intervals for  \( \beta^* \) in the case where \( K = 1 \), \( \phi_n > 0 \), \( \phi_p < 1 \), i.e.
 estimating prevalence from a simple random sample with an imperfect assay.
-Section~\ref{sec:weight-perfect} is concerned with confidence intervals for  \( \beta^* \) in the case where \( k > 1 \), \( \phi_n = 0 \), \( \phi_p = 1 \), i.e.
+Section~\ref{sec:weight-perfect} is concerned with confidence intervals for  \( \beta^* \) in the case where \( K > 1 \), \( \phi_n = 0 \), \( \phi_p = 1 \), i.e.
 estimating prevalence from a weighted sample with a perfect assay.
-Section~\ref{sec:weight-imperfect} is concerned with confidence intervals for  \( \beta^* \) in the case where \( k > 1 \), \( \phi_n > 0 \), \( \phi_p < 1 \), i.e.
+Section~\ref{sec:weight-imperfect} is concerned with confidence intervals for  \( \beta^* \) in the case where \( K > 1 \), \( \phi_n > 0 \), \( \phi_p < 1 \), i.e.
 estimating prevalence from a weighted sample with an imperfect assay.
@@
 
-First, we consider the scenario where \( k = 1 \), \( \phi_n > 0 \), and \( \phi_p < 1 \).
+First, we consider the scenario where \( K = 1 \), \( \phi_n > 0 \), and \( \phi_p < 1 \).
 We develop a confidence interval for the population prevalence, \( \beta^* \).
-When \( k = 1 \), the estimand in Equation~\ref{eq:long-beta} becomes $\beta^* = (\theta_1 - \phi_n)/(\phi_p-\phi_n)$.
-We have $\phi_p > \phi_n$ for any useful assay, and when the sample is a mixture of individuals with and without the disease of interest, $\phi_p \geq \theta_1 \geq \phi_n$.
+When \( K = 1 \), the estimand in Equation~\ref{eq:long-beta} becomes $\beta^* = (\theta_1 - \phi_n)/(\phi_p-\phi_n)$.
+We have $\phi_p > \phi_n$ for any useful assay, and since the sample is a mixture of individuals with and without the disease of interest, $\phi_p \geq \theta_1 \geq \phi_n$.
 The estimator of $\beta^*$ is
@@
 For each of these, we use distributions associated with  the exact binomial confidence interval.
-For a binomial experiment with \( x \) successes out of \( n \) trials, the lower confidence distribution is \( \operatorname{Beta}(x, n - x + 1) \) with associated random variable \( B^L \), and the upper confidence distribution  is \( \operatorname{Beta}(x + 1, n - x)\) with random variable \( B^U \).
+For a binomial experiment with \( x \) successes out of \( n \) trials, the lower confidence distribution is \( \operatorname{Beta}(x, n - x + 1) \) with associated random variable \( B^L \), and the upper confidence distribution  is \( \operatorname{Beta}(x + 1, n - x)\) with random variable \( B^U \), where for $a>0$ we let \( \operatorname{Beta}(0,a) \) and \( \operatorname{Beta}(a,0) \) be point masses at 0 and 1, respectively.
 Let \( q(a, W) \) be the \( a \)th quantile of a random variable \( W \).
@@
 
-Next, we present a confidence interval for the population prevalence, \( \beta^* \), in the scenario \( k > 1 \), \( \phi_n = 0 \), \( \phi_p = 1 \).
-Our method is a straightforward adaptation of the gamma confidence interval presented in Fay and Feuer\cite{FayF:1997}, which was developed to create confidence intervals for a population rate which is assumed to a weighted sum of Poisson rate parameters.
+Next, we present a confidence interval for the population prevalence, \( \beta^* \), in the scenario \( K > 1 \), \( \phi_n = 0 \), \( \phi_p = 1 \).
+Our method is a straightforward adaptation of the gamma confidence interval presented in Fay and Feuer\cite{FayF:1997}, which was developed to create confidence intervals for a population rate which is assumed to be a weighted sum of Poisson rate parameters.
 We note that for sufficiently large sample size \( n \) and small rate \( \lambda \), a \( \operatorname{Poisson}(n\lambda) \) distribution is approximately equal in distribution to a \( \operatorname{Binomial}(n, \lambda) \) distribution.
-Under this Poisson assumption, we suggest the \( 1 - \alpha \)\% gamma confidence interval for \( \beta^* \):
+Under this Poisson assumption, we suggest the \( 100(1 - \alpha) \)\% gamma confidence interval for \( \beta^* \):
 
@@
 \begin{equation*}
-    y = \sum_{i=1}^k \frac{w_i}{n_i} x_i
-\end{equation*}
-
-\begin{equation*}
-    v = \sum_{i=1}^k \left( \frac{w_i}{n_i}\right)^2 x_i
-\end{equation*}
-
-\begin{equation*}
-    y^* = y + \max\left(\frac{w_1}{n_1}, \ldots, \frac{w_k}{n_k} \right)
-\end{equation*}
-
-\begin{equation*}
-    v^* = v + \left\{ \max\left(\frac{w_1}{n_1}, \ldots, \frac{w_k}{n_k} \right) \right\}^2
+    y = \sum_{i=1}^K \frac{w_i}{n_i} x_i
+\end{equation*}
+
+\begin{equation*}
+    v = \sum_{i=1}^K \left( \frac{w_i}{n_i}\right)^2 x_i
+\end{equation*}
+
+\begin{equation*}
+    y^* = y + \max\left(\frac{w_1}{n_1}, \ldots, \frac{w_K}{n_K} \right)
+\end{equation*}
+
+\begin{equation*}
+    v^* = v + \left\{ \max\left(\frac{w_1}{n_1}, \ldots, \frac{w_K}{n_K} \right) \right\}^2.
 \end{equation*}
@@
 with \( x_{\text{eff}} = n_{\text{eff}} \sum_{i=1}^k w_i \hat{\theta}_i \), and \( n_{\text{eff}} \) defined in Equation~\ref{eq:neff}.
-Although, Dean and Pagano \cite{Dean:2015} expressed this in terms of the F distributions, the beta distribution representation is equivalent.
+Although Dean and Pagano \cite{Dean:2015} expressed this in terms of the F distributions, the beta distribution representation is equivalent.
 
@@
 
-Lastly, we develop a confidence interval for the population prevalence, \( \beta^* \), in the case where \( k > 1 \), \( \phi_n > 0 \), \( \phi_p < 1 \).
+Lastly, we develop a confidence interval for the population prevalence, \( \beta^* \), in the case where \( K > 1 \), \( \phi_n > 0 \), \( \phi_p < 1 \).
 
@@
 
-The alternative method is that used in Kalish, et al \cite{Kali:2021}.
-We use the  modification of \cite{Korn:1998} presented in \cite{Dean:2015}, as in Section~\ref{sec:weight-perfect}, to derive the \( 1 - \alpha \)\% confidence interval for \( \beta^* \):
-
-\begin{equation}
-    \left\{ q \left( \frac{\alpha}{2}, \frac{B_{KG}^L - B_{\phi_n}^U }{B_{\phi_p}^U - B_{\phi_n}^U }  \right),  q \left( 1 - \frac{\alpha}{2}, \frac{B_{KG}^U - B_{\phi_n}^L}{B_{\phi_p}^L - B_{\phi_n}^L}  \right) \right\}.
+The alternative method is very similar to that used in Kalish, et al \cite{Kali:2021}.
+We use the  modification of \cite{Korn:1998} presented in \cite{Dean:2015}, as in Section~\ref{sec:weight-perfect}, to derive the \( 100(1 - \alpha) \)\% confidence interval for \( \beta^* \):
+
+\begin{equation}
+    \left\{ q \left( \frac{\alpha}{2}, g\left[B_{KG}^L, B_{\phi_n}^U, B_{\phi_p}^U\right]  \right),  q \left( 1 - \frac{\alpha}{2}, g\left[B_{KG}^U, B_{\phi_n}^L, B_{\phi_p}^L\right]  \right) \right\}.
 \end{equation}
@@
 
+\subsection{Applications to More Complex Surveys}
+\label{sec:complex-surveys}
+
+\subsubsection{When Can We Use These Methods}
+
+In Section~\ref{sec-notation}, we derived methods assuming that the apparent prevalence was a weighted sum of binomial random variables,
+$\beta = \sum_{i=1}^{K} w_i \frac{X_i}{n_i}$, where $X_i \sim \textrm{Binomial}(n_i,\theta_i)$. We used the fact that for small $\theta_i$ and large $n_i$
+the binomial can be approximated by the Poisson, giving $X_i \stackrel{\cdot}{\sim} \textrm{Poisson}( n_i \theta_i)$.
+Thus, whenever we can model a complex survey estimator of apparent prevalence as a weighted sum of Poisson variates, then we can apply the methods of this paper.
+
+In the upcoming Section~\ref{sec-MultPoisson}, we give a detailed review relating the multinomial sampling model  to a weighted sum of Poisson variates model.
+The multinomial sampling model treats the survey sample as if it is a sampling with replacement from the entire population of $N$ individuals, where each of the $N$
+individuals has a probability of $P_j$ of being sampled for each of the $n$ samples from the survey, with $\sum_{j=1}^{N} P_j = 1$. Under this model the number of times each of the $N$ individuals
+is included in the sample is a multinomial with parameters $n$ and $[P_1,\ldots, P_N]$.
+The multinomial model describes sampling with replacement, but it is nevertheless used to approximate a sampling design where the $j$th  individual is sampled {\it without} replacement with probability $P_j$, even though under that design (unlike the multinomial model) no individual is included in the sample more than once.
+The multinomial model is a common approximation for other complex survey designs; \citep[see e.g., ][p.
+14]{Korn:1999}.
+For example, in the  Kalish, et al\cite{Kali:2021} analysis of Section~\ref{sec-Application} each individual in the sample is assigned a pseudo-weight approximating one over their sampling probability from
+a multinomial model.
+The actual sample was not a probability sample.
+In fact, it was a quota sample from a very large pool of self-selected volunteers, and the pseudo-weights were calculated using a different large survey that was a probability weighted survey.
+The pseudo-weights were calculated such that if they were analyzed under the multinomial model, they would adjust for selection bias due to self-selection of the volunteers and the imperfection of the quota sampling.
+
+\subsubsection{Multinomial Sampling Model}
+\label{sec-MultPoisson}
+
+Let $Y_1,\ldots, Y_N$ be the binary indicators of event in the $N$ individuals  in the population of interest,
+so the prevalence is $\beta = N^{-1} \sum_{j=1}^{N} Y_j$. There are many ways to design a complex survey sample, and it is often useful to analyze them as if
+individuals were sampled with replacement with the sampling probability of the $j$th  individual equal to $P_j$, with $\sum_{j=1}^{N} P_j = 1$
+In other words, we treat the sample as if it was $n$ independent multinomial samples each with one trial and selection probability vector  $[P_1,\ldots, P_N]$.
+Let $I_{ij}=1$ if the $i$th draw for the sample is individual $j$ in the population, and $0$ otherwise. Then let $y_i = Y_j$ and $p_i=P_j$ when $I_{ij}=1$.
+Here, following the tradition in the survey literature, we use capital letters for the population of interest (e.g., N,Y,P), and lower case letters for the sample (e.g., n,y,p).
+In this notation, both $y_i$ and $Y_j$ are fixed, and only the variables representing the sampling (i.e., the $I_{ij}$ variables) are random.
+Under this independent multinomial model, since $E(I_{ij})=P_j$, an unbiased estimator of $\beta$ is
+\begin{eqnarray}
+\hat{\beta} & = & \frac{1}{n} \sum_{i=1}^{n} \frac{ y_i}{N p_i} = \frac{1}{n} \sum_{i=1}^{n} \sum_{j=1}^{N}  \frac{ I_{ij}  Y_j}{N P_j}
+\label{eq:betahatMultinomial}
+\end{eqnarray}
+and an unbiased estimator of $\textrm{var}(\hat{\beta})$ under the multinomial model is
+\begin{eqnarray}
+\widehat{\textrm{var}}_{M}(\hat{\beta}) & = & \frac{1}{n (n-1)} \sum_{i=1}^{n} \left( \frac{y_i}{Np_i} - \hat{\beta}  \right)^2
+\label{eq:varMbetahat}
+\end{eqnarray}
+(see Korn and Graubard \cite{Korn:1999} Problem 2.2-10). We can write $\hat{\beta}$ as a weighted sum. Traditional survey weighting defines the weights so that
+the weight for the $i$th sampled individual can be interpreted as the number of individuals in the population that the $i$th sampled individual represents.
+Following that tradition, let   $w_i^{(trad)}= 1/(np_i)$ and $W_j^{trad)}=1/(nP_j)$, then the expected sum of the sampled weights is $N$,
+\begin{eqnarray*}
+E \left( \sum_{i=1}^{n} w_i^{(trad)} \right)  & = & E \left(  \sum_{i=1}^{n} \sum_{j=1}^{N} I_{ij} W_j^{(trad)} \right) =    \sum_{i=1}^{n} \sum_{j=1}^{N} \frac{ E(I_{ij})}{ n P_j} =   \sum_{i=1}^{n} \sum_{j=1}^{N} \frac{1}{n} = N.
+\end{eqnarray*}
+Sometimes the weights are scaled after selection so that the scaled weights are $w_i^{(strad)} = \frac{ N w_i^{(trad)} }{\sum_{i=1}^{n} w_i^{(trad)}}$ and are forced to sum to $N$.
+For example, in Kalish et al \cite{Kali:2021} rescaling (sometimes called post-stratification) was done in a more complicated manner to ensure that the weights summed to the US census population within age group, sex, race, ethnicity and region.
+
+For this paper we define the weights differently, because we want to model our estimator as a weighted sum of Poisson random variables.
+Thus, we use $w_i = 1/(nNp_i)$ and $W_j= 1/(nNP_j)$ so that the sums have expectation $1$.
+In the complex survey case,
+we start with the independent multinomial model as in equation~\ref{eq:betahatMultinomial}, then we use the relationship between the multinomial and Poisson distributions.
+Using the ``multinomial-Poisson transformation'', the maximum
+likelihood estimates (MLE) for a multinomial random variable are equivalent to the MLEs for independent Poisson random variables, and
+the variances are asymptotically equivalent (see Baker\cite{Baker:1994}).
+Even though we model $\hat{\beta}$ using multinomial random variables where there are many missing values (which occurs in our situation whenever $I_{ij}=0$),
+that multinomial-Poisson relationship holds even when there are missing variables (see Baker\cite{Baker:1994}, Section 3).
+For both the Poisson and multinomial models, $E(I_{ij}) = P_j$, and $\hat{\beta}$ is unbiased under either model.
+For the Poisson model, all the $I_{ij}$ are independent and each mean equals its variance, so that the variance of $\hat{\beta}$ under this model is
+\begin{eqnarray*}
+\textrm{var}_P \left(\hat{\beta} \right) & = & \textrm{var}_P \left(  \frac{1}{n}  \sum_{i=1}^{n} \sum_{j=1}^{N}  \frac{ I_{ij}  Y_j}{N P_j} \right)  \\
+& = &    \sum_{i=1}^{n} \sum_{j=1}^{N}  \frac{ \textrm{var}_P( I_{ij})  Y_j^2}{n^2 N^2 P_j^2}  \\
+& = &    \sum_{i=1}^{n} \sum_{j=1}^{N}  \frac{   Y_j}{n^2 N^2 P_j}.
+\end{eqnarray*}
+We estimate $\textrm{var}_P \left(\hat{\beta} \right)$ by multiplying each term in the sum by $I_{ij}/P_j$, which has an expectation of $1$ and eliminates terms of non-selected individuals, giving
+\begin{eqnarray}
+\widehat{\textrm{var}}_P \left(\hat{\beta} \right)
+& = &   \sum_{i=1}^{n} \sum_{j=1}^{N}  \frac{ I_{ij}  Y_j}{n^2 N^2 P_j^2}  =  \sum_{i=1}^{n}  \frac{  y_i}{n^2 N^2 p_i^2} \label{eq:hatvarbetahat1}
+\end{eqnarray}
+Under the Poisson model $\widehat{\textrm{var}}_P \left(\hat{\beta} \right)$ is an unbiased estimator of $\textrm{var}_P \left(\hat{\beta} \right)$.
+
 \section{Simulations}
@@
 
-We assess and compare our new method (Melding) to that of Lang and Reiczigel (LR) in a variety of simulated settings.
+We assess and compare our new method (Melding, i.e., equation~\ref{eq:srs-conf-int}) to that of Lang and Reiczigel (LR) in a variety of simulated settings.
 In each simulation, 100 subjects are tested to estimate prevalence, 60 are tested to estimate sensitivity, and 300 are tested to estimate specificity.
@@
     \includegraphics[width=0.8\textwidth]{figures/simple_coverage_comparison_plot.pdf}
-    \caption{Coverage properties of 95\% confidence intervals for our new method (Melding) and the state of the art method (Lang-Reiczigel) in a variety of settings, each simulated 10,000 times.}
+    \caption{Coverage properties of 95\% confidence intervals for our new method (Melding) and the Lang-Reiczigel method in a variety of settings, each simulated 10,000 times.}
     \label{fig:coverage_comparison_plot}
@@
     \includegraphics[width=0.8\textwidth]{figures/simple_lower_error_frequency_comparison_plot.pdf}
-    \caption{Lower error properties of 95\% confidence intervals for our new method (Melding) and the state of the art method (Lang-Reiczigel) in a variety of settings, each simulated 10,000 times.}
+    \caption{Lower error properties of 95\% confidence intervals for our new method (Melding) and the Lang-Reiczigel method in a variety of settings, each simulated 10,000 times.}
     \label{fig:lower_error_frequency_comparison_plot}
@@
     \includegraphics[width=0.8\textwidth]{figures/simple_upper_error_frequency_comparison_plot.pdf}
-    \caption{Upper error properties of 95\% confidence intervals for our new method (Melding) and the state of the art method (Lang-Reiczigel) in a variety of settings, each simulated 10,000 times.}
+    \caption{Upper error properties of 95\% confidence intervals for our new method (Melding) and the Lang-Reiczigel method in a variety of settings, each simulated 10,000 times.}
     \label{fig:upper_error_frequency_comparison_plot}
@@
 \subsection{Estimating Prevalence from a Weighted Sample with a Perfect Assay}
-
+\label{sim-perfect}
 We compare the wsPoisson method to the more traditional Dean-Pagano modification of the Agresti-Coull (DPAC) method and the Korn-Graubard (KG) method for survey proportions in a variety of settings.
-Our simulations examine varying levels of disease prevalence (0.5\% or 5\%), types of groups surveyed (50 groups 200 subjects or 8000 groups of 1 subject), distributions of weights among the groups (coefficient of variation from approximately 0\% to nearly 6\%), the number of groups with non-zero prevalence, and the weights of the groups with non-zero prevalence.
-For each scenario, 10,000 data sets are simulated and assessed.
+Our simulations examine varying levels of disease prevalence (0.5\% or 5\%), different types  survey designs (50 sampling strata with  200 subjects each or 8000 individuals, each with their own weight), distributions of weights among the sampling strata or individuals (coefficient of variation from approximately 0\% to nearly 600\%), and the number and weights of sampling strata with non-zero prevalence.
+For each combination of prevalence \( p \), and group type, up to 500 sets of weights are simulated.
+These 500 sets of weights are designed to span a range of coefficients of variation.
+For a target coefficient of variation, \( v \), \( n \) weights (\(w_i\)) are simulated by generating \( n \) samples from a \( \text{Beta} \left(\frac{1}{v^2} - \frac{1}{nv^2} - \frac{1}{n}, \frac{n-1}{v^2} - \frac{n-1}{nv^2} - \frac{n-1}{n} \right) \) distribution and normalizing so that \( \sum_{i=1}^n w_i = 1 \).
+This assures that the coefficient of variation among these weights is approximately \( v \).
+Then, certain weights are chosen to have non-zero prevalence (5\%, 25\%, or 75\% distributed either among the highest weights, lowest weights, or distributed uniformly).
+These weights with non-zero prevalence are given a prevalence such that \( \sum_{i=1}^n w_i \theta_i = p \).
+For each simulated set of parameters and weights, 10,000 data sets are simulated and assessed.
 
@@
 \includegraphics[width=0.8\textwidth]{figures/perfect_coverage_50_groups_0_005_prev.pdf}
-\caption{Coverage properties for the wsPoisson model and two standard methods, the Dean-Pagano modification of Agresti-Coull and Korn-Graubard
+\caption{Coverage properties for the wsPoisson model and two standard methods, the Dean-Pagano modification of the Agresti-Coull method and of the Korn-Graubard method.
 Each point represents 10,000 simulations of datasets from a population with 0.5\% Prevalence where 50 groups of 200 people are sampled.
 The horizontal dashed line indicates the nominal coverage, 95\%.
-Colored dashed lines are estimates from a logistic regression model using cubic splines.}
+Colored dashed lines are estimates from a logistic regression model using quadratic splines.}
 \label{fig:perfect_coverage_50_groups_0_005_prev}
@@
 \includegraphics[width=0.8\textwidth]{figures/perfect_coverage_8000_groups_0_005_prev.pdf}
-\caption{Coverage properties for the wsPoisson model and two standard methods, the Dean-Pagano modification of Agresti-Coull and Korn-Graubard
+\caption{Coverage properties for the wsPoisson model and two standard methods, the Dean-Pagano modification of the Agresti-Coull method and of the Korn-Graubard method.
 Each point represents 10,000 simulations of datasets from a population with 0.5\% Prevalence where 8000 individuals are sampled.
 The horizontal dashed line indicates the nominal coverage, 95\%.
-Colored dashed lines are estimates from a logistic regression model using cubic splines.}
+Colored dashed lines are estimates from a logistic regression model using quadratic splines.}
 \label{fig:perfect_coverage_8000_groups_0_005_prev}
@@
 \includegraphics[width=0.8\textwidth]{figures/perfect_coverage_50_groups_0_05_prev.pdf}
-\caption{Coverage properties for the wsPoisson model and two standard methods, the Dean-Pagano modification of Agresti-Coull and Korn-Graubard
+\caption{Coverage properties for the wsPoisson model and two standard methods, the Dean-Pagano modification of the Agresti-Coull method and of the Korn-Graubard method.
 Each point represents 10,000 simulations of datasets from a population with 5\% Prevalence where 50 groups of 200 people are sampled.
 The horizontal dashed line indicates the nominal coverage, 95\%.
-Colored dashed lines are estimates from a logistic regression model using cubic splines.}
+Colored dashed lines are estimates from a logistic regression model using quadratic splines.}
 \label{fig:perfect_coverage_50_groups_0_05_prev}
@@
 The horizontal dashed line indicates the nominal coverage, 95\%.
-Colored dashed lines are estimates from a logistic regression model using cubic splines.}
+Colored dashed lines are estimates from a logistic regression model using quadratic splines.}
 \label{fig:perfect_coverage_8000_groups_0_05_prev}
@@
 In each scenario, the assay has 95\% sensitivity.
-Each scenario is simulated 10,000 times, with new prevalence, sensitivity, and specificity surveys generated and 95\% confidence intervals are created.
+Each scenario creates up to 500 new sets of weights and $\theta_i$ parameters (as in Section~\ref{sim-perfect}), and each of those is simulated 10,000 times, with new prevalence, sensitivity, and specificity surveys generated and 95\% confidence intervals are created.
 Modelled after the study of Kalish, et al \cite{Kali:2021}, the simulated sensitivity is assessed based on 60 tests, while specificity is based on 300 tests.
@@
 The horizontal dashed line indicates the nominal coverage, 95\%.
-Colored dashed lines are estimates from a logistic regression model using cubic splines.}
+Colored dashed lines are estimates from a logistic regression model using quadratic splines.}
 \label{fig:imperfect_coverage_50_groups_0_005_prev}
@@
 The horizontal dashed line indicates the nominal coverage, 95\%.
-Colored dashed lines are estimates from a logistic regression model using cubic splines.}
+Colored dashed lines are estimates from a logistic regression model using quadratic splines.}
 \label{fig:imperfect_coverage_8000_groups_0_005_prev}
@@
 The horizontal dashed line indicates the nominal coverage, 95\%.
-Colored dashed lines are estimates from a logistic regression model using cubic splines.}
+Colored dashed lines are estimates from a logistic regression model using quadratic splines.}
 \label{fig:imperfect_coverage_50_groups_0_05_prev}
@@
 The horizontal dashed line indicates the nominal coverage, 95\%.
-Colored dashed lines are estimates from a logistic regression model using cubic splines.}
+Colored dashed lines are estimates from a logistic regression model using quadratic splines.}
 \label{fig:imperfect_coverage_8000_groups_0_05_prev}
@@
 Based on Figures~\ref{fig:imperfect_lower_error_frequency_50_groups_0_05_prev}--\ref{fig:imperfect_upper_error_frequency_8000_groups_0_05_prev}, we note that, in most settings, the two melding procedures result in conservative confidence intervals, often nearing 100\% coverage.
-With perfect specificity, the WprevSeSp Binomial method fails to maintain nominal coverage when the coefficient of variation among the weights is high.
+With perfect specificity, the WprevSeSp Binomial method fails to maintain nominal coverage when the coefficient of variation among the weights is high and specificity is perfect.
 Only our proposed WprevSeSp Poisson method maintains or exceed the desired coverage in all scenarios.
@@
 This method results in approximately 0\% coverage in any scenarios where specificity is less than perfect.
+For this reason, results from method are omitted in the figures.
 Because our methods appear to be very conservative, with coverage near 100\% in some cases, we present the widths of the confidence intervals in Figures~\ref{fig:imperfect_confidence_interval_width_50_groups_0_005_prev}--\ref{fig:imperfect_confidence_interval_width_8000_groups_0_05_prev}.
 The WprevSeSp Binomial and  WprevSeSp Poisson methods typically produce wide intervals of approximately the same size - sometimes as wide as 12\%, even when true prevalence is 0.05\%.
-One notable exception to this is presented in Figure \ref{fig:imperfect_confidence_interval_width_8000_groups_0_005_prev}, which shows that for tests with perfect specificity, the WprevSeSP produces much narrower confidence intervals than the other methods.
+One notable exception to this is presented in Figure \ref{fig:imperfect_confidence_interval_width_8000_groups_0_005_prev}, which shows that for tests with perfect specificity, the WprevSeSP Binomial method produces much narrower confidence intervals than the other method.
 
 \section{Applications}
-
-We also apply these two methods to a real data set from
+\label{sec-Application}
+
+We  apply these two methods to a real data set from
 Kalish, et al \cite{Kali:2021}.
-This data set was collected to estimate seroprevalence of SARS-CoV-2 in the United States between May and July 2020.
+This data set was collected to estimate seroprevalence of SARS-CoV-2 in undiagnosed adults in the United States between May and July 2020.
 The assay used in this data is estimated to have perfect sensitivity, based on 56 tests on individuals with confirmed SARS-CoV-2 and perfect specificity based on 300 tests on individuals confirmed to not have SARS-CoV-2.
 First we apply the methods to the full data set (\( n =  8058, \text{weight coefficient of variation} = 252\%\)).
-The Korn and Graubard type melded confidence interval with imperfect assay adjustments (WprevSeSp Binomial) produced the 95\% confidence interval for population prevalence (2.53\%, 6.68\%), while the wsPoisson type melded confidence interval with imperfect assay adjustments (WprevSeSp Poisson) produce the 95\% confidence interval (2.56\%, 7.54\%).
+The seroprevalence in Kalish, et al was 4.6\% with (95\% CI: 2.6\% to 6.5\%), using a confidence interval method that was nearly the same as the WprevSeSp Binomial method (the method Kalish et al  included a calculation of the variability of the weights due to the estimation of the weights, whereas in this paper we treat the weights as fixed constants).
+The Korn and Graubard type melded confidence interval with imperfect assay adjustments (WprevSeSp Binomial) studied in this paper produced the 95\% confidence interval for population prevalence nearly the equivalent, (2.53\%, 6.68\%).
+while the wsPoisson type melded confidence interval with imperfect assay adjustments (WprevSeSp Poisson) produced the 95\% confidence interval (2.56\%, 7.54\%).
 We also apply the wsPoisson method from Section~\ref{sec:weight-perfect}, which does not account for imperfections in the assay, resulting in a 95\% confidence interval of (3.04\%, 7.39\%).
 While all three intervals overlap to a large degree, the WprevSeSp Poisson interval is the widest.
-Our simulations show that the three procedures have similar coverage when specificity and weight coefficient of variation are both high, so this is unsurprising.
-
-We also apply the methods to the subset of only Hispanic participants (\( n = 1281, \text{weight coefficient of variation} = 306\% \)).
+Our simulations show that in this situation, the WprevSeSp Binomial interval may be the best, because with coefficient of variance about 250\% (see Figures~B15 and B20, top right panel) the error on both sides of the confidence interval is bounded at 2.5\% and the width of the intervals are better (Figure~B23).
+
+We also apply the methods to the subset of only Hispanic participants (\( n = 1281, \text{weight coefficient of variation} = 306\% \)), where Kalish et al estimated the undiagnosed adult seroprevalence estimate as 6.1\% (95\% CI: 2.4\% to 11.5\%).
 The WprevSeSp Binomial method produces a 95\% confidence interval for population prevalence (2.35\%, 11.75\%), while the WprevSeSp Poisson method produces a 95\% confidence interval (2.40\%, 20.02\%).
 The wsPoisson method produces a 95\% confidence interval of (2.80\%, 19.63\%).
-In this case, the two melded confidence intervals are much wider than the WprevSeSp Binomial interval, which is as expected since the melding method is designed to guarantee coverage.
-The somewhat unexpected smaller WprevSeSp Binomial interval, but may be because prevalence is concentrated among respondents with lower weights, or be related to the smaller sample size used to measure prevalence, which is not reflected in our simulations.
+In this case, the two melded confidence intervals are much wider than the WprevSeSp Binomial interval, which is as expected since the melding method is designed to guarantee coverage, although the simulations show that the WprevSeSp Binomial interval may be reasonable (see e.g., Figure~B20).
+The smaller WprevSeSp Binomial interval is also unsurprising and is similar to the results observed in our simulation study.
 
@@
 
-% Misc quotes from Mike to incorporate:
-
-% \begin{itemize}
-%     \item The last time we met, you mentioned that it would be nice to report the weights in terms of coefficient of variation.
-I went back to the data from the COVID seroprevalence paper in undiagnosed adults, and I calculated a coefficient of variation  of 2.52 = 252\% for all 8058 individuals, and looking at subsets, I found that the Hispanics had a CV=306\%.
-%     \item For some weighting for surveys to adjust for selection bias, the coefficient of variation may be large.
-For example, the coefficient of variation of the weights (CVW) for the main estimate of seroprevalence in Kalish, et al (2021) had CVW=252\%, and it could be even larger for subsets of the population (e.g., Hispanics had CVW=306\%).
-% \end{itemize}
-
 \section{Discussion}
 
-We presented several methods for creating confidence to assess disease prevalence in variety of settings, including simple random samples with imperfect tests, weighted sampling with perfect tests, and weighted sampling with imperfect tests.
+We presented several methods for creating confidence intervals to assess disease prevalence in variety of settings, including simple random samples with imperfect tests, weighted sampling with perfect tests, and weighted sampling with imperfect tests.
+One of the new methods was very similar to the method used by Kalish et al\cite{Kali:2021}, and in this paper we have explored its properties.
 These new confidence intervals appear to guarantee coverage in most simulated settings, and in general to demonstrate higher coverage than competitor methods.
-In the case of the simple random sample with an imperfect test, we are able to bound the lower error rate for a 95\% confidence interval at 2.5\%, while the state-of-the-art method maintains 95\% coverage by allowing a higher lower error rate.
+In the case of the simple random sample with an imperfect test, our new methods are able to bound the lower error rate for a 95\% confidence interval at 2.5\%, while the Lang-Reiczigel\cite{Lang:2014} method maintains 95\% coverage by allowing a higher lower error rate.
+A big advantage of our method is that it may be applied with complex survey methods, where each individual has their own weight, such as in Kalish et al\cite{Kali:2021}. 
+However, our method  only studied fixed weights and not when the weights are estimated as in Kalish et al.
+Further worked is needed to address such cases.
+In addition, further worked is needed to consider other complex sample designs such as multistage cluster designs that are used in  household and institutional surveys such hospital and medical practice surveys.
+
+Our method was slightly different to that used in Kalish, et al\cite{Kali:2021}, in that the latter method included estimates of the variability of the weights; however, recalculating the confidence intervals on the same data shows that in that case there was little difference.
+%[BARRY TO ADD MORE DISCUSSION AND REFERENCES ABOUT ESTIMATING VARIABILITY IN %WEIGHTS, ETC., AND TRIMMING WEIGHTS].
+
 Our methods' conservative properties are especially advantageous in settings where the competitor methods exhibit much lower than nominal coverage.
@@
 1 &	\hat{\phi}_n < \hat{\phi}_p < \hat{\theta}_1 \\
-\frac{\hat{\theta}_1 - \hat{\phi}_n}{\hat{\phi}_p - \hat{\phi}_n} & \hat{\phi}_n < \hat{\phi}_p = \hat{\theta}_1 \\
+\frac{\hat{\theta}_1 - \hat{\phi}_n}{\hat{\phi}_p - \hat{\phi}_n} = 1 & \hat{\phi}_n < \hat{\phi}_p = \hat{\theta}_1 \\
 \frac{\hat{\theta}_1 - \hat{\phi}_n}{\hat{\phi}_p - \hat{\phi}_n} & \hat{\phi}_n < \hat{\theta}_1 < \hat{\phi}_p \\
@@
 0 & \hat{\theta}_1 < \hat{\phi}_n < \hat{\phi}_p  \\
-\frac{\hat{\theta}_1 - \hat{\phi}_n}{\hat{\phi}_p - \hat{\phi}_n} & \hat{\phi}_n = \hat{\theta}_1 < \hat{\phi}_p \\
+\frac{\hat{\theta}_1 - \hat{\phi}_n}{\hat{\phi}_p - \hat{\phi}_n} = 0 & \hat{\phi}_n = \hat{\theta}_1 < \hat{\phi}_p \\
 \frac{\hat{\theta}_1 - \hat{\phi}_n}{\hat{\phi}_p - \hat{\phi}_n} &	\hat{\phi}_n < \hat{\theta}_1 < \hat{\phi}_p \\
-\frac{\hat{\theta}_1 - \hat{\phi}_n}{\hat{\phi}_p - \hat{\phi}_n} & \hat{\phi}_n < \hat{\theta}_1 = \hat{\phi}_p \\
+\frac{\hat{\theta}_1 - \hat{\phi}_n}{\hat{\phi}_p - \hat{\phi}_n} = 1 & \hat{\phi}_n < \hat{\theta}_1 = \hat{\phi}_p \\
 1 & \hat{\phi}_n < \hat{\phi}_p < \hat{\theta}_1 \\
@@
 \includegraphics[width=0.8\textwidth]{figures/perfect_lower_error_frequency_50_groups_0_005_prev.pdf}
-\caption{Lower error properties for the wsPoisson model and two standard methods, the Dean-Pagano modification of Agresti-Coull and Korn-Graubard
+\caption{Lower error properties for the wsPoisson model and two standard methods, the Dean-Pagano modification of the Agresti-Coull method and of the Korn-Graubard method.
 Each point represents 10,000 simulations of datasets from a population with 0.5\% Prevalence where 50 groups of 200 people are sampled.
 The horizontal dashed line indicates the nominal lower error rate, 2.5\%.
-Colored dashed lines are estimates from a logistic regression model using cubic splines.}
+Colored dashed lines are estimates from a logistic regression model using quadratic splines.}
 \label{fig:perfect_lower_error_frequency_50_groups_0_005_prev}
@@
 \includegraphics[width=0.8\textwidth]{figures/perfect_lower_error_frequency_8000_groups_0_005_prev.pdf}
-\caption{Lower error properties for the wsPoisson model and two standard methods, the Dean-Pagano modification of Agresti-Coull and Korn-Graubard
+\caption{Lower error properties for the wsPoisson model and two standard methods, the Dean-Pagano modification of the Agresti-Coull method and of the Korn-Graubard method.
 Each point represents 10,000 simulations of datasets from a population with 0.5\% Prevalence where 8000 individuals are sampled.
 The horizontal dashed line indicates the nominal lower error rate, 2.5\%.
-Colored dashed lines are estimates from a logistic regression model using cubic splines.}
+Colored dashed lines are estimates from a logistic regression model using quadratic splines.}
 \label{fig:perfect_lower_error_frequency_8000_groups_0_005_prev}
@@
 \includegraphics[width=0.8\textwidth]{figures/perfect_lower_error_frequency_50_groups_0_05_prev.pdf}
-\caption{Lower error properties for the wsPoisson model and two standard methods, the Dean-Pagano modification of Agresti-Coull and Korn-Graubard
+\caption{Lower error properties for the wsPoisson model and two standard methods, the Dean-Pagano modification of the Agresti-Coull method and of the Korn-Graubard method.
 Each point represents 10,000 simulations of datasets from a population with 5\% Prevalence where 50 groups of 200 people are sampled.
 The horizontal dashed line indicates the nominal lower error rate, 2.5\%.
-Colored dashed lines are estimates from a logistic regression model using cubic splines.}
+Colored dashed lines are estimates from a logistic regression model using quadratic splines.}
 \label{fig:perfect_lower_error_frequency_50_groups_0_05_prev}
@@
 \includegraphics[width=0.8\textwidth]{figures/perfect_lower_error_frequency_8000_groups_0_05_prev.pdf}
-\caption{Lower error properties for the wsPoisson model and two standard methods, the Dean-Pagano modification of Agresti-Coull and Korn-Graubard
+\caption{Lower error properties for the wsPoisson model and two standard methods, the Dean-Pagano modification of the Agresti-Coull method and of the Korn-Graubard method.
 Each point represents 10,000 simulations of datasets from a population with 5\% Prevalence where 8000 individuals are sampled.
 The horizontal dashed line indicates the nominal lower error rate, 2.5\%.
-Colored dashed lines are estimates from a logistic regression model using cubic splines.}
+Colored dashed lines are estimates from a logistic regression model using quadratic splines.}
 \label{fig:perfect_lower_error_frequency_8000_groups_0_05_prev}
@@
 \includegraphics[width=0.8\textwidth]{figures/perfect_upper_error_frequency_50_groups_0_005_prev.pdf}
-\caption{Upper error properties for the wsPoisson model and two standard methods, the Dean-Pagano modification of Agresti-Coull and Korn-Graubard
+\caption{Upper error properties for the wsPoisson model and two standard methods, the Dean-Pagano modification of the Agresti-Coull method and of the Korn-Graubard method.
 Each point represents 10,000 simulations of datasets from a population with 0.5\% Prevalence where 50 groups of 200 people are sampled.
 The horizontal dashed line indicates the nominal upper error rate, 2.5\%.
-Colored dashed lines are estimates from a logistic regression model using cubic splines.}
+Colored dashed lines are estimates from a logistic regression model using quadratic splines.}
 \label{fig:perfect_upper_error_frequency_50_groups_0_005_prev}
@@
 \includegraphics[width=0.8\textwidth]{figures/perfect_upper_error_frequency_8000_groups_0_005_prev.pdf}
-\caption{Upper error properties for the wsPoisson model and two standard methods, the Dean-Pagano modification of Agresti-Coull and Korn-Graubard
+\caption{Upper error properties for the wsPoisson model and two standard methods, the Dean-Pagano modification of the Agresti-Coull method and of the Korn-Graubard method.
 Each point represents 10,000 simulations of datasets from a population with 0.5\% Prevalence where 8000 individuals are sampled.
 The horizontal dashed line indicates the nominal upper error rate, 2.5\%.
-Colored dashed lines are estimates from a logistic regression model using cubic splines.}
+Colored dashed lines are estimates from a logistic regression model using quadratic splines.}
 \label{fig:perfect_upper_error_frequency_8000_groups_0_005_prev}
@@
 \includegraphics[width=0.8\textwidth]{figures/perfect_upper_error_frequency_50_groups_0_05_prev.pdf}
-\caption{Upper error properties for the wsPoisson model and two standard methods, the Dean-Pagano modification of Agresti-Coull and Korn-Graubard
+\caption{Upper error properties for the wsPoisson model and two standard methods, the Dean-Pagano modification of the Agresti-Coull method and of the Korn-Graubard method.
 Each point represents 10,000 simulations of datasets from a population with 5\% Prevalence where 50 groups of 200 people are sampled.
 The horizontal dashed line indicates the nominal upper error rate, 2.5\%.
-Colored dashed lines are estimates from a logistic regression model using cubic splines.}
+Colored dashed lines are estimates from a logistic regression model using quadratic splines.}
 \label{fig:perfect_upper_error_frequency_50_groups_0_05_prev}
@@
 \includegraphics[width=0.8\textwidth]{figures/perfect_upper_error_frequency_8000_groups_0_05_prev.pdf}
-\caption{Upper error properties for the wsPoisson model and two standard methods, the Dean-Pagano modification of Agresti-Coull and Korn-Graubard
+\caption{Upper error properties for the wsPoisson model and two standard methods, the Dean-Pagano modification of the Agresti-Coull method and of the Korn-Graubard method.
 Each point represents 10,000 simulations of datasets from a population with 5\% Prevalence where 8000 individuals are sampled.
 The horizontal dashed line indicates the nominal upper error rate, 2.5\%.
-Colored dashed lines are estimates from a logistic regression model using cubic splines.}
+Colored dashed lines are estimates from a logistic regression model using quadratic splines.}
 \label{fig:perfect_upper_error_frequency_8000_groups_0_05_prev}
@@
 \includegraphics[width=0.8\textwidth]{figures/perfect_confidence_interval_width_50_groups_0_005_prev}
-\caption{Confidence interval width properties for the wsPoisson model and two standard methods, the Dean-Pagano modification of Agresti-Coull and Korn-Graubard
+\caption{Confidence interval width properties for the wsPoisson model and two standard methods, the Dean-Pagano modification of the Agresti-Coull method and of the Korn-Graubard method.
 Each point represents 10,000 simulations of datasets from a population with 0.5\% Prevalence where 50 groups of 200 people are sampled.
-Colored dashed lines are estimates from a logistic regression model using cubic splines.}
+Colored dashed lines are estimates from a logistic regression model using quadratic splines.}
 \label{fig:perfect_confidence_interval_width_50_groups_0_005_prev}
@@
 \includegraphics[width=0.8\textwidth]{figures/perfect_confidence_interval_width_50_groups_0_05_prev}
-\caption{Confidence interval width properties for the wsPoisson model and two standard methods, the Dean-Pagano modification of Agresti-Coull and Korn-Graubard
+\caption{Confidence interval width properties for the wsPoisson model and two standard methods, the Dean-Pagano modification of the Agresti-Coull method and of the Korn-Graubard method.
 Each point represents 10,000 simulations of datasets from a population with 5\% Prevalence where 50 groups of 200 people are sampled.
-Colored dashed lines are estimates from a logistic regression model using cubic splines.}
+Colored dashed lines are estimates from a logistic regression model using quadratic splines.}
 \label{fig:perfect_confidence_interval_width_50_groups_0_05_prev}
@@
 \includegraphics[width=0.8\textwidth]{figures/perfect_confidence_interval_width_8000_groups_0_005_prev}
-\caption{Confidence interval width properties for the wsPoisson model and two standard methods, the Dean-Pagano modification of Agresti-Coull and Korn-Graubard
+\caption{Confidence interval width properties for the wsPoisson model and two standard methods, the Dean-Pagano modification of the Agresti-Coull method and of the Korn-Graubard method.
 Each point represents 10,000 simulations of datasets from a population with 0.5\% Prevalence where 8000 individuals are sampled.
-Colored dashed lines are estimates from a logistic regression model using cubic splines.}
+Colored dashed lines are estimates from a logistic regression model using quadratic splines.}
 \label{fig:perfect_confidence_interval_width_8000_groups_0_005_prev}
@@
 \includegraphics[width=0.8\textwidth]{figures/perfect_confidence_interval_width_8000_groups_0_05_prev}
-\caption{Confidence interval width properties for the wsPoisson model and two standard methods, the Dean-Pagano modification of Agresti-Coull and Korn-Graubard
+\caption{Confidence interval width properties for the wsPoisson model and two standard methods, the Dean-Pagano modification of the Agresti-Coull method and of the Korn-Graubard method.
 Each point represents 10,000 simulations of datasets from a population with 5\% Prevalence where 8000 individuals are sampled.
-Colored dashed lines are estimates from a logistic regression model using cubic splines.}
+Colored dashed lines are estimates from a logistic regression model using quadratic splines.}
 \label{fig:perfect_confidence_interval_width_8000_groups_0_05_prev}
@@
 The horizontal dashed line indicates the nominal lower error rate, 2.5\%.
-Colored dashed lines are estimates from a logistic regression model using cubic splines. If the WprevSeSp Binomial line is not visible, then it is covered by the WprevSe Sp Poisson line.}
+Colored dashed lines are estimates from a logistic regression model using quadratic splines. If the WprevSeSp Binomial line is not visible, then it is covered by the WprevSeSp Poisson line.}
 \label{fig:imperfect_lower_error_frequency_50_groups_0_05_prev}
@@
 The horizontal dashed line indicates the nominal lower error rate, 2.5\%.
-Colored dashed lines are estimates from a logistic regression model using cubic splines.}
+Colored dashed lines are estimates from a logistic regression model using quadratic splines.}
 \label{fig:imperfect_lower_error_frequency_50_groups_0_005_prev}
@@
 The horizontal dashed line indicates the nominal lower error rate, 2.5\%.
-Colored dashed lines are estimates from a logistic regression model using cubic splines.}
+Colored dashed lines are estimates from a logistic regression model using quadratic splines.}
 \label{fig:imperfect_lower_error_frequency_8000_groups_0_05_prev}
@@
 The horizontal dashed line indicates the nominal lower error rate, 2.5\%.
-Colored dashed lines are estimates from a logistic regression model using cubic splines.}
+Colored dashed lines are estimates from a logistic regression model using quadratic splines.}
 \label{fig:imperfect_lower_error_frequency_8000_groups_0_005_prev}
@@
 The horizontal dashed line indicates the nominal upper error rate, 2.5\%.
-Colored dashed lines are estimates from a logistic regression model using cubic splines.}
+Colored dashed lines are estimates from a logistic regression model using quadratic splines.}
 \label{fig:imperfect_upper_error_frequency_50_groups_0_005_prev}
@@
 The horizontal dashed line indicates the nominal upper error rate, 2.5\%.
-Colored dashed lines are estimates from a logistic regression model using cubic splines.}
+Colored dashed lines are estimates from a logistic regression model using quadratic splines.}
 \label{fig:imperfect_upper_error_frequency_8000_groups_0_005_prev}
@@
 The horizontal dashed line indicates the nominal upper error rate, 2.5\%.
-Colored dashed lines are estimates from a logistic regression model using cubic splines.}
+Colored dashed lines are estimates from a logistic regression model using quadratic splines.}
 \label{fig:imperfect_upper_error_frequency_50_groups_0_05_prev}
@@
 The horizontal dashed line indicates the nominal upper error rate, 2.5\%.
-Colored dashed lines are estimates from a logistic regression model using cubic splines.}
+Colored dashed lines are estimates from a logistic regression model using quadratic splines.}
 \label{fig:imperfect_upper_error_frequency_8000_groups_0_05_prev}
@@
 Each datasets also includes simulated results of tests to evaluate the sensitivity and specificity of the assay performed on 60 and 300 individuals, respectively.
-Colored dashed lines are estimates from a logistic regression model using cubic splines.}
+Colored dashed lines are estimates from a logistic regression model using quadratic splines.}
 \label{fig:imperfect_confidence_interval_width_50_groups_0_005_prev}
@@
 Each datasets also includes simulated results of tests to evaluate the sensitivity and specificity of the assay performed on 60 and 300 individuals, respectively.
-Colored dashed lines are estimates from a logistic regression model using cubic splines.}
+Colored dashed lines are estimates from a logistic regression model using quadratic splines.}
 \label{fig:imperfect_confidence_interval_width_50_groups_0_05_prev}
@@
 Each datasets also includes simulated results of tests to evaluate the sensitivity and specificity of the assay performed on 60 and 300 individuals, respectively.
-Colored dashed lines are estimates from a logistic regression model using cubic splines.}
+Colored dashed lines are estimates from a logistic regression model using quadratic splines.}
 \label{fig:imperfect_confidence_interval_width_8000_groups_0_005_prev}
@@
 Each datasets also includes simulated results of tests to evaluate the sensitivity and specificity of the assay performed on 60 and 300 individuals, respectively.
-Colored dashed lines are estimates from a logistic regression model using cubic splines.}
+Colored dashed lines are estimates from a logistic regression model using quadratic splines.}
 \label{fig:imperfect_confidence_interval_width_8000_groups_0_05_prev}

### 2022-08-28 response_to_decision_letter.tex
Updates from Overleaf

\documentclass[11pt]{article}
\usepackage{xcolor}
\begin{document}

\textbf{Response to Review for Manuscript Number: SIM-22-0426}

Title: "Confidence Intervals for Prevalence Estimates from Complex Surveys with Imperfect Assays"

We are grateful to the editor and reviewers for their thoughtful comments and the opportunity to improve and resubmit our manuscript.
Our response to individual comments from each reviewer follow.

\textbf{Reviewer: 1}
(There are no comments.)

\textbf{Reviewer 2}

\begin{itemize}
    \item \textbf{This paper has many strengths and yet could benefit from a revision that clarifies the main contribution(s) of the work. The new method is mathematically clever and appears to have the nice property of guaranteeing nominal CI coverage (though it is unclear if this has been rigorously proved); the contribution alone of generalizing the melded CI to more than 2 parameters is interesting, as well as the applicability of their method to complex surveys where each individual has their own weight. There was clearly painstaking detail taken in simulation studies to evaluate the new method.}

    \item \textbf{The abstract and introduction imply that a main contribution of the work is that the new methods have better properties in simulations, and no drawbacks are hinted at. However, it is not clear that the new methods achieved better performance. Performance is strong at very low prevalences, but fades at higher prevalences. This is probably because the gamma CI method uses a Poisson approximation to the binomial that assumes a small binomial parameter, i.e., a small prevalence closer to 0 than 1.}

    \textbf{“our methods appear to guarantee coverage in simulated settings, while competing methods are shown to achieve much lower than nominal coverage” (Abstract).}

    \textbf{“we…show through simulations that [our new method] beats the best of [the established frequentist competitors] in each of the three stages **with respect to guaranteeing coverage**” (Introduction, last paragraph; emphasis added.) The three stages are (1) random samples with misclassification; (2) weighted samples without misclassification (using a perfect assay); and (3) weighted samples with misclassification.}

    We have added some mentions in the text about the drawbacks to our proposed methods and clarify the scenarios when our methods are shown to be superior:

    Abstract:
    ``We demonstrate that our methods appear to guarantee coverage in simulated settings, while competing methods are shown to achieve much lower than nominal coverage in some settings, especially when overall prevalence is very low. In other settings, our methods are shown to be overly conservative."

    Introduction:

    ``However, in some simulated settings, our proposed methods are overly conservative, while competitor methods maintain closer to nominal coverage."

    Discussion:
    ``These new confidence intervals appear to guarantee coverage in most simulated settings, including some scenarios where competitor methods dramatically under-cover.
    In general, our methods demonstrate higher coverage than competitor methods in most scenarios, sometimes being very conservative while competitor methods demonstrate closer to nominal coverage.""

    \item \textbf{The new method may guarantee coverage well, but it seems to do so by using conservative intervals that over-cover. Should such intervals be preferred to intervals that are more permissive (anti-conservative)?}

    \textcolor{red}{Mike, can you add any comments about this?}

    \item \textbf{For Stage 1 (Sections 2.2/3.1), consider Figure 1. The text states that “both [our new and the existing Lang-Reiczigel] methods achieve approximately nominal coverage, with the melding method being somewhat more conservative.” This definition of “approximately nominal” is debatable; the figure shows that the existing Lang-Reiczigel method achieves nominal 95\% coverage in most situations, while the melding method usually over-covers.}

    We have updated the text to more accurately reflect the simulation results:

    ``Figure~1 shows that, when specificity is less than perfect, the Lang-Reiczigel method achieves approximately nominal coverage, while the melding method is slightly more conservative, generally demonstrating 96\%-97\% coverage with 95\% confidence intervals."

    \item \textbf{(The discussion of lower and upper error probabilities in Section 3.1 is similar. The authors criticize the Lang-Reiczigel intervals for having “lower error above 2.5\%, which is undesirable…”. However, neither the lower nor upper errors of the melding method achieves nominal 2.5\% in any scenario. This is undesirable and unremarked upon. As a minor point, no reason for focusing on lower and upper error probabilities is stated; those Figures may be better relegated to the appendices.)}

    We have updated the text to motivate the figures and remark upon the undesirable lower error properties of the melding method:

    ``For a more nuanced depiction of each method's properties, we separate the overall coverage into lower and upper errors.
    Figure~3 shows that both methods make upper errors with roughly the same frequency.
    Figure~2 demonstrates that while the melding procedure bounds the lower error frequency below 2.5\%, the Lang-Reiczigel method generally has lower error above 2.5\%.
    Each of these behaviors may be undesirable, depending on the context in which the methods are applied.
    For applications in which there is a need to bound the lower errors, the melding method is superior."

    \item \textbf{For Stage 2 (Sections 2.3/3.2), Figures 4-5 display scenarios where prevalence is 0.5\%, and the new wsPoisson method generally performs well compared to competitors. However, the competitor methods demonstrate almost uniformly better properties (coverage closer to nominal) than the authors’ wsPoisson method when prevalence is 5\% in Figures 6-7. This is not pointed out in the textual description in the last paragraph of Section 3.2}

    We have updated the text to reflect this observation:
    ``In scenarios with higher overall prevalence, the Agresti-Coul and Korn-Graubard methods achieve close to nominal coverage, while the wsPoisson method strongly over-covers."

    \item \textbf{For Stage 3 (Sections 2.4/3.3), the only comparator shown in the Figures is the WprevSeSp Binomial developed in the Kalish et al. paper (despite the text saying wsPoisson was also compared). Again, the textual description belies the results in the Figures. While there are some scenarios in Figures 8-11 where the WprevSeSp Binomial interval under-covers dramatically, most scenarios appear to show that binomial interval having consistently closer-to-nominal coverage compared to the over-covering WprevSeSp Poisson.}

    In our simulations, we did compare the wsPoisson method to the two melding methods, but the results were poor and made comparison between the melding methods more difficult to observe in the figures.
    We have clarified this point in the text.
    We have also noted the generally superior performance of the WprevSeSp Binomial method:

    ``In the other scenarios tested, the WprevSeSp Binomial generally achieves closer to nominal coverage than the WprevSeSp Poisson."

    \item \textbf{Is there a substantive reason that the prevalences assessed in simulations are 0.5\% and 5\%? While the number of scenarios evaluated are clearly substantial, it would be interesting to understand the methods’ performance across a larger portion of the [0, 1] prevalence parameter space.}

    We only evaluated 0.5\% and 5\% because the greater prevalence leads to over-coverage for our methods.
    We have updated the text to point to this drawback throughout.

    \item If the main contribution of the paper is superior coverage properties, then the above issues of the Poisson approximation assuming a small prevalence as well as simulation results and interpretation should be addressed. The authors could instead elaborate on other contributions of the work detailed above.

    \item Minor issues:

    \begin{itemize}
        \item \textbf{2.2 Line 23-24: “where we define 0/0” seems unusual when this is typically taken as an indeterminate value. Clarify what is meant? The estimator in Equation 5 seems to be the Rogan-Gladen (1978) estimator with truncation in cases when the estimator falls outside the parameter range of [0, 1]?}

        We have adjusted the definition of the estimator to avoid defining 0/0 = 0. It is now presented as
        \begin{equation}
        \hat{\beta}^* \equiv 
        g(\hat{\theta}_1, \hat{\phi}_n, \hat{\phi}_p)
        \equiv 
        \left\{ 
        \begin{array}{ll}
        1 & \mbox{ if $\hat{\phi}_n < \hat{\phi}_p < \hat{\theta}_1$ }  \\
        \frac{\hat{\theta}_1 - \hat{\phi}_n}{\hat{\phi}_p - \hat{\phi}_n} & 
        \mbox{ if $\hat{\phi}_p > \hat{\theta}_1 \geq \hat{\phi}_n$ } \\
        0 & \mbox{ otherwise.} 
        \end{array}
        \right.
        \end{equation}

        \item \textbf{2.2 Lines 24-32: It would be helpful for the unfamiliar reader to include more background on the melding method. For instance, what exactly is the definition of the confidence distribution? Why are the confidence distributions Beta for a binomial experiment?}

        I have added the definition of the confidence distribution to section 2.2
        \textcolor{red}{Mike, feel free to add more context/intution.}

        \item \textbf{As a formatting note, the paper could be much more concise if (a) many of the figures were moved to appendices, and (b) fewer lines are used for equations, e.g., the definition of the Lang-Reiczigel interval in Section 2.2.}

        We have adjusted the presentation of Section 2.2 to reduce the lines used.

        \item \textbf{Please elaborate on why the third equality in Section 2.5.2, p. 8, lines 17-25 (variance of  beta-hat) holds.}

        The referenced equation is reproduced here:
        \begin{eqnarray*}
        \textrm{var}_P \left(\hat{\beta} \right) & = & \textrm{var}_P \left(  \frac{1}{n}  \sum_{i=1}^{n} \sum_{j=1}^{N}  \frac{ I_{ij}  Y_j}{N P_j} \right)  \\
        & = &    \sum_{i=1}^{n} \sum_{j=1}^{N}  \frac{ \textrm{var}_P( I_{ij})  Y_j^2}{n^2 N^2 P_j^2}  \\
        & = &    \sum_{i=1}^{n} \sum_{j=1}^{N}  \frac{   Y_j}{n^2 N^2 P_j}.
        \end{eqnarray*}

        The third equality holds because \( \textrm{var}_P( I_{ij}) = P_j \) and \( Y_j^2= Y_j \), because \( Y_j \) is binary.

        We have clarified this in the text:

        \begin{eqnarray*}
        \textrm{var}_P \left(\hat{\beta} \right) & = & \textrm{var}_P \left(  \frac{1}{n}  \sum_{i=1}^{n} \sum_{j=1}^{N}  \frac{ I_{ij}  Y_j}{N P_j} \right)  \\
        & = &    \sum_{i=1}^{n} \sum_{j=1}^{N}  \frac{ \textrm{var}_P( I_{ij})  Y_j^2}{n^2 N^2 P_j^2}  \\
        & = &    \sum_{i=1}^{n} \sum_{j=1}^{N}  \frac{ \textrm{var}_P( I_{ij})  Y_j}{n^2 N^2 P_j^2}  \\
        & = &    \sum_{i=1}^{n} \sum_{j=1}^{N}  \frac{   Y_j}{n^2 N^2 P_j}.
        \end{eqnarray*}

        \item \textbf{There are several typographical errors that distract the reader. The manuscript should be reread with this attention to detail in mind. Some instances: 2.3 Line 52: “the wsPoison method”; Section 5: “Further worked is needed”; the inconsistency about the assessment of wsPoisson in the simulations; etc.}

        \textcolor{red}{Damon: I fixed these errors and a few more. Mike and Barry should also take a look for proofreading.}

    \end{itemize}
\end{itemize}

\end{document}

### 2022-08-28 PrevAdjSurvey.tex
Updates from Overleaf

@@
 \usepackage{moreverb}
-
+\usepackage{pdfpages}
 \DeclareMathOperator{\Var}{Var}
@@
 \begin{document}
-
+\includepdf{pub_form-coversheet-peer_reviewed-2.pdf}
 \title{Confidence Intervals for Prevalence Estimates from Complex Surveys with Imperfect Assays}
@@
 Our methods use survey results and measurements of test sensitivity and specificity to construct melded confidence intervals.
-We demonstrate that our methods appear to guarantee coverage in simulated settings, while competing methods are shown to achieve much lower than nominal coverage.
+We demonstrate that our methods appear to guarantee coverage in simulated settings, while competing methods are shown to achieve much lower than nominal coverage in some settings, especially when overall prevalence is very low.
+In other settings, our methods are shown to be overly conservative.
 We apply our method to a seroprevalence survey of SARS-CoV-2 in undiagnosed adults in the United States between May and July 2020.}
@@
 
-In simulations we compare our method to established frequentist competitors.
-and  show through simulations that it beats the best of those in each of the three stages with respect to guaranteeing coverage. 
+In simulations we compare our method to established frequentist competitors and  show through simulations that it beats the best of those in each of the three stages with respect to guaranteeing coverage.
+However, in some simulated settings, our proposed methods are overly conservative, while competitor methods maintain closer to nominal coverage.
 We did not include in our simulations the new methods that have been developed in response to the COVID-19 pandemic and are not yet in print in peer reviewed journals \cite{Cai:2020,DiCi:2021,rosin2021estimating}.
@@
 \frac{\hat{\theta}_1 - \hat{\phi}_n}{\hat{\phi}_p - \hat{\phi}_n} & 
-\mbox{ if $\hat{\phi}_p \geq \hat{\theta}_1 \geq \hat{\phi}_n$ } \\
-0 & \mbox{ otherwise} 
+\mbox{ if $\hat{\phi}_p > \hat{\theta}_1 \geq \hat{\phi}_n$ } \\
+0 & \mbox{ otherwise.} 
 \end{array}
@@
 \end{equation}
-where we define $0/0=0$.
-% Damon, that definition is arbitrary, it is just used so that everything is defined
+% Damon, that definition is arbitrary, it is just used so that
 
 To create a confidence interval for \( \hat{\beta}^* \), we use a generalization of the melding method \cite{FayP:2015}, which makes use of lower and upper confidence distributions on functions of independent estimators to account for variability in \( \hat{\theta}_1 \), \( \hat{\phi}_n \), and \( \hat{\phi}_p \).
-Confidence distributions are like frequentist posterior distributions\cite{Xie2013}.
+Confidence distributions are frequentist estimators of a parameter, which can be used similarly to the bootstrap or posterior distributions.
+Formally, a confidence distribution is a function \(H_{n}(\cdot)=H_{n}(\mathbf{x}, \cdot)\) on \(\mathcal{X} \times \Theta \rightarrow[0,1]\), where \( \Theta \) is the parameter space of the parameter of interest (\( \theta \)) and \( \mathcal{X} \) is the sample space corresponding to sample data \(\mathbf{x}=\left\{x_{1}, \ldots, x_{n}\right\}\), which has two properties: (i) For each \(\mathbf{x} \in \mathcal{X}, H_{n}(\cdot)\) is a cumulative distribution function on \(\Theta \).
+(ii) At the true parameter value \(\theta=\theta_{0}, H_{n}\left(\theta_{0}\right) \equiv H_{n}\left(\mathbf{x}, \theta_{0}\right)\), as a function of the sample \(\mathbf{x}\), follows the uniform distribution \(U[0,1]\) \cite{Xie2013}.
+
 The lower and upper confidence distributions are used with discrete responses to ensure the validity of the resulting inferences, and for the binomial case they are equivalent to the posterior distributions that result from using well-calibrated null preference priors \cite{Fay2021}.
@@
 
-\begin{equation*}
-    d\beta = 2 \cdot q_Z^2 \cdot\left\{ \beta_1^{*\prime} \cdot \frac{\phi_p^\prime (1 - \phi_p^\prime)}{m_p^\prime} - (1 - \beta_1^{*\prime}) \cdot \frac{(1 - \phi_n^\prime) \phi_n^\prime}{m_n^\prime}  \right\}
-\end{equation*}
-
-\begin{equation*}
-    \Var(\beta_1^{*\prime}) = \frac{ \frac{\beta_1^{*\prime}(1 - \beta_1^{*\prime})}{n_1} + \left(\beta_1^{*\prime}\right)^2 \frac{\phi_p^\prime (1 - \phi_p^\prime)}{m_p} + \left(1 + \beta_1^{*\prime}\right)^2 \frac{(1 - \phi_n^\prime) \phi_n^\prime}{ m_n}}{(\phi_p^\prime - \phi_n^\prime)^2}
-\end{equation*}
-
-\begin{equation*}
-    m_p^\prime = m_p +2
-\end{equation*}
-
-\begin{equation*}
-    m_n^\prime = m_n + 2
-\end{equation*}
-
-\begin{equation*}
-    \phi_p^\prime = \frac{m_p \cdot \hat{\phi}_p + 1}{m_p + 2}
-\end{equation*}
-
-\begin{equation*}
-   1 - \phi_n^\prime = \frac{m_n \cdot (1 - \hat{\phi}_n) + 1}{m_n + 2} 
-\end{equation*}
-
-\begin{equation*}
-   \beta_1^{*\prime} = \frac{\beta_1^\prime - \phi_n^\prime}{\phi_p^\prime - \phi_n^\prime} 
-\end{equation*}
-and 
-\begin{equation*}
-    \beta_1^\prime = \frac{n_1 \cdot \hat{\theta}_1 + q_Z^2 / 2}{n_1 + q_Z^2}.
-\end{equation*}
+\begin{align*}
+    d\beta =& 2 \cdot q_Z^2 \cdot\left\{ \beta_1^{*\prime} \cdot \frac{\phi_p^\prime (1 - \phi_p^\prime)}{m_p^\prime} - (1 - \beta_1^{*\prime}) \cdot \frac{(1 - \phi_n^\prime) \phi_n^\prime}{m_n^\prime}  \right\}\\
+    \Var(\beta_1^{*\prime}) =& \frac{ \frac{\beta_1^{*\prime}(1 - \beta_1^{*\prime})}{n_1} + \left(\beta_1^{*\prime}\right)^2 \frac{\phi_p^\prime (1 - \phi_p^\prime)}{m_p} + \left(1 + \beta_1^{*\prime}\right)^2 \frac{(1 - \phi_n^\prime) \phi_n^\prime}{ m_n}}{(\phi_p^\prime - \phi_n^\prime)^2}
+\end{align*}
+
+\begin{align*}
+    m_p^\prime =& m_p +2 &
+    m_n^\prime =& m_n + 2 \\
+    \phi_p^\prime =& \frac{m_p \cdot \hat{\phi}_p + 1}{m_p + 2} &
+   1 - \phi_n^\prime =& \frac{m_n \cdot (1 - \hat{\phi}_n) + 1}{m_n + 2} \\
+   \beta_1^{*\prime} =& \frac{\beta_1^\prime - \phi_n^\prime}{\phi_p^\prime - \phi_n^\prime} &
+    \beta_1^\prime =& \frac{n_1 \cdot \hat{\theta}_1 + q_Z^2 / 2}{n_1 + q_Z^2}.
+\end{align*}
 
@@
 
-\begin{equation*}
-    G_{\beta^*}^L \sim \operatorname{Gamma}\left( \frac{y^2}{v}, \frac{v}{y} \right)
-\end{equation*}
-
-\begin{equation*}
-    G_{\beta^*}^U \sim \operatorname{Gamma}\left( \frac{y^{*2}}{v^*}, \frac{v^*}{y^*} \right)
-\end{equation*}
-
-\begin{equation*}
-    y = \sum_{i=1}^K \frac{w_i}{n_i} x_i
-\end{equation*}
-
-\begin{equation*}
-    v = \sum_{i=1}^K \left( \frac{w_i}{n_i}\right)^2 x_i
-\end{equation*}
-
-\begin{equation*}
-    y^* = y + \max\left(\frac{w_1}{n_1}, \ldots, \frac{w_K}{n_K} \right)
-\end{equation*}
-
-\begin{equation*}
-    v^* = v + \left\{ \max\left(\frac{w_1}{n_1}, \ldots, \frac{w_K}{n_K} \right) \right\}^2.
-\end{equation*}
-
-We call this the wsPoison method, since it assumes a weighted sum of Poissons.
+\begin{align*}
+    G_{\beta^*}^L \sim& \operatorname{Gamma}\left( \frac{y^2}{v}, \frac{v}{y} \right) &
+    G_{\beta^*}^U \sim& \operatorname{Gamma}\left( \frac{y^{*2}}{v^*}, \frac{v^*}{y^*} \right) \\
+    y =& \sum_{i=1}^K \frac{w_i}{n_i} x_i &
+    v =& \sum_{i=1}^K \left( \frac{w_i}{n_i}\right)^2 x_i \\
+    y^* =& y + \max\left(\frac{w_1}{n_1}, \ldots, \frac{w_K}{n_K} \right) &
+    v^* =& v + \left\{ \max\left(\frac{w_1}{n_1}, \ldots, \frac{w_K}{n_K} \right) \right\}^2.
+\end{align*}
+
+We call this the wsPoisson method, since it assumes a weighted sum of Poissons.
 We compare the wsPoisson confidence interval to two methods presented in Dean and Pagano\cite{Dean:2015}, which were recommended for scenarios with low prevalence.
@@
 
-\begin{equation*}
-   \tilde{x} = \left( \sum_{i=1}^k w_i \hat{\theta}_i \right) n_{\text{eff}} + c 
-\end{equation*}
-
-\begin{equation*}
-   \tilde{n} = n_{\text{eff}} + 2c 
-\end{equation*}
-
-\begin{equation*}
-    \tilde{p} = \tilde{x} / \tilde{n}
-\end{equation*}
-
-\begin{equation*}
-   c = q_Z^2/2
-\end{equation*}
+\begin{align*}
+   \tilde{x} =& \left( \sum_{i=1}^k w_i \hat{\theta}_i \right) n_{\text{eff}} + c &
+   \tilde{n} =& n_{\text{eff}} + 2c \\
+    \tilde{p} =& \tilde{x} / \tilde{n} &
+   c =& q_Z^2/2
+\end{align*}
 
@@
 where analogously to the Clopper-Pearson interval (see equation~\ref{eq:C-P}),
-\begin{equation*}
+\begin{align*}
     % B^L_{KG} \sim \operatorname{Beta}\left(n_{\text{eff}} \sum_{i=1}^k w_i \hat{\theta}_i, n_{\text{eff}} \left(1 -  \sum_{i=1}^k w_i \hat{\theta}_i\right) + 1\right)
-    B^L_{KG} \sim \operatorname{Beta}\left(x_{\text{eff}},  n_{\text{eff}} -  x_{\text{eff}} + 1 \right)
-\end{equation*}
-
-\begin{equation*}
+    B^L_{KG} \sim& \operatorname{Beta}\left(x_{\text{eff}},  n_{\text{eff}} -  x_{\text{eff}} + 1 \right) &
     % B^U_{KG} \sim \operatorname{Beta}\left(\left(n_{\text{eff}} \sum_{i=1}^k w_i \hat{\theta}_i\right) + 1, n_{\text{eff}} \left(1 - \sum_{i=1}^k w_i \hat{\theta}_i \right)\right)
-    B^U_{KG} \sim \operatorname{Beta}\left(x_{\text{eff}} + 1, n_{\text{eff}} - x_{\text{eff}} \right)
-\end{equation*}
+    B^U_{KG} \sim& \operatorname{Beta}\left(x_{\text{eff}} + 1, n_{\text{eff}} - x_{\text{eff}} \right)
+\end{align*}
 
@@
 & = &    \sum_{i=1}^{n} \sum_{j=1}^{N}  \frac{ \textrm{var}_P( I_{ij})  Y_j^2}{n^2 N^2 P_j^2}  \\
+& = &    \sum_{i=1}^{n} \sum_{j=1}^{N}  \frac{ \textrm{var}_P( I_{ij})  Y_j}{n^2 N^2 P_j^2}  \\
 & = &    \sum_{i=1}^{n} \sum_{j=1}^{N}  \frac{   Y_j}{n^2 N^2 P_j}.
@@
 
-Figure~\ref{fig:coverage_comparison_plot} shows that, when specificity is less than perfect, both methods achieve approximately nominal coverage, with the melding method being somewhat more conservative.
-When specificity is 100\%, both methods are conservative.
+Figure~\ref{fig:coverage_comparison_plot} shows that, when specificity is less than perfect, the Lang-Reiczigel method achieves approximately nominal coverage, while the melding method is slightly more conservative, generally demonstrating 96\%-97\% coverage with 95\% confidence intervals.
+When specificity is 100\%, both methods are very conservative, achieving nearly 100\% coverage.
+For a more nuanced depiction of each method's properties, we separate the overall coverage into lower and upper errors.
 Figure~\ref{fig:upper_error_frequency_comparison_plot} shows that both methods make upper errors with roughly the same frequency.
-Figure~\ref{fig:lower_error_frequency_comparison_plot} demonstrates that while the melding procedure bounds the lower error frequency below 2.5\%, the Lang-Reiczigel method generally has lower error above 2.5\%, which is undesirable for applications for which there is a need to bound the lower errors.
+Figure~\ref{fig:lower_error_frequency_comparison_plot} demonstrates that while the melding procedure bounds the lower error frequency below 2.5\%, the Lang-Reiczigel method generally has lower error above 2.5\%.
+Each of these behaviors may be undesirable, depending on the context in which the methods are applied.
+For applications in which there is a need to bound the lower errors, the melding method is superior.
 
@@
 In all cases, the wsPoisson method is more conservative than the competitor methods.
+In scenarios with higher overall prevalence, the Agresti-Coul and Korn-Graubard methods achieve close to nominal coverage, while the wsPoisson method strongly over-covers.
 This is similar to the behavior observed in Fay and Feuer\cite{FayF:1997}, where, in simulations, the overall error rate for the gamma intervals decreased as the variance of the weights increased.
@@
 
-We compare properties our melded confidence interval WprevSeSp Poisson, to another melded confidence interval method WprevSeSp Binomial, and one method, wsPoisson, which does not account for the imperfect assay.
+We compare properties our melded confidence interval WprevSeSp Poisson, to another melded confidence interval method, WprevSeSp Binomial.
 The methods are assessed in a several simulated scenarios with varying levels of disease prevalence (0.5\% or 5\%), types of groups surveyed (50 groups 200 subjects or 8000 groups of 1 subject), distributions of weights among the groups (coefficient of variation from approximately 0\% to nearly 6\%), the number of groups with non-zero prevalence, and the specificity of the assay (80\% - 100\%).
@@
 With perfect specificity, the WprevSeSp Binomial method fails to maintain nominal coverage when the coefficient of variation among the weights is high and specificity is perfect.
-Only our proposed WprevSeSp Poisson method maintains or exceed the desired coverage in all scenarios.
+In the other scenarios tested, the WprevSeSp Binomial generally achieves closer to nominal coverage than the WprevSeSp Poisson, which strongly over-covers.
+Our proposed WprevSeSp Poisson method maintains or exceed the desired coverage in all scenarios.
 In these scenarios, we also assess properties of the wsPoisson procedure, which does not account for the the imperfect assay.
@@
 One of the new methods was very similar to the method used by Kalish et al\cite{Kali:2021}, and in this paper we have explored its properties.
-These new confidence intervals appear to guarantee coverage in most simulated settings, and in general to demonstrate higher coverage than competitor methods.
+These new confidence intervals appear to guarantee coverage in most simulated settings, including some scenarios where competitor methods dramatically under-cover.
+In general, our methods demonstrate higher coverage than competitor methods in most scenarios, sometimes being very conservative while competitor methods demonstrate closer to nominal coverage.
 In the case of the simple random sample with an imperfect test, our new methods are able to bound the lower error rate for a 95\% confidence interval at 2.5\%, while the Lang-Reiczigel\cite{Lang:2014} method maintains 95\% coverage by allowing a higher lower error rate.
@@
 However, our method  only studied fixed weights and not when the weights are estimated as in Kalish et al.
-Further worked is needed to address such cases.
+Further work is needed to address such cases.
 In addition, further worked is needed to consider other complex sample designs such as multistage cluster designs that are used in  household and institutional surveys such hospital and medical practice surveys.
 
-Our method was slightly different to that used in Kalish, et al\cite{Kali:2021}, in that the latter method included estimates of the variability of the weights; however, recalculating the confidence intervals on the same data shows that in that case there was little difference.
+Our method was slightly different to that used in Kalish, et al\cite{Kali:2021}, in that thdatae latter method included estimates of the variability of the weights; however, recalculating the confidence intervals on the same data shows that in that case there was little difference.
 %[BARRY TO ADD MORE DISCUSSION AND REFERENCES ABOUT ESTIMATING VARIABILITY IN %WEIGHTS, ETC., AND TRIMMING WEIGHTS].
@@
 % \end{acks}
+
+\section{Data Availability Statement}
+Data sharing is not applicable to this article as no new data were created or analyzed in this study.
 

### 2023-02-01 response_to_decision_letter.tex
fix typos

@@
 
+\textbf{ Associate Editor}
+
+Comments to Author:
+\textbf{Your article has been thoroughly reviewed by an expert in the field.
+You will see that they have several suggestions and comments for you to address, and they see multiple contributions from the article.
+As the reviewer suggests please ensure it is clear in the introduction what are the major research gap(s) the article addresses, and it is clear in the discussion what contribution(s) you believe the article has made.}
+
+We have addressed the reviewers comments in detail below.
+We have rewritten the abstract and expanded the first paragraph of the introduction to be clear about the research gaps this article addresses and to be clear about what is new in our article.
+We have also rewritten the discussion to make our main contributions clear.
+
 \textbf{Reviewer: 1}
@@
 
+We have clarified our contributions (see answers below). 
+We have also now explicitly stated in the first paragraph of the introduction that while our confidence interval is designed to guarantee coverage, there is no proof of that property given in the paper.
+The conjecture of guaranteed coverage is supported by simulation only.
+
     \item \textbf{The abstract and introduction imply that a main contribution of the work is that the new methods have better properties in simulations, and no drawbacks are hinted at.
@@
 
-    We have added some mentions in the text about the drawbacks to our proposed methods and clarify the scenarios when our methods are shown to be superior:
+We have rewritten the introduction and discussion to be clear
+that a main point of the paper is that there did not exist 
+established methods for creating confidence intervals for prevalence estimates from complex surveys when the assays are imperfect.
+Our paper has developed methods for that situation
+(closely related to the Kalish, et al method, for which the properties were not fully studied), and studied the properties  of those methods.
 
-    Abstract:
-    ``We demonstrate that our methods appear to guarantee coverage in simulated settings, while competing methods are shown to achieve much lower than nominal coverage in some settings, especially when overall prevalence is very low.
+In the special cases (e.g., simple random samples with imperfect 
+assays, or complex samples with perfect assays), we could compare our method to established methods. 
+    We have added some mentions in the text about the drawbacks to our proposed methods compared to the established ones and to clarify the scenarios when our methods are shown to be superior:
+
+    \begin{description}
+\item[    Abstract:]
+    ``In some simulations, our methods appear to guarantee coverage, while competing methods have much lower than nominal coverage, especially when overall prevalence is very low.
 In other settings, our methods are shown to be overly conservative."
 
-    Introduction:
+\item[    Introduction:]
 
@@
 
-    Discussion:
+\item[    Discussion:]
     ``These new confidence intervals appear to guarantee coverage in most simulated settings, including some scenarios where competitor methods dramatically under-cover.
     In general, our methods demonstrate higher coverage than competitor methods in most scenarios, sometimes being very conservative while competitor methods demonstrate closer to nominal coverage.""
+\end{description}
 
@@
 
-    \textcolor{red}{Mike, can you add any comments about this?}
+  First, we make the point again, that was not made clear enough in our previous version, that the new methods that we study in this paper (WprevSeSp Poisson and WprevSeSp Binomial)
+do not have an established comparator method.
+There are no previously established tractable methods to give confidence intervals for prevalence from complex surveys with imperfect assays.
+(This is excluding valid methods that were developed recently and were not in print when we submitted, such as DiCiccio et al.
+See remarks in our introduction about those recently developed methods).
+
+For the special cases where there are alternative analyses (e.g., for a simple random sample with an imperfect assay, where we could use the method of Lang and Reiczigel), then the decision on which method to use would depend on the application.
+If at least nominal coverage are important, and directional inferences are important (e.g., you want to know if the prevalence is larger than some value, so you are interested in the lower error of the confidence interval), then the new methods seem attractive.
+If approximately nominal coverage for the two-sided interval is desired, then the method of Lang and Reiczigel may be recommended.
 
@@
     Each of these behaviors may be undesirable, depending on the context in which the methods are applied.
-    For applications in which there is a need to bound the lower errors, the melding method is superior."
+    For applications in which there is a need to bound the lower errors, the melding method appears to be superior."
 
@@
 
-    We only evaluated 0.5\% and 5\% because the greater prevalence leads to over-coverage for our methods.
-    We have updated the text to point to this drawback throughout.
+The simulation prevalence of 5\% is very close to the value from our motivating data example.
+The 0.5\% was chosen as to see how well the method does for a much lower value. 
+Although it would be interesting to study the performance across a larger portion of the prevalence parameter space, we leave that to future work because we already have an extensive set of simulation results in this paper.
 
-    \item If the main contribution of the paper is superior coverage properties, then the above issues of the Poisson approximation assuming a small prevalence as well as simulation results and interpretation should be addressed.
-The authors could instead elaborate on other contributions of the work detailed above.
+In response to your comment, we have added a paragraph to the beginning of the simulation section and another paragraph in the discussion section to emphasize the limitation of the simulations with respect to prevalence values.
+
+In the discussion we have added: ``Although this paper has done extensive simulations, the focus of the simulations was for low prevalence and high 
+sensitivity and specificity. For other situations, especially high prevalence situations, more work is needed to more fully explore the properties of these methods.''
+
+    \item \textbf{If the main contribution of the paper is superior coverage properties, then the above issues of the Poisson approximation assuming a small prevalence as well as simulation results and interpretation should be addressed.
+The authors could instead elaborate on other contributions of the work detailed above.}
+
+    The main contribution of the paper is to have a confidence interval method that can be applied to complex surveys when there is also misclassification.
+    Although Kalish {\it et al} 2021 (note: the second and third authors of the submitted paper were also authors on Kalish {\it et al}) did have a method that could be applied to that type of data, but since the focus of that paper was the results of the survey, it did not study the properties of that method.
+    This paper is in some sense a companion paper to that paper, in that it can study the properties an interval very similar to
+     the method in Kalish {\it et al} and also propose modifications of it (the WprevSeSp Poisson method proposed in this paper).
 
@@
         \begin{array}{ll}
-        1 & \mbox{ if $\hat{\phi}_n < \hat{\phi}_p < \hat{\theta}_1$ }  \\
+        1 & \mbox{ if $\hat{\phi}_n < \hat{\phi}_p \leq \hat{\theta}_1$ }  \\
         \frac{\hat{\theta}_1 - \hat{\phi}_n}{\hat{\phi}_p - \hat{\phi}_n} & 
@@
 
-        I have added the definition of the confidence distribution to section 2.2
-        \textcolor{red}{Mike, feel free to add more context/intution.}
+       We have added more background on the melding method, giving an intuitive definition of the confidence distribution (and referencing the more formal modern definition).
+       We also now give some insight into why the lower and upper confidence distributions for the binomial are beta distributions.
 
@@
 
-        We have adjusted the presentation of Section 2.2 to reduce the lines used.
+        We have adjusted the some of the presentation in Sections 2.2 and 2.5.2  to reduce the lines used.
 
@@
 
-        \textcolor{red}{Damon: I fixed these errors and a few more. Mike and Barry should also take a look for proofreading.}
+        We have corrected a the errors described here and several others found upon further review.
 

### 2023-02-01 PrevAdjSurvey.tex
fix typos

@@
 
-\abstract[Abstract]{We present several related methods for creating confidence intervals to assess disease prevalence in variety of survey sampling settings.
-These include simple random samples with imperfect tests, weighted sampling with perfect tests, and weighted sampling with imperfect tests, with the first two settings considered special cases of the third.
-Our methods use survey results and measurements of test sensitivity and specificity to construct melded confidence intervals.
-We demonstrate that our methods appear to guarantee coverage in simulated settings, while competing methods are shown to achieve much lower than nominal coverage in some settings, especially when overall prevalence is very low.
-In other settings, our methods are shown to be overly conservative.
+\abstract[Abstract]{There are established methods for estimating disease prevalence with associated confidence intervals for complex surveys with perfect assays, or simple random sample surveys with imperfect assays.
+We develop and study methods for the complicated case of complex surveys with imperfect assays.
+The new methods use the melding method to combine gamma intervals for directly standardized rates and established adjustments for imperfect assays by estimating sensitivity and specificity.
+One of the new methods appears to have at least nominal coverage in all simulated scenarios.
+We compare our new methods to established methods in special cases (complex surveys with perfect
+assays or simple surveys with imperfect assays).
+In some simulations, our methods appear to guarantee coverage, while competing methods have much lower than nominal coverage, especially when overall prevalence is very low.
+In other settings, our methods are shown to have higher than nominal coverage.
 We apply our method to a seroprevalence survey of SARS-CoV-2 in undiagnosed adults in the United States between May and July 2020.}
 
-\keywords{confidence distributions, seroprevalence, survey sampling, weighted sampling}
+\keywords{confidence distributions, melding confidence intervals, seroprevalence, survey sampling, weighted sampling}
 
@@
 Estimating and quantifying uncertainty for disease prevalence is a standard task in epidemiology.
-For rare events, these estimates are highly sensitive to misclassification \cite{hemenwaySelfDefense}, making adjustments for sensitivity and specificity critically important.
+For rare events, these estimates are highly sensitive to misclassification,\cite{hemenwaySelfDefense} making adjustments for sensitivity and specificity critically important.
 While estimating prevalence (or any event proportion in a population) in complex surveys and adjusting estimates for misclassification have been well studied separately, performing both of these tasks simultaneously remains relatively unexplored.
-Recent overviews of methods for estimating prevalence in surveys without misclassification are provided by Dean and Pagano\cite{Dean:2015} and Franco, et al\cite{franco2019}.
-For  simple random sample surveys with imperfect sensitivity and specificity, Lang and Reiczigel\cite{Lang:2014} proposed an approximate method that performed well in simulations.
-Recent work by DiCiccio, et al \cite{DiCi:2021} and Cai et al \cite{Cai:2020} study both valid (i.e., exact) and approximate methods.
-Their valid methods use test inversion and the adjustment of Berger and Boos \cite{Berg:1994}, while their approximation methods use the bootstrap with the test inversion approach.
+This paper fills that gap by studying estimates and confidence intervals for prevalence from complex surveys with misclassification.
+We develop a new tractable confidence interval procedure designed to guarantee coverage.
+Our confidence interval combines three statistical methods: (1) the gamma confidence interval for directly standardized rates is applied to the apparent prevalence\cite{FayF:1997}
+and (2) standard misclassification adjustments to that apparent prevalence for sensitivity and specificity \cite{Roga:1978} are used together with (3) the melding method, which allows combination of confidence intervals for different parameters.\cite{FayP:2015}
+We show by simulation only (there are no proofs of guaranteed coverage) that, with a complex survey with low prevalence and misclassification, our method appears to have at least nominal coverage.
+Even in special cases (e.g., simple random samples with imperfect assays, or weighted samples with perfect assays) where there are existing methods, our new method has at least nominal simulated coverage.
+while some of the tractable existing methods may under-cover.
+The cost for apparently achieving nominal coverage is that our intervals may be quite wide in some situations.
+
+Recent overviews of confidence interval procedures for prevalence in surveys without misclassification are provided by Dean and Pagano\cite{Dean:2015} and Franco, et al.\cite{franco2019}
+For simple random sample surveys with imperfect sensitivity and specificity, Lang and Reiczigel\cite{Lang:2014} proposed an approximate confidence interval that performed well in simulations.
+Recent work by DiCiccio, et al \cite{DiCi:2021} and Cai et al\cite{Cai:2020} study both valid (i.e., exact) and approximate intervals.
+Their valid intervals use test inversion and the adjustment of Berger and Boos,\cite{Berg:1994} while their approximation intervals use the bootstrap with the test inversion approach.
 Fewer methods are available for for constructing frequentist confidence intervals for prevalence estimates from complex surveys while adjusting for sensitivity and specificity.
 Kalish et al\cite{Kali:2021} developed one such method that is closely related to one of the methods presented here, but that method's properties were not studied.
-Cai et al \cite{Cai:2020} (see also discussion in DiCiccio et al \cite{DiCi:2021}) modify their approximation approach to allow sample weights, but it assumes that the number of counts of events within the strata are large (see their Remark 4).
-Thus, it would not apply to a weighted survey method where each individual their own weight.
-Another recent advancement is the method developed by Rosin et al \cite{rosin2021estimating} that 
- makes use of asymptotic normal approximations which reduce to the Wald interval when sensitivity and specificity are perfect.
-This problem has also previously been addressed in Bayesian literature, recently by Gelman and Carpenter\cite{GelmanBayes}.
+Cai et al\cite{Cai:2020} (see also discussion in DiCiccio et al\cite{DiCi:2021}) modify their approximation approach to allow sample weights for strata or individual specific weights.
+Another recent advancement is the method developed by Rosin et al\cite{rosin2021estimating} that makes use of asymptotic normal approximations which reduce to the Wald interval when sensitivity and specificity are perfect.
+This problem has also previously been addressed in Bayesian literature, recently by Gelman and Carpenter. \cite{GelmanBayes}
 
@@
 Finally, in Section~\ref{sec:complex-surveys} we show how certain complex surveys may fit into the format for our new method.
-Our new method is designed to guarantee coverage in all situations.
 
 In simulations we compare our method to established frequentist competitors and show through simulations that it beats the best of those in each of the three stages with respect to guaranteeing coverage.
-However, in some simulated settings, our proposed methods are overly conservative, while competitor methods maintain closer to nominal coverage.
-We did not include in our simulations the new methods that have been developed in response to the COVID-19 pandemic and are not yet in print in peer reviewed journals \cite{Cai:2020,DiCi:2021,rosin2021estimating}.
-The exact method of DiCiccio, et al \cite{DiCi:2021} would guarantee coverage, although applying it to a survey with a large number of strata would be ``computationally expensive'', and it has not been applied to surveys using post-stratification weighting.
+However, in some simulated settings, our proposed methods are overly conservative, meaning that they demonstrate higher than nominal coverage, while competitor methods maintain closer to nominal coverage.
+We did not include in our simulations some recent methods that have been developed in response to the COVID-19 pandemic.\cite{Cai:2020,DiCi:2021,rosin2021estimating}
+The exact method of DiCiccio, et al\cite{DiCi:2021} would guarantee coverage, although applying it to a survey with a large number of strata would be ``computationally expensive,'' and it has not been applied to surveys using post-stratification weighting.
 In contrast, our new method can very tractable in those situations.
@@
 To introduce notation, consider first the stratified simple random sample.
-Suppose we have a population partitioned into   \( K \) strata, with \( N_1, N_2, \ldots, N_K \) individuals in the  K strata of the population.
-We sample \( n_1, n_2, \ldots, n_K \) individuals via a simple random sample from each of the \( K \)  strata to have an assay performed to determine who has a disease.
+Suppose we have a population partitioned into \( K \) strata, with \( N_1, N_2, \ldots, N_K \) individuals in the \( K \) strata of the population.
+We sample \( n_1, n_2, \ldots, n_K \) individuals via a simple random sample from each of the \( K \) strata to have an assay performed on each individual to determine who has the disease.
 Let \( X_i \) be the number of positive results from an assay performed on the \( n_i \) individuals from stratum \( i \) and assume \( X_i \sim \operatorname{Binomial}(n_i, \theta_i) \), where \( \theta_i \) is the population frequency of positive results for assays performed on individuals from stratum \( i \).
@@
 negative controls (i.e., individuals known to be without the disease), respectively. Then
-$\theta_i = \phi_p \theta_i^* + \phi_n (1-\theta_i^*)$, or equivalently,  
+$\theta_i = \phi_p \theta_i^* + \phi_n (1-\theta_i^*)$, or equivalently,\cite{Roga:1978}
 \begin{eqnarray*}
@@
 This estimator serves as an important basis for developing confidence intervals in this work.
-Section~\ref{sec:srs-imperfect} is concerned with confidence intervals for  \( \beta^* \) in the case where \( K = 1 \), \( \phi_n > 0 \), \( \phi_p < 1 \), i.e.
-estimating prevalence from a simple random sample with an imperfect assay.
-Section~\ref{sec:weight-perfect} is concerned with confidence intervals for  \( \beta^* \) in the case where \( K > 1 \), \( \phi_n = 0 \), \( \phi_p = 1 \), i.e.
-estimating prevalence from a weighted sample with a perfect assay.
-Section~\ref{sec:weight-imperfect} is concerned with confidence intervals for  \( \beta^* \) in the case where \( K > 1 \), \( \phi_n > 0 \), \( \phi_p < 1 \), i.e.
-estimating prevalence from a weighted sample with an imperfect assay.
+Section~\ref{sec:srs-imperfect} is concerned with confidence intervals for \( \beta^* \) in the case where \( K = 1 \), \( \phi_n > 0 \), \( \phi_p < 1 \), i.e., estimating prevalence from a simple random sample with an imperfect assay.
+Section~\ref{sec:weight-perfect} is concerned with confidence intervals for \( \beta^* \) in the case where \( K > 1 \), \( \phi_n = 0 \), \( \phi_p = 1 \), i.e., estimating prevalence from a weighted sample with a perfect assay.
+Section~\ref{sec:weight-imperfect} is concerned with confidence intervals for \( \beta^* \) in the case where \( K > 1 \), \( \phi_n > 0 \), \( \phi_p < 1 \), i.e., estimating prevalence from a weighted sample with an imperfect assay.
 
@@
 
-First, we consider the scenario where \( K = 1 \), \( \phi_n > 0 \), and \( \phi_p < 1 \).
+First we consider the scenario where \( K = 1 \), \( \phi_n > 0 \), and \( \phi_p < 1 \).
 We develop a confidence interval for the population prevalence, \( \beta^* \).
@@
 \begin{array}{ll}
-1 & \mbox{ if $\hat{\phi}_n < \hat{\phi}_p < \hat{\theta}_1$ }  \\
+1 & \mbox{ if $\hat{\phi}_n < \hat{\phi}_p \leq \hat{\theta}_1$ }  \\
 \frac{\hat{\theta}_1 - \hat{\phi}_n}{\hat{\phi}_p - \hat{\phi}_n} &
@@
 
-To create a confidence interval for \( \hat{\beta}^* \), we use a generalization of the melding method \cite{FayP:2015}, which makes use of lower and upper confidence distributions on functions of independent estimators to account for variability in \( \hat{\theta}_1 \), \( \hat{\phi}_n \), and \( \hat{\phi}_p \).
+To create a confidence interval for \( \hat{\beta}^* \), we use a generalization of the melding method, \cite{FayP:2015} which makes use of lower and upper confidence distributions on functions of independent estimators to account for variability in \( \hat{\theta}_1 \), \( \hat{\phi}_n \), and \( \hat{\phi}_p \).
+Before describing the melding method, we briefly review confidence distributions.
+
 Confidence distributions are frequentist estimators of a parameter, which can be used similarly to the bootstrap or posterior distributions.
-Formally, a confidence distribution is a function \(H_{n}(\cdot)=H_{n}(\mathbf{x}, \cdot)\) on \(\mathcal{X} \times \Theta \rightarrow[0,1]\), where \( \Theta \) is the parameter space of the parameter of interest (\( \theta \)) and \( \mathcal{X} \) is the sample space corresponding to sample data \(\mathbf{x}=\left\{x_{1}, \ldots, x_{n}\right\}\), which has two properties: (i) For each \(\mathbf{x} \in \mathcal{X}, H_{n}(\cdot)\) is a cumulative distribution function on \(\Theta \).
-(ii) At the true parameter value \(\theta=\theta_{0}, H_{n}\left(\theta_{0}\right) \equiv H_{n}\left(\mathbf{x}, \theta_{0}\right)\), as a function of the sample \(\mathbf{x}\), follows the uniform distribution \(U[0,1]\) \cite{Xie2013}.
-
-The lower and upper confidence distributions are used with discrete responses to ensure the validity of the resulting inferences, and for the binomial case they are equivalent to the posterior distributions that result from using well-calibrated null preference priors \cite{Fay2021}.
-
-Each estimated component in Equation~\ref{eq:srs-beta-est} is a binomial probability parameter.
-For each of these, we use distributions associated with  the exact binomial confidence interval.
+For continuous responses (and asymptotically for discrete responses), one can formally define confidence distributions without relying on previously derived confidence interval procedures,\cite{Xie2013} but for intuition with discrete responses, it is easier to derive confidence distributions the classical way, i.e., directly from confidence interval procedures.
+For discrete responses there are two confidence distributions (the lower and upper ones), used to ensure validity of the resulting inferences.
+Under the classical derivation, we can create random variables associated with the lower and upper confidence distributions from two one-sided, nested, confidence interval procedures, where for a nested confidence interval procedure, the $(1-\alpha_1)$ interval is a subset of the $(1-\alpha_2)$ interval whenever $(1-\alpha_1) \leq (1-\alpha_2)$.
+Denote those one-sided intervals by $[L({\bf x},1-\alpha), \infty)$ and $(-\infty, U({\bf x},1-\alpha)]$, which are defined for any observed data ${\bf x}$, and $(1-\alpha) \in (0,1)$.
+For fixed ${\bf x}$, define the lower and upper confidence distribution random variables as $L({\bf x}, A)$ and $U({\bf x},B)$, where $A$ and $B$ are independent uniform random variables.
+Then a $100(1-\alpha)\%$ central confidence interval has the $(\alpha/2)$th quantile of $L({\bf x}, A)$ as the lower limit, and the $(1-\alpha/2)$th quantile of $U({\bf x},B)$ as the upper limit.
+
+Because each estimated component in Equation~\ref{eq:srs-beta-est} is a binomial probability parameter, we now focus on the confidence distributions associated with the exact binomial confidence interval.
 For a binomial experiment with \( x \) successes out of \( n \) trials, the lower confidence distribution is \( \operatorname{Beta}(x, n - x + 1) \) with associated random variable \( B^L \), and the upper confidence distribution is \( \operatorname{Beta}(x + 1, n - x)\) with random variable \( B^U \), where for $a>0$ we let \( \operatorname{Beta}(0,a) \) and \( \operatorname{Beta}(a,0) \) be point masses at 0 and 1, respectively.
+This result comes from the relationship between the binomial and beta distributions, namely $\mathrm{Pr}[X \leq x] = \mathrm{Pr}[B > \theta]$, where $B \sim \operatorname{Beta}(x + 1, n - x)$ for $x \in \left\{ -1,0, 1, \ldots, n \right\}$ (see e.g., \cite[Section~2]{Blyth1986}, \cite[Section~S2]{Fay2021}).
+Additionally, in the binomial case, the lower and upper confidence distributions are equivalent to
+the posterior distributions that result from using well-calibrated null preference priors.\cite{Fay2021}
 Let \( q(a, W) \) be the \( a \)th quantile of a random variable \( W \).
@@
 
-Fay et al \cite{FayP:2015} proposed a method for obtaining confidence intervals for functions of two parameters that are monotonic within the allowable range  for each parameter given the other is fixed.
-Here we generalize that to $\beta^*$, which is a function of 3 parameters.
+Fay et al\cite{FayP:2015} proposed the melding method for obtaining confidence intervals for functions of two parameters that are monotonic within the allowable range for each parameter given the other is fixed.
+The melding method uses quantiles of those functions except replacing lower or upper confidence distribution random variables for their associated parameter in the function.
+Here we generalize that method to $\beta^*$, which is a function of three parameters.
 When $1 \geq \phi_p > \theta_1 > \phi_n \geq 0$ then $\beta^*$ is monotonically increasing in $\theta_1$, monotonically decreasing in $\phi_p$, and monotonically decreasing in $\phi_n$.
@@
 where $g(\cdot)$ is defined in equation~\ref{eq:srs-beta-est}.
+In equation~\ref{eq:srs-conf-int}, the choice of confidence distribution random variable (lower or upper) is determined by the associated the direction of the monotonicity to attempt to ensure coverage.
+As the sample sizes (e.g., $n_i$, $m_p$, and $m_n$) increase, there is little difference between the lower and upper confidence distributions.
 
 The quantiles of these melded distributions are calculated by Monte Carlo sampling from each of the component distributions.
-We compare this method to one described in Lang and Reiczigel \cite{Lang:2014} as implemented in prevSeSp function in \cite{asht}, which provides approximate confidence intervals for true prevalence when sensitivity and specificity are estimated from independent samples, as they are  in this section.
+We compare this method to one described in Lang and Reiczigel\cite{Lang:2014} as implemented in prevSeSp function in the \texttt{asht} R package,\cite{asht} which provides approximate confidence intervals for true prevalence when sensitivity and specificity are estimated from independent samples, as they are in this section.
 The Lang-Reiczigel interval is given by
 \begin{equation}
-\beta_1^{*\prime} + d\beta \pm q\left( 1 - \frac{\alpha}{2}, Z \right) \cdot \Var(\beta_1^{*\prime})^{1/2}    
-\end{equation}
-
-where \( q_Z \equiv q\left( 1 - \frac{\alpha}{2}, Z \right)\) and \( Z \sim N(0,1) \).
+\beta_1^{*\prime} + d\beta \pm q\left( 1 - \frac{\alpha}{2}, Z \right) \cdot \Var(\beta_1^{*\prime})^{1/2},
+\end{equation}
+
+where \( q_Z \equiv q\left( 1 - \frac{\alpha}{2}, Z \right)\), \( Z \sim N(0,1) \),
 
 \begin{align*}
-    d\beta =& 2 \cdot q_Z^2 \cdot\left\{ \beta_1^{*\prime} \cdot \frac{\phi_p^\prime (1 - \phi_p^\prime)}{m_p^\prime} - (1 - \beta_1^{*\prime}) \cdot \frac{(1 - \phi_n^\prime) \phi_n^\prime}{m_n^\prime}  \right\}\\
-    \Var(\beta_1^{*\prime}) =& \frac{ \frac{\beta_1^{*\prime}(1 - \beta_1^{*\prime})}{n_1} + \left(\beta_1^{*\prime}\right)^2 \frac{\phi_p^\prime (1 - \phi_p^\prime)}{m_p} + \left(1 + \beta_1^{*\prime}\right)^2 \frac{(1 - \phi_n^\prime) \phi_n^\prime}{ m_n}}{(\phi_p^\prime - \phi_n^\prime)^2}
+    d\beta =& 2 \cdot q_Z^2 \cdot\left\{ \beta_1^{*\prime} \cdot \frac{\phi_p^\prime (1 - \phi_p^\prime)}{m_p^\prime} - (1 - \beta_1^{*\prime}) \cdot \frac{(1 - \phi_n^\prime) \phi_n^\prime}{m_n^\prime} \right\},\\
+    \Var(\beta_1^{*\prime}) =& \frac{ \frac{\beta_1^{*\prime}(1 - \beta_1^{*\prime})}{n_1} + \left(\beta_1^{*\prime}\right)^2 \frac{\phi_p^\prime (1 - \phi_p^\prime)}{m_p} + \left(1 + \beta_1^{*\prime}\right)^2 \frac{(1 - \phi_n^\prime) \phi_n^\prime}{ m_n}}{(\phi_p^\prime - \phi_n^\prime)^2},
 \end{align*}
@@
 \begin{align*}
-    m_p^\prime =& m_p +2 &
-    m_n^\prime =& m_n + 2 \\
-    \phi_p^\prime =& \frac{m_p \cdot \hat{\phi}_p + 1}{m_p + 2} &
-   1 - \phi_n^\prime =& \frac{m_n \cdot (1 - \hat{\phi}_n) + 1}{m_n + 2} \\
-   \beta_1^{*\prime} =& \frac{\beta_1^\prime - \phi_n^\prime}{\phi_p^\prime - \phi_n^\prime} &
+    m_p^\prime =& m_p +2, &
+    m_n^\prime =& m_n + 2, \\
+    \phi_p^\prime =& \frac{m_p \cdot \hat{\phi}_p + 1}{m_p + 2}, &
+   1 - \phi_n^\prime =& \frac{m_n \cdot (1 - \hat{\phi}_n) + 1}{m_n + 2}, \\
+   \beta_1^{*\prime} =& \frac{\beta_1^\prime - \phi_n^\prime}{\phi_p^\prime - \phi_n^\prime}, &
     \beta_1^\prime =& \frac{n_1 \cdot \hat{\theta}_1 + q_Z^2 / 2}{n_1 + q_Z^2}.
@@
 Next, we present a confidence interval for the population prevalence, \( \beta^* \), in the scenario \( K > 1 \), \( \phi_n = 0 \), \( \phi_p = 1 \).
-Our method is a straightforward adaptation of the gamma confidence interval presented in Fay and Feuer\cite{FayF:1997}, which was developed to create confidence intervals for a population rate which is assumed to be a weighted sum of Poisson rate parameters.
+Our method is a straightforward adaptation of the gamma confidence interval presented in Fay and Feuer,\cite{FayF:1997} which was developed to create confidence intervals for a standardized population rate which is assumed to be a weighted sum of Poisson rate parameters.
 We note that for sufficiently large sample size \( n \) and small rate \( \lambda \), a \( \operatorname{Poisson}(n\lambda) \) distribution is approximately equal in distribution to a \( \operatorname{Binomial}(n, \lambda) \) distribution.
@@
 \begin{equation}
-    \left( q\left( \frac{\alpha}{2}, G_{\beta^*}^L \right), q \left( 1 - \frac{\alpha}{2},  G_{\beta^*}^U \right) \right)
+    \left( q\left( \frac{\alpha}{2}, G_{\beta^*}^L \right), q \left( 1 - \frac{\alpha}{2}, G_{\beta^*}^U \right) \right),
 \end{equation}
@@
 \begin{align*}
-    G_{\beta^*}^L \sim& \operatorname{Gamma}\left( \frac{y^2}{v}, \frac{v}{y} \right) &
-    G_{\beta^*}^U \sim& \operatorname{Gamma}\left( \frac{y^{*2}}{v^*}, \frac{v^*}{y^*} \right) \\
-    y =& \sum_{i=1}^K \frac{w_i}{n_i} x_i &
-    v =& \sum_{i=1}^K \left( \frac{w_i}{n_i}\right)^2 x_i \\
-    y^* =& y + \max\left(\frac{w_1}{n_1}, \ldots, \frac{w_K}{n_K} \right) &
+    G_{\beta^*}^L \sim& \operatorname{Gamma}\left( \frac{y^2}{v}, \frac{v}{y} \right), &
+    G_{\beta^*}^U \sim& \operatorname{Gamma}\left( \frac{y^{*2}}{v^*}, \frac{v^*}{y^*} \right), \\
+    y =& \sum_{i=1}^K \frac{w_i}{n_i} x_i, &
+    v =& \sum_{i=1}^K \left( \frac{w_i}{n_i}\right)^2 x_i, \\
+    y^* =& y + \max\left(\frac{w_1}{n_1}, \ldots, \frac{w_K}{n_K} \right), &
     v^* =& v + \left\{ \max\left(\frac{w_1}{n_1}, \ldots, \frac{w_K}{n_K} \right) \right\}^2.
@@
 We call this the wsPoisson method, since it assumes a weighted sum of Poissons.
-We compare the wsPoisson confidence interval to two methods presented in Dean and Pagano\cite{Dean:2015}, which were recommended for scenarios with low prevalence.
+We compare the wsPoisson confidence interval to two methods presented in Dean and Pagano,\cite{Dean:2015} which were recommended for scenarios with low prevalence.
 Dean and Pagano showed in simulations that the standard Wald interval had poor coverage with low prevalence (e.g., Fig.
 1 of that paper showed 95\% confidence intervals with coverage of less than 85\% for prevalence values less than 2\%).
-Since the confidence interval of Rosin, et al \cite{rosin2021estimating} reduces to the Wald interval with perfect assays, we will not include that method in the simulation comparisons.
+Since the confidence interval of Rosin, et al\cite{rosin2021estimating} reduces to the Wald interval with perfect assays, we will not include that method in the simulation comparisons.
 
@@
 \begin{equation}
-    \tilde{p} \pm q_Z \sqrt{\tilde{p}(1 - \tilde{p}) / \tilde{n}}
+    \tilde{p} \pm q_Z \sqrt{\tilde{p}(1 - \tilde{p}) / \tilde{n}},
 \end{equation}
@@
 \begin{align*}
-   \tilde{x} =& \left( \sum_{i=1}^k w_i \hat{\theta}_i \right) n_{\text{eff}} + c &
-   \tilde{n} =& n_{\text{eff}} + 2c \\
-    \tilde{p} =& \tilde{x} / \tilde{n} &
-   c =& q_Z^2/2
+   \tilde{x} =& \left( \sum_{i=1}^k w_i \hat{\theta}_i \right) n_{\text{eff}} + c, &
+   \tilde{n} =& n_{\text{eff}} + 2c, \\
+    \tilde{p} =& \tilde{x} / \tilde{n}, &
+   c =& q_Z^2/2,
 \end{align*}
@@
 \begin{equation}
-   n_{\text{eff}} = \frac{\left( \sum_{i=1}^k w_i \hat{\theta}_i \right) \left(1 - \sum_{i=1}^k w_i \hat{\theta}_i \right)}{\sum_{i=1}^k \frac{w_i^2}{n_i}\hat{\theta}_i} 
+   n_{\text{eff}} = \frac{\left( \sum_{i=1}^k w_i \hat{\theta}_i \right) \left(1 - \sum_{i=1}^k w_i \hat{\theta}_i \right)}{\sum_{i=1}^k \frac{w_i^2}{n_i}\hat{\theta}_i}.
    \label{eq:neff}
@@
 
-We also compare our suggested method to Dean and Pagano's modification of the method of Korn and Graubard\cite{Korn:1998,Dean:2015}.
+We also compare our suggested method to Dean and Pagano's modification of the method of Korn and Graubard.\cite{Korn:1998,Dean:2015}
 This interval is given by
@@
 \begin{equation}
-    \left( q \left( \frac{\alpha}{2}, B^L_{KG} \right), q \left( 1 - \frac{\alpha}{2}, B^U_{KG} \right)  \right)
-\end{equation}
-
-where analogously to the Clopper-Pearson interval (see equation~\ref{eq:C-P}),
+    \left( q \left( \frac{\alpha}{2}, B^L_{KG} \right), q \left( 1 - \frac{\alpha}{2}, B^U_{KG} \right) \right),
+\end{equation}
+
+where analogously to the Clopper-Pearson interval (see Equation~\ref{eq:C-P}),
 \begin{align*}
     % B^L_{KG} \sim \operatorname{Beta}\left(n_{\text{eff}} \sum_{i=1}^k w_i \hat{\theta}_i, n_{\text{eff}} \left(1 -  \sum_{i=1}^k w_i \hat{\theta}_i\right) + 1\right)
-    B^L_{KG} \sim& \operatorname{Beta}\left(x_{\text{eff}},  n_{\text{eff}} -  x_{\text{eff}} + 1 \right) &
+    B^L_{KG} \sim& \operatorname{Beta}\left(x_{\text{eff}}, n_{\text{eff}} - x_{\text{eff}} + 1 \right), &
     % B^U_{KG} \sim \operatorname{Beta}\left(\left(n_{\text{eff}} \sum_{i=1}^k w_i \hat{\theta}_i\right) + 1, n_{\text{eff}} \left(1 - \sum_{i=1}^k w_i \hat{\theta}_i \right)\right)
-    B^U_{KG} \sim& \operatorname{Beta}\left(x_{\text{eff}} + 1, n_{\text{eff}} - x_{\text{eff}} \right)
+    B^U_{KG} \sim& \operatorname{Beta}\left(x_{\text{eff}} + 1, n_{\text{eff}} - x_{\text{eff}} \right),
 \end{align*}
@@
 with \( x_{\text{eff}} = n_{\text{eff}} \sum_{i=1}^k w_i \hat{\theta}_i \), and \( n_{\text{eff}} \) defined in Equation~\ref{eq:neff}.
-Although Dean and Pagano \cite{Dean:2015} expressed this in terms of the F distributions, the beta distribution representation is equivalent.
+Although Dean and Pagano\cite{Dean:2015} expressed this in terms of \(F\)-distributions, the beta distribution representation is equivalent.
 
@@
 The two methods we discuss are closely related to each other and the methods discussed in Sections~\ref{sec:srs-imperfect} and \ref{sec:weight-perfect}.
-As in Section~\ref{sec:srs-imperfect}, we use the melding method \cite{FayP:2015} to create \( 1 - \alpha \)\% confidence interval very similar to Equation~\ref{eq:srs-conf-int}.
+As in Section~\ref{sec:srs-imperfect}, we use the melding method\cite{FayP:2015} to create \( 1 - \alpha \)\% confidence interval very similar to Equation~\ref{eq:srs-conf-int}.
 The confidence distributions for \( \phi_p \) and \( \phi_n \) are the same Beta distributions as in Section~\ref{sec:srs-imperfect}.
@@
 
-In the first case, we use the adaptation of the gamma confidence interval \cite{FayF:1997} presented in Section~\ref{sec:weight-perfect} to derive the \( 1 - \alpha \)\% confidence interval for \( \beta^* \):
+In the first case, we use the adaptation of the gamma confidence interval\cite{FayF:1997} presented in Section~\ref{sec:weight-perfect} to derive the \( 1 - \alpha \)\% confidence interval for \( \beta^* \):
 
@@
        g \left[G^U_{\beta^*}, B^L_{\phi_n}, B^L_{\phi_p} \right] \right)
-       \right\}
+       \right\},
 \end{equation}
@@
 
-The alternative method is very similar to that used in Kalish, et al \cite{Kali:2021}.
-We use the  modification of \cite{Korn:1998} presented in \cite{Dean:2015}, as in Section~\ref{sec:weight-perfect}, to derive the \( 100(1 - \alpha) \)\% confidence interval for \( \beta^* \):
-
-\begin{equation}
-    \left\{ q \left( \frac{\alpha}{2}, g\left[B_{KG}^L, B_{\phi_n}^U, B_{\phi_p}^U\right]  \right),  q \left( 1 - \frac{\alpha}{2}, g\left[B_{KG}^U, B_{\phi_n}^L, B_{\phi_p}^L\right]  \right) \right\}.
+The alternative method is very similar to that used in Kalish, et al.\cite{Kali:2021}
+We use the modification of Korn and Graubard's method\cite{Korn:1998} presented by Dean and Pagano,\cite{Dean:2015} as in Section~\ref{sec:weight-perfect}, to derive the \( 100(1 - \alpha) \)\% confidence interval for \( \beta^* \):
+
+\begin{equation}
+    \left\{ q \left( \frac{\alpha}{2}, g\left[B_{KG}^L, B_{\phi_n}^U, B_{\phi_p}^U\right] \right), q \left( 1 - \frac{\alpha}{2}, g\left[B_{KG}^U, B_{\phi_n}^L, B_{\phi_p}^L\right] \right) \right\},
 \end{equation}
@@
 where \( B_{KG}^L \) and \( B_{KG}^U \) are as defined in Section~\ref{sec:weight-perfect}.
-Although equivalent, this expression looks different than in Kalish, et al\cite{Kali:2021} because they used a parameter for specificity, rather than $\phi_n$, which is 1 minus specificity.
-We refer to this as WprevSeSp Binomial - weighted prevalence with sensitivity and specificity, where the prevalence confidence distribution is based on a binomial variance assumption.
+Although equivalent, this expression looks different than the one used in Kalish, et al\cite{Kali:2021} because they used a parameter for specificity, rather than $\phi_n$, which is 1 minus specificity.
+We refer to this as WprevSeSp Binomial - weighted prevalence with sensitivity and specificity, where the prevalence confidence distributions are based on a binomial assumption.
 
@@
 
-\subsubsection{When Can We Use These Methods}
-
-In Section~\ref{sec-notation}, we derived methods assuming that the apparent prevalence was a weighted sum of binomial random variables,
-$\beta = \sum_{i=1}^{K} w_i \frac{X_i}{n_i}$, where $X_i \sim \textrm{Binomial}(n_i,\theta_i)$. We used the fact that for small $\theta_i$ and large $n_i$
+\subsubsection{When We Can Use These Methods}
+
+In Section~\ref{sec-notation}, we assumed that the apparent prevalence was a weighted sum of binomial random variables,
+$\beta = \sum_{i=1}^{K} w_i \frac{X_i}{n_i}$, where $X_i \sim \textrm{Binomial}(n_i,\theta_i)$.
+Then in Section~\ref{sec:weight-perfect}, we used the fact that for small $\theta_i$ and large $n_i$
 the binomial can be approximated by the Poisson, giving $X_i \stackrel{\cdot}{\sim} \textrm{Poisson}( n_i \theta_i)$.
@@
 The multinomial model describes sampling with replacement, but it is nevertheless used to approximate a sampling design where the $j$th individual is sampled {\it without} replacement with probability $P_j$, even though under that design (unlike the multinomial model) no individual is included in the sample more than once.
-The multinomial model is a common approximation for other complex survey designs; \citep[see e.g., ][p.
+The multinomial model is a common approximation for other complex survey designs.\citep[see e.g.,][p.
 14]{Korn:1999}.
-For example, in the  Kalish, et al\cite{Kali:2021} analysis of Section~\ref{sec-Application} each individual in the sample is assigned a pseudo-weight approximating one over their sampling probability from
+For example, in the Kalish, et al\cite{Kali:2021} analysis of Section~\ref{sec-Application}, each individual in the sample is assigned a pseudo-weight approximating one over their sampling probability from
 a multinomial model.
@@
 so the prevalence is $\beta = N^{-1} \sum_{j=1}^{N} Y_j$. There are many ways to design a complex survey sample, and it is often useful to analyze them as if
-individuals were sampled with replacement with the sampling probability of the $j$th  individual equal to $P_j$, with $\sum_{j=1}^{N} P_j = 1$
-In other words, we treat the sample as if it was $n$ independent multinomial samples each with one trial and selection probability vector  $[P_1,\ldots, P_N]$.
+individuals were sampled with replacement with the sampling probability of the $j$th individual equal to $P_j$, with $\sum_{j=1}^{N} P_j = 1.$
+In other words, we treat the sample as if it were $n$ independent multinomial samples each with one trial and selection probability vector $[P_1,\ldots, P_N]$.
 Let $I_{ij}=1$ if the $i$th draw for the sample is individual $j$ in the population, and $0$ otherwise. Then let $y_i = Y_j$ and $p_i=P_j$ when $I_{ij}=1$.
@@
 \begin{eqnarray}
-\hat{\beta} & = & \frac{1}{n} \sum_{i=1}^{n} \frac{ y_i}{N p_i} = \frac{1}{n} \sum_{i=1}^{n} \sum_{j=1}^{N}  \frac{ I_{ij}  Y_j}{N P_j}
+\hat{\beta} & = & \frac{1}{n} \sum_{i=1}^{n} \frac{ y_i}{N p_i} = \frac{1}{n} \sum_{i=1}^{n} \sum_{j=1}^{N} \frac{ I_{ij} Y_j}{N P_j},
 \label{eq:betahatMultinomial}
@@
 \end{eqnarray}
-(see Korn and Graubard \cite{Korn:1999} Problem 2.2-10). We can write $\hat{\beta}$ as a weighted sum. Traditional survey weighting defines the weights so that
+(see Korn and Graubard\cite{Korn:1999} Problem 2.2-10). We can write $\hat{\beta}$ as a weighted sum. Traditional survey weighting defines the weights so that
 the weight for the $i$th sampled individual can be interpreted as the number of individuals in the population that the $i$th sampled individual represents.
@@
 Sometimes the weights are scaled after selection so that the scaled weights are $w_i^{(strad)} = \frac{ N w_i^{(trad)} }{\sum_{i=1}^{n} w_i^{(trad)}}$ and are forced to sum to $N$.
-For example, in Kalish et al \cite{Kali:2021} rescaling (sometimes called post-stratification) was done in a more complicated manner to ensure that the weights summed to the US census population within age group, sex, race, ethnicity and region.
+For example, in Kalish et al\cite{Kali:2021} rescaling (sometimes called post-stratification) was done in a more complicated manner to ensure that the weights summed to the US census population within age group, sex, race, ethnicity and region.
 
@@
 the variances are asymptotically equivalent (see Baker\cite{Baker:1994}).
-Even though we model $\hat{\beta}$ using multinomial random variables where there are many missing values (which occurs in our situation whenever $I_{ij}=0$),
-that multinomial-Poisson relationship holds even when there are missing variables (see Baker\cite{Baker:1994}, Section 3).
+Even though we model $\hat{\beta}$ using multinomial random variables, where there are many missing values (which occurs in our situation whenever $I_{ij}=0$),
+the multinomial-Poisson relationship holds even when there are missing variables (see Baker\cite{Baker:1994}, Section 3).
 For both the Poisson and multinomial models, $E(I_{ij}) = P_j$, and $\hat{\beta}$ is unbiased under either model.
@@
 \begin{eqnarray*}
-\textrm{var}_P \left(\hat{\beta} \right) & = & \textrm{var}_P \left(  \frac{1}{n}  \sum_{i=1}^{n} \sum_{j=1}^{N}  \frac{ I_{ij}  Y_j}{N P_j} \right)  \\
-& = &    \sum_{i=1}^{n} \sum_{j=1}^{N}  \frac{ \textrm{var}_P( I_{ij})  Y_j^2}{n^2 N^2 P_j^2}  \\
-& = &    \sum_{i=1}^{n} \sum_{j=1}^{N}  \frac{ \textrm{var}_P( I_{ij})  Y_j}{n^2 N^2 P_j^2}  \\
-& = &    \sum_{i=1}^{n} \sum_{j=1}^{N}  \frac{   Y_j}{n^2 N^2 P_j}.
+\textrm{var}_P \left(\hat{\beta} \right) & = & \textrm{var}_P \left( \frac{1}{n} \sum_{i=1}^{n} \sum_{j=1}^{N} \frac{ I_{ij} Y_j}{N P_j} \right)
+ = \sum_{i=1}^{n} \sum_{j=1}^{N} \frac{ \textrm{var}_P( I_{ij}) Y_j^2}{n^2 N^2 P_j^2} \\
+& = & \sum_{i=1}^{n} \sum_{j=1}^{N} \frac{ \textrm{var}_P( I_{ij}) Y_j}{n^2 N^2 P_j^2}
+ =     \sum_{i=1}^{n} \sum_{j=1}^{N} \frac{ Y_j}{n^2 N^2 P_j}.
 \end{eqnarray*}
@@
 
+We explore simulations in a variety of scenarios; however, despite this variety, we limit the scenarios to cases similar to the application of Section~\ref{sec-Application}, which has low prevalence (when the Poisson assumption is adequate), and high
+sensitivity and specificity (i.e., good assays).
+
 \subsection{Estimating Prevalence from a Simple Random Sample with an Imperfect Assay}
@@
 Figure~\ref{fig:upper_error_frequency_comparison_plot} shows that both methods make upper errors with roughly the same frequency.
-Figure~\ref{fig:lower_error_frequency_comparison_plot} demonstrates that while the melding procedure bounds the lower error frequency below 2.5\%, the Lang-Reiczigel method generally has lower error above 2.5\%.
+Figure~\ref{fig:lower_error_frequency_comparison_plot} demonstrates that while the melding procedure bounds the lower error frequency below 2.5\%, the Lang-Reiczigel method generally has lower error frequency above 2.5\%.
 Each of these behaviors may be undesirable, depending on the context in which the methods are applied.
-For applications in which there is a need to bound the lower errors, the melding method is superior.
+For applications in which there is a need to bound the lower errors, the melding method appears to be superior.
 
@@
 From Figures~\ref{fig:perfect_coverage_50_groups_0_005_prev}--\ref{fig:perfect_coverage_8000_groups_0_05_prev}, we note that the two competitor methods generally exhibit lower coverage as the coefficient of variation among the weights increases.
-In Figure~\ref{fig:perfect_coverage_50_groups_0_005_prev}, this coverage falls below 60\% when the prevalence very low and is concentrated among the highest weights, and the coefficient of variation among the weights exceeds 4.
+In Figure~\ref{fig:perfect_coverage_50_groups_0_005_prev}, this coverage falls below 60\% when the prevalence is very low and is concentrated among the highest weights, and the coefficient of variation among the weights exceeds 4.
 Uniform distribution of prevalence among the weights, increased overall prevalence, and larger sample sizes among fewer groups all appear to lessen the severity of this problem.
@@
 In scenarios with higher overall prevalence, the Agresti-Coul and Korn-Graubard methods achieve close to nominal coverage, while the wsPoisson method strongly over-covers.
-This is similar to the behavior observed in Fay and Feuer\cite{FayF:1997}, where, in simulations, the overall error rate for the gamma intervals decreased as the variance of the weights increased.
+This is similar to the behavior observed in Fay and Feuer,\cite{FayF:1997} where, in simulations, the overall error rate for the gamma intervals decreased as the variance of the weights increased.
 Because our methods appear to be very conservative, with coverage near 100\% in some cases, we present the widths of the confidence intervals in Figures~\ref{fig:perfect_confidence_interval_width_50_groups_0_005_prev}--\ref{fig:perfect_confidence_interval_width_8000_groups_0_05_prev}.
@@
 \caption{Coverage properties for the wsPoisson model and two standard methods, the Dean-Pagano modification of the Agresti-Coull method and of the Korn-Graubard method.
-Each point represents 10,000 simulations of datasets from a population with 0.5\% Prevalence where 50 groups of 200 people are sampled.
+Each point represents 10,000 simulations of datasets from a population with 0.5\% prevalence where 50 groups of 200 people are sampled.
 The horizontal dashed line indicates the nominal coverage, 95\%.
@@
 \caption{Coverage properties for the wsPoisson model and two standard methods, the Dean-Pagano modification of the Agresti-Coull method and of the Korn-Graubard method.
-Each point represents 10,000 simulations of datasets from a population with 0.5\% Prevalence where 8000 individuals are sampled.
+Each point represents 10,000 simulations of datasets from a population with 0.5\% prevalence where 8000 individuals are sampled.
 The horizontal dashed line indicates the nominal coverage, 95\%.
@@
 \caption{Coverage properties for the wsPoisson model and two standard methods, the Dean-Pagano modification of the Agresti-Coull method and of the Korn-Graubard method.
-Each point represents 10,000 simulations of datasets from a population with 5\% Prevalence where 50 groups of 200 people are sampled.
+Each point represents 10,000 simulations of datasets from a population with 5\% prevalence where 50 groups of 200 people are sampled.
 The horizontal dashed line indicates the nominal coverage, 95\%.
@@
 \includegraphics[width=0.8\textwidth]{figures/perfect_coverage_8000_groups_0_05_prev.pdf}
-\caption{Coverage properties for the wsPoisson model and two standard methods, the Dean-Pagano modification of Agresti-Coull and Korn-Graubard
-Each point represents 10,000 simulations of datasets from a population with 5\% Prevalence where 8000 individuals are sampled.
+\caption{Coverage properties for the wsPoisson model and two standard methods, the Dean-Pagano modification of Agresti-Coull and Korn-Graubard.
+Each point represents 10,000 simulations of datasets from a population with 5\% prevalence where 8000 individuals are sampled.
 The horizontal dashed line indicates the nominal coverage, 95\%.
@@
 
-We compare properties our melded confidence interval WprevSeSp Poisson, to another melded confidence interval method, WprevSeSp Binomial.
-The methods are assessed in a several simulated scenarios with varying levels of disease prevalence (0.5\% or 5\%), types of groups surveyed (50 groups 200 subjects or 8000 groups of 1 subject), distributions of weights among the groups (coefficient of variation from approximately 0\% to nearly 6\%), the number of groups with non-zero prevalence, and the specificity of the assay (80\% - 100\%).
+We compare properties of our melded confidence interval, WprevSeSp Poisson, to another melded confidence interval method, WprevSeSp Binomial, for cases with weighted samples and imperfect assays.
+The methods are assessed in a several simulated scenarios with varying levels of disease prevalence (0.5\% or 5\%), types of groups surveyed (50 groups of 200 subjects each or 8000 groups of 1 subject), distributions of weights among the groups (coefficient of variation from approximately 0\% to nearly 600\%), the number of groups with non-zero prevalence, and the specificity of the assay (80\% - 100\%).
 In each scenario, the assay has 95\% sensitivity.
 Each scenario creates up to 500 new sets of weights and $\theta_i$ parameters (as in Section~\ref{sim-perfect}), and each of those is simulated 10,000 times, with new prevalence, sensitivity, and specificity surveys generated and 95\% confidence intervals are created.
-Modelled after the study of Kalish, et al \cite{Kali:2021}, the simulated sensitivity is assessed based on 60 tests, while specificity is based on 300 tests.
+Modeled after the study of Kalish, et al,\cite{Kali:2021} the simulated sensitivity is assessed based on 60 tests, while specificity is based on 300 tests.
 
@@
 \caption{Coverage properties for the confidence interval procedures, WprevSeSp Binomial and WprevSeSp Poisson.
-Each point represents 10,000 simulations of datasets from a population with 0.5\% Prevalence where 50 groups of 200 people are sampled.
+Each point represents 10,000 simulations of datasets from a population with 0.5\% prevalence where 50 groups of 200 people are sampled.
 Each datasets also includes simulated results of tests to evaluate the sensitivity and specificity of the assay performed on 60 and 300 individuals, respectively.
@@
 \caption{Coverage properties for the confidence interval procedures, WprevSeSp Binomial and WprevSeSp Poisson.
-Each point represents 10,000 simulations of datasets from a population with 0.5\% Prevalence where 8000 individuals are sampled.
+Each point represents 10,000 simulations of datasets from a population with 0.5\% prevalence where 8000 individuals are sampled.
 Each datasets also includes simulated results of tests to evaluate the sensitivity and specificity of the assay performed on 60 and 300 individuals, respectively.
@@
 \caption{Coverage properties for the confidence interval procedures, WprevSeSp Binomial and WprevSeSp Poisson.
-Each point represents 10,000 simulations of datasets from a population with 5\% Prevalence where 50 groups of 200 people are sampled.
+Each point represents 10,000 simulations of datasets from a population with 5\% prevalence where 50 groups of 200 people are sampled.
 Each datasets also includes simulated results of tests to evaluate the sensitivity and specificity of the assay performed on 60 and 300 individuals, respectively.
@@
 \caption{Coverage properties for the confidence interval procedures, WprevSeSp Binomial and WprevSeSp Poisson.
-Each point represents 10,000 simulations of datasets from a population with 5\% Prevalence where 8000 individuals are sampled.
+Each point represents 10,000 simulations of datasets from a population with 5\% prevalence where 8000 individuals are sampled.
 Each datasets also includes simulated results of tests to evaluate the sensitivity and specificity of the assay performed on 60 and 300 individuals, respectively.
@@
 In the other scenarios tested, the WprevSeSp Binomial generally achieves closer to nominal coverage than the WprevSeSp Poisson, which strongly over-covers.
-Our proposed WprevSeSp Poisson method maintains or exceed the desired coverage in all scenarios.
+Our proposed WprevSeSp Poisson method maintains or exceeds the desired coverage in all scenarios.
 In these scenarios, we also assess properties of the wsPoisson procedure, which does not account for the the imperfect assay.
 This method results in approximately 0\% coverage in any scenarios where specificity is less than perfect.
-For this reason, results from method are omitted in the figures.
-Because our methods appear to be very conservative, with coverage near 100\% in some cases, we present the widths of the confidence intervals in Figures~\ref{fig:imperfect_confidence_interval_width_50_groups_0_005_prev}--\ref{fig:imperfect_confidence_interval_width_8000_groups_0_05_prev}.
+For this reason, results from that method are omitted in the figures.
+Because both WprevSeSp methods appear to be very conservative, with coverage near 100\% in some cases, we present the widths of the confidence intervals in Figures~\ref{fig:imperfect_confidence_interval_width_50_groups_0_005_prev}--\ref{fig:imperfect_confidence_interval_width_8000_groups_0_05_prev}.
 The WprevSeSp Binomial and WprevSeSp Poisson methods typically produce wide intervals of approximately the same size - sometimes as wide as 12\%, even when true prevalence is 0.05\%.
@@
 
-\section{Applications}
+\section{Application}
 \label{sec-Application}
 
-We  apply these two methods to a real data set from
-Kalish, et al \cite{Kali:2021}.
+We apply these two methods to a real data set from Kalish, et al.\cite{Kali:2021}
 This data set was collected to estimate seroprevalence of SARS-CoV-2 in undiagnosed adults in the United States between May and July 2020.
@@
 First we apply the methods to the full data set (\( n = 8058, \text{weight coefficient of variation} = 252\%\)).
-The seroprevalence in Kalish, et al was 4.6\% with (95\% CI: 2.6\% to 6.5\%), using a confidence interval method that was nearly the same as the WprevSeSp Binomial method (the method Kalish et al  included a calculation of the variability of the weights due to the estimation of the weights, whereas in this paper we treat the weights as fixed constants).
-The Korn and Graubard type melded confidence interval with imperfect assay adjustments (WprevSeSp Binomial) studied in this paper produced the 95\% confidence interval for population prevalence nearly the equivalent, (2.53\%, 6.68\%).
-while the wsPoisson type melded confidence interval with imperfect assay adjustments (WprevSeSp Poisson) produced the 95\% confidence interval (2.56\%, 7.54\%).
+The seroprevalence in Kalish, {\it et al } was 4.6\% with (95\% CI: 2.6\% to 6.5\%), using a confidence interval method that was nearly the same as the WprevSeSp Binomial method (the method Kalish et al included a calculation of the variability of the weights due to the estimation of the weights, whereas in this paper we treat the weights as fixed constants).
+The Korn and Graubard type melded confidence interval with imperfect assay adjustments (WprevSeSp Binomial) studied in this paper produced a 95\% confidence interval for population prevalence of (2.53\%, 6.68\%), very similar to that of Kalish, et al, while the wsPoisson type melded confidence interval with imperfect assay adjustments (WprevSeSp Poisson) produced the 95\% confidence interval (2.56\%, 7.54\%).
 We also apply the wsPoisson method from Section~\ref{sec:weight-perfect}, which does not account for imperfections in the assay, resulting in a 95\% confidence interval of (3.04\%, 7.39\%).
@@
 The wsPoisson method produces a 95\% confidence interval of (2.80\%, 19.63\%).
-In this case, the two melded confidence intervals are much wider than the WprevSeSp Binomial interval, which is as expected since the melding method is designed to guarantee coverage, although the simulations show that the WprevSeSp Binomial interval may be reasonable (see e.g., Figure~B20).
+In this case, the two Poisson-based confidence intervals are much wider than the WprevSeSp Binomial interval, which is as expected since the melding method is designed to guarantee coverage, although the simulations show that the WprevSeSp Binomial interval may be reasonable (see e.g., Figure~B20).
 The smaller WprevSeSp Binomial interval is also unsurprising and is similar to the results observed in our simulation study.
@@
 We presented several methods for creating confidence intervals to assess disease prevalence in variety of settings, including simple random samples with imperfect tests, weighted sampling with perfect tests, and weighted sampling with imperfect tests.
-One of the new methods was very similar to the method used by Kalish et al\cite{Kali:2021}, and in this paper we have explored its properties.
+A main point of this paper was to develop and study methods for the last setting, where there has been little previous work.
+Two methods were studied for that setting, WprevSeSp Poisson and WprevSeSp Binomial, the latter of which was very similar to the method used by Kalish et al.\cite{Kali:2021}
+In simulations based on the Kalish et al application, the WprevSeSp Poisson method had greater than nominal coverage in all cases but could be very conservative, while the WprevSeSp Binomial was slightly less conservative but had less than nominal coverage in a few scenarios.
+
+In less complicated scenarios, we could compare the new methods to established methods.
 These new confidence intervals appear to guarantee coverage in most simulated settings, including some scenarios where competitor methods dramatically under-cover.
@@
 In the case of the simple random sample with an imperfect test, our new methods are able to bound the lower error rate for a 95\% confidence interval at 2.5\%, while the Lang-Reiczigel\cite{Lang:2014} method maintains 95\% coverage by allowing a higher lower error rate.
-A big advantage of our method is that it may be applied with complex survey methods, where each individual has their own weight, such as in Kalish et al\cite{Kali:2021}. 
-However, our method  only studied fixed weights and not when the weights are estimated as in Kalish et al.
-Further work is needed to address such cases.
-In addition, further worked is needed to consider other complex sample designs such as multistage cluster designs that are used in  household and institutional surveys such hospital and medical practice surveys.
-
-Our method was slightly different to that used in Kalish, et al\cite{Kali:2021}, in that thdatae latter method included estimates of the variability of the weights; however, recalculating the confidence intervals on the same data shows that in that case there was little difference.
-%[BARRY TO ADD MORE DISCUSSION AND REFERENCES ABOUT ESTIMATING VARIABILITY IN %WEIGHTS, ETC., AND TRIMMING WEIGHTS].
+
+A big advantage of the new methods is that they may be applied with complex survey methods, where each individual has their own weight, such as in Kalish et al.\cite{Kali:2021}
+However, in this paper we have only studied fixed weights and not when the weights are estimated as in Kalish et al.
+Further, we have not included estimates of the variability of the weights as was done in Kalish, et al; however, recalculating the confidence intervals on the same data shows that ignoring variability of the weights made little difference in that case.
+Further work is needed to address this issue.
+In addition, further work is needed to consider other complex sample designs such as multistage cluster designs that are used in household and institutional surveys such hospital and medical practice surveys.
+
+Although the new methods have coverage that is at least nominal in nearly all simulated situations, the cost is that they can be overly conservative.
+Future work could create less conservative methods by, for example, modifying the new methods by replacing the lower or upper confidence distributions with a mixture of the two (as in Veronese and Melilli\cite{veronese2015}), or using a mid-p version of the gamma intervals (as in Fay and Sungwook\cite{FayK:2017}).
+
+Although this paper has done extensive simulations, the focus of the simulations was for low prevalence and high
+sensitivity and specificity. For other situations, especially high prevalence situations, more work is needed to more fully explore the properties of these methods.
 
 Our methods' conservative properties are especially advantageous in settings where the competitor methods exhibit much lower than nominal coverage.
-For example, there is high variance among the sample weights and prevalence is concentrated among the highest-weighted samples competitor coverage of 95\% confidence intervals can fall to 60\% for competitor methods, while our method exhibits > 95\% coverage.
+For example, when there is high variance among the sample weights and prevalence is concentrated among the highest-weighted samples, competitor coverage of 95\% confidence intervals can fall to 60\%, while our method exhibits \( > \) 95\% coverage.
 Thus, we suggest that our melding methods be employed when working with survey settings which involve high variance among the weights or lower errors are particularly undesirable.
@@
 \section{Bibliography}
-\nocite{*}% Show all bib entries - both cited and uncited; comment this line to view only cited bib entries;
+% \nocite{*}% Show all bib entries - both cited and uncited; comment this line to view only cited bib entries;
 \bibliography{refs}%
@@
 
-\section{Monotonicity of \( g \)}
+\section{Monotonicity of \texorpdfstring{\( \MakeLowercase{g} \)}{g}}
 \label{monotonicity}
@@
 
-\subsection{Monotonicity in \( \hat{\phi}_p \)}
+\subsection{Monotonicity in \texorpdfstring{\( \hat{\phi}_p \)}{ϕp}}
 
@@
 \begin{array}{ll}
-0 & \hat{\phi}_p < \hat{\theta}_1 < \hat{\phi}_n  \\
+0 \hspace*{3em} & \hat{\phi}_p < \hat{\theta}_1 < \hat{\phi}_n  \\
 0 & \hat{\theta}_1 = \hat{\phi}_p < \hat{\phi}_n \\
@@
 0 & \hat{\phi}_p < \hat{\theta}_1 = \hat{\phi}_n	\\
-\frac{\hat{\theta}_1 - \hat{\phi}_n}{\hat{\phi}_p - \hat{\phi}_n} = \frac{0}{0} = 0 & \hat{\phi}_p = \hat{\theta}_1 = \hat{\phi}_n 	\\
+\frac{\hat{\theta}_1 - \hat{\phi}_n}{\hat{\phi}_p - \hat{\phi}_n} = \frac{0}{0} \equiv 0 & \hat{\phi}_p = \hat{\theta}_1 = \hat{\phi}_n 	\\
 \frac{\hat{\theta}_1 - \hat{\phi}_n}{\hat{\phi}_p - \hat{\phi}_n} = \frac{0}{\hat{\phi}_p - \hat{\phi}_n} = 0 & \hat{\theta}_1 = \hat{\phi}_n < \hat{\phi}_p	\\
@@
 
-\subsection{Monotonicity in \( \hat{\theta}_1 \)}
+\subsection{Monotonicity in \texorpdfstring{\( \hat{\theta}_1 \)}{θ1}}
 
@@
 \begin{array}{ll}
-0 & \hat{\theta}_1 < \hat{\phi}_p < \hat{\phi}_n  \\
+0 \hspace*{3em} & \hat{\theta}_1 < \hat{\phi}_p < \hat{\phi}_n  \\
 0 & \hat{\phi}_p = \hat{\theta}_1 < \hat{\phi}_n \\
@@
 0 & \hat{\theta}_1 < \hat{\phi}_p = \hat{\phi}_n	\\
-\frac{\hat{\theta}_1 - \hat{\phi}_n}{\hat{\phi}_p - \hat{\phi}_n} = \frac{0}{0} = 0 & \hat{\theta}_1 = \hat{\phi}_p = \hat{\phi}_n 	\\
+\frac{\hat{\theta}_1 - \hat{\phi}_n}{\hat{\phi}_p - \hat{\phi}_n} = \frac{0}{0} \equiv 0 & \hat{\theta}_1 = \hat{\phi}_p = \hat{\phi}_n 	\\
 0 & \hat{\phi}_p = \hat{\phi}_n < \hat{\theta}_1	\\
@@
 
-\subsection{Monotonicity in \( \hat{\phi}_n \)}
+\subsection{Monotonicity in \texorpdfstring{\( \hat{\phi}_n \)}{ϕ n}}
 
@@
 \begin{array}{ll}
-1 & \hat{\phi}_n < \hat{\phi}_p < \hat{\theta}_1  \\
+1 \hspace*{3em} & \hat{\phi}_n < \hat{\phi}_p < \hat{\theta}_1  \\
 0 & \hat{\phi}_p = \hat{\phi}_n < \hat{\theta}_1 \\
@@
 \frac{\hat{\theta}_1 - \hat{\phi}_n}{\hat{\phi}_p - \hat{\phi}_n} = 1 & \hat{\phi}_n < \hat{\theta}_1 = \hat{\phi}_p	\\
-\frac{\hat{\theta}_1 - \hat{\phi}_n}{\hat{\phi}_p - \hat{\phi}_n} = \frac{0}{0} = 0 & \hat{\phi}_n = \hat{\theta}_1 = \hat{\phi}_p 	\\
+\frac{\hat{\theta}_1 - \hat{\phi}_n}{\hat{\phi}_p - \hat{\phi}_n} = \frac{0}{0} \equiv 0 & \hat{\phi}_n = \hat{\theta}_1 = \hat{\phi}_p 	\\
 0 & \hat{\theta}_1 = \hat{\phi}_p < \hat{\phi}_n	\\
@@
 \caption{Lower error properties for the wsPoisson model and two standard methods, the Dean-Pagano modification of the Agresti-Coull method and of the Korn-Graubard method.
-Each point represents 10,000 simulations of datasets from a population with 0.5\% Prevalence where 50 groups of 200 people are sampled.
+Each point represents 10,000 simulations of datasets from a population with 0.5\% prevalence where 50 groups of 200 people are sampled.
 The horizontal dashed line indicates the nominal lower error rate, 2.5\%.
@@
 \caption{Lower error properties for the wsPoisson model and two standard methods, the Dean-Pagano modification of the Agresti-Coull method and of the Korn-Graubard method.
-Each point represents 10,000 simulations of datasets from a population with 0.5\% Prevalence where 8000 individuals are sampled.
+Each point represents 10,000 simulations of datasets from a population with 0.5\% prevalence where 8000 individuals are sampled.
 The horizontal dashed line indicates the nominal lower error rate, 2.5\%.
@@
 \caption{Lower error properties for the wsPoisson model and two standard methods, the Dean-Pagano modification of the Agresti-Coull method and of the Korn-Graubard method.
-Each point represents 10,000 simulations of datasets from a population with 5\% Prevalence where 50 groups of 200 people are sampled.
+Each point represents 10,000 simulations of datasets from a population with 5\% prevalence where 50 groups of 200 people are sampled.
 The horizontal dashed line indicates the nominal lower error rate, 2.5\%.
@@
 \caption{Lower error properties for the wsPoisson model and two standard methods, the Dean-Pagano modification of the Agresti-Coull method and of the Korn-Graubard method.
-Each point represents 10,000 simulations of datasets from a population with 5\% Prevalence where 8000 individuals are sampled.
+Each point represents 10,000 simulations of datasets from a population with 5\% prevalence where 8000 individuals are sampled.
 The horizontal dashed line indicates the nominal lower error rate, 2.5\%.
@@
 \caption{Upper error properties for the wsPoisson model and two standard methods, the Dean-Pagano modification of the Agresti-Coull method and of the Korn-Graubard method.
-Each point represents 10,000 simulations of datasets from a population with 0.5\% Prevalence where 50 groups of 200 people are sampled.
+Each point represents 10,000 simulations of datasets from a population with 0.5\% prevalence where 50 groups of 200 people are sampled.
 The horizontal dashed line indicates the nominal upper error rate, 2.5\%.
@@
 \caption{Upper error properties for the wsPoisson model and two standard methods, the Dean-Pagano modification of the Agresti-Coull method and of the Korn-Graubard method.
-Each point represents 10,000 simulations of datasets from a population with 0.5\% Prevalence where 8000 individuals are sampled.
+Each point represents 10,000 simulations of datasets from a population with 0.5\% prevalence where 8000 individuals are sampled.
 The horizontal dashed line indicates the nominal upper error rate, 2.5\%.
@@
 \caption{Upper error properties for the wsPoisson model and two standard methods, the Dean-Pagano modification of the Agresti-Coull method and of the Korn-Graubard method.
-Each point represents 10,000 simulations of datasets from a population with 5\% Prevalence where 50 groups of 200 people are sampled.
+Each point represents 10,000 simulations of datasets from a population with 5\% prevalence where 50 groups of 200 people are sampled.
 The horizontal dashed line indicates the nominal upper error rate, 2.5\%.
@@
 \caption{Upper error properties for the wsPoisson model and two standard methods, the Dean-Pagano modification of the Agresti-Coull method and of the Korn-Graubard method.
-Each point represents 10,000 simulations of datasets from a population with 5\% Prevalence where 8000 individuals are sampled.
+Each point represents 10,000 simulations of datasets from a population with 5\% prevalence where 8000 individuals are sampled.
 The horizontal dashed line indicates the nominal upper error rate, 2.5\%.
@@
 \caption{Confidence interval width properties for the wsPoisson model and two standard methods, the Dean-Pagano modification of the Agresti-Coull method and of the Korn-Graubard method.
-Each point represents 10,000 simulations of datasets from a population with 0.5\% Prevalence where 50 groups of 200 people are sampled.
+Each point represents 10,000 simulations of datasets from a population with 0.5\% prevalence where 50 groups of 200 people are sampled.
 Colored dashed lines are estimates from a logistic regression model using quadratic splines.}
@@
 \caption{Confidence interval width properties for the wsPoisson model and two standard methods, the Dean-Pagano modification of the Agresti-Coull method and of the Korn-Graubard method.
-Each point represents 10,000 simulations of datasets from a population with 5\% Prevalence where 50 groups of 200 people are sampled.
+Each point represents 10,000 simulations of datasets from a population with 5\% prevalence where 50 groups of 200 people are sampled.
 Colored dashed lines are estimates from a logistic regression model using quadratic splines.}
@@
 \caption{Confidence interval width properties for the wsPoisson model and two standard methods, the Dean-Pagano modification of the Agresti-Coull method and of the Korn-Graubard method.
-Each point represents 10,000 simulations of datasets from a population with 0.5\% Prevalence where 8000 individuals are sampled.
+Each point represents 10,000 simulations of datasets from a population with 0.5\% prevalence where 8000 individuals are sampled.
 Colored dashed lines are estimates from a logistic regression model using quadratic splines.}
@@
 \caption{Confidence interval width properties for the wsPoisson model and two standard methods, the Dean-Pagano modification of the Agresti-Coull method and of the Korn-Graubard method.
-Each point represents 10,000 simulations of datasets from a population with 5\% Prevalence where 8000 individuals are sampled.
+Each point represents 10,000 simulations of datasets from a population with 5\% prevalence where 8000 individuals are sampled.
 Colored dashed lines are estimates from a logistic regression model using quadratic splines.}
@@
 \caption{Lower error properties for the confidence interval procedures, WprevSeSp Binomial and WprevSeSp Poisson.
-Each point represents 10,000 simulations of datasets from a population with 0.5\% Prevalence where 50 groups of 200 people are sampled.
+Each point represents 10,000 simulations of datasets from a population with 0.5\% prevalence where 50 groups of 200 people are sampled.
 Each datasets also includes simulated results of tests to evaluate the sensitivity and specificity of the assay performed on 60 and 300 individuals, respectively.
@@
 \caption{Lower error properties for the confidence interval procedures, WprevSeSp Binomial and WprevSeSp Poisson.
-Each point represents 10,000 simulations of datasets from a population with 0.5\% Prevalence where 8000 individuals are sampled.
+Each point represents 10,000 simulations of datasets from a population with 0.5\% prevalence where 8000 individuals are sampled.
 Each datasets also includes simulated results of tests to evaluate the sensitivity and specificity of the assay performed on 60 and 300 individuals, respectively.
@@
 \caption{Lower error properties for the confidence interval procedures, WprevSeSp Binomial and WprevSeSp Poisson.
-Each point represents 10,000 simulations of datasets from a population with 5\% Prevalence where 50 groups of 200 people are sampled.
+Each point represents 10,000 simulations of datasets from a population with 5\% prevalence where 50 groups of 200 people are sampled.
 Each datasets also includes simulated results of tests to evaluate the sensitivity and specificity of the assay performed on 60 and 300 individuals, respectively.
@@
 \caption{Lower error properties for the confidence interval procedures, WprevSeSp Binomial and WprevSeSp Poisson.
-Each point represents 10,000 simulations of datasets from a population with 5\% Prevalence where 8000 individuals are sampled.
+Each point represents 10,000 simulations of datasets from a population with 5\% prevalence where 8000 individuals are sampled.
 Each datasets also includes simulated results of tests to evaluate the sensitivity and specificity of the assay performed on 60 and 300 individuals, respectively.
@@
 \caption{Upper error properties for the confidence interval procedures, WprevSeSp Binomial and WprevSeSp Poisson.
-Each point represents 10,000 simulations of datasets from a population with 0.5\% Prevalence where 50 groups of 200 people are sampled.
+Each point represents 10,000 simulations of datasets from a population with 0.5\% prevalence where 50 groups of 200 people are sampled.
 Each datasets also includes simulated results of tests to evaluate the sensitivity and specificity of the assay performed on 60 and 300 individuals, respectively.
@@
 \caption{Upper error properties for the confidence interval procedures, WprevSeSp Binomial and WprevSeSp Poisson.
-Each point represents 10,000 simulations of datasets from a population with 0.5\% Prevalence where 8000 individuals are sampled.
+Each point represents 10,000 simulations of datasets from a population with 0.5\% prevalence where 8000 individuals are sampled.
 Each datasets also includes simulated results of tests to evaluate the sensitivity and specificity of the assay performed on 60 and 300 individuals, respectively.
@@
 \caption{Upper error properties for the confidence interval procedures, WprevSeSp Binomial and WprevSeSp Poisson.
-Each point represents 10,000 simulations of datasets from a population with 5\% Prevalence where 50 groups of 200 people are sampled.
+Each point represents 10,000 simulations of datasets from a population with 5\% prevalence where 50 groups of 200 people are sampled.
 Each datasets also includes simulated results of tests to evaluate the sensitivity and specificity of the assay performed on 60 and 300 individuals, respectively.
@@
 \caption{Upper error properties for the confidence interval procedures, WprevSeSp Binomial and WprevSeSp Poisson.
-Each point represents 10,000 simulations of datasets from a population with 5\% Prevalence where 8000 individuals are sampled.
+Each point represents 10,000 simulations of datasets from a population with 5\% prevalence where 8000 individuals are sampled.
 Each datasets also includes simulated results of tests to evaluate the sensitivity and specificity of the assay performed on 60 and 300 individuals, respectively.
@@
 \caption{Confidence interval width properties for the confidence interval procedures, WprevSeSp Binomial and WprevSeSp Poisson.
-Each point represents 10,000 simulations of datasets from a population with 0.5\% Prevalence where 50 groups of 200 people are sampled.
+Each point represents 10,000 simulations of datasets from a population with 0.5\% prevalence where 50 groups of 200 people are sampled.
 Each datasets also includes simulated results of tests to evaluate the sensitivity and specificity of the assay performed on 60 and 300 individuals, respectively.
@@
 \caption{Confidence interval width properties for the confidence interval procedures, WprevSeSp Binomial and WprevSeSp Poisson.
-Each point represents 10,000 simulations of datasets from a population with 5\% Prevalence where 50 groups of 200 people are sampled.
+Each point represents 10,000 simulations of datasets from a population with 5\% prevalence where 50 groups of 200 people are sampled.
 Each datasets also includes simulated results of tests to evaluate the sensitivity and specificity of the assay performed on 60 and 300 individuals, respectively.
@@
 \caption{Confidence interval width properties for the confidence interval procedures, WprevSeSp Binomial and WprevSeSp Poisson.
-Each point represents 10,000 simulations of datasets from a population with 0.5\% Prevalence where 8000 individuals are sampled.
+Each point represents 10,000 simulations of datasets from a population with 0.5\% prevalence where 8000 individuals are sampled.
 Each datasets also includes simulated results of tests to evaluate the sensitivity and specificity of the assay performed on 60 and 300 individuals, respectively.
@@
 \caption{Confidence interval width properties for the confidence interval procedures, WprevSeSp Binomial and WprevSeSp Poisson.
-Each point represents 10,000 simulations of datasets from a population with 5\% Prevalence where 8000 individuals are sampled.
+Each point represents 10,000 simulations of datasets from a population with 5\% prevalence where 8000 individuals are sampled.
 Each datasets also includes simulated results of tests to evaluate the sensitivity and specificity of the assay performed on 60 and 300 individuals, respectively.

### 2023-02-03 code/function_with_example_for_asht.R
function_with_example_for_asht

@@ -1,0 +1,162 @@
+#' @param method either "binomial" or "poisson"
+#' @param x integer vector of apparent positive tests for each group
+#' @param n integer vector of number of tests for each group
+#' @param w numeric vector of weights for each group (must sum to 1)
+#' @param cn number of positive tests for negative controls
+#' @param mn number of positive tests results on negative controls
+#' @param cp number of positive tests for positive controls
+#' @param mp number of positive tests results on positive controls
+#' @param conf.level confidence level of the interval
+#' @param nmc number of Monte Carlo replications
+#' @param seed seed for random number generation
+#'
+#' @return A list with class "htest" containing the following components:
+#' `estimate` the adjusted prevalence estimate, adjusted for sensitivity and specificity
+#' `statistic` the estimated sensitivity given by cp / mp
+#' `parameter` the estimated specificity given by 1 - cp / mp
+#' `conf.int` a confidence interval for the prevalence
+#' `data.name` a character string giving the unadjusted prevalence value
+#' `method` the character string describing the output.
+#' @export
+#'
+#' @examples
+WprevSeSp <- function(method = c("binomial", "poisson"),
+                      x, n, w, cn, mn, cp, mp,
+                      conf.level = 0.95,
+                      nmc = 1e5, seed = 49201) {
+  method <- match.arg(method)
+
+  if (!all.equal(length(x), length(n), length(w))) {
+    stop("x, n, and w must be of equal length")
+  }
+
+  if (!isTRUE(all.equal(sum(w), 1))) {
+    stop("Weights must sum to 1.")
+  }
+
+  if (!is.null(seed)) set.seed(seed)
+
+  g <- function(theta_1, phi_n, phi_p) {
+    result <- numeric(length(theta_1))
+
+    ind_for_computed <- which((phi_p >= theta_1) & (theta_1 >= phi_n))
+    computed <- (theta_1 - phi_n) / (phi_p - phi_n)
+
+    result[(phi_n < phi_p) & (phi_p < theta_1)] <- 1
[…]

### 2023-02-04 code/function_with_example_for_asht.R
fix test for function_with_example_for_asht.R

@@ -26,7 +26,7 @@ WprevSeSp <- function(method = c("binomial", "poisson"),
                       nmc = 1e5, seed = 49201) {
   method <- match.arg(method)
 
-  if (!all.equal(length(x), length(n), length(w))) {
+  if (length(unique(sapply(list(x, n, w), length))) > 1) {
     stop("x, n, and w must be of equal length")
   }
 

### 2023-02-04 code/function_with_example_for_asht.R
style fixes for function_with_example_for_asht

@@ -102,61 +102,74 @@ WprevSeSp <- function(method = c("binomial", "poisson"),
     ifelse(method == "binomial", "Korn-Graubard", "Fay and Feuer"),
     " with melding)"
   )
-  output <- list(estimate = estimate,
-                 statistic = statistic,
-                 parameter = parameter,
-                 conf.int = ci,
-                 data.name = data,
-                 method = method_text)
+  output <- list(
+    estimate = estimate,
+    statistic = statistic,
+    parameter = parameter,
+    conf.int = ci,
+    data.name = data,
+    method = method_text
+  )
   class(output) <- "htest"
   output
 }
 
 
 # Example -----------------------------------------------------------------
-example_data_WprevSeSp <-
-  list(x = c(53, 47, 63, 50, 54, 54, 57, 51, 66, 51, 52, 48, 37, 44, 59,
-             55, 50, 58, 52, 54, 41, 45, 49, 54, 37, 53, 57, 58, 55, 55, 56,
-             42, 58, 47, 49, 63, 54, 54, 54, 41, 43, 56, 44, 49, 47, 45, 62,
-             53, 54, 47),
-       n = c(200, 200, 200, 200, 200, 200, 200, 200, 200, 200, 200, 200,
-             200, 200, 200, 200, 200, 200, 200, 200, 200, 200, 200, 200, 200,
-             200, 200, 200, 200, 200, 200, 200, 200, 200, 200, 200, 200, 200,
-             200, 200, 200, 200, 200, 200, 200, 200, 200, 200, 200, 200),
-       w = c(0.0205962892844504, 0.0204062236737538, 0.0203843096373626,
-             0.0202785701233134, 0.0202617051778543, 0.0202138087214499, 0.0201972974884707,
-             0.0201818190015587, 0.0201631543739836, 0.0201560795402158, 0.0201555234250465,
-             0.0201461978246263, 0.0201342022821394, 0.0201264004067009, 0.0201167314250592,
-             0.0201015081093692, 0.0201003484427457, 0.0201002680000886, 0.0200817537259523,
-             0.0200573433887284, 0.0200443907258367, 0.0200358187073312, 0.0200349749335002,
[…]

### 2023-02-04 code/function_with_example_for_asht.R
fix for 0 AP in function_with_example_for_asht

@@ -57,11 +57,13 @@ WprevSeSp <- function(method = c("binomial", "poisson"),
   samples_B_phi_p_L <- rbeta(n = nmc, shape1 = cp, shape2 = mp - cp + 1)
   samples_B_phi_p_U <- rbeta(n = nmc, shape1 = cp + 1, shape2 = mp - cp)
 
-
-  # For binomial
   if (method == "binomial") {
-    n_eff <- (s_w_theta_hat * (1 - s_w_theta_hat)) / (sum(w^2 / n * theta_hat))
-    n_eff <- ifelse(n_eff == 0, sum(n), n_eff)
+    n_eff <-
+      if (s_w_theta_hat == 0) {
+      sum(n)
+      } else {
+        (s_w_theta_hat * (1 - s_w_theta_hat)) / (sum(w^2 / n * theta_hat))
+    }
     x_eff <- n_eff * s_w_theta_hat
 
     samples_B_KG_L <- rbeta(n = nmc, shape1 = x_eff, shape2 = n_eff - x_eff + 1)
@@ -76,7 +78,13 @@ WprevSeSp <- function(method = c("binomial", "poisson"),
     y_star <- y + wm
     v_star <- v + wm^2
 
-    samples_G_beta_star_L <- rgamma(n = nmc, y^2 / v, scale = v / y)
+    samples_G_beta_star_L <-
+      if (y == 0) {
+        numeric(nmc)
+      } else {
+        rgamma(n = nmc, y^2 / v, scale = v / y)
+      }
+
     samples_G_beta_star_U <- rgamma(n = nmc, y_star^2 / v_star, scale = v_star / y_star)
 
     samples_g_L <- g(samples_G_beta_star_L, samples_B_phi_n_U, samples_B_phi_p_U)
@@ -162,10 +170,55 @@ WprevSeSp(
   mp = example_data_WprevSeSp$mp
 )
 
+WprevSeSp(
+  method = "poisson",
+  x = example_data_WprevSeSp$x,
+  n = example_data_WprevSeSp$n,
+  w = example_data_WprevSeSp$w,
+  cn = example_data_WprevSeSp$cn,
+  mn = example_data_WprevSeSp$mn,
+  cp = example_data_WprevSeSp$cp,
+  mp = example_data_WprevSeSp$mp
+)
+
+# Check error handling:
+WprevSeSp(
+  method = "missing method",
+  x = example_data_WprevSeSp$x,
[…]

### 2023-02-06 code/function_with_example_for_asht.R
Typos for cn and mn

@@ -96,7 +96,7 @@ WprevSeSp <- function(method = c("binomial", "poisson"),
 
   ci <- c(confidence_limit_L, confidence_limit_U)
   AP <- g(s_w_theta_hat, cn / mn, cp / mp)
-  Sp <- 1 - cp / mp
+  Sp <- 1 - cn / mn
   Se <- cp / mp
 
   estimate <- c("adjusted prevalence" = g(s_w_theta_hat, cn / mn, cp / mp))
@@ -104,7 +104,7 @@ WprevSeSp <- function(method = c("binomial", "poisson"),
   statistic <- Se
   names(statistic) <- paste0("Sensitivity (using nSe=", mp, ")")
   parameter <- Sp
-  names(parameter) <- paste0("Specificity (using nSp=", mp, ")")
+  names(parameter) <- paste0("Specificity (using nSp=", mn, ")")
   method_text <- paste0(
     "Prevalence Adjusted for Sensitivity and Specificity (CI by ",
     ifelse(method == "binomial", "Korn-Graubard", "Fay and Feuer"),
